### 2016-03-07 Numerical solution of DEs/Chapter1/homework1/LaTeX/homework1.tex
FEIP

\documentclass[12pt]{article}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\lstset{
	numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
	keywordstyle=\bf\color{blue},
	identifierstyle=\bf,
	numberstyle=\color[RGB]{0,192,192},
	commentstyle=\it\color[RGB]{0,96,96},
	stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
	showstringspaces=false
    }

\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

\title{Homework 2016-03-02}
\author{Chuan Lu\\ 
13300180056}

\maketitle

\begin{problem}{1}
\text{ }\\
\end{problem}

\begin{proof}
The code is shown as follows.

\begin{lstlisting}[language={MATLAB}]
% homework1
% author: chuanlu
% 2016-03-02
format long
xx = 10 .^ [-1:-1:-16];
yy = (1 - cos(xx)) ./ (xx .^ 2);
semilogx(xx, yy);    
\end{lstlisting}

The result is shown as follows.
\end{proof}

\begin{problem}{2}
\text{ }\\
$(1)$ Prove: If $[a] \in \Z_{n}$ is a unit, then $[a]$ is not a zero divisor.\\
$(2)$ Prove: If $[b] \in \Z_{n}$ is a zero divisor, then $[b]$ is not a unit.
\end{problem}

\begin{proof}

\end{proof}

\begin{problem}{3}
\text{ }\\
Show that every nonzero element of $\Z_{n}$ is either a unit or a zero divisor.
\end{problem}

\begin{proof}

\end{proof}

\begin{problem}{4}
\text{ }\\
Suppose that $[a]$ is a unit in $\Z_{n}$ and $[b]$ is an element of $\Z_{n}$. Prove that the equation $[a]x = b$ has exactly one solution in $\Z_{n}$
\end{problem}

\begin{proof}

\end{proof}

\begin{problem}{5}
\text{ }\\
Suppose that $[a]$ and $[b]$ are both units in $\Z_{n}$.  Show that the product $[a] \cdot [b]$ is also a unit in $\Z_{n}.$ (Note that this confirms closure under multiplication in the group $U_{n})$.
\end{problem}

\begin{proof}

\end{proof}

\begin{problem}{6}
\text{ }\\
Which of the following are Groups? Which of the following are not groups, and why?\\

\indent (1)  $G = \{{2, 4, 6, 8}\}$ in $\Z_{10}$.  Where $a \star b = ab$\\
\indent (2)  $G = \Q^{\ast}$, where $a \star b = \frac{a}{b}$\\
\indent (3) $G = \Z$, where $a \star b = a - b$\\
\indent (4) $G = \{ {2^{x}\mid x \in \Q} \}$, where $a \star b = ab$\\

\end{problem}

\begin{proof}

\end{proof}

\begin{problem}{7}
\text{ }\\
Consider the set $Q =$ \{ $\pm$1, $\pm$i, $\pm$j, $\pm$k\} of the complex matrices as follows:\\
\[
1=
  \begin{bmatrix}
    1 & 0\\
    0 & 1\\
  \end{bmatrix}
\]

\[
i=
  \begin{bmatrix}
    i & 0\\
    0 & $-$i\\
  \end{bmatrix}
\]

\[
j=
  \begin{bmatrix}
    0 & 1\\
    $-$1 & 0\\
  \end{bmatrix}
\]

\[
k=
  \begin{bmatrix}
    0 & i\\
    i & 0\\
  \end{bmatrix}
\]
Show that $Q$ is a group under matrix multiplication by writing out its multiplicaiton table. (Note: $Q$ is called the quartenion group).
\end{problem}
\begin{proof}

\end{proof}

\end{document}

### 2016-03-07 DSP/homework1/convolution.m

@@ -1,0 +1,12 @@
+function [y] = convolution(x, h)
+% convolution of the two vectors x and h
+% when the two vectors are row vectors
+[row1, col1] = size(x);
+[row2, col2] = size(h);
+
+A = zeros(col1 + col2 - 1, col2);
+for i = 1:col2
+    A(i:i + col1 - 1, i) = transpose(x);
+end
+y = A * transpose(h);
+

### 2016-03-07 FEIP/python/img_basic_handle.py

@@ -1,0 +1,136 @@
+import numpy as np
+import cv2
+import matplotlib.pyplot as plt
+import copy
+
+def histogram(img):
+	pixels_at_level = np.zeros([1, 256])[0]
+	for row in img:
+		for col in row:
+			pixels_at_level[col] += 1
+	# plt.hist(pixels_at_level, 100)
+	# plt.show()
+	return pixels_at_level
+
+def point_operator(img, func):
+	[row, col] = list(img.shape)[:2]
+	for i in range(row):
+		for j in range(col):
+			img[i][j] = func(img[i][j])
+	return img
+
+def histogram_normalization(img):
+	[row, col] = list(img.shape)[:2]
+	shaped_img = img.reshape(1, img.size)
+	maxim = shaped_img.max(1)[0]
+	minim = shaped_img.min(1)[0]
+	rangeim = maxim - minim
+	for i in range(row):
+		for j in range(col):
+			img[i][j] = (img[i][j] - minim) * 255 / rangeim;
+	return img
+
+def histogram_equalization(img):
+	rangeim = 255
+	number = img.size
+	pixels_at_level= [0 for i in range(rangeim + 1)]
+	[row, col] = list(img.shape)[:2]
+	for i in range(col):
+		for j in range(row):
+			pixels_at_level[img[i][j]] += 1
+	hist = [0 for i in range(rangeim + 1)]
+	sumim = 0
+	for i in range(rangeim):
+		sumim += pixels_at_level[i]
+		hist[i] = rangeim/number * sumim
+	for i in range(col):
+		for j in range(row):
+			img[i][j] = hist[img[i][j]]
+	return img
+
+def uniformed_thresholding(img, threshold):
+	[row, col] = list(img.shape)[:2]
+	for i in range(row):
+		for j in range(col):
+			if img[i][j] < threshold:
+				img[i][j] = 0
+			else:
+				img[i][j] = 255
+	return img
+
+def ostu_thresholding(img):
+	N = 255
+	[row, col] = list(img.shape)[:2]
+	pixels_at_level = histogram(img) / (row * col)
+	mu = lambda k, pixel: sum([(i+1) * pixel[i] for i in range(k)])
+	omega = lambda k, pixel: sum([pixel[i] for i in range(k)])
+	mu_T = lambda pixel:sum([(i+1) * pixel[i] for i in range(N+1)])
[…]

### 2016-03-07 FEIP/test/test1-2.cpp

@@ -1,0 +1,8 @@
+#include "cv.h"
+#include "highgui.h"
+
+int main(int argc, char const *argv[])
+{
+	/* code */
+	return 0;
+}

### 2016-03-07 Numerical solution of DEs/Chapter1/homework2/newton_raphson_iter.m

@@ -1,0 +1,36 @@
+function [ root, root_list ] = newton_raphson_iter( func1, func2, x0, tol, order )
+% Extract root ROOT of function FUNC1 with its derivative FUNC2 and
+% init point X0 given
+
+if nargin < 3
+    error('More arguments are needed --newton_raphson_iter');
+elseif nargin == 3
+    tol = 1e-6;
+    order = 100;
+elseif nargin == 4
+    order = 100;
+end
+
+count = 0;
+root_list = zeros(1, 1);
+while 1
+    count = count + 1;
+    root_list(count) = x0;
+    f1 = feval(func1, x0);
+    f2 = feval(func2, x0);
+    x1 = x0 - f1 / f2;
+    if abs(x1 - x0) < tol
+        disp(count);
+        root = x1;
+        return
+    elseif count >= order
+        root = x1;
+        return
+    elseif count > 100
+        warning('Count over 100, may not be convergence');
+        root = x1;
+        return
+    end
+    x0 =x1;
+end
+

### 2016-03-09 Numerical solution of DEs/Chapter1/homework3/1/get_coeff.m
Homework3 for DES

@@ -1,0 +1,24 @@
+function[ coeff ] = get_coeff( order )
+% get_coeff of newton_cotes formula of interval
+% order means the order of the formula
+switch order
+    case 1
+        coeff = [1, 1];
+    case 2
+        coeff = [1, 4, 1];
+    case 3
+        coeff  = [1,3,3,1];
+    case 4
+        coeff = [7,32, 12, 32, 7];
+    case 5
+        coeff = [19, 75, 50, 50, 75, 19];
+    case 6
+        coeff = [41, 216, 27, 272, 27, 216, 41];
+    case 7
+        coeff = [751, 3577, 1323, 2989, 2989, 1323, 3577, 751];
+    case 8
+        coeff = [989, 5888, -928, 10496, -4540, 10496, -928, 5888, 989];
+    otherwise
+        error('order should be between 0 and 8 --get_cotes_coeff');
+end
+    coeff = coeff / sum(coeff);

### 2016-03-09 Numerical solution of DEs/Chapter1/homework3/1/newton_cotes.m

@@ -1,0 +1,43 @@
+function [ result ] = newton_cotes( func, inteval, order )
+%NEWTON_COTES 采用Newton-Cotes公式计算积分的近似值
+%其中func为被积函数，inteval为积分区间，表示为一个1*2的向量，order为N-C公式的阶数
+%author: chuanlu@2015.11.19
+
+if nargin < 2
+    error(' Too few inputted arguments, please check if function and inteval for integrating have been inputted or not  -- Newton_Cotes');
+elseif nargin == 2
+    order = 2;
+    % 这里，我们认为默认条件下，采用Simpson公式
+end
+
+% if order < 0 || order > 8
+%     error(' Order Error: The order should be between 0 and 8. --Newton_Cotes ');
+% end
+
+low = inteval( 1 );
+high = inteval( 2 );
+
+if order == 0
+    result = feval(func, (low + high) / 2) * (high - low);
+else
+%     coeff = zeros(8, 9);
+%     %coeff为8行9列的系数矩阵，行号为order，列号为每一个order对应的系数向量
+% 
+%     %初始化coeff
+%     coeff(1, 1 : 2) = [1,1] / 2;
+%     coeff(2, 1 : 3) = [1,4,1] / 6;
+%     coeff(3, 1 : 4) = [1,3,3,1] / 8;
+%     coeff(4, 1 : 5) = [7,32,12,32,7] / 90;
+%     coeff(5, 1 : 6) = [19,75,50,50,75,19] / 288;
+%     coeff(6, 1 : 7) = [41,216,27,272,27,216,41] / 840;
+%     coeff(7, 1 : 8) = [751,3577,1323,2989,2989,1323,3577,751] / 17280;
+%     coeff(8, 1 : 9) = [989,5888,-928,10496,-4540,10496,-928,5888,989] / 28350;
+    coeff = get_coeff(order);
+
+    eval_points = low : (high - low) / order : high;
+    eval_points = transpose( eval_points );
+    result = sum( coeff * feval(func, eval_points)) * (high - low);
+%     coeff = cotes_coefficient(order);
+%    coeff = new_cotes_coefficient(order);
+%      result = sum(transpose(coeff) * func(eval_points)) *( high - low );
+end

### 2016-03-09 Numerical solution of DEs/Chapter1/homework3/2/runge.m

@@ -1,0 +1,15 @@
+f = @(x)(1 ./ (1 + 25 * (x .^ 2)));
+plot_points = -1:1e-6:1;
+yy = feval(f, plot_points);
+plot(plot_points, yy);
+hold on
+
+for n = 4:4:12
+    given_points = -1:1/n:1;
+    function_values = feval(f, given_points);
+    f_series = Newton_eval(given_points, function_values, plot_points);
+    plot(plot_points, f_series);
+    hold on
+end
+axis([-1, 1, -1, 1]);
+legend('f(x)', 'n = 4', 'n = 8', 'n = 12', 'Location', 'best');

### 2016-03-11 Numerical solution of DEs/Chapter1/homework4/gauss_integral.m
Homework4 of DEs

@@ -1,0 +1,13 @@
+function [ value ] = gauss_integral( func, order )
+%GAUSS_INTEGRAL Calculate the intergral of func in [0, 1] with
+%Gauss-Legendre Formula.
+if order == 1
+    value = feval(func, 0.5);
+    return
+end
+[point, weight] = gauss_coefficient_legendre(order - 1);
+transfered_point = point * 0.5 + 0.5;
+value = weight * feval(func, transfered_point) * 0.5;
+
+end
+

### 2016-03-21 FEIP/python/cconvolve.c
homework 5

@@ -1,3 +1,0 @@
-#include "Python.h"
-
-int convolve()

### 2016-03-21 FEIP/python/test_python_c/len_vec_swig.c

@@ -1,0 +1,13 @@
+#include "len_vec_swig.h"
+#include "math.h"
+
+double lenv4(int* vec) {
+	int length = vec[0];
+	int i = 1;
+	double count = 0;
+	for(; i < length; i++) {
+		count += vec[i]*vec[i];
+	}
+	return sqrt(count);
+}
+

### 2016-03-21 FEIP/python/test_python_c/len_vec_swig.py

@@ -1,0 +1,78 @@
+# This file was automatically generated by SWIG (http://www.swig.org).
+# Version 2.0.11
+#
+# Do not make changes to this file unless you know what you are doing--modify
+# the SWIG interface file instead.
+
+
+
+
+
+from sys import version_info
+if version_info >= (2,6,0):
+    def swig_import_helper():
+        from os.path import dirname
+        import imp
+        fp = None
+        try:
+            fp, pathname, description = imp.find_module('_len_vec_swig', [dirname(__file__)])
+        except ImportError:
+            import _len_vec_swig
+            return _len_vec_swig
+        if fp is not None:
+            try:
+                _mod = imp.load_module('_len_vec_swig', fp, pathname, description)
+            finally:
+                fp.close()
+            return _mod
+    _len_vec_swig = swig_import_helper()
+    del swig_import_helper
+else:
+    import _len_vec_swig
+del version_info
+try:
+    _swig_property = property
+except NameError:
+    pass # Python < 2.2 doesn't have 'property'.
+def _swig_setattr_nondynamic(self,class_type,name,value,static=1):
+    if (name == "thisown"): return self.this.own(value)
+    if (name == "this"):
+        if type(value).__name__ == 'SwigPyObject':
+            self.__dict__[name] = value
+            return
+    method = class_type.__swig_setmethods__.get(name,None)
+    if method: return method(self,value)
+    if (not static):
+        self.__dict__[name] = value
+    else:
+        raise AttributeError("You cannot add attributes to %s" % self)
+
+def _swig_setattr(self,class_type,name,value):
+    return _swig_setattr_nondynamic(self,class_type,name,value,0)
+
+def _swig_getattr(self,class_type,name):
+    if (name == "thisown"): return self.this.own()
+    method = class_type.__swig_getmethods__.get(name,None)
+    if method: return method(self)
+    raise AttributeError(name)
+
+def _swig_repr(self):
+    try: strthis = "proxy of " + self.this.__repr__()
+    except: strthis = ""
+    return "<%s.%s; %s >" % (self.__class__.__module__, self.__class__.__name__, strthis,)
+
+try:
+    _object = object
+    _newclass = 1
+except AttributeError:
+    class _object : pass
+    _newclass = 0
+
+
+
+def lenv4(*args):
+  return _len_vec_swig.lenv4(*args)
+lenv4 = _len_vec_swig.lenv4
+# This file is compatible with both classic and new-style classes.
+
+

### 2016-03-21 FEIP/python/test_python_c/len_vec_swig_wrap.c

@@ -1,0 +1,3692 @@
+/* ----------------------------------------------------------------------------
+ * This file was automatically generated by SWIG (http://www.swig.org).
+ * Version 2.0.11
+ *
+ * This file is not intended to be easily readable and contains a number of
+ * coding conventions designed to improve portability and efficiency. Do not make
+ * changes to this file unless you know what you are doing--modify the SWIG
+ * interface file instead.
+ * ----------------------------------------------------------------------------- */
+
+#define SWIGPYTHON
+#define SWIG_PYTHON_DIRECTOR_NO_VTABLE
+
+/* -----------------------------------------------------------------------------
+ *  This section contains generic SWIG labels for method/variable
+ *  declarations/attributes, and other compiler dependent labels.
+ * ----------------------------------------------------------------------------- */
+
+/* template workaround for compilers that cannot correctly implement the C++ standard */
+#ifndef SWIGTEMPLATEDISAMBIGUATOR
+# if defined(__SUNPRO_CC) && (__SUNPRO_CC <= 0x560)
+#  define SWIGTEMPLATEDISAMBIGUATOR template
+# elif defined(__HP_aCC)
+/* Needed even with `aCC -AA' when `aCC -V' reports HP ANSI C++ B3910B A.03.55 */
+/* If we find a maximum version that requires this, the test would be __HP_aCC <= 35500 for A.03.55 */
+#  define SWIGTEMPLATEDISAMBIGUATOR template
+# else
+#  define SWIGTEMPLATEDISAMBIGUATOR
+# endif
+#endif
+
+/* inline attribute */
+#ifndef SWIGINLINE
+# if defined(__cplusplus) || (defined(__GNUC__) && !defined(__STRICT_ANSI__))
+#   define SWIGINLINE inline
+# else
+#   define SWIGINLINE
+# endif
+#endif
+
+/* attribute recognised by some compilers to avoid 'unused' warnings */
+#ifndef SWIGUNUSED
+# if defined(__GNUC__)
+#   if !(defined(__cplusplus)) || (__GNUC__ > 3 || (__GNUC__ == 3 && __GNUC_MINOR__ >= 4))
+#     define SWIGUNUSED __attribute__ ((__unused__))
+#   else
+#     define SWIGUNUSED
[…]

### 2016-03-21 FEIP/python/test_python_c/setup_swig.py

@@ -1,0 +1,9 @@
+from distutils.core import setup, Extension
+
+len_vec_swig_module = Extension('_len_vec_swig',
+							sources = ['len_vec_swig_wrap.c', 'len_vec_swig.c'],)
+
+setup(name = 'len_vec_swig',
+	ext_modules = [len_vec_swig_module],
+	py_modules = ["len_vec_swig"],
+	)

### 2016-03-21 Numerical solution of DEs/Chapter2/Homework4/implicit_iter.m

@@ -1,0 +1,18 @@
+function [t, u] = implicit_iter(func, inteval, u1, delta_t)
+% IMPLICIT_ITER Implicit Euler Iteration
+
+t = inteval(1):delta_t:inteval(2);
+n = length(t);
+u = zeros(1, n);
+f = @(u, u0, t, delta_t)(u - delta_t * feval(func, t, u) - u0);
+
+for i = 1 : n - 1
+    u(i) = u1;
+    t_i = t(i + 1);
+    u0 = u1;
+    u1 = fsolve(@(u) f(u, u0, t_i, delta_t), 1);
+end
+u(n) = u1;
+
+end
+

### 2016-03-21 Numerical solution of DEs/Chapter2/Homework4/revised_iter.m
revised_iter

@@ -1,0 +1,14 @@
+function [t, u] = revised_iter(func, inteval, u1, delta_t)
+% REVISED_ITER Revised Euler Iteration
+t = inteval(1):delta_t:inteval(2);
+n = length(t);
+u = zeros (1, n);
+
+for i = 1:n - 1 
+    u( i ) = u1;
+    u_half = delta_t * feval(func ,t(i), u(i)) / 2 + u1;
+    t_half = (t(i) + t(i + 1))/2;
+    u1 = u1 + delta_t * feval (func, t_half, u_half);
+end
+u(n) = u1;
+end

### 2016-03-26 Statistical Computing/homework1/LaTeX/main.tex
Homework6

\documentclass{article}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}
\lstset{
	numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
	keywordstyle=\bf\color{blue},
	identifierstyle=\bf,
	numberstyle=\color[RGB]{0,192,192},
	commentstyle=\it\color[RGB]{0,96,96},
	stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
	showstringspaces=false
    }

\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

\title{Homework 2016-03-21}
\author{Chuan Lu\\
13300180056}

\maketitle

\begin{problem}{1}
\text{ }\\
Calculate the confidence interval with a confidence level of 0.95 of the samples given.
\end{problem}
\begin{proof}
Firstly, the mean of the samples $\overline{x} = \frac{1}{10}\sum_{i}{x_{i}} = 10.05,$ the variance of the samples $\sigma = \frac{1}{10}\sum_{i}{(x_{i} - \overline{x})^{2}} = 0.0525.$ We can then check from the t-distribution table that the confidence interval is $[\overline{X} - t_{\alpha/2}(n-1)\frac{\sigma}{\sqrt{n}}, \overline{X} + t_{\alpha/2}(n-1)\frac{\sigma}{\sqrt{n}}] = [9.9854, 10.1146]$
\end{proof}

\begin{problem}{2}
\text{ }\\
If the rate of abnormality in this area is below the average with the information provided.
\end{problem}
\begin{proof}
$P(\mbox{Only one person is of abnormality}\vert\mbox{The rate of abnormality is 0.01}) =  \dbinom{400}{1}*(1-0.01)^{399}*0.01 = 0.0725 > 0.05$, which implies that this phenomenon is just possible, hence the rate of abnormality in this area can NOT be seen as below the average.
\end{proof}

\begin{problem}{3}
\text{ } \\
Derive out the EM algorithm of a distribution mixed by three normal distributions.
\end{problem}
\begin{proof}
Let \[z_{ij} = \begin{cases} 
		1&\text{$X_{i}$ belongs to the $j^{th}$ distribution},\\ 
		0&\text{others},\end{cases}\] and $P(z_{i} = 1) = t_{i}$, where $\sum_{i=1}^{3}{t_{i}} = 1.$\\
Then the likelihood function is $L(\theta;X,Z) = \prod_{i=1}^{n}{\prod_{j=1}^{3}{t_{j}\frac{1}{(\sqrt{2\pi})^{n}\sqrt(det(\Sigma_{j}))}e^{-\frac{1}{2}(x-\mu)^{T}\Sigma^{-1}(x-\mu)}}}$, the log-likelihood of which is $l(\theta;x,z) = \sum_{i=1}^{n}{\sum_{j=1}^{3}{z_{ij}[log(t_{j})-\frac{d}{2}log(2\pi)-\frac{1}{2}(x_{i} - \mu_{j})^{T}\Sigma^{-1}(x-\mu)]}}$. \\
\quad E-step: \\
Assume there are a vector of $\theta_{n}$, then $Q(\theta|\theta_{m}) = E(l(\theta; x, z)) = \sum_{i=1}^{n}{\sum_{j=1}^{3}{T_{i,j}^{(m)}[log(t_{j})-\frac{d}{2}log(2\pi)-\frac{1}{2}(x_{i} - \mu_{j})^{T}\Sigma^{-1}(x-\mu)]}}$, in which $T_{ij}^{(m)} = P(z_{ij} = 1|X_{i} = x_{i}; \theta_{m}) = \frac{t_{j}^{(m)}f(x_{i}; \mu_{j}^{(m)},\Sigma_{j}^{(m)})}{\sum_{k=1}^{3}{t_{k}^{(m)}f(x_{i}; \mu_{k}^{(m)},\Sigma_{k}^{(m)})}}, j=1,2,3.$ \\
\quad M-step: \\
For $t_{m+1}$,\\ $t_{m+1} = argmax_{t}Q(\theta|\theta_{m}) = argmax_{t}\lgroup[\sum_{i=1}^{n}{T_{i, 1}^{(m)}}]log(t_1)+[\sum_{i=1}^{n}{T_{i, 2}^{(m)}}]log(t_2)+[\sum_{i=1}^{n}{T_{i, 3}^{(m)}}]log(t_3)\rgroup,$ so $t_{j}^{(m+1)} = \frac{1}{n}\sum_{i=1}^{n}{T_{i, j}^{(m)}}.$ \\
For $\mu_{m+1}, \sigma_{m+1}, \\(\mu_{m+1}, \sigma_{m+1}) = argmax_{\mu, \sigma}Q(\theta|\theta_{m})$, so $\mu_{j}^{(m+1)} = \frac{\sum_{i=1}^{n}{T_{i, j}^{(m)}}x_{i}}{\sum_{i=1}^{n}{T_{i, j}^{(m)}}},$ and $\sigma_{j}^{(m+1)} = \frac{\sum_{i=1}^{n}{T_{i, j}^{(m)}(x_{i} - \mu_{j}^{(m)})(x_{i} - \mu_{j}^{(m)})^{T}}}{\sum_{i=1}^{n}{T_{i, j}^{(m)}}}$
\end{proof}

\begin{problem}{4}
\text{ }\\
Estimate the arguments with the data given.
\end{problem}

\begin{proof}
\subsection{The code is shown as follows.}
\begin{lstlisting}[language = {R}]
source('em_func.R')
em = function(x, dim, mu, sigma, t, maxit = 100, error = 1e-6) {
  # mu, sigma, t are listsa containing init data
  # Init
  n = nrow(x)
  T = matrix(rep(0, n*dim), ncol=dim)

  for(step in 1:maxit) {

    # E-step
    for(j in 1:dim) {
      for(i in 1:n) {
        # print(x[i, ])
        T[i, j] = em_FUNC(x[i, ], mu[[j]], sigma[[j]]) * t(j)
      }
    }
    T = T/rowSums(T)

    sigma0 = sigma
    t0 = t
    mu0 = mu

    # M-step
    for(j in 1:dim) {
      v1 = sum(T[, j])
      v2 = matrix(rep(0, ncol(x)), nrow=1)
      for(i in 1:n) {
        v2 = v2 + (T[i, j] * x[i, ])
      }
      mu[[j]] = v2 / v1
      t[j] = v1 / n
      v3 = matrix(rep(0, ncol(x)^2), nrow=ncol(x))
      for(i in 1:n) {
        temp1 = matrix(x[i, ])
        temp2 = matrix(mu[[j]])
        delta = temp1 - temp2
        v3 = v3 + (T[i, j] * delta %*% t(delta))
      }
      sigma[[j]] = (v3/v1)
    }
    mu_sum = 0
    sigma_sum = 0
    for(i in 1:length(mu)) {
      mu_sum = mu_sum + sum(abs(mu0[[i]] - mu[[i]]))
    }
    for(i in 1:length(sigma)) {
      sigma_sum = sigma_sum + sum(abs(sigma0[[i]] - sigma[[i]]))
    }
    # Check if converged
    if(mu_sum < error & sigma_sum < error & sum(abs(t-t0)) < error)
      break
  }
  returnlist = list(mu, sigma, t)

  return(returnlist)
}
\end{lstlisting}
\begin{lstlisting}[language={R}]
em_FUNC <- function(x, mu, sigma) {
  n = ncol(t(matrix(x)))
  res = 1/((sqrt(2*pi))^n * sqrt(abs(det(sigma)))) * exp(-1/2 * (x-mu)%*%solve(sigma)%*%t(x-mu))
  return (res)
}
\end{lstlisting}
\begin{lstlisting}[language={R}]
# Exercise 4
source('EM.R')
data = read.csv('Data1.csv')
x1 = data['V1']
x2 = data['V2']
x = data.frame(x1, x2)
x = data.matrix(x)
dim = 3
n = 2
mu = list(t(matrix(runif(n))), t(matrix(runif(n))), t(matrix(runif(n))))
sigma = list(matrix(runif(n*n), ncol = n), matrix(runif(n*n), ncol = n), matrix(runif(n*n), ncol = n))
t = c(0.1, 0.7, 0.2)
rlist = em(x, dim, mu, sigma, t)
print(rlist[[1]])
print(rlist[[2]])
print(rlist[[3]])
\end{lstlisting}
\subsection{The result is shown as follows, in which rlist[[1] is mu, rlist[[2]] is sigma, rlist[[3]] is t.}
\begin{lstlisting}[language = {R}]
> print(rlist[[1]])
[[1]]
          [,1]      [,2]
[1,] -2.274075 -3.209265

[[2]]
         [,1]      [,2]
[1,] 5.271368 -2.079697

[[3]]
          [,1]       [,2]
[1,] 0.8930116 -0.6144073

> print(rlist[[2]])
[[1]]
           [,1]       [,2]
[1,]  0.6014583 -0.1520107
[2,] -0.1520107  0.8660930

[[2]]
             [,1]         [,2]
[1,]  1.577730561 -0.009383941
[2,] -0.009383941  1.104548710

[[3]]
         [,1]     [,2]
[1,] 4.439728 3.414217
[2,] 3.414217 4.359960

> print(rlist[[3]])
[1] 0.1783595 0.4624902 0.3591504
\end{lstlisting}
\end{proof}

\begin{problem}{5}
\text{ }\\
Estimate the average height of men and women with the data givem.
\end{problem}

\begin{proof}
\subsection{The code is shown as follows, and the function `EM' is given within the answer to the former exercise.}
\begin{lstlisting}[language = {R}]
# Exercise5
source('EM.R')
x = matrix(c(171, 174, 159, 176, 164, 169, 170, 173, 159,
             172, 166, 175, 161, 186, 160, 168, 166, 174,
             159, 178, 165, 189, 164, 168, 165, 185, 160,
             175, 172, 168, 167, 171, 160, 174, 168, 174,
             167, 175, 162, 177))
dim = 2
mu = list(matrix(c(163)), matrix(c(176)))
sigma = list(matrix(runif(1)), matrix(runif(1)))
t = c(0.2, 0.8)
rlist = em(x, dim, mu, sigma, t)
print(rlist[[1]])
print(rlist[[2]])
print(rlist[[3]])
\end{lstlisting}
\subsection{The result is shown as follows, in which rlist[[1]] is mu, rlist[[2]] is sigma, rlist[[3]] is t.}
\begin{lstlisting}[language = {R}]
> print(rlist[[1]])
[[1]]
         [,1]
[1,] 163.6147

[[2]]
         [,1]
[1,] 172.5814

> print(rlist[[2]])
[[1]]
        [,1]
[1,] 14.6682

[[2]]
         [,1]
[1,] 46.11688

> print(rlist[[3]])
[1] 0.3269247 0.6730753
\end{lstlisting}
\end{proof}

% % \begin{problem}{6}
% % \text{ }\\
% % Which of the following are Groups? Which of the following are not groups, and why?\\

% % \indent (1)  $G = \{{2, 4, 6, 8}\}$ in $\Z_{10}$.  Where $a \star b = ab$\\
% % \indent (2)  $G = \Q^{\ast}$, where $a \star b = \frac{a}{b}$\\
% % \indent (3) $G = \Z$, where $a \star b = a - b$\\
% % \indent (4) $G = \{ {2^{x}\mid x \in \Q} \}$, where $a \star b = ab$\\

% % \end{problem}

% % \begin{proof}

% % \end{proof}

% % \begin{problem}{7}
% % \text{ }\\
% % Consider the set $Q =$ \{ $\pm$1, $\pm$i, $\pm$j, $\pm$k\} of the complex matrices as follows:\\
% % \[
% % 1=
% %   \begin{bmatrix}
% %     1 & 0\\
% %     0 & 1\\
% %   \end{bmatrix}
% % \]

% % \[
% % i=
% %   \begin{bmatrix}
% %     i & 0\\
% %     0 & $-$i\\
% %   \end{bmatrix}
% % \]

% % \[
% % j=
% %   \begin{bmatrix}
% %     0 & 1\\
% %     $-$1 & 0\\
% %   \end{bmatrix}
% % \]

% % \[
% % k=
% %   \begin{bmatrix}
% %     0 & i\\
% %     i & 0\\
% %   \end{bmatrix}
% % \]
% % Show that $Q$ is a group under matrix multiplication by writing out its multiplicaiton table. (Note: $Q$ is called the quartenion group).
% % \end{problem}
% % \begin{proof}

% % \end{proof}

\end{document}

### 2016-03-26 Numerical solution of DEs/Chapter2/Homework6/taylor_iter_2order.m

@@ -1,0 +1,13 @@
+function [t, u] = taylor_iter_2order(func, F, inteval, u1, delta_t)
+%TAYLOR_ITER_2ORDER The 2nd-order taylor iteration
+
+t = inteval(1):delta_t:inteval(2);
+n = length(t);
+u = zeros(1, n);
+
+for i = 1:n
+    u(i) = u1;
+    delta = feval(func, t(i), u(i)) + feval(F, t(i), u(i))*delta_t/2;
+    u1 = u1 + delta_t * delta;
+end
+

### 2016-03-26 Statistical Computing/R_test/1st.R

@@ -1,0 +1,2 @@
+a <- "str"
+print(a)

### 2016-03-26 Statistical Computing/homework1/em_func.R

@@ -1,0 +1,5 @@
+em_FUNC <- function(x, mu, sigma) {
+  n = ncol(t(matrix(x)))
+  res = 1/((sqrt(2*pi))^n * sqrt(abs(det(sigma)))) * exp(-1/2 * (x-mu)%*%solve(sigma)%*%t(x-mu))
+  return (res)
+}

### 2016-05-10 DSP/homework3/down_sampling.m
Update

@@ -1,0 +1,6 @@
+function [x] = down_sampling(xx)
+% DOWN_SAMPLING 
+n = length(xx);
+x = xx(2:2:n);
+end
+

### 2016-05-10 DSP/homework3/haar_reconstruction.m

@@ -1,0 +1,19 @@
+function [a] = haar_reconstruction(A, B)
+% Reconstruction of Haar Wavelet
+% B : The result of haar_decomposition, with some kind of handling;
+
+[row, col] = size(B);
+
+h = [1, -1];
+l = [1, 1];
+a = A(row, 1:max(1, col/(2^(row-1))));
+length(a)
+for i = row-1:-1:1
+    a1 = up_sampling(a);
+    a1 = convolution(a1, l);
+    b = up_sampling(B(i, 1:col/(2^(i))));
+    b = convolution(b, h);
+    length(b)
+    a = a1 + b;
+end
+

### 2016-05-10 DSP/homework4/daubechies_coeff.m

@@ -1,0 +1,18 @@
+function [ y ] = daubechies_coeff( x )
+% DAUBECHIES_COEFF 
+% solve the coefficients of daubechies matrix
+% x is the initial vector
+% return a vector;
+
+y = fsolve(@daubechies_r, x);
+
+end
+
+function [ y ] = daubechies_r( x )
+
+y = zeros(1, 4);
+y(1) = x * transpose(x) - 1;
+y(2) = x(1) * x(4) + x(2) * x(3);
+y(3) = x(4) - x(3) + x(2) - x(1);
+y(4) = -x(3) + 2*x(2) - 3*x(1);
+end

### 2016-05-10 DSP/homework4/sampling.m

@@ -1,0 +1,15 @@
+function [x, y] = sampling(interval, num, func)
+% Sampling of a signal;
+% func : The function of the signal;
+% interval : The sampling interval of the signal;
+% num : The number of points, MUST BE the power of 2;
+
+len = interval(2) - interval(1);
+n = num - 1;
+delta = len/n;
+x = interval(1):delta:interval(2);
+y = feval(func, x);
+
+
+end
+

### 2016-05-10 DSP/homework5/DFT.m

@@ -1,0 +1,11 @@
+function [ y ] = DFT( A )
+% DFT 
+% Discrete Fourier Transform
+% Using Basis-2 FFT
+
+% A: A col vector
+
+
+
+end
+

### 2016-05-10 Statistical Computing/homework1/exercise5.R

@@ -13,3 +13,4 @@ rlist = em(x, dim, mu, sigma, t)
 print(rlist[[1]])
 print(rlist[[2]])
 print(rlist[[3]])
+

### 2016-05-10 Statistical Computing/homework3/test.R

@@ -1,0 +1,29 @@
+# TEST
+source("main.R")
+
+# Problem 1.1
+lambda = 0.5
+k = 4
+a = matrix(c(1, 10000))
+# r1 = p11(a, lambda, k)
+# hist(r1)
+# 
+# Problem 1.2
+# r2 = p12(a, lambda, k)
+# hist(r2)
+
+# Problem 2
+# r3 = p2(a)
+# hist(r3)
+
+# Problem 3
+# r3 = p3(a)
+# hist(r3)
+
+# Problem 4
+r4 = p4(a)
+hist(r4)
+
+# Problem 5
+r5 = p5(a, lambda = 0.5)
+hist(r5)

### 2016-05-10 ml/HMM.py

@@ -1,0 +1,10 @@
+# HMM
+
+class HMM:
+	'''
+	Hidden Markov Model
+	'''
+	def __init__(self, A, B):
+		'''
+		A is the transforming Matrix, 
+		B is the 

### 2016-05-31 Statistical Computing/homework4/gibbs_sampling.R
h4, 1,3,5

@@ -1,0 +1,43 @@
+######### Gibbs Sampling for problem 3 ###########
+sample3 = function(param1, param2) {
+  lambda = 1/(param1 + param2 + 1);
+  ##### Using inverse transform algorithm to generate the distribution:
+  ##### f(x|lambda) = lambda*exp(-lambda*x);
+  u = runif(1);
+  x = -lambda*log(lambda*u);
+  return(x);
+}
+
+gibbs_sampling3 = function(n, init_param) {
+  ##### Initialize parameters;
+  x = rep(0, n);
+  y = rep(0, n);
+  z = rep(0, n);
+  x[1] = init_param[1];
+  y[1] = init_param[2];
+  z[1] = init_param[3];
+  
+  ##### Iterative Sampling;
+  for(i in 2:n) {
+    x[i] = sample3(y[i-1], z[i-1]);
+    y[i] = sample3(x[i], z[i-1]);
+    z[i] = sample3(x[i], y[i]);
+  }
+  rlist = list(x, y, z);
+  return(rlist);
+}
+
+estimate3 = function(n) {
+  res = gibbs_sampling3(2*n, c(1, 1, 1));
+  X = res[[1]];
+  Y = res[[2]];
+  Z = res[[3]];
+  X_sample = X[(n+1):(2*n)];
+  Y_sample = Y[(n+1):(2*n)];
+  Z_sample = Z[(n+1):(2*n)];
+
+  sum = sum(X_sample)*sum(Y_sample)*sum(Z_sample);
+  return(sum/(n^3));
+}
+
+estimate3(100000)

### 2016-05-31 Statistical Computing/homework4/mixed_gauss_distribution.R

@@ -1,0 +1,60 @@
+##### Gibbs Sampling for Problem 5 ###
+sample5 = function(mu, sigma, x) {
+  mean = mu[2]+sigma[2,1]*(1/sigma[1,1])*(x-mu[1]);
+  sd = sigma[2,2]-sigma[2,1]*(1/sigma[1,1])*sigma[1,2];
+  return(rnorm(1, mean, sd));
+}
+
+gibbs_sampling5 = function(n, mu, sigma, init_param) {
+  x1 = rep(0, n);
+  x2 = rep(0, n);
+  x1[1] = init_param[1];
+  x2[1] = init_param[2];
+  
+  mu2 = c(mu[2], mu[1]);
+  sigma2 = matrix(c(sigma[2,2], sigma[2,1], sigma[1,2], sigma[1,1]), ncol = 2);
+  
+  for(i in 2:n) {
+    x2[i] = sample5(mu, sigma, x1[i-1]);
+    x1[i] = sample5(mu2, sigma2, x2[i]);
+  }
+  rlist = list(x1, x2);
+  return(rlist);
+}
+
+simulate5 = function(n) {
+  mu1 = c(1, 4);
+  mu2 = c(-2, -1);
+  sigma1 = matrix(c(1, 0.3, 0.3, 2), ncol = 2);
+  sigma2 = matrix(c(3, 0.4, 0.4, 1), ncol = 2);
+  
+  Z = matrix(rep(0, 2*n), nrow = 2);
+  ##### Each col in Z is a sample point #####
+  
+  X = gibbs_sampling5(4*n, mu1, sigma1, c(1, 1));
+  Y = gibbs_sampling5(4*n, mu2, sigma2, c(-3, -3));
+  
+  x1 = X[[1]];
+  x2 = X[[2]];
+  y1 = Y[[1]];
+  y2 = Y[[2]];
+
+  ##### Take the last 1/4 of samples as a simulation ###
+  for(i in 1:n) {
+    u = runif(1);
+    if(u > 0.5) {
+      Z[1, i] = x1[i + 3*n];
+      Z[2, i] = x2[i + 3*n];
+    }
+    else {
+      Z[1, i] = y1[i + 3*n];
+      Z[2, i] = y2[i + 3*n];
+    }
+  }
+  return(Z);
+}
+
+
+n = 10000
+z = simulate5(n)
+plot(z[1, ], z[2, ])

### 2016-09-21 Config Files/Assignment-TEX/assignment.tex
modification

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Homework 1}{16.9.21, Chuan Lu}

\problem{1}{Rewrite the target function of K-means in matrix form.}
\solution{Solution}{
$f(x) = argmin_{\mathcal{S}}\sum_{i=1}^{k}\sum_{x_j\in S_j}\sum_{1\le m\le p}\lvert x_{jl} - x_{jm} \rvert^2.$
}

\problem{2}{Cluster $Data_i.csv$ with K-means, judge the number of clusters, and compare differences between different evaluating methods.}
\solution{Solution}{
The code of K-means, evaluating and test scripts can be found from attachments(kmeans.R, evaluate.R, hw1.2.R).
}
\solution{Result}{
For Data1.csv, we cluster with k = 3. The result is shown as below.
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw2_data1_cluster.eps}
\caption{The clusters of Data1.csv with k = 3}
\label{clusters of data1}
\end{figure}
\\[1mm]

For choosing k, the result of Data1.csv is shown below; The first is the result of Calinski-Harabasz method, the second Hartigan method and the last Gap Statistic. \\[3pt]
The result of CH method is 9, if we may add a limit that $k\le 10.$ The result of H method is 3, and result of GAP statistic is 3.\\[3pt]

\begin{figure}[htbp]
\centering
\subfloat[CH method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_CH.eps}}\hfill
\subfloat[H method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_H.eps}}\hfill
\subfloat[GAP statistic]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_GAP.eps}}\hfill
\caption{The three evaluating methods of choosing k for Data1.csv}
\label{EVA Data1}
\end{figure}

For Data2.csv, since each data point is of 3 dims, we cannot plot its clustering result here. But after deploying the evaluating methods we consider k = 3. The type of datas can be find in attachments(CLUSTER\_DATA2.txt). \\[3pt]

The result of CH method is 8, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
The pics are shown below.

\begin{figure}[htbp]
\centering
\subfloat[CH method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_CH.eps}}\hfill
\subfloat[H method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_H.eps}}\hfill
\subfloat[GAP statistic]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_GAP.eps}}\hfill
\caption{The three evaluating methods of choosing k for Data2.csv}
\label{EVA Data2}
\end{figure}

For Data3.csv, we fix k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA3.txt). \\[3pt]

The result of CH method is 9, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
The pics are shown below.

\begin{figure}[htbp]
\centering
\subfloat[CH method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_CH.eps}}\hfill
\subfloat[H method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_H.eps}}\hfill
\subfloat[GAP statistic]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_GAP.eps}}\hfill
\caption{The three evaluating methods of choosing k for Data3.csv}
\label{EVA Data2}
\end{figure}

For Data4.csv, we found k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA4.txt). \\[3pt]

The result of CH method is 7, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
The pics are shown below.

\begin{figure}[htbp]
\centering
\subfloat[CH method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_CH.eps}}\hfill
\subfloat[H method]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_H.eps}}\hfill
\subfloat[GAP statistic]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_GAP.eps}}\hfill
\caption{The three evaluating methods of choosing k for Data4.csv}
\label{EVA Data2}
\end{figure}
}
\solution{Analysis}{
It is suprising that result of Calinski-Harabasz method does not agree with the other methods. I consider it as the result that I misunderstood the meaning of $W(k), B(k)$. I calculate the former as the target function of cluster; the latter as $\sum_{c_i, c_j \in C}\lVert c_i - c_j \rVert^2$, in which $C$ is the set of cluster centers.
}

\problem{3}{Use hierarchical clustering methods to cluster $Data_i.csv$}
\solution{Solution}{
The code of hierarchical clustering and the test script can be found from attachments(hierarchical\_clustering.R, hw1.3.R).
}
\solution{Result}{
It is somehow embarrassing that I still did't know how to draw trees in R without $hcluster()$. The result can be shown is the attachments, (HC\_DATA1.txt and HC\_DATA2.txt). \\[3pt]
Each result is a (n-1) * narg matrix, in which n is the number of data points and narg is the number of dims in each data point. Each row in the matrix(for example, A[1, ]) means a step when two points merged with each other; A[1, 1] and A[1, 2] merged into a new A[1, 1], and the point represented by A[1, 2] is abandoned. \\[3pt]
It is possible to draw the tree and do Tree-Cut with the results.
}

\end{document}

### 2016-09-21 Config Files/CV/cv_13.tex
modification

%!TEX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Chuan Lu} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 18-628, 440 Guoding Road\\ % Address line 1
\> 200433 Shanghai \\ % Address line 2
% {\bf Date of Birth} \> 14$^{th}$ December 1996 \\ % Date of birth 
% {\bf Nationality} \> British % Nationality
{\bf Homepage} \> \href{http://chuanlu.xyz}{http://chuanlu.xyz} \\
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Home Phone} \> +0 (000) 111 1111 \\ % Home phone
{\bf Phone} \> +86 130-6266-1218 \\ % Mobile phone
{\bf Email} \> \href{mailto:chuanlu13@fudan.edu.cn}{chuanlu13@fudan.edu.cn} \\ % Email address
{\bf GitHub} \> \href{http://github.com/orcuslc}{http://github.com/orcuslc}
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

% \section{Personal Profile}

% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor sed sagittis. Cras justo lorem, volutpat mattis lacus vel, consequat aliquam quam. Interdum et malesuada fames ac ante ipsum primis in faucibus. Integer blandit, massa at tincidunt ornare, dolor magna interdum felis, ac blandit urna neque in turpis.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabblock
{2013-}{Present}{BSc, Information and Computing Sciences - \href{http://math.fudan.edu.cn}{Fudan University, Expected 2017}}
{Bsc Minor, Data Science - \href{http://www.sds.fudan.edu.cn/}{Fudan University}}
{\textit{GPA} \> 3.21/4.00 \> \textit{Rank} \> 12/71\\
\textit{GRE} \> 330 \> \textit{TOEFL-iBT} \> 104 \\
\textit{\href{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=3152}{Mathematical Analysis AII}} \> A- \>
\textit{\href{http://homepage.fudan.edu.cn/qhxie/}{Advanced Algebra II}} \> B+ \\
\textit{\href{http://homepage.fudan.edu.cn/yaoyaojr/}{College Physics B I, II}} \> A- \> \textit{\href{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=2137}{Real Analysis}} \> B+ \\
\textit{\href{http://homepage.fudan.edu.cn/weilin/}{ODE}} \> B+ \> \textit{\href{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=2209}{Probability Theory}} \> A- \\
\textit{\href{http://homepage.fudan.edu.cn/yangfeng/}{Numerical Approximation}} \> A \> \textit{\href{http://homepage.fudan.edu.cn/wggao/}{Computational Methods}} \> A- \\
\textit{\href{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=3140}{Digital Signal Processing}} \> A \> \textit{\href{http://homepage.fudan.edu.cn/zqwang/}{PDE}} \> B+ \\
\textit{\href{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=3144}{Statistical Computing}} \> B+ \\
}
% %------------------------------------------------

% \tabbedblock{
% \bf{2001-2003} \> Advanced Secondary Education - \href{http://www.berkeleycollege.edu}{Berkeley College, California}\\[5pt]
% \>\+
% \textit{Pure Mathematics} \> A \\
% \textit{Statistics (AS)} \> A \\
% \textit{Physics} \> A \\
% \textit{Economics} \> B
% }

%------------------------------------------
%   RESEARCH SECTION
%------------------------------------------
\section{RESEARCH}
\research
{Apr 2016 -}{Present}
{BigVid Lab, School of Computer Sciences}
{Prof. Yugang Jiang}{http://yugangjiang.info/}
{Member of Fudan-NTT team in TRECVID 2016 - MED}
{
\begin{itemize-noindent} \itemsep -2pt
\item{In charge of audio speech recognition.}
\item{Build an automatic ASR module with \href{http://kaldi-asr.org}{Kaldi-ASR}, code:\\\href{https://github.com/Orcuslc/MED2016}{https://github.com/Orcuslc/MED2016}}
\item{Developed a server-client structure for word to vector inquiry, code:\\\href{https://github.com/Orcuslc/Word2Vec-server}{https://github.com/Orcuslc/Word2Vec-server}}
\item{Established an automatic module for keyword extraction, word root extraction and word to vector using \href{http://www.nltk.org/}{Python-NLTK} and \href{http://nlp.stanford.edu/projects/glove/}{data from Wikipedia.}}
\item{Conducted some research on far field voice/background seperation using FFT-based filters, IIR filters and statistical learning mathods like nearest neighbours and neural networks, and improved recognization by 20 percent.}
\item{Now doing research on voice/background seperation using Markov Chains.}
\end{itemize-noindent}
}

\research
{June 2016 -}{Present}
{School of Mathematical Sciences}
{Prof. Donghua Zhao}{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=3140}
{To establish a big data platform for Eastern China State Grid}
{
\begin{itemize-noindent} \itemsep -2pt
\item{Performed as the main programmer in the group}
\item{In charge of mid-term and long-term load forecasting}
\item{Established a model for long term max load forecasting using SVR and NN forests, code:\\ \href{https://github.com/Orcuslc/ECSGCC-Data}{https://github.com/Orcuslc/ECSGCC-Data}}
\item{Developed a 24-hour load forecasting model using Monte Carlo methods.}
\end{itemize-noindent}
}

\research
{Oct 2015 - }{Present}
{School of Mathematical Sciences}
{Prof. Yashan Xu}{http://math.fudan.edu.cn/ShowPeople.aspx?info_lb=548&flag=526&info_id=3129}
{To study the trends in stock prices with their public attention}
{
\begin{itemize-noindent} \itemsep -2pt
\item{Performed as the main programmer in the group}
\item{Developed an online platform to test the profit of stock investing strategies, code:\\\href{http://chuanlu.xyz/easyshares}{http://chuanlu.xyz/easyshares}}
\item{Proposed a novel method to quantify the degree of public attention on stocks.}
\item{Now using statistical methods to continue the research.}
\end{itemize-noindent}
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------
\section{Work Experience}

\job
{June 2015 -}{Oct 2015}
% {Lehman Brothers, 1234 Mario Park, San Francisco, CA, United States}
{Sinolink Innovation Investment, Shanghai}
{http://www.gjll.com.cn/}
{Research Intern, Quantitative Trading Department}
{\begin{itemize-noindent} \itemsep -2pt
\item{Implemented two trading strategies modified on momentum factors proposed by collegues.}
\item{Established and maintained a local database for stock information.}
\item{Collaborated on the developing of a value-reversal strategy in option market.}
\end{itemize-noindent}
\rule{0mm}{3mm}\textbf{Technologies:} Python 3.4, Python-sqlalchemy, tushare, numpy, scipy, matplotlib, flask; MongoDB, NoSQL; R, C++.}

%------------------------------------------------

% \job
% {Oct 2009 -}{Sep 2010}
% {Initech Inc., Otis St, CA 94025, United States}
% {http://www.initech.com}
% {Analyst}
% {Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor:

% \begin{itemize-noindent}
% \item{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals.)}
% \item{Managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.}
% \end{itemize-noindent}

% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor sed sagittis.}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages and Scientific Computing Related Skills}
{
\textbf{Experienced in:} Python(3.4, 2.7), MATLAB, C/C++, LaTeX, git, sqlite3\\[3pt]
\textbf{Proficient in:} Linux Shell, R, Markdown, Scala\\[3pt]
\textbf{Frequent user of:} MIT-Scheme, MongoDB, MySQL, Pascal\\
}

%------------------------------------------------

\skillgroup{Web-Related Development}
{
\textbf{Experienced in:} Web spiders, Apache, Nginx, HTML5, Python-Flask, BeautifulSoup \\[3pt]
\textbf{Frequent user of:} Javascript, jQuery, CSS \\
% \skill{Experienced in}{Web spiders, Apache, Nginx, HTML5, Python-Flask, BeautifulSoup}
% \skill{Frequent user of:}{Javascript, jQuery, CSS}
}

\skillgroup{Computer Vision Tools}
{
\textbf{Experienced in:} OpenCV, Kaldi-ASR, Word2Vec tools, Tesseract-OCR
}
\vspace{2mm}

%------------------------------------------------

% \skillgroup{Miscellaneous}
% {
% \textit{Microsoft SQL Server 2000/2005} - database architecture and administration\\
% \textit{Transact-SQL} - data definition and manipulation\\
% \textit{SQL Profiler} - performance tuning and debugging\\
% \textit{MySQL Server}\\
% \textit{CVS, DARCS, git} - source version control
% }

%---------------------------------------------------------------
%         Projects Section
%---------------------------------------------------------------
\section{Projects}
\awardgroup{
\project{GrabCut}{An implementation of \href{http://dl.acm.org/citation.cfm?id=1015720}{\textit{Grabcut: Interactive foreground extraction using iterated graph cuts}}}{https://github.com/orcuslc/GrabCut}
\project{EasyShares}{A platform to test yields of stock portfolios, see at \href{http://chuanlu.xyz/easyshares}{http://chuanlu.xyz/easyshares}}{https://github.com/orcuslc/stock}
\project{W2V API}{A server-client structure for word to vector querying, reduced load cost to 1/1000}{https://github.com/orcuslc/word2vec-server}
\project{Auto ASR}{The auto ASR module for TRECVID-MED 2016}{https://github.com/orcuslc/MED2016}
\project{xq spider}{A web spider for \href{https://xueqiu.com}{https://xueqiu.com}, in order to get stock comments and follows}{https://github.com/orcuslc/xueqiu\_spider}
\project{BingBest}{An application of changing desktop background from \href{https://cn.bing.com}{https://bing.com} for Windows and Linux}{https://github.com/orcuslc/bingbest}
\project{ECSGCC}{Scripts for the program to build a big-data platform for State Grid of China}{https://github.com/orcuslc/ecsgcc-data}
\project{Learning}{Homework of my courses, implementation of algorithms and answers to problems in publications}{https://github.com/orcuslc/learning}
}

%----------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------
\section{Awards}
\awardgroup{
\award{Nov 2014}{Third Prize Scholarship of Fudan University}
\award{Nov 2014}{Academic Scholarship of Fudan University}
\award{Dec 2015}{Academic Scholarship of Fudan University}
}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{Interests}

% \interestsgroup{
% \interest{Badminton, Tennis, Running, Cycling, Sailing}
% \interest{Travelling}
% \interest{Creative Writing}
% \interest{Photography}
% \interest{Car Mechanics}
% }

\section{Extra-Curricular Activities}
\awardgroup{
\award{Oct 2013}{Joined Infinity Volleyball Association as a member of liaison department.}
\award{Feb 2014}{Elected Head of Liaison Department, Infinity Volleyball Association.}
\award{Sept 2014}{Elected Vice Chair, Infinity Volleyball Association.}
}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

% \section{Referees}

% \parbox{0.5\textwidth}{ % First block
% \begin{tabbing}
% \hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Name} \> Bill Lumbergh \\ % Referee name
% {\bf Company} \> Initech Inc. \\ % Referee company
% {\bf Position} \> Vice President \\ % Referee job title 
% {\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
% \end{tabbing}}
% \hfill % Horizontal space between the two blocks
% \parbox{0.5\textwidth}{ % Second block
% \begin{tabbing}
% \hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
% {\bf Company} \> Burbank Buy More \\ % Referee company
% {\bf Position} \> Store Manager \\ % Referee job title 
% {\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
% \end{tabbing}}

% %----------------------------------------------------------------------------------------

\end{document}

### 2016-09-21 Statistical Learning/Homework1/hierarchical_clustering.R

@@ -1,0 +1,88 @@
+source('kmeans.R')
+
+hc = function(A, linkage = 'single') {
+  # Hierarchical Clustering: The request is that no two data points are the same.
+  # A: The data matrix;
+  # linkage: The mode of linkage, choose from ['single', 'complete', 'average'];
+  ndata = nrow(A);
+  for(i in 1:(ndata - 1)) {
+    for(j in (i+1):ndata) {
+      if(identical(A[i, ], A[j, ])) {
+        cat("ERROR: There are two data points of the same");
+        return(0);
+      }
+    }
+  }
+  TEMP = A;
+  status = rep(0, ndata); # The flag to mark if a node has been merged; 0:no; 1:yes;
+  dist_matrix = matrix(rep(0, ndata*ndata), ncol = ndata);
+  pairs = matrix(rep(0, 2*(ndata-1)), ncol = 2);
+  for(i in 1:ndata) { # Init The dist_matrix
+    for(j in 1:ndata) {
+      if(i != j) {
+        dist_matrix[i, j] = calc_dist(A[i, ], A[j, ]);
+      }
+    }
+  }
+  for(i in 1:(ndata - 1)) {
+    res = update_node(A, dist_matrix, status, linkage);
+    pair = res[[1]];
+    pairs[i, ] = pair;
+    dist_matrix = res[[2]];
+  }
+  return(pairs);
+}
+
+update_node = function(A, dist_matrix, status, linkage) {
+  # Find a nearest node and update the nodes;
+  # A: The data matrix;
+  # status: The status vector to flag if a node has been merged;
+  #         if so, it should be considered Inf;
+  ndata = nrow(A);
+  narg = ncol(A);
+  # print(dist_matrix);
+  # print(min(dist_matrix[which(dist_matrix != 0)]))
+  min_pair = which(dist_matrix == min(dist_matrix[which(dist_matrix != 0)]))[1];
+  # print(min_pair)
+  x2 = min_pair %% ndata;
+  if(x2 == 0) {
+    x2 = ndata;
+  }
+  x1 = (min_pair - x2) / ndata + 1;
+  # print(c(x1, x2, dist_matrix[x1, x2]))
+  if(linkage == 'single') {
+    for(j in 1:ndata) {
+      if(j != x1){
[…]

### 2016-09-22 Numerical Algorithm and Case Studies/Homework1/structure.tex
modified

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified By Orcuslc, 2016-9-21
% Modified for Assignments
% http://github.com/orcuslc
%
% Wilson Resume/CV
% Structure Specification File
% Version 1.0 (22/1/2015)
%
% This file has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt]{article}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{clrscode3e}

\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\usepackage[a4paper, hmargin=25mm, vmargin=30mm, top=20mm]{geometry} % Use A4 paper and set margins

\usepackage{fancyhdr} % Customize the header and footer

\usepackage{lastpage} % Required for calculating the number of pages in the document

\usepackage{hyperref} % Colors for links, text and headings

\setcounter{secnumdepth}{0} % Suppress section numbering

%\usepackage[proportional,scaled=1.064]{erewhon} % Use the Erewhon font
%\usepackage[erewhon,vvarbb,bigdelims]{newtxmath} % Use the Erewhon font
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{fontspec} % Required for specification of custom fonts
\setmainfont[Path = ./fonts/,
Extension = .otf,
BoldFont = Erewhon-Bold,
ItalicFont = Erewhon-Italic,
BoldItalicFont = Erewhon-BoldItalic,
SmallCapsFeatures = {Letters = SmallCaps}
]{Erewhon-Regular}

\usepackage{color} % Required for custom colors
\definecolor{slateblue}{rgb}{0.17,0.22,0.34}

\usepackage{sectsty} % Allows customization of titles
\sectionfont{\color{slateblue}} % Color section titles

\fancypagestyle{plain}{\fancyhf{}\cfoot{\thepage\ of \pageref{LastPage}}} % Define a custom page style
\pagestyle{plain} % Use the custom page style through the document
\renewcommand{\headrulewidth}{0pt} % Disable the default header rule
\renewcommand{\footrulewidth}{0pt} % Disable the default footer rule

\setlength\parindent{0pt} % Stop paragraph indentation

% Non-indenting itemize
\newenvironment{itemize-noindent}
{\setlength{\leftmargini}{0em}\begin{itemize}}
{\end{itemize}}

% Text width for tabbing environments
\newlength{\smallertextwidth}
\setlength{\smallertextwidth}{\textwidth}
\addtolength{\smallertextwidth}{-2cm}

\newcommand{\sqbullet}{~\vrule height .8ex width .6ex depth -.05ex} % Custom square bullet point

\renewcommand{\title}[2] {
{\Huge{\color{slateblue}\textbf{#1}}}
\hfill
\LARGE{\color{slateblue}\textbf{#2}} \\[10pt]
\large{\color{slateblue}\textbf{Chuan Lu, 13300180056, chuanlu13@fudan.edu.cn}} \\[1mm]
\rule{\textwidth}{0.5mm}
}

\newcommand{\problem}[2] {
\vspace{20pt}
\LARGE{\color{slateblue}\textbf{Problem #1.}}
\vspace{2mm}
#2 \\[5pt]
}

\newcommand{\solution}[2] {
\large{\color{slateblue}\textit{\textbf{#1.}}}
#2 \qed \\[3mm]
}

\newcommand{\algorithm}[2] {
\begin{codebox}
\Procname{$\proc{Algorithm #1}$}
#2
\end{codebox}
}

\newcommand{\refgroup}[1] {
\LARGE{\color{slateblue}\textbf{Reference}} 
\begin{tabbing}
\hspace{5mm} \= \kill
#1
\end{tabbing}
}

\newcommand{\reference}[1] {
\sqbullet \ \  \large{#1} \\
}
% \newcommand{\solution}[2] {
% \LARGE{\color{slateblue}\textit{#1}}
% \ #2 \qed
% }

% \newenvironment{problem}[2][Problem]{\begin{trivlist}
% \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

### 2016-09-23 Numerical Algorithm and Case Studies/Homework1/assignment.tex
modified
add a homework

--- 2016-09-21 Config Files/Assignment-TEX/assignment.tex
@@
   numbers=left,
-    framexleftmargin=10mm,
-    frame=none,
-    backgroundcolor=\color[RGB]{245,245,244},
-  keywordstyle=\bf\color{blue},
+  frame=shadowbox,
+  keywordstyle=\bf\color{blue!70},
   identifierstyle=\bf,
@@
 
-\title{Homework 1}{16.9.21, Chuan Lu}
+\title{Homework 1}{16.9.21}
 
-\problem{1}{Rewrite the target function of K-means in matrix form.}
-\solution{Solution}{
-$f(x) = argmin_{\mathcal{S}}\sum_{i=1}^{k}\sum_{x_j\in S_j}\sum_{1\le m\le p}\lvert x_{jl} - x_{jm} \rvert^2.$
+% \parbox{0.3\textwidth}{
+% Chuan Lu}
+% \hfill
+% \parbox{0.3\textwidth}{
+% 13300180056}
+% \hfill
+% \parbox{0.3\textwidth}{
+% chuanlu13@fudan.edu.cn}
+
+\problem{1}{}
+\solution{Abstract}{
+\\[5pt]
+About the computation of roots and its sensitivity on coefficients of a quadratic polynomial.
 }
 
-\problem{2}{Cluster $Data_i.csv$ with K-means, judge the number of clusters, and compare differences between different evaluating methods.}
-\solution{Solution}{
-The code of K-means, evaluating and test scripts can be found from attachments(kmeans.R, evaluate.R, hw1.2.R).
+\solution{Introduction and Algorithm}{
+\\[5pt]
+In middle school we learned that the roots of a quadratic polynomial $ax^2+bx+c=0$ can be expressed as $x_1 = \frac{-b+\sqrt{b^2-4ac}}{2a}, x_2 = \frac{-b-\sqrt{b^2-4ac}}{2a}$. \\[5pt] 
+However in computation, when $4ac\ll b^2$, the so-called catastrophic cancellation would happen: if $b\ge 0$, then $\sqrt{b^2-4ac}\approx b$, which would cause a decreas in the number of significant digits of $-b+\sqrt{b^2-4ac}$.
+This statement also holds when $b\le 0$.
+\\[10pt]
+In order to avoid this, we use a different but equivalent expression for the roots. \\[10pt]
+When $b\ge 0$, $\left\{
+\begin{aligned}
+x_1 & = & \frac{-b-\sqrt{b^2-4ac}}{2a} \\
+x_2 & = & \frac{-2c}{b+\sqrt{b^2-4ac}}
+\end{aligned}
+\right.$; 
+when $b < 0$, $\left\{
+\begin{aligned}
+x_1 & = & \frac{-b+\sqrt{b^2-4ac}}{2a} \\
+x_2 & = & \frac{2c}{-b+\sqrt{b^2-4ac}} 
+\end{aligned}
+\right.$ \\[10pt]
+The correctness can be easily proved by using Vieta theorem.
+}
+
+\solution{Code}{
+\\[5pt]
+The code can be found in the attachment(\texttt{extract\_quadratic.m}); We use the name \texttt{\textbf{MyFunc}} to refer this function in the following sections.
+}
+
+\solution{Results}{
+\\[5pt]
+In the following sections, we always use $x_1$ to refer to the larger root, and $x_2$ to the smaller root. \\[5pt]
+For $(b=-56, c=1)$, the result is in Table 1 below: \\
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|}
+\hline
+& $x_1$ & $x_2$ \\
+\hline
+\texttt{MyFunc()} & 55.9821 & 0.0179 \\
+\hline
+\texttt{root()} & 55.9821 & 0.0179 \\
+\hline
+\end{tabular}
+\caption{Result of $(b=-56, c=1)$}
+\end{table}\\
+For $(b=-10^8, c=1)$, the result is in Table 2 below:\\
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|}
+\hline
+& $x_1$ & $x_2$ \\
+\hline
+\texttt{MyFunc()} & 100000000 & 1.0000e-08 \\
+\hline
+\texttt{root()} & $1.0000*10^8$  & $0.0000*10^8$ \\
+\hline
+\end{tabular}
+\caption{Result of $(b=-10^8,c=1)$}
+\end{table} \\
+When $4ac\approx b^2$, the results are the same; but when $4ac\ll b^2$, the significant number of the smaller root using \texttt{root} is eliminated.
+}
+
+\solution{Sensitivity}{
+\\[5pt]
+According to Taylor series, $$x(t+\delta)\approx x(t)+\delta\frac{dx}{dt}(t).$$
+Therefore the sensitivity of x on t can be defined as $s_x(t) = dx/dt$. \\[5pt]
+In this problem, $F(x, b, c) = x^2+bx+c$. According to implicit function theorem, $$\frac{\partial x}{\partial b} = -\frac{F_x}{F_b} = -\frac{2x+b}{x} = -2+\frac{b}{x}, $$
+$$\frac{\partial x}{\partial c} = -\frac{F_x}{F_c} = -(2x+b).$$ \\[5pt]
+In consequence, when $\lvert x\rvert\ll\lvert b\rvert$, $x$ is very sensitive to a little change in $b$. Similarly, when $\lvert2x+b\rvert\gg 1$, $x$ is very sensitive to a little change in $c$.
+}
+
+\solution{Discussion and Conclusion}{
+With the conclusion in Sensitivity part, we can make some explanation for the difference between results of \texttt{MyFunc} and \texttt{root}. \\[5pt]
+1. For the first case, when $b=-56, c=1$, and the result $x_1\approx56, x_2\approx0.018$. \\[5pt]
+In this case $\frac{\partial x_1}{\partial b} \approx -3, \frac{\partial x_1}{\partial c}\approx -56,$ and $\frac{\partial x_2}{\partial b} \approx -3113, \frac{\partial x_1}{\partial c}\approx 56$.
+Since the sensitivities are not large enough to have strong effects on a \texttt{\textbf{format short}} computation, the result of \texttt{MyFunc} and \texttt{root} seems the same.
+\\[5pt]
+2. For the second case, when $b=-10^8, c=1$, and the result $x_1\approx 10^8, x_2\approx 10^{-8}.$ \\[5pt]
+In this case $\frac{\partial x_1}{\partial b} \approx -3, \frac{\partial x_1}{\partial c}\approx -10^8,$ and $\frac{\partial x_2}{\partial b} \approx 10^16, \frac{\partial x_2}{\partial c} \approx 10^8$.
+\\[5pt]
+Apparently, sensitivity of $x_2$ on both $b$ and $c$ are large enough to make a obvious change in significant numbers. It leads to that the result of $x_2$ being $0$ when using \texttt{root}.
+In this scenario we may regard this numerial problem an ill-conditioned one; though the numerical algorithm by MATLAB may be a stable one, the results can be far from true ones.
+}
+
+\problem{2}{}
+\solution{Abstract}{
+\\[5pt]
+(a) Program row and column oriented algorithms and compare the time cost between them \\
+(b) Program algorithms for update a matrix using different methods and compare the time cost.
+}
+
+\solution{Introduction and Algrithm}{
+\\[5pt]
+For problem (a), we will use back substitution algorithm in row-oriented and column-oriented ways for solving an upper triangular system. 
+\algorithm{1.1, Row-oriented Back Substitution}{
+\zi Input: An upper triangular matrix $U\in \mathbb{R}^{n\times n}$, and a vector $b\in \mathbb{R}^{n}$.
+\zi Output: Updated $b\in \mathbb{R}^{n}$.
+\li $b(n) = b(n)/U(n, n)$
+\li \For $i \gets n-1$ \To $1$ \By $-1$
+\li   \Do
+          $b(i) = (b(i)-U(i, i+1:n)\cdot b(i+1:n))/U(i, i)$
+      \End
+\li \Return $b$
+}
+\algorithm{1.2, Column-oriented Back Substitution}{
+\zi Input: An upper triangular matrix $U\in \mathbb{R}^{n\times n}$, and a vector $b\in \mathbb{R}^{n}$.
+\zi Output: Updated $b\in \mathbb{R}^{n}$.
+\li \For $j \gets n$ \To $2$ \By $-1$
+\li   \Do
+          $b(j) = b(j)/U(j, j)$
+\li       $b(1:j-1)=b(1:j-1)-b(j)\cdot U(1:j-1, j)$
+      \End
+\li $b(1) = b(1)/U(1, 1)$
+}
+These two algorithms do not need extra space. \\
+
+For problem (b), the five algorithms are shown below.
+
+\algorithm{2.1, Loop-update}{
+\zi Input: Three matrices $A, B, C\in\mathbb{R}^{n\times n}$.
+\zi Output: The updated $C\in\mathbb{R}^{n\times n}$.
+\li \For $i \gets 1$ \To n
+\li   \Do
+      \For $j \gets 1$ \To n
+\li     \Do
+        \For $k \gets 1$ \To n
+\li         \Do
+              $C(i, j) = C(i, j)+A(i, k)\cdot B(k, j)$
+            \End
+        \End
+      \End
+\li \Return $C$      
+}
+\algorithm{2.2, Dot-update}{
+\zi Input: Three matrices $A, B, C\in\mathbb{R}^{n\times n}$.
+\zi Output: The updated $C\in\mathbb{R}^{n\times n}$.
+\li \For $i \gets 1$ \To $n$
+\li   \Do
+        \For $j \gets 1$ \To $n$
+\li       \Do
+            $C(i, j) = C(i, j)+A(i, :)\cdot B(:, j)$
+          \End
+      \End
+\li \Return $C$
+}
+\algorithm{2.3, Daxpy-update}{
+\zi Input: Three matrices $A, B, C\in\mathbb{R}^{n\times n}$.
+\zi Output: The updated $C\in\mathbb{R}^{n\times n}$.
+\li \For $i \gets 1$ \To $n$
+\li   \Do
+        \For $j \gets 1$ \To $n$
+\li       \Do
+            $C(:, i) = C(:, i)+A(:, j)\cdot B(j, i)$
+          \End
+      \End
+\li \Return $C$        
+}
+\algorithm{2.4, MatVec-update}{
+\zi Input: Three matrices $A, B, C\in\mathbb{R}^{n\times n}$.
+\zi Output: The updated $C\in\mathbb{R}^{n\times n}$.
+\li \For $i \gets 1$ \To $n$
+\li   \Do
+        $C(:, i) = C(:, i)+A\cdot B(:, i)$
+      \End
+\li \Return $C$
+}
+
+\algorithm{2.5, OuterDot-update}{
+\zi Input: Three matrices $A, B, C\in\mathbb{R}^{n\times n}$.
+\zi Output: The updated $C\in\mathbb{R}^{n\times n}$.
+\li \For $i \gets 1$ \To $n$
+\li   \Do
+        $C = C+A(:, i)\cdot \B(i, :)$
+      \End
+\li \Return $C$
+}
+I am not quite sure about the MatVec update.
+}
+
+\solution{Code}{
+The code can be found in the attachments(\texttt{row\_back\_substitute.m},\ \texttt{col\_back\_substitute.m},\ \texttt{mmloop.m},\ \texttt{mmdot.m},\ \texttt{mmdaxpy.m},\ \texttt{mmmatvec.m},\ \texttt{mmouterdot.m}).
+And the test script is \texttt{test.m}.\\[5pt]
+Code for checking errors is ignored here, since I think in this problem it is of less importance.
 }
 \solution{Result}{
-For Data1.csv, we cluster with k = 3. The result is shown as below.
-\begin{figure}[htbp]
-\centering
-\includegraphics[width = 15cm]{pics/hw2_data1_cluster.eps}
-\caption{The clusters of Data1.csv with k = 3}
-\label{clusters of data1}
-\end{figure}
-\\[1mm]
+For problem (a), the time cost is in Table 3 below.
+(Of course I know that MATLAB is using some precompile skills to accelerate the computing speed, so I run the same test several times after the time cost converge to a stable status.) \\[5pt]
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+n & 128 & 256 & 512 & 1024 \\
+\hline
+row-oriented & 0.000477 &  0.000957 & 0.002858 & 0.009390\\
+\hline
+col-oriented & 0.000436 & 0.000912 & 0.002631 & 0.006705\\
+\hline
+\end{tabular}
+\caption{Time cost of solving a upper triangle system}
+\end{table}
+However, after test my program several times, I found that when $n$ is small, which, to be exact, when $n<50$, difference between solution of row-oriented and col-oriented algorithms $\lVert x_r - x_c \rVert$ is quite small.
+In this case $\lVert x_r - x_c \rVert \le 10^{-4} \Vert U\Vert$.
+However, when $n$ is larger, the difference becomes larger.
+Table 4 shows the relative norm of difference vectors between result of the two als and result of directly using MATLAB's inner functions(i represents MATLAB's inner function).
+$$\Vert\Delta_{error}\Vert = \frac{\Vert x_1 - x_2\Vert}{\Vert U\Vert}$$
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+n & 128 & 256 & 512 & 1024 \\
+\hline
+r-c & $5.948e^{-6}$ & $1.504e^{27}$ & $6.904e^{85}$ & $4.179e^{168}$\\
+\hline
+r-i & $5.680e^{-6}$ & $1.521e^{27}$ & $2.952e^{85}$ & $6.968e^{167}$\\
+\hline
+c-i & $1.091e^{-6}$ & $1.693e^{25}$ & $2.261e^{85}$ & $4.875e^{168}$ \\
+\hline
+\end{tabular}
+\caption{Relative norm of difference vector}
+\end{table}
 
-For choosing k, the result of Data1.csv is shown below; The first is the result of Calinski-Harabasz method, the second Hartigan method and the last Gap Statistic. \\[3pt]
-The result of CH method is 9, if we may add a limit that $k\le 10.$ The result of H method is 3, and result of GAP statistic is 3.\\[3pt]
+For Problem (b), the time cost for als is shown in Table 5 below.
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+n & 128 & 256 & 512 & 1024 \\
+\hline
+loop & 0.050033 & 0.425775 & 3.196842 & 39.002625 \\
+\hline
+dot & 0.026959 & 0.134890 & 0.787452 & 13.141148 \\
+\hline
+daxpy & 0.003710 & 0.023131 & 0.158915 & 1.182440 \\
+\hline
+matvec & 0.001167 & 0.005713 & 0.026144 & 0.375322 \\
+\hline
+outerdot & 0.007415 & 0.030481 & 0.426991 & 4.375097 \\
+\hline
+\end{tabular}
+\caption{Time cost of updating a matrix}
+\end{table}
 
-\begin{figure}[htbp]
-\centering
-\subfloat[CH method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_CH.eps}}\hfill
-\subfloat[H method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_H.eps}}\hfill
-\subfloat[GAP statistic]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_GAP.eps}}\hfill
-\caption{The three evaluating methods of choosing k for Data1.csv}
-\label{EVA Data1}
-\end{figure}
+The norm of relative error (with MATLAB inner *) is shown in Table 6 below.
+$$\Vert\Delta_{error}\Vert = \frac{\Vert\hat{C} - C\Vert}{\Vert C\Vert}$$
+\begin{table}[htbp] \large \centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+n & 128 & 256 & 512 & 1024 \\
+\hline
+loop & $1.841e^{-15}$ & $2.614e^{-15}$ & $1.408e^{-14}$ & $2.660e^{-14}$ \\
+\hline
+dot & $3.515e^{-15}$ & $6.756e^{-15}$ & $5.502e^{-15}$ & $6.474e^{-15}$ \\
+\hline
+daxpy & $1.144e^{-15}$ & $2.614e^{-15}$ & $1.408e^{-14}$ & $2.660e^{-14}$ \\
+\hline
+matvec & $1.178e^{-15}$ & $1.643e^{-15}$ & $1.385e^{-14}$ & $2.628e^{-14}$ \\
+\hline
+outerdot & $1.195e^{-13}$ & $2.614e^{-15}$ & $1.408e^{-14}$ & $2.660e^{-14}$ \\
+\hline
+\end{tabular}
+\caption{Norm of error in updating a matrix}
+\end{table}
+}
+\solution{Discussion}{
+From result of problem (a), we found that column-oriented algorithm is slightly quicker that row-oriented algorithm in solving upper triangular system. \\[5pt]
+From the algorithm's point of view, in $i^{th}$ loop, col-oriented al need to do (i-1) times' multiplication, (i-1) times' subtraction, and 1 division, while row-oriented al need to do (n-i) times multiplication, (n-i) times addition, and 1 division.
+\\[5pt]
+In consequence, C-O al need to do $\frac{(n-1)(n-2)}{2}$ times' multiplication and substraction, and (n-1) times' division; while R-O al need to do 1 more division than C-O.
+So I am curious why C-O cost only 2/3 time comparing with R-O when $U \in\mathbb{R}^{1024\times 1024}$.
+\\[5pt]
+On the other hand, since the matrices are generated by random numbers, it is of much possibility that those matrices are nearly singular.
+It is not difficult to understand why the result of $x$ has such a huge error.
+\\[5pt]
 
-For Data2.csv, since each data point is of 3 dims, we cannot plot its clustering result here.
-But after deploying the evaluating methods we consider k = 3.
-The type of datas can be find in attachments(CLUSTER\_DATA2.txt).
-\\[3pt]
-
-The result of CH method is 8, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
-The pics are shown below.
-
-\begin{figure}[htbp]
-\centering
-\subfloat[CH method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_CH.eps}}\hfill
-\subfloat[H method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_H.eps}}\hfill
-\subfloat[GAP statistic]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_GAP.eps}}\hfill
-\caption{The three evaluating methods of choosing k for Data2.csv}
-\label{EVA Data2}
-\end{figure}
-
-For Data3.csv, we fix k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA3.txt). \\[3pt]
-
-The result of CH method is 9, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
-The pics are shown below.
-
-\begin{figure}[htbp]
-\centering
-\subfloat[CH method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_CH.eps}}\hfill
-\subfloat[H method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_H.eps}}\hfill
-\subfloat[GAP statistic]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_GAP.eps}}\hfill
-\caption{The three evaluating methods of choosing k for Data3.csv}
-\label{EVA Data2}
-\end{figure}
-
-For Data4.csv, we found k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA4.txt). \\[3pt]
-
-The result of CH method is 7, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
-The pics are shown below.
-
-\begin{figure}[htbp]
-\centering
-\subfloat[CH method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_CH.eps}}\hfill
-\subfloat[H method]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_H.eps}}\hfill
-\subfloat[GAP statistic]{ %
-	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_GAP.eps}}\hfill
-\caption{The three evaluating methods of choosing k for Data4.csv}
-\label{EVA Data2}
-\end{figure}
-}
-\solution{Analysis}{
-It is suprising that result of Calinski-Harabasz method does not agree with the other methods.
-I consider it as the result that I misunderstood the meaning of $W(k), B(k)$.
-I calculate the former as the target function of cluster; the latter as $\sum_{c_i, c_j \in C}\lVert c_i - c_j \rVert^2$, in which $C$ is the set of cluster centers.
+For problem (b), result of the five algorithms are of good precision, which can be found with norm of errors. \\[5pt]
+Let's analysis the flops of the als.
+Loop update needs $n^3$ times of loops, each contains a multiplication and an addition.
+Dot update needs $n^2$ times of loops, each contains an addition and a Vectorized Dot.
+Daxpy update needs $n^2$ times of loops, each contains an Vectorized Addition and a Vectorized Scalar multiplication with a vector.
+MatVec update needs $n$ times of loops, each contains a Vectorized Addition and a Vectorized Scalar multiplication with a matrix.
+OuterDot update needs $n$ times of loops, each contains a Vectorized Addtion with a matrix and an outer dot of two vectors.\\[5pt]
+Though the total flops of the five als are the same, we all know that in MATLAB, \texttt{for} loops are much slower that vectorized computations. So the result of experiment is trivial.
 }
 
-\problem{3}{Use hierarchical clustering methods to cluster $Data_i.csv$}
-\solution{Solution}{
-The code of hierarchical clustering and the test script can be found from attachments(hierarchical\_clustering.R, hw1.3.R).
-}
-\solution{Result}{
-It is somehow embarrassing that I still did't know how to draw trees in R without $hcluster()$. The result can be shown is the attachments, (HC\_DATA1.txt and HC\_DATA2.txt). \\[3pt]
-Each result is a (n-1) * narg matrix, in which n is the number of data points and narg is the number of dims in each data point.
-Each row in the matrix(for example, A[1, ]) means a step when two points merged with each other; A[1, 1] and A[1, 2] merged into a new A[1, 1], and the point represented by A[1, 2] is abandoned.
-\\[3pt]
-It is possible to draw the tree and do Tree-Cut with the results.
+\refgroup{
+\reference{Jixiu Chen, \textit{Mathematical Analysis II}, Page 174-175.}
+\reference{D. P. O’Leary, \textit{Scientific Computing with case studies}, Page 23-24.}
+\reference{Gene H. Golub, \textit{Matrix Computations}, Page 10-11.}
 }

### 2016-09-23 Numerical Algorithm and Case Studies/Homework1/code/gen_rand.m

@@ -1,0 +1,5 @@
+function[A, b] = gen_rand(n)
+% Generate a random matrix and a random vector;
+
+A = rand(n);
+b = rand([n, 1]);

### 2016-09-23 Numerical Algorithm and Case Studies/Homework1/code/mmmatvec.m

@@ -1,0 +1,9 @@
+function [C] = mmmatvec(A, B, C)
+% Using MatVec update to calculate matrix multiplication;
+% A, B, C: n*n Matrix;
+
+[n, ~] = size(A);
+
+for j = 1:n
+    C(:, j) = C(:, j) + A*B(:, j);
+end

### 2016-09-27 Numerical Algorithm and Case Studies/Homework1/assignment.tex
updated PAC files
Modified some files

@@
 \usepackage{listings}
-\lstset{
-  numbers=left,
-  frame=shadowbox,
-  keywordstyle=\bf\color{blue!70},
-  identifierstyle=\bf,
-  numberstyle=\color[RGB]{0,192,192},
-  commentstyle=\it\color[RGB]{0,96,96},
-  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
-  showstringspaces=false,
-  extendedchars=false
-    }
+\usepackage{xcolor}
+\usepackage{courier}
+\renewcommand{\sfdefault}{phv}
+
 \DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}
@@
 
-\title{Homework 1}{16.9.21}
+\title{Homework 1}{16.9.22}
+\tiny{Code of this assignment are in the attachment, and they can also be found in GitHub: https://github.com/Orcuslc/Learning/tree/master/Numerical\%20Algorithm\%20and\%20Case\%20Studies/Homework1/code}
 
@@
 \right.$ \\[10pt]
-The correctness can be easily proved by using Vieta theorem.
+\textbf{Verification}: The correctness can be easily proved by using Vieta theorem.
 }
@@
 Apparently, sensitivity of $x_2$ on both $b$ and $c$ are large enough to make a obvious change in significant numbers. It leads to that the result of $x_2$ being $0$ when using \texttt{root}.
-In this scenario we may regard this numerial problem an ill-conditioned one; though the numerical algorithm by MATLAB may be a stable one, the results can be far from true ones.
+In this scenario we may regard this numerial problem an ill-conditioned one; though the numerical algorithm by MATLAB may be a stable one, the results can be far from true ones. \\[5pt]
+}
+\solution{Remarks}{
+I used Python to solve the equation $x^2 - 1e^8x+1 = 0$:
+\lstinputlisting[language=Python]{code/rt_extract.py}
+The result is: $x_1 = 1e^{-8}, x_2 = 1e^8.$ So I am wondering, since \texttt{Scipy} could solve this equation perfectly, why can't MATLAB?
+The \texttt{roots()} function even doesn't provide a chance to choose the initial points.
 }
@@
 }
-I am not quite sure about the MatVec update.
+The template used here for these algorithms is \texttt{clrscode3e}.
 }
 
-\solution{Code}{
+\solution{Code and Implementation issues}{
 The code can be found in the attachments(\texttt{row\_back\_substitute.m},\ \texttt{col\_back\_substitute.m},\ \texttt{mmloop.m},\ \texttt{mmdot.m},\ \texttt{mmdaxpy.m},\ \texttt{mmmatvec.m},\ \texttt{mmouterdot.m}).
 And the test script is \texttt{test.m}.\\[5pt]
-Code for checking errors is ignored here, since I think in this problem it is of less importance.
-}
+Code for checking and handling errors in each function is omitted, since I think in this problem it is of less importance. \\[5pt]
+The input and output of these algorithms are listed within the algorithms, and they only used scalar and vector multiplication contained in MATLAB. \\[5pt]
+\textbf{Verification}: It is not difficult to find 
+that all these algorithms are equal to the first, triple-loop algorithm.}
 \solution{Result}{
+All the data used are sampled by using \texttt{rand()}. To be specific, each number in each matrix is sampled with a \texttt{rand()}. \\[5pt]
 For problem (a), the time cost is in Table 3 below.
-(Of course I know that MATLAB is using some precompile skills to accelerate the computing speed, so I run the same test several times after the time cost converge to a stable status.) \\[5pt]
+(I know that MATLAB is using some precompile skills to accelerate the computing speed, so I run the same test several times until the time cost converge to a stable status.) \\[5pt]
 \begin{table}[htbp] \large \centering
@@
 On the other hand, since the matrices are generated by random numbers, it is of much possibility that those matrices are nearly singular.
-It is not difficult to understand why the result of $x$ has such a huge error.
+So it is not difficult to understand why the result of $x$ has such a huge error.
 \\[5pt]
-
 For problem (b), result of the five algorithms are of good precision, which can be found with norm of errors. \\[5pt]
@@
 \refgroup{
-\reference{Jixiu Chen, \textit{Mathematical Analysis II}, Page 174-175.}
+\reference{Jixiu Chen \textit{et al}, \textit{Mathematical Analysis II}, Page 174-175.}
 \reference{D. P. O’Leary, \textit{Scientific Computing with case studies}, Page 23-24.}
-\reference{Gene H. Golub, \textit{Matrix Computations}, Page 10-11.}
+\reference{Gene H. Golub \textit{et al}, \textit{Matrix Computations}, Page 10-11.}
+\reference{Shufang Xu \textit{et al}, \textit{Numerical Linear Algebra}, Page 11-13.}
 }

### 2016-10-09 Numerical Algorithm and Case Studies/Homwwork2/assignment.tex
hw

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{courier}
\renewcommand{\sfdefault}{phv}

\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 2}{16.10.2}
\tiny{Code of this assignment are in the attachment, and they can also be found in GitHub: https://github.com/Orcuslc/Learning/tree/master/Numerical\%20Algorithm\%20and\%20Case\%20Studies/Homework2/code}

% \parbox{0.3\textwidth}{
% Chuan Lu}
% \hfill
% \parbox{0.3\textwidth}{
% 13300180056}
% \hfill
% \parbox{0.3\textwidth}{
% chuanlu13@fudan.edu.cn}

\problem{1 \& 2}{}
\solution{Abstract}{
\\[5pt]
Details of the implementation of LU decomposition in MATLAB.
}
\solution{Introduction}{
\\[5pt]
In most cases pivoting is necessary. If we randomly choose a matrix $M\in \mathbb{R}^{n\times n}$, the probability that $M(1, 1) = max_{i}M(i, 1)$ is $\frac{1}{n}$. So the efficiency of pivoting is a great concern. \\[5pt]
In the experiment below, we generate the matrix $M$ by using MATLAB function \texttt{randn(n, n)}; and we use seperately
$$\texttt{[L, U] = lu(A)}$$
$$\texttt{[L, U, P] = lu(A)}$$
for the two problems.
}
\solution{Results \& Discussion}{
After trying for several times with different $n$, the dimension of the random matrix, we found that in most cases, calling \texttt{[L, U] = lu(A)} leads to $L$ not being a lower triangular matrix, but $U$ is always an upper triangular matrix. \\[5pt]
When we count the number of non-zero elements of each row in $L$, we can find out the list of the numbers is a permutation of \texttt{[1, 2, ..., n]}. \\[5pt]
Thus I tried to call \texttt{[L1, U1, P] = lu(A)}, and the $P$ is exactly the permutation matrix: $$PL1 = L$$.
So it is obvious how MATLAB express the $P$: it simply multiplied it with the L; In order to represent this, I guess that MATLAB records the number of lines that need interchanging in each step; when the algorithm ends, it conbines the records to gain a permutation matrix. \\[5pt]
In order to realize $P*b$, we should use the pernutation record: in each of the $n$ steps, change the elements of two lines, and it will only need $O(n)$ time, and no extra space.
}

\problem{3}{}
\solution{Abstract \& Introduction}{
As is known to all, using Cholesky decomposition for a symmetric positive definite matrix will need half of the flops comparing LU decomposition; In the mean time, since there is no need of pivoting for a symmetric positive definite matrix, in each step $n-1$ times of comparing and $2n$ times of exchanging will be saved on average.
}
\solution{Result}{
We generate the symmetric matrix A by
$$\texttt{A = randn(n, n); A = A + A';}$$
and we did the experiment with $n = 4, 6, 8, 10$. The result of calling 
$$\texttt{L = chol(A)}$$
is:
$$\texttt{Error using \textbf{chol}: Matrix must be positive definite}.$$
}
\solution{Analysis}{
If $A\in \mathbb{R}^{n\times n}$ is not positive definite, then according to the properties of symmetric elementary transformations, $PAP^\top$ is still not positive definite, where $P$ is a permutation matrix. \\[5pt]
Thus, we can assume $A(1:2, 1:2)$ is not positive definite. According to the algorithm, we have
$$l_{11} = \sqrt{a_{11}},$$
$$l_{21} = \frac{a_{21}}{l_{11}},$$
$$l_{22} = (a_{22} - l_{21}^2)^{1/2}.$$
That means $l_{22} = a_{22} - \frac{a_{21}^2}{a_{11}} = \frac{a_{22}a_{11} - a_{21}^2}{a_{11}}$. Since A is symmetric and not positive definite, we have $a_{22}a_{11}-a_{21}^2 = a_{22}a_{11}-a{21}a_{12}<0$. So $l_{22}$ does not exist.
}

\problem{4}{}
\solution{Introduction}{
The $LDL^\top$ decomposition is used for Hermitian indefinite matrices.
}
\solution{Discussion}{
I found an introduction to $LDL^\top$ decomposition from Golub's \textit{Matrix Computations}, Page 186. It said the method was developed by Bunch and Parlett. I searched their paper in Google Scholar, but it seemed that our school has no access to siam.org, so I cannot read the paper.
}

\refgroup{
\reference{Gene H. Golub \textit{et al}, \textit{Matrix Computations}, Page 186-187.}
}

\end{document}

### 2016-10-09 Statistical Learning/Homework2/assignment.tex
hw

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Homework 2}{16.10.9}

% \parbox{0.3\textwidth}{
% Chuan Lu}
% \hfill
% \parbox{0.3\textwidth}{
% 13300180056}
% \hfill
% \parbox{0.3\textwidth}{
% chuanlu13@fudan.edu.cn}

\problem{1}{Explain the relationship between spectral clustering, normalized spectral clustering and graph cut.}
\solution{Solution}{
We assume $k=2$ in the following explanation. \n
For spectral clustering, we already know that the eigenvector $u_2$ corresponding to the second smallest eigenvalue $\lambda_2$ of the Laplacian matrix of the graph is the solution for the minimization
$$ \min_{\tbf{f}} \ \tbf{f}^\top\tbf{L}\tbf{f},$$
$$s.t. \quad \tbf{f}^\top \tbf{f} = 1, \tbf{f}^\top\tbf{1} = 0$$
In fact, if we define 
$$G(f) = G(f_1, \cdots)$$
For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)\tr$
}

% \problem{2}{Cluster $Data_i.csv$ with K-means, judge the number of clusters, and compare differences between different evaluating methods.}
% \solution{Solution}{
% The code of K-means, evaluating and test scripts can be found from attachments(kmeans.R, evaluate.R, hw1.2.R).
% }
% \solution{Result}{
% For Data1.csv, we cluster with k = 3. The result is shown as below.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width = 15cm]{pics/hw2_data1_cluster.eps}
% \caption{The clusters of Data1.csv with k = 3}
% \label{clusters of data1}
% \end{figure}
% \\[1mm]

% For choosing k, the result of Data1.csv is shown below; The first is the result of Calinski-Harabasz method, the second Hartigan method and the last Gap Statistic. \\[3pt]
% The result of CH method is 9, if we may add a limit that $k\le 10.$ The result of H method is 3, and result of GAP statistic is 3.\\[3pt]

% \begin{figure}[htbp]
% \centering
% \subfloat[CH method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_CH.eps}}\hfill
% \subfloat[H method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_H.eps}}\hfill
% \subfloat[GAP statistic]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data1_k_GAP.eps}}\hfill
% \caption{The three evaluating methods of choosing k for Data1.csv}
% \label{EVA Data1}
% \end{figure}

% For Data2.csv, since each data point is of 3 dims, we cannot plot its clustering result here. But after deploying the evaluating methods we consider k = 3. The type of datas can be find in attachments(CLUSTER\_DATA2.txt). \\[3pt]

% The result of CH method is 8, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
% The pics are shown below.

% \begin{figure}[htbp]
% \centering
% \subfloat[CH method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_CH.eps}}\hfill
% \subfloat[H method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_H.eps}}\hfill
% \subfloat[GAP statistic]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data2_k_GAP.eps}}\hfill
% \caption{The three evaluating methods of choosing k for Data2.csv}
% \label{EVA Data2}
% \end{figure}

% For Data3.csv, we fix k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA3.txt). \\[3pt]

% The result of CH method is 9, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
% The pics are shown below.

% \begin{figure}[htbp]
% \centering
% \subfloat[CH method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_CH.eps}}\hfill
% \subfloat[H method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_H.eps}}\hfill
% \subfloat[GAP statistic]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data3_k_GAP.eps}}\hfill
% \caption{The three evaluating methods of choosing k for Data3.csv}
% \label{EVA Data2}
% \end{figure}

% For Data4.csv, we found k = 3 after evaluating k with H method and GAP statistic; The result of clustering can be found in attachments(CLUSTER\_DATA4.txt). \\[3pt]

% The result of CH method is 7, if we limit that $k\le 10$. The result of H method and result of GAP statistic are 3. \\[3pt]
% The pics are shown below.

% \begin{figure}[htbp]
% \centering
% \subfloat[CH method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_CH.eps}}\hfill
% \subfloat[H method]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_H.eps}}\hfill
% \subfloat[GAP statistic]{ %
% 	\includegraphics[width = 0.3\textwidth]{pics/hw2_data4_k_GAP.eps}}\hfill
% \caption{The three evaluating methods of choosing k for Data4.csv}
% \label{EVA Data2}
% \end{figure}
% }
% \solution{Analysis}{
% It is suprising that result of Calinski-Harabasz method does not agree with the other methods. I consider it as the result that I misunderstood the meaning of $W(k), B(k)$. I calculate the former as the target function of cluster; the latter as $\sum_{c_i, c_j \in C}\lVert c_i - c_j \rVert^2$, in which $C$ is the set of cluster centers.
% }

% \problem{3}{Use hierarchical clustering methods to cluster $Data_i.csv$}
% \solution{Solution}{
% The code of hierarchical clustering and the test script can be found from attachments(hierarchical\_clustering.R, hw1.3.R).
% }
% \solution{Result}{
% It is somehow embarrassing that I still did't know how to draw trees in R without $hcluster()$. The result can be shown is the attachments, (HC\_DATA1.txt and HC\_DATA2.txt). \\[3pt]
% Each result is a (n-1) * narg matrix, in which n is the number of data points and narg is the number of dims in each data point. Each row in the matrix(for example, A[1, ]) means a step when two points merged with each other; A[1, 1] and A[1, 2] merged into a new A[1, 1], and the point represented by A[1, 2] is abandoned. \\[3pt]
% It is possible to draw the tree and do Tree-Cut with the results.
% }

% \refgroup{
% \reference{a a a a  a a}
% \reference{b b b b b b}
% \reference{c c c c c c}
% \reference{b}

% }

\end{document}

### 2016-10-09 Statistical Learning/Homework2/assignment.tex
update

@@
 In fact, if we define 
-$$G(f) = G(f_1, \cdots)$$
-For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)\tr$
+$$G(f) = G(f_1,\cdots, f_n) = f\tr\tbf{L}f - \lambda_1 (f\tr f-1) - \lambda_2 f\tr\tbf{1} $$ $$ =  \frac{1}{2}\sum_{i,j=1}^{n}w_{ij}(f_i-f_j)^2-\lambda_1(\sum_{i=1}^{n}f_i^2-1)-\lambda_2\sum_{i=1}^n f_i$$
+Then according to Lagrange Theorm, we let
+$$\frac{\partial G}{\partial f_i} = \sum_{j=1}^n (f_i-f_j) - 2\lambda_1 f_i - \lambda_2 = 0, \quad  i=1:n$$
+If we add the $n$ equations, we get
+$$2\lambda_1\sum_{i, j=1}^n f_i + n\lambda_2=0$$
+Since $f\tr\tbf{1} = 0$, then $\lambda_2 = 0$. So
+$$\sum_{j=1}^n w_{ij}f_{j} = \lambda f_i, \quad i=1:n,$$
+which means $f$ is an eigenvector of $\tbf{L}$.\n
+For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)^\top$
 }

### 2016-10-18 Statistical Learning/Homework2/assignment.tex
Add an assignment

@@
 Since $f\tr\tbf{1} = 0$, then $\lambda_2 = 0$. So
-$$\sum_{j=1}^n w_{ij}f_{j} = \lambda f_i, \quad i=1:n,$$
+$$\sum_{j=1}^n w_{ij}f_{j} = \lambda f_i,\quad \lambda = \sum_{j=1}^{n}w_{ij}-2\lambda_1,\quad i=1:n, $$
 which means $f$ is an eigenvector of $\tbf{L}$.\n
-For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)^\top$
+For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)^\top\in\mbb{R}^n$,
+$$\bra{f_i}{1}{-1}{if\ v_i\in\mbb{A}}{if\ v_i\in\mbb{\bar{A}}}$$
+Then
+$$\bra{(f_i-f_j)^2}{4}{0}{i\in\mbb{A},j\in\mbb{\bar{A}}}{else}$$
+So 
+$$MCut(A_1,\cdots,A_k) = \sum_{i=1}^{k}cut(A_i, \bar{A_i}) = \frac{1}{4}f\tr\tbf{L}f$$
+We can minimize this with the $f$ from spectral clustering. \n
+For Ratio Cut, we can define $f$ as
+$$\bra{f_i}{\sqrt{\vt{\bar{A}}/\vt{\bar{A}}}}{-\sqrt{\vt{A}/\vt{\bar{A}}}}{v_i\in\mbb{A}}{v_i\in\mbb{\bar{A}}}$$
+Then
+$$\bra{(f_i-f_j)^2}{\frac{\vt{A}}{\vt{\bar{A}}}+\frac{\vt{\bar{A}}}{\vt{A}}+2}{0}{v_i, v_j\ in \ the \ same \ part}{else}$$
+So 
+$$RCut(A, \bar{A}) = \frac{1}{2}\frac{\vt{A}\vt{\bar{A}}}{(\vt{A}+\vt{\bar{A}})^2}\frac{1}{\vt{A}+\vt{\bar{A}}}\sum_{i, j}(f_i-f_j)^2w_{ij}=\frac{f\tr\tbf{L}f}{2n^2}$$
+For normalized spectral clustering, we have
+$$L_{sym} = I - D^{-1/2}WD^{-1/2} = D^{-1/2}LD^{-1/2}$$
+and normalized cut can be done using $g^*$, the Fiedler vector of $D^{-1/2}LD^{-1/2}.$ \\[1cm]
+When $k \geq 3$, we can find $k$ points $x_i$ in $\mbb{R}^k$, s.t. $\vt{x_i-x_j} = \vt{x_k - x_l}$, for each $i, j, k, l$. \\
+Then define $f_i = x_i$, and it is same with $k = 2$.
 }
 
-% \problem{2}{Cluster $Data_i.csv$ with K-means, judge the number of clusters, and compare differences between different evaluating methods.}
+\problem{2}{Cluster Data.csv with spectral clustering, construct three different graphs and compare the difference with result of K-means.}
+\solution{Solution}{
+For Data1.csv, the result is shown as follows.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_2_data1_kmeans.eps}
+\caption{Kmeans}
+\label{Kmeans for data 1}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Full-connect1]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_2_data1_full_1.eps}}\hfill
+\subfloat[Full-connect2]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_2_data1_full_2.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Epsilon = 0.1]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_epsilon_01.eps}}\hfill
+\subfloat[Epsilon = 1]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_epsilon_1.eps}}\hfill
+\subfloat[Epsilon = 3]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_epsilon_3.eps}}	
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Directed, n = 3]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_directed_3.eps}}\hfill
+\subfloat[Directed, n = 5]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_directed_5.eps}}\hfill
+\subfloat[Directed, n = 10]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_directed_10.eps}}	
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Undirected, n = 3]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_undirected_3.eps}}\hfill
+\subfloat[Undirected, n = 5]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_undirected_5.eps}}\hfill
+\subfloat[Undirected, n = 20]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data1_undirected_20.eps}}	
+\end{figure}
+\\[1cm]
+For Data3.csv, the result is shown as follows.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_2_data3_kmeans.eps}
+\caption{Kmeans}
+\label{Kmeans for data 3}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Full-connect1]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_2_data3_full_1.eps}}\hfill
+\subfloat[Full-connect2]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_2_data3_full_2.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[Epsilon = 0.1]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data3_epsilon_0_1.eps}}\hfill
+\subfloat[Epsilon = 2]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data3_epsilon_2.eps}}\hfill
+\subfloat[Epsilon = 5]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_2_data3_epsilon_5.eps}}	
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_2_data3_directed_3.eps}
+\caption{directed, n = 3}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_2_data3_undirected_3.eps}
+\caption{Undirected, n = 3}
+\end{figure} \\
+From the results we can know that for these groups, spectral clustering is not always better than kmeans. The parameters in spectral clustering are also important.
+}
+\newpage
+
+\problem{3}{Cluster circles, curves with spectral clustering}
+\solution{Solution}{
+The results of circles.csv is as follows.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_3_circle_full.eps}
+\caption{full connection}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[epsilon = 1]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_epsilon_1.eps}}\hfill
+\subfloat[epsilon = 2]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_epsilon_2.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[directed, n = 5]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_directed_5.eps}}\hfill
+\subfloat[directed, n = 10]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_directed_10.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[undirected, n = 2]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_undirected_2.eps}}\hfill
+\subfloat[undirected, n = 5]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_circle_undirected_5.eps}}
+\end{figure}
+\\
+The result of curves.csv is shown as follows.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width = 10cm]{pics/hw2_3_curve_full.eps}
+\caption{full connection}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[epsilon = 1]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_epsilon_1.eps}}\hfill
+\subfloat[epsilon = 3]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_epsilon_3.eps}}\hfill
+\subfloat[epsilon = 10]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_epsilon_10.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[directed, n = 10]{ %
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_directed_10.eps}}\hfill
+\subfloat[directed, n = 20]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_directed_20.eps}}\hfill
+\subfloat[directed, n = 30]{
+	\includegraphics[width = 0.3\textwidth]{pics/hw2_3_curve_directed_30.eps}}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\subfloat[undirected, n = 5]{ %
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_curve_undirected_5.eps}}\hfill
+\subfloat[undirected, n = 10]{
+	\includegraphics[width = 0.45\textwidth]{pics/hw2_3_curve_undirected_10.eps}}
+\end{figure}
+}
+
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[width = 10cm]{pics/hw2_data1_cluster.eps}
+% \caption{The clusters of Data1.csv with k = 3}
+% \label{clusters of data1}
+% \end{figure}
+% \\[1mm]
+% \problem{2}{Cluster $Data_i.csv$ with K-means, judge the number of clusters, and compare differences between different evaluating methodss.}
 % \solution{Solution}{
@@
 % \centering
-% \includegraphics[width = 15cm]{pics/hw2_data1_cluster.eps}
+% \includegraphics[width = 10cm]{pics/hw2_data1_cluster.eps}
 % \caption{The clusters of Data1.csv with k = 3}

### 2016-10-18 Statistical Learning/Homework2/code/kmeans.R

@@ -1,0 +1,169 @@
+kmeans = function(A, k, max_iter = 1000, min_error = 1e-6) {
+  # Kmeans, using Lloyd Algorithm;
+  # While one of the types have NO points,
+  # Kick the farthest point in the largest type out and mark it the NULL type;
+  
+  # A: The data matrix, each record being a row;
+  # k: The number of cluster centers;
+  # max_iter: The number of max iteration;
+  # min_error: The min error for stable judgement;
+  
+  ndata = nrow(A);  # The length of data;
+  narg = ncol(A);  # The number of arguments;
+  center_index = sort(sample(1:ndata, k));  # The init index of cluster centers;
+  centers = A[center_index, ];  # The data of centers;
+  ncenters = matrix(rep(0, k*narg), ncol = narg);
+  type = c(rep(0, ndata));  # The type of each points;
+  count = 0;  # Number of iter count;
+  
+  while(TRUE && count <= max_iter) {
+	  for(i in 1:ndata) {
+	   type[i] = nearest_center(A[i, ], centers);
+  	}
+    
+  # To add robustance; rearrange types;
+    while(TRUE) {
+      type_count = rep(0, k);
+      for(j in 1:k) {
+        type_count[j] = length(which(type == j));
+      }
+      if(min(type_count) > 0) {
+        break;
+      }
+      largest_type = which(type_count == max(type_count))[1];
+      for(j in 1:k) {
+        if(type_count[j] == 0) {
+          # type[which(type == largest_type)[1]] = j;
+          t = which(type == largest_type);
+          B = A[t, ];
+          ln = length(t);
+          dist_t = rep(0, ln);
+          for(m in 1:ln) {
+            # print(t[m])
+            dist_t = calc_dist(B[m, ], centers[largest_type, ]);
+          }
+          min_t = which(dist_t == min(dist_t))[1];
+          type[which(type == largest_type)[min_t]] = j;
+        }
+      }
+    }
+  
+  	for(i in 1:k) {
+  	  A_t = A[which(type == i), ];
[…]

### 2016-11-05 Statistical Learning/Homework3/code/test.R
Add NMF

@@ -1,4 +1,5 @@
 source('PCA.R')
+source('NMF.R')
 library(rgl)
 # library("rgl")
 # x = sort(runif(100))
@@ -30,8 +31,8 @@ library(rgl)
 # print(r6$rate);
 
 ## Problem 2 ##
-data = read('../data/assignment32.csv');
-# data[is.na(data)] = 0;
+data = read('../data/assign32.csv');
+data[is.na(data)] = 0;
 # r1 = PCA(data, 1);
 # r1_X = r1$X;
 # plot(r1_X, rep(0, length(r1_X)));
@@ -51,3 +52,6 @@ data = read('../data/assignment32.csv');
 # print(r6$rate);
 
 ## Problem 2.2 ##
+r1 = NMF(data, 2);
+# print(r1$W)
+print(r1$rate);

### 2016-11-05 Statistical Learning/Homework3/assignment.tex
assignment 3

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Homework 3}{16.11.4}

% \parbox{0.3\textwidth}{
% Chuan Lu}
% \hfill
% \parbox{0.3\textwidth}{
% 13300180056}
% \hfill
% \parbox{0.3\textwidth}{
% chuanlu13@fudan.edu.cn}

\problem{1}{Perform PCA to assign31.csv.}
\solution{Result}{
Since there are many NAs in assign31.csv, we changed those NA to 0. \n
The results are as follows: The rate in the table is the rate of information reserved after PCA.
\begin{table}[htbp] \large \centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
k & 1 & 2 & 3 & 5 & 10 & 14  \\
\hline
Rate & 0.2139058 &  0.396026 & 0.5165856 & 0.6697862 & 0.920202 & 1\\
\hline
\end{tabular}
\caption{Reserved information rate of different orders in PCA.}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw1_pca_1.eps}
\caption{PCA, k = 1}
\label{PCA1}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw1_pca_2.eps}
\caption{PCA, k = 2}
\label{PCA2}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw1_pca_3.png}
\caption{PCA, k = 3}
\label{PCA3}
\end{figure}
From these figures(when $k = 1, 2, 3$) we can find that after PCA the data points still seem to be random and messy. When we calculate the rate of reserved information we can know that not until $k = 10$ the rate is less than 0.9, which is thought to be unsatisfying.
}

\problem{2}{Perform PCA and NMF to assign2.csv, and explain the difference.}
\solution{Result}{
For PCA, the result is as follows:
\begin{table}[htbp] \large \centering
\begin{tabular}{|c|c|c|c|}
\hline
k & 1 & 2 & 3  \\
\hline
Rate & 0.4326317 &  0.7648243 & 0.9298461 \\
\hline
\end{tabular}
\caption{Reserved information rate of different orders in PCA.}
\end{table}
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw2_pca_1.eps}
\caption{PCA, k = 1}
\label{PCA1}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw2_pca_2.eps}
\caption{PCA, k = 2}
\label{PCA2}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width = 15cm]{pics/hw2_pca_3.png}
\caption{PCA, k = 3}
\label{PCA3}
\end{figure}
From figure(k = 1) we can assert nothing; from figure(k = 2) it seems the data can be simulated by two parallel lines. From the table we can find when k = 3, the rate of reserved information is over 0.9, which means k = 3 is a good estimation. \n
For NMF, the result of error rate is as follows:
$$ rate = \frac{\vt{A - WH}_F}{\vt{A}_F} $$
\begin{table}[htbp] \large \centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
k & 1 & 2 & 3 & 5 & 10\\
\hline
Rate & 0.6764784 &  0.6904373 & 2.629497 & 4.993591 & 14.36354\\
\hline
\end{tabular}
\caption{Error rates of different orders in NMF.}
\end{table}
It must be wrong somewhere that with k being larger, the estimation becoming worse. I think it should be the number of iterations, which is fixed at 1000.
}

\problem{3}{Perform PCA and nmf to test2.csv}
\solution{Result}{
For PCA, the result is shown as follows:
\begin{figure}[htbp]
\centering
\includegraphics[width = 5cm]{pics/hw3_original.png}
\caption{Original Picture}
\label{Original}
\end{figure}

\begin{figure}[htbp]
\centering
\subfloat[k = 1]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_1.png}}\hfill
\subfloat[k = 2]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_2.png}}\hfill
\subfloat[k = 3]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_3.png}}	
\end{figure}
\begin{figure}[htbp]
\centering
\subfloat[k = 4]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw4_pca_4.png}}\hfill
\subfloat[k = 5]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_5.png}}\hfill
\subfloat[k = 10]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_10.png}}	
\end{figure}
\begin{figure}[htbp]
\centering
\subfloat[k = 20]{ %
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_20.png}}\hfill
\subfloat[k = 50]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_50.png}}\hfill
\subfloat[k = 200]{
	\includegraphics[width = 0.3\textwidth]{pics/hw3_pca_200.png}}	
\end{figure}
For NMF, 
}
\end{document}

### 2016-11-05 Statistical Learning/Homework3/code/test.R

@@ -1,7 +1,7 @@
 source('PCA.R')
 source('NMF.R')
 library(rgl)
-# library("rgl")
+library("rgl")
 # x = sort(runif(100))
 # y = 2*x+runif(100)*0.5
 # plot(x, y)
@@ -16,7 +16,7 @@ library(rgl)
 # r1_X = r1$X;
 # plot(r1_X, rep(0, length(r1_X)));
 # print(r1$rate);
-# 
+
 # r2 = PCA(data, 2);
 # r2_X = r2$X;
 # plot(r2_X[, 1], r2_X[, 2]);
@@ -26,8 +26,8 @@ library(rgl)
 # r3_X = r3$X;
 # plot3d(r3_X[,1], r3_X[,2], r3_X[,3]);
 # print(r3$rate)
-# 
-# r6 = PCA(data, 10);
+
+# r6 = PCA(data, 14);
 # print(r6$rate);
 
 ## Problem 2 ##
@@ -42,7 +42,7 @@ data[is.na(data)] = 0;
 # r2_X = r2$X;
 # plot(r2_X[, 1], r2_X[, 2]);
 # print(r2$rate);
-# 
+# # 
 # r3 = PCA(data, 3);
 # r3_X = r3$X;
 # plot3d(r3_X[,1], r3_X[,2], r3_X[,3]);
@@ -52,6 +52,6 @@ data[is.na(data)] = 0;
 # print(r6$rate);
 
 ## Problem 2.2 ##
-r1 = NMF(data, 2);
+r1 = NMF(data, 10);
 # print(r1$W)
 print(r1$rate);

### 2016-11-09 Statistical Learning/Homework3/assignment.tex
HW3

@@
 \usepackage{subfig}
+\usepackage{float}
 \usepackage{listings}
@@
 \solution{Result}{
-Since there are many NAs in assign31.csv, we changed those NA to 0. \n
+Since there are many NAs in assign31.csv, I changed those NA to 0. \n
 The results are as follows: The rate in the table is the rate of information reserved after PCA.
@@
 \end{table}
-
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \end{table}
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \caption{PCA, k = 1}
-\label{PCA1}
+\label{PCA2_1}
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \caption{PCA, k = 2}
-\label{PCA2}
+\label{PCA2_2}
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \caption{PCA, k = 3}
-\label{PCA3}
+\label{PCA2_3}
 \end{figure}
@@
 \n
-For NMF, the result of error rate is as follows:
+For NMF, the result is as follows: \n
+Firstly, we use the Divergence objective function
+$$min\quad \Sigma_{i, j}(A_{ij}log(\frac{A_{ij}}{WH_{ij}})-A_{ij}+WH_{ij})$$
+which assumes the elements in A obey a Poisson distribution. The error rate is defined as follows for both Divergence objective function and Mean squared obj. function.
 $$ rate = \frac{\vt{A - WH}_F}{\vt{A}_F} $$
-\begin{table}[htbp] \large \centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-k & 1 & 2 & 3 & 5 & 10\\
-\hline
-Rate & 0.6764784 &  0.6904373 & 2.629497 & 4.993591 & 14.36354\\
-\hline
-\end{tabular}
-\caption{Error rates of different orders in NMF.}
-\end{table}
-It must be wrong somewhere that with k being larger, the estimation becoming worse. I think it should be the number of iterations, which is fixed at 1000.
+The basis of NMF(divergence obj func) are as follows:\n
+\begin{figure}[H]
+\centering
+\includegraphics[width = 15cm]{pics/hw2_nmf_d_basis.eps}
+\caption{NMF, D, basis, n=1:10}
+\label{NMF_D1}
+\end{figure}
+And the error rate is as follows:
+\begin{figure}[H]
+\centering
+\includegraphics[width = 5cm]{pics/hw2_nmf_d_error.eps}
+\caption{NMF, error rate, n=1:20}
+\label{NMF_D2}
+\end{figure}
+From the curve of error rates we can know, that in this case the assumption that entries obeys Poisson distribution is not acceptable.
+So I tried Mean squared error objective function instead.
+In the meantime, MSE converged much quicker than D.\n
+When using Mean squared error objective function
+$$min\quad \vt{A-WH}_F^2$$
+The basis is as follows:
+\begin{figure}[H]
+\centering
+\includegraphics[width = 15cm]{pics/hw2_nmf_m_basis.eps}
+\caption{NMF, M, basis, n=1:10}
+\label{NMF_M1}
+\end{figure}
+And the error rate is as follows:
+\begin{figure}[H]
+\centering
+\includegraphics[width = 5cm]{pics/hw2_nmf_m_error.eps}
+\caption{NMF, M, basis, n=1:20}
+\label{NMF_M2}
+\end{figure}
+One can tell from the error curve, that when we choose $k=6$, the result is good enough to represent the data from A.
 }
 
-\problem{3}{Perform PCA and nmf to test2.csv}
+\problem{3}{Perform PCA and NMF to test2.csv}
+\solution{Analysis}{
+When we do PCA to an image, we assume each row being a data point. Then PCA can be presented as
+$$Y = XP$$
+where $P$ is the matrix constructed by eigenvectors of $X\tr X$. Then 
+$$X\tr X = P\Sigma P\tr$$
+where $\Sigma$ is a diagonal matrix.
+So choosing the first $k$ principle conponents is equivalent to choosing the first $k$ columns of $P$. We denote it as $P_1$.\n
+If we let $A = XP_1 P_1\tr$, then
+$$A\tr A = P_1 P_1\tr X\tr XP_1 P_1\tr = P_1 P_1\tr PDP\tr P_1 P_1\tr$$ 
+$$ = P_1 D_{1:k} P_1\tr $$
+So 
+$$\hat{X} = XP_1 P_1\tr$$ is a approximation of $X$, and it is equivalent to restoring $X$ with its first $k$ singular values.
+}
 \solution{Result}{
-For PCA, the result is shown as follows:
-\begin{figure}[htbp]
+For PCA, the result is shown as follows:\n
+(I used Python-OpenCV to draw these images.)
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-
-\begin{figure}[htbp]
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-For NMF, 
+For NMF, when we use Mean squared error obj func, the results are as follows:
+\begin{figure}[H]
+\centering
+\includegraphics[width = 15cm]{pics/hw3_nmf_m.eps}
+\caption{NMF, using MSE}
+\label{hw3_NMF1}
+\end{figure}
+When we use Divergence squared error obj func, the results are as follows:
+\begin{figure}[H]
+\centering
+\includegraphics[width = 15cm]{pics/hw3_nmf_d.eps}
+\caption{NMF, using Divergence}
+\label{hw3_NMF2}
+\end{figure}
+One can tell from the images that using mean squared error is almost the same as using divergence obj func, and their results are better than using PCA.
+I think it is because entries in a image are nonnegative, so if we use NMF, then the new basis are nonnegative which could be more appropriate.
+However, since PCA can be performed easily using SVD, the speed of PCA is hundreds faster than NMF.
 }

### 2016-11-09 Statistical Learning/Homework3/code/PCA.R

@@ -37,6 +37,9 @@ draw = function(X) {
     }
 }
 
+Recover = function(X, P) {
+    return(X%*%P%*%t(P));
+}
 # # data = read("../data/assign32.csv");
 # data = read.csv("../data/test2.csv");
 # # ndata = matrix(rep(0, nrow(data)*ncol(data)*3), ncol = 3);

### 2016-11-16 Statistical Learning/Homework4/code/test.R
Assignment 4

@@ -1,12 +1,20 @@
 source("LR.R")
 
 ## Problem 1 ##
-data = read('../data/simplelr1.csv')
+# data = read('../data/simplelr1.csv')
+# X = data$X;
+# Y = data$Y;
+# plot(X[, 2], Y);
+# beta = LR(X, Y);
+# lines(X, beta[1, 1]+beta[2, 1]*X);
+# inference_t(X, Y, beta, i = 1, beta_0 = 0);
+# inference_F(X, Y, beta, c(1));
+
+## Problem 2 ##
+data = read('../data/lr2.csv');
 X = data$X;
 Y = data$Y;
-plot(X[, 2], Y);
 beta = LR(X, Y);
-print(beta);
-lines(X, beta[1, 1]+beta[2, 1]*X);
-inference_t(X, Y, beta, 1);
-inference_F(X, Y, beta, c(1));
+# print(beta);
+# # inference_t(X, Y, beta, i = 5, beta_0 = -10)
+inference_F(X, Y, beta, i = c(1, 4, 5))

### 2016-12-02 Statistical Learning/Homework5/code/Best_Subset.R
2/3

@@ -1,6 +1,7 @@
 source('std.R')
 
 Best_Subset = function(X, Y, k) {
+	print(k)
 	Y = Y - mean(Y); # Standardize Y;
 	X = apply(X, 2, std); # Standardize each col of X, formula (1.1);
 	n = nrow(X);
@@ -24,7 +25,6 @@ Best_Subset = function(X, Y, k) {
 			error[index_j] = norm(beta_j - beta_0);
 		}
 	}
-	print(which(error == min(error)))
 	best_subset = subset[, which(error == min(error))];
 	bs = best_subset[which(best_subset != 0)];
 	X_bs = X[, bs];

### 2016-12-02 Statistical Learning/Homework5/code/Forward_Stagewise.R

@@ -1,0 +1,3 @@
+Forward_Stagewise = function(X, Y, delta) {
+	
+}

### 2017-03-15 Numerical solution of DEs/Assignment1/Assignment_week_1.tex
update

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 1}
\\
Code can be obtained at https://github.com/orcuslc/Learning/

% \parbox{0.3\textwidth}{
% Chuan Lu}
% \hfill
% \parbox{0.3\textwidth}{
% 13300180056}
% \hfill
% \parbox{0.3\textwidth}{
% chuanlu13@fudan.edu.cn}

\problem{1}{Show the numerical result of $f(x) = \frac{1 - cos(x)}{x ^{2}}$ when $x \to 0^+$.}
\solution{Solution}{
The result is as follows.
\begin{figure}[h!]
	\centering
    \includegraphics[width=15cm]{pics/problem1.eps}
    \caption{problem1}
    \label{problem1}
\end{figure}
}

\problem{2}{Analyse the inversed iteration of $u_{n+2} = 3u_{n+1}-2u_n$}
\solution{Solution}{
The inversed iteration is
$$u_n = \frac{3}{2}u_{n+1}-\frac{1}{2}u_{n+2}.$$
And the computed value is
$$\hat{u_n} = \frac{3}{2}\hat{u_{n+1}}-\frac{1}{2}\hat{u_{n+2}}+\epsilon_n.$$
If we let
$$w_n = \left(\begin{array}{cc} u_n \\ u_{n+1}\end{array}\right),A = \left(\begin{array}{cc} \frac{3}{2} & -\frac{1}{2} \\ 1 & 0\end{array}\right), \hat{w_n} = \left(\begin{array}{cc} \hat{u_n} \\ \hat{u_{n+1}}\end{array}\right), \hat{\epsilon_n} = \left(\begin{array}{cc} \epsilon_n \\ 0\end{array}\right)$$
Then
$$w_{n} = Aw_{n+1}, \hat{w_n} = A\hat{w_{n+1}}+\hat{\epsilon_n}$$
Define the error as $e_n = \hat{w_n} - w_n$, then 
$$e_n = Ae_{n+1} + \hat{\epsilon_n}$$
Since $A$ has the eigenvalue decomposition
$$P^{-1}AP = \Lambda, P = \left(\begin{array}{cc} 1 & \frac{1}{2} \\ 1 & 1\end{array}\right), \Lambda = \left(\begin{array}{cc} 1 & 0 \\ 0 & \frac{1}{2}\end{array}\right)$$
the iteration can be wrote as
$$P^{-1}e_n = \Lambda P^{-1}e_{n+1} + P^{-1}\hat{\epsilon_n}$$
With the same analysis of Page 13 of the textbook, we can know that $e_0$ is under control by a constant value of $e_n$.
}

\problem{3}{Prove (1.2.8) of the textbook}
\solution{Proof}{
From (1.2.7) we can know
$$\|x_{n+1} - x_{n}\| \leqslant \alpha^n\|x_1 - x_0\|$$
So
$$\|x^{*} - x_n\| \leqslant \sum_{k = n}^{\infty}\|x_{k+1} - x_k\| \leqslant \sum_{k = n}^{\infty} \alpha^k\|x_1 - x_0\| = \frac{\alpha^n}{1-\alpha}\|x_1 - x_0\|$$
}

\end{document}

### 2017-03-15 Numerical solution of DEs/Assignment2/Assignment_week_2.tex
update

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 2}
\\
Code can be obtained at https://github.com/orcuslc/Learning/

\problem{1}{Given $G(x) = e^{-x}$ and $F(x) = x - e^{-x}$, compare Fixed-point iteration and Newton-Raphson iteration.}
\solution{Solution}{
The result is as follows.
\begin{tabular}{c|c}
   \hline
   Fixed-point iter & Newton-Raphson iter\\
   \hline
   % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
   1.000000000000000 &  1.000000000000000\\
  \hline
   0.367879441171442 &  0.537882842739990\\
   \hline
   0.692200627555346 &  0.566986991405413\\
   \hline
   0.500473500563637 &  0.567143285989123\\
   \hline
   0.606243535085597 &  \\
   \hline
   0.545395785975027 &  \\
   \hline
   0.579612335503379 &  \\
   \hline
   0.560115461361089 &  \\
   \hline
   0.571143115080177 &  \\
   \hline
   0.564879347391050 &  \\
   \hline
   0.568428725029061 &  \\
   \hline
   0.566414733146883 &  \\
   \hline
   0.567556637328283 &  \\
   \hline
   0.566908911921495 &  \\
   \hline
   0.567276232175570 &  \\
   \hline
   0.567067898390788 &  \\
   \hline
   0.567186050099357 &  \\
   \hline
   0.567119040057215 &  \\
   \hline
   0.567157044001298 &  \\
   \hline
   0.567135490206278 &  \\
   \hline
   0.567147714260119 &  \\
   \hline
   0.567140781458298 &  \\
   \hline
   0.567144713346570 &  \\
   \hline
   0.567142483401307 &  \\
   \hline
   Root &  Root\\
   \hline
   0.567143748099411 & 0.567143290409784\\
   \hline
 \end{tabular}
}
\solution{Analysis}{
When using Newton-Raphson iteration to extract the root of an equation, according to (1.2.22), the error is of second order, while the error of fixed point iteration is of first order. Hence, the speed of convergence is much quicker for Newton-Raphson iteration. 
}

\problem{2}{For a n-dimension vector \textbf{x}, when $1\leqslant p\leqslant q,$ prove $\Vert\textbf{x}\Vert_q \leqslant\Vert\textbf{x}\Vert_p\leqslant n^{\frac{1}{p}-\frac{1}{q}}\Vert\textbf{x}\Vert_q$.}
\solution{Proof}{
On one hand, assume $\Vert\textbf{x}\Vert_q = 1$, then $$\Vert x_i\Vert\leqslant 1,\quad for\quad 1\leqslant i \leqslant n$$\\
Because $1\leqslant p\leqslant q,$ then $\Vert x_{i}\Vert^{q}\leqslant\Vert x_{i}\Vert^{p}.$ Hence, $(\sum_{i=1}^{n}\Vert x_{i}\Vert^p)^\frac{1}{p}\geqslant(\sum_{i=1}^{n}\Vert x_{i}\Vert^q)^\frac{1}{q},$ which means $\Vert x\Vert_q\leqslant\Vert x\Vert_p.$\\
On the other hand, according to $H\ddot{o}lder$ inequation, $$\frac{(\sum_{i=1}^{n}\Vert x_{i}\Vert^{p})^\frac{1}{p}}{n^\frac{1}{p}} \leqslant \frac{(\sum_{i=1}^{n}\Vert x_{i}\Vert^{q})^\frac{1}{q}}{n^\frac{1}{q}},$$ hence $$\Vert\textbf{x}\Vert_p\leqslant n^{\frac{1}{p}-\frac{1}{q}}\Vert\textbf{x}\Vert_q$$
}

\end{document}

### 2017-03-15 C++ primer/chpt4.cpp

@@ -1,0 +1,48 @@
+#include <iostream>
+#include <string>
+using namespace std;
+
+struct oregi {
+	std::string name;
+	int height;
+	float age;
+};
+
+// int main() {
+// 	using namespace std;
+	
+// 	// int n = 3;
+// 	// int months[n];
+// 	// for(int i = 0; i < n; i++) {
+// 		// cin >> months[i];
+// 	// }
+// 	// for(int i = 0; i < n; i++) {
+// 		// cout << months[i] << endl;
+// 	// }
+// 	// oregi a = {
+// 	// 	"abc",
+// 	// 	120,
+// 	// 	123.4
+// 	// };
+// 	// cout << a.name << a.height << a.age << endl;
+// 	string a;
+// 	while(1) {
+// 		getline(cin, a);
+// 		cout << &a << endl;
+// 		if(a == "exit") {
+// 			break;
+// 		}
+// 	}
+// 	string * n;
+// 	n = &a;
+// 	cout << *n << endl;
+// 	return(0);
+// }
+
+
+int main() {
+	int* abc;
+	*abc = 1203;
+	cout << &abc << endl;
+	return(0);
+}

### 2017-03-15 Data Processing/test.py

@@ -1,0 +1,24 @@
+import pandas as pd
+import numpy as np
+
+data = pd.read_csv('E:\\Desktop\\LSG_order_flow_16.csv', encoding='gb2312', index_col='date')
+dates = sorted(list(set(data.index)))
+types = sorted(list(set(data['type'])))
+
+def sort_by_type():
+	# grouped = data.groupby([data.index, 'type'])
+	# print(grouped.first())
+	# data2 = data.copy()
+	# data2.index = pd.MultiIndex.from_arrays([dates, types], names = ['date', 'type'])
+	nd = pd.DataFrame(np.zeros((len(dates), len(types))), columns = types, index = dates, dtype = 'int')
+	for i in range(len(data.index)):
+		nd.loc[data.index[i]][data.iloc[i]['type']] += data.iloc[i]['amount']
+	return nd
+
+def sort_by
+
+if __name__ == '__main__':
+	# print(dates)
+	# print(types)
+	# bd = sort_by_type()
+	# bd.to_csv('E:\\Desktop\\LSG_order_flow_16_by_type.csv')

### 2017-04-06 Numerical solution of DEs/Assignment4/assignment.tex
add assignment 4&5

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 4}{17.4.1}

\problem{1}{Prove Implicit Euler Iteration is of first-order convergence for Dahlquist test.}
\solution{Proof}{
\quad According to (2.2.20), $u_{n} = \frac{1}{(1-a\Delta t)^{n}}u_{0}.$ For $e_{n} = u(t_{n}) - u_{n},$ we have $e_{n} = u_{0}(e^{at_{n}} - e^{-nln(1-a\Delta t)}).$ From Taylor expansion we can know that $$e_{n} = -u_{0}e^{at_{n}}(\frac{a^{2}t_{n}}{2}\Delta t + O(\Delta t^{2})).$$\\
\quad In consequence, for a fixed $T = N\Delta t,$ $\Vert u(T) - u(N)\Vert\leqslant C\Delta t,$ which means the implicit iteration is of first-order convergence.
}

\problem{2}{Compute $\frac{du}{dt} = au$ with Euler Iterations, and show the convergence by image.}
\solution{Result}{
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{img/converge.eps}
\caption{The convergence of Euler Iteration.}
\label{Convergence}
\end{figure}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{img/error_list.eps}
\caption{The error of Euler Iteration.}
\label{Error}
\end{figure}
}

\end{document}

### 2017-04-06 Numerical solution of DEs/Assignment5/assignment.tex
add assignment 4&5

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 5}{17.4.5}

\problem{1}{Analysis the stability and absolute stable interval of Modified and Revised Euler Iteration for Dahlquist test.}
\solution{For Modified Euler Iteration:}{
{\centering \[\ u_{n+1} = u_{n} + \frac{\Delta t}{2}(f_{n} + f_{n+1})\]}
\quad Assume that the disturbed initiate value is $\widetilde{u_{0}}$ and the exact initiate value is $u_{0}$. Mark the following value calculated by the Modified Euler Iteration as $\widetilde{u_{i}}, i = 1, 2, \cdots$. Then $\widetilde{u_{n}} = \widetilde{u_{n-1}} + \frac{\Delta t}{2}(a\widetilde{u_{n-1}} + a\widetilde{u_{n}}), \quad \widetilde{u_{n}} = \frac{1+\frac{a\Delta t}{2}}{1 - \frac{a\Delta t}{2}}\widetilde{u_{n-1}},\quad u_{n} = \frac{1+\frac{a\Delta t}{2}}{1 - \frac{a\Delta t}{2}}u_{n-1}$.\quad Hence, $\Vert\widetilde{u_{n}} - u_{n}\Vert =  \frac{1+\frac{a\Delta t}{2}}{1 - \frac{a\Delta t}{2}}\Vert\widetilde{u_{n-1}} - u_{n-1}\Vert = \dots = (\frac{1+\frac{a\Delta t}{2}}{1 - \frac{a\Delta t}{2}})^{n}\Vert\widetilde{u_{0}} - u_{0}\Vert.$\\
\quad If we expect that to a fixed $\Delta t$, when $n\to\infty$, the error can still be of control, then it must be true: $$\Arrowvert\frac{1+\frac{a\Delta t}{2}}{1 - \frac{a\Delta t}{2}}\Arrowvert\leqslant 1.$$ Hence, because that $\Delta t \geqslant 0,$ it can only be true when $a\leqslant 0,$ and $0\leqslant\Delta t < \frac{2}{\vert a\vert}.$\\
\quad On the other hand, take $z = a\Delta t,$ we have $\Arrowvert\frac{2+z}{2-z}\Arrowvert\leqslant 1, \quad z\in\mathcal{Z}.$
}
\solution{For Revised Euler Iteration:}{
{\centering \[\ u_{n+1} = u_{n} + \Delta ta(u_{n} + \frac{\Delta t}{2}au_{n})\]}
\quad Claimed as above, we have $\widetilde{u_{n+1}} = \widetilde{u_{n}}(1+\Delta ta + \frac{1}{2}(\Delta ta)^{2}).$ Hence, $\Vert\widetilde{u_{n}} - u_{n}\Vert = (1+\Delta ta + \frac{1}{2}(\Delta ta)^{2})^{n}\Vert\widetilde{u_{0}} - u_{0}\Vert.$ As shown above, $\Vert 1+\Delta ta+\frac{1}{2}(\Delta ta)^{2}\Vert\leqslant 1.$
\quad On the other hand, take $z = a\Delta t, $ we have $\Vert z^{2} + 2z + 2\Vert\leqslant 2.$
}

\problem{2}{Draw the convergence order of 1st-4th-order format}
\solution{Result}{
\begin{figure}[!h]
\centering
\includegraphics[width=15cm]{errorlist.eps}
\caption{The convergence order of 1-4 order format}
\label{convergence}
\end{figure}
}

\end{document}

### 2017-04-26 Undergraduate Thesis/Numerical Simulation/generate.py
u

@@ -8,7 +8,7 @@ delta_t = 1e-3 # step
 omega, sigma = 2, 1/2
 omega_b, sigma_b = 5, 1/2
 gamma_b, d_gamma, sigma_gamma = 1, 2, 1/3
-gamma_hat, b_hat = 1, 2
+gamma_hat, b_hat_re, b_hat_im = 1, 2, 1
 
 def f(t):
 	return np.sin(t)
@@ -20,18 +20,29 @@ def complex_white_noise():
 def white_noise():
 	return random.normalvariate(0, 1)
 
+# def func(vec, t):
+# 	u, b, gamma = vec.tolist()
+# 	return (-gamma+1j*omega)*u+b+f(t)+sigma*complex_white_noise(), \
+# 		(-gamma_b+1j*omega_b)*(b-b_hat)+sigma_b*complex_white_noise(), \
+# 		-d_gamma*(gamma-gamma_hat)+sigma_gamma*white_noise()
+
 def func(vec, t):
-	u, b, gamma = vec.tolist()
-	return (-gamma+1j*omega)*u+b+f(t)+sigma*complex_white_noise(), \
-		(-gamma_b+1j*omega_b)*(b-b_hat)+sigma_b*complex_white_noise(), \
-		-d_gamma*(gamma-gamma_hat)+sigma_gamma*white_noise()
+	u_re, u_im, b_re, b_im, gamma = vec.tolist()
+	return (-gamma*u_re-omega*u_im+b_re+f(t)+sigma*white_noise(), \
+			omega*u_re-gamma*u_im+b_im+sigma*white_noise(), \
+			-gamma_b*(b_re-b_hat_re)-omega_b*(b_im-b_hat_im)+sigma_b*white_noise(), \
+			-gamma_b*(b_im-b_hat_im)+omega_b*(b_re-b_hat_re)+sigma_b*white_noise(), \
+			-d_gamma*(gamma-gamma_hat)+sigma_gamma*white_noise()
+			)
 
 t = np.arange(0, 10, 0.02)
-u_0 = complex_white_noise()
-b_0 = complex_white_noise()
+u_0_re = white_noise()
+u_0_im = white_noise()
+b_0_re = white_noise()
+b_0_im = white_noise()
 gamma_0 = white_noise()
 
-track = odeint(func, (u_0, b_0, gamma_0), t)
+track = odeint(func, (u_0_re, u_0_im, b_0_re, b_0_im, gamma_0), t)
 print(track)
 # Plotting
 # fig = plt.figure()

### 2017-04-27 Undergraduate Thesis/Numerical Simulation/simulaton.py
u

@@ -1,0 +1,74 @@
+import numpy as np
+from scipy.integrate import odeint
+import random
+from matplotlib import pyplot as plt
+from generate import white_noise, func, Monte_Carlo, plot
+
+############# Parameters ###############
+d = 1.5
+sigma = 0.1549
+omega = 1.78
+gamma_b = 0.1*d
+sigma_gamma = 5*sigma
+sigma_b = 5*sigma
+omega_b = omega
+b_hat_re = 0
+b_hat_im = 0
+d_gamma = 0.01*d
+
+def f(t):
+	return 0
+########################################
+
+def func_(vec, t):
+	u_re, u_im, b_re, b_im = vec.tolist()
+	return -d*u_re-omega*u_im+b_re+sigma*white_noise(), \
+			omega*u_re-d*u_im+b_im+sigma*white_noise(), \
+			-gamma_b*(b_re-b_hat_re)-omega_b*(b_im-b_hat_im)+sigma_b*white_noise(), \
+			-gamma_b*(b_im-b_hat_im)+omega_b*(b_re-b_hat_re)+sigma_b*white_noise()
+
+######### Parameters for Computation ##########
+NUM_POINT = 1000
+END = 500
+t = np.arange(0, END, END/NUM_POINT)
+###############################################
+
+def Monte_Carlo_(n, t):
+	u_re, u_im, b_re, b_im = np.zeros(NUM_POINT), np.zeros(NUM_POINT), np.zeros(NUM_POINT), np.zeros(NUM_POINT)
+	for i in range(n):
+		u_0_re = white_noise()
+		u_0_im = white_noise()
+		b_0_re = white_noise()
+		b_0_im = white_noise()
+		track = odeint(func_, (u_0_re, u_0_im, b_0_re, b_0_im), t)
+		track_ = lambda i: np.asarray([ts[i] for ts in track])
+		u_re += track_(0)
+		u_im += track_(1)
+		b_re += track_(2)
+		b_im += track_(3)
+	return u_re/n, u_im/n, b_re/n, b_im/n
+
+def plot_(n, t):
+	u_re, u_im, b_re, b_im = Monte_Carlo_(n, t)
+	plt.subplot(411)
+	plt.plot(t, u_re)
+	plt.ylabel('Re(u)')
+
+	plt.subplot(412)
+	plt.plot(t, u_im)
+	plt.ylabel('Im(u)')
+
[…]

### 2017-04-29 Numerical solution of DEs/Assignment7/assignment.tex
Ass Assignment 7

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 7}{17.4.26}

\problem{1}{Derive A-B, A-M and Gear Formula with Newton Interpolation.}
\solution{Solution}{
With Newton Interpolation on $t_{n+1}, t_{n}, \cdots, t_{n+1-k}$, $f(t, u) = f_{n+1-k} + f_{n+1-k, n+2-k}(t - t_{n+1-k}) + \dots + f_{n+1-k, n+2-k ,\cdots, n+1}\Pi_{i=1}^{k}(t-t_{n-k+i}) + f_{n+1-k, n+2-k, \cdots, n+1, t}\Pi_{i=1}^{k+1}(t-t_{n-k+i}).$ \\
Let $p_{n, k}(t) = f(t, u) - f_{n+1-k, n+2-k, \cdots, n+1, t}\Pi_{i=1}^{k+1}(t-t_{n-k+i})$, 
Integrate within $[t_{n}, t_{n+1}]$, $u_{n+1} - u_{n} = \Delta t\Sigma_{i=0}^{k}b_{k, i}f_{i}$. 
\subsection{Adams-Bashforth Formula}
Like Adams-Moulton formula, with Newton interpolation on $t_{n}, t_{n-1}, \cdots, t_{n-k}$, $f(t, u) = f_{n-k} + f_{n-k, n+1-k}(t - t_{n-k}) + \dots + f_{n-k, n+1-k ,\cdots, n}\Pi_{i=0}^{k-1}(t-t_{n-k+i}) + f_{n-k, n+1-k, \cdots, n, t}\Pi_{i=0}^{k}(t-t_{n-k+i}).$ \\
Let $p_{n, k}(t) = f(t, u) - f_{n-k, n+1-k, \cdots, n, t}\Pi_{i=0}^{k}(t-t_{n-k+i})$, 
Integrate within $[t_{n}, t_{n+1}]$, $u_{n+1} - u_{n} = \Delta t\Sigma_{i=0}^{k}b_{k, i}f_{i}$. 
\subsection{Gear Formula}
Let $I_{k}u = u_{n-k+1} + u_{n-k+1, n-k+2}(t - t_{n-k+1}) + \cdots + u_{n-k+1, n-k+2, \cdots, n+1}\Pi_{i = n-k+1}^{n}(t-t_{i})$. \\
Use derivative of $I_{n}u(t)$ to take the place of the derivative of $u(t)$ when $t = t_{n+1}$, there exists $$f(t, u)|_{t = t_{n+1}} = \frac{du}{dt}|_{t=t_{n+1}} = \frac{dI_{k}u}{dt}|_{t=t_{n+1}}$$. \\
In consequence, $\Delta tf_{n+1} = (\Delta t)^{2}(u_{n-k+1} + u_{n-k+1, n-k+2}(t - t_{n-k+1}) + \cdots + u_{n-k+1, n-k+2, \cdots, n+1}\Pi_{i = n-k+1}^{n}(t-t_{i}))$.
}

\problem{2}{Consider the equation $$\frac{du}{dt}=\lambda(-u + cos(t))$$}
\solution{Solution}{

\subsection{The exact solution of the equation.}
The exact solution is $u(t) = c_{0}e^{-\lambda t}+\int_{0}^{t}e^{-\lambda(t-s)}\lambda cos(s)ds$.

\subsection{For $\lambda = 1,10,100,1000,$ use explicit and implicit Euler iteration to solve.}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{lambda=1.eps}
\caption{lambda = 1}
\label{Lambda1}
\end{figure}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{lambda=10.eps}
\caption{lambda = 10}
\label{Lambda2}
\end{figure}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{lambda=100.eps}
\caption{lambda = 100}
\label{Lambda3}
\end{figure}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{lambda=1000.eps}
\caption{lambda = 1000}
\label{Lambda4}
\end{figure}

\subsection{Use Adams and Gear iteration to solve the equation when $\lambda=1000$.}
\begin{figure}[!h]
\centering
\includegraphics[width = 15cm]{3.eps}
\caption{Adams and Gear}
\label{Lambda}
\end{figure}
.
}

\end{document}

### 2017-04-30 Undergraduate Thesis/Numerical Simulation/simulation2.py
add numerical simulation of mean

@@ -1,0 +1,168 @@
+import numpy as np
+from scipy.integrate import odeint
+import random
+from matplotlib import pyplot as plt
+import scipy
+
+############# Parameters ###############
+d = 1.5
+sigma = 0.1549
+omega = 1.78
+gamma_b = 0.1*d
+sigma_gamma = 5*sigma
+sigma_b = 5*sigma
+omega_b = omega
+b_hat_re = 0
+b_hat_im = 0
+d_gamma = 0.01*d
+gamma_hat = 0
+
+EM_STEP = 4
+A_f = 1
+omega_f = 0.15
+def f(t):
+	return 0
+########################################
+
+def randn():
+	return random.normalvariate(0, 1)
+
+def func(vec, t):
+	u_re, u_im, b_re, b_im, gamma = vec.tolist()
+	return -gamma*u_re-omega*u_im+b_re+f(t)+sigma*randn(), \
+			omega*u_re-gamma*u_im+b_im+sigma*randn(), \
+			-gamma_b*(b_re-b_hat_re)-omega_b*(b_im-b_hat_im)+sigma_b*randn(), \
+			-gamma_b*(b_im-b_hat_im)+omega_b*(b_re-b_hat_re)+sigma_b*randn(), \
+			-d_gamma*(gamma-gamma_hat)+sigma_gamma*randn()
+
+def func_(vec, t):
+	u_re, u_im, b_re, b_im = vec.tolist()
+	return -d*u_re-omega*u_im+b_re+sigma*randn(), \
+			omega*u_re-d*u_im+b_im+sigma*randn(), \
+			-gamma_b*(b_re-b_hat_re)-omega_b*(b_im-b_hat_im)+sigma_b*randn(), \
+			-gamma_b*(b_im-b_hat_im)+omega_b*(b_re-b_hat_re)+sigma_b*randn()
+
+######### Parameters for Computation ##########
+NUM_POINT = 200
+END = 0.2
+t = np.arange(0, END, END/NUM_POINT)
+###############################################
+
+def kernel0(t):
+	u_0_re = randn()
+	u_0_im = randn()
+	b_0_re = randn()
+	b_0_im = randn()
+	gamma_0 = randn()
[…]

### 2017-05-07 Numerical solution of DEs/Assignment8/assignment.tex
assignment 8

%!TEX program = xelatex

% \documentclass[10pt]{article}
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  numbers=left,
    framexleftmargin=10mm,
    frame=none,
    backgroundcolor=\color[RGB]{245,245,244},
  keywordstyle=\bf\color{blue},
  identifierstyle=\bf,
  numberstyle=\color[RGB]{0,192,192},
  commentstyle=\it\color[RGB]{0,96,96},
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},
  showstringspaces=false,
  extendedchars=false
    }
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Assignment 8}{17.5.6}

\problem{1}{Explain that when $c(x) < 0$, the extremum principle may not stand.}
\solution{Proof}{
Consider the 1-dimension Helmholtz equation:
$$
\frac{d^2u}{dx^2}+k^2u = 1, \quad u(0) = u(1) = 0.
$$
We can find the solution of this equation has a form like
$$
u(x) = \frac{\cos k+1}{k^2\sin k}\cos kx-\frac{1}{k^2}\sin kx+\frac{1}{k^2}.
$$
If we let $k = \frac{\pi}{2}$, then $u'(\frac{1}{2}) = 0$, but $u(\frac{1}{2}) = \frac{4(1-\sqrt{2})}{\pi^2} < 0$. So this time the extremum principle does not stand.
}

\problem{2}{If $u(0) = u(1) = 0$, and $\frac{d^2u}{dx^2} = f(x)$. Prove
$$
u(x) = \int_0^1 G(x; x_0)f(x_0) dx_0
$$
with Green function.}
\solution{Proof}{
In fact, we just check if $u(x)$ satisfies the conditions in the problem. \\
First,
\begin{equation}
\begin{split}
&u(0) = \int_0^1 x_0\times0\times f(x_0)dx_0 = 0, \\
&u(1) = \int_0^1 x_0\times0\times f(x_0)dx_0 = 0.
\end{split}
\end{equation}
Second,
\begin{equation}
\begin{split}
u'(x) &= \int_0^x (1-x_0)f(x_0)dx_0 + (1-x)xf(x) + \int_x^1-x_0f(x_0)dx_0-x(1-x)f(x) \\
&= \int_0^x f(x_0)dx_0-\int_0^1x_0f(x_0)dx_0,
\end{split}
\end{equation}
So $u''(x) = f(x)$, with uniqueness of Cauchy problem, we can prove the $u(x)$ is the function we need.
}

\problem{3}{Consider the equation
$$
-a\frac{d^2u}{dx^2}+b\frac{du}{dx}+cu=1,
$$
with boundary conditions $u(0) = 0$, $\frac{du}{dx}(1)+u(1)=0$, and parameters $a > 0, c\geqslant 0$ in $(0, 1)$. Solve the equation in accurate form and by difference scheme.
}
\solution{Accurate}{
The characteristic equation of this differential equation is 
$$
-a\lambda^2+b\lambda+c = 0.
$$
Case 1: $b = c = 0$. In this case, $u(x) = \frac{-x^2+2}{2a}.$ \\
Case 2: $c = 0, b \ne 0.$ The roots of the characteristic equation are $x_1 = 0, x_2 = -\frac{a}{b}.$ So the general solution is $u(x) = k_1e^{bx/a}+k_2$ for the homogeneous problem. And a special solution of the nonhomogeneous problem is $u = \frac{x}{b}$, and the accurate solution is 
$$
u(x) = -\frac{a}{b^2}e^{bx/a} - \frac{1}{b}e^{b/a} + \frac{x}{b}- \frac{a}{b^2}.
$$
considering the boundary conditions. \\
Case 3: $b, c\ne 0.$ Using the same techniques, the accurate solution is
$$
u(x) = \frac{e^{\lambda_2}-(1+\lambda_1)}{c((1+\lambda_2)e^{\lambda_1}-(1+\lambda_1)e^{\lambda_2})}e^{\lambda_1x} + \frac{e^{\lambda_1}-(1+\lambda_2)}{c((1+\lambda_1)e^{\lambda_2}-(1+\lambda_2)e^{\lambda_1})}e^{\lambda_2x}+\frac{1}{c},
$$
in which $\lambda_1, \lambda_2$ are roots of $-a\lambda^2+b\lambda+c=0$.
}

\solution{Numerical}{
The computing scheme of this problem is
\begin{equation}
-a\frac{u_{i+1}-2u_i+u_{i-1}}{h^2}+b\frac{u_{i+1}-u_{i-1}}{2h}+cu_i = f_i, \quad i = 1, 2, \cdots, N-1.
\end{equation}
Then the linear equation can be written as
$$
\mathbf{Au}+\mathbf{Bu}+\mathbf{Cu} = \mathbf{f},
$$
with
$$
\mathbf{A} = \mathrm{tridiag}(1, -2, 1),
$$
$$
\mathbf{B} = \mathrm{tridiag}(-1, 0, 1),
$$
$$
\mathbf{C} = \mathrm{diag}(1),
$$
$$
\mathbf{f}=\left(                 
  \begin{array}{cccccc}   
    1\\  
    1\\  
    ...\\
    ...\\
    1\\
    1\\
    \end{array}
\right)+\left(                 
  \begin{array}{cccccc}   
    \frac{a}{h^{2}}u_{0}-\frac{b}{2h}u_{0}\\  
    0\\  
    ...\\
    ...\\
    0\\
    \frac{a}{h^{2}}u_{N}-\frac{b}{2h}u_{N}\\
    \end{array}
\right).
$$
We can simply give the solution by
$$
\mathbf{u} = (\mathbf{A+B+C})^{-1}\mathbf{f}.
$$
The numerical simulation is as follows, in which we choose $a = 1, b = 10, c = 10.$
\begin{figure}[!h] \centering
\includegraphics[width = 15cm]{code/Simulation.eps}
\caption{Simulation and Accurate results}
\end{figure}
Relative error is as follows:
\begin{figure}[!h] \centering
\includegraphics[width = 15cm]{code/error.eps}
\caption{Relative error}
\end{figure}
}

\end{document}

### 2017-05-07 Numerical solution of DEs/Assignment8/code/demo.m

@@ -1,0 +1,29 @@
+h = 1e-2;
+t = 0:h:1;
+N = length(t);
+a = 1; b = 10; c = 10;
+u_accu = accurate(a, b, c, t);
+u_diff = three_point_diff(a, b, c, N-1, u_accu(1), u_accu(N));
+u_diff = [u_accu(1), u_diff, u_accu(N)];
+
+figure(1);
+plot(t, u_accu, '*-'); hold on;
+plot(t, u_diff, '.-');
+legend('Accurate', 'Numerical', 'Location', 'Best');
+
+figure(2);
+T = 3;
+err = zeros(1, T);
+% step = (2.^(-3:-1:-10));
+step = (0.1.^(1:T));
+for i=1:T
+    h = step(i);
+    t = 0:h:1;
+    u_accu = accurate(a, b, c, t);
+    N = length(t);
+    disp(N)
+    u_diff = three_point_diff(a, b, c, N-1, u_accu(1), u_accu(N));
+    u_diff = [u_accu(1), u_diff, u_accu(N)];
+    err(i) = max(abs((u_diff - u_accu)./u_accu));
+end
+loglog(step, err);

### 2017-05-07 Numerical solution of DEs/Assignment8/code/three_point_diff.m

@@ -1,0 +1,11 @@
+function[u] = three_point_diff(a, b, c, N, u0, uN)
+    format long;
+    h = 1/N;
+    A = -a/(h^2)*(diag(ones(N-2, 1), -1) + diag(ones(N-2, 1), 1) + diag(ones(N-1, 1)*-2, 0));
+    B = b/(2*h)*(diag(ones(N-2, 1), -1) + diag(ones(N-2, 1), 1));
+    C = c*eye(N-1);
+    f = ones(N-1, 1);
+    f(1) = f(1) + a/(h^2)*u0-b/(2*h)*u0;
+    f(N-1) = f(N-1) + a/(h^2)*uN-b/(2*h)*uN;
+    u = (A+B+C)\f;
+    u = transpose(u);

### 2017-05-11 Undergraduate Thesis/NumericalSimulation/demo.py
update

@@ -6,10 +6,10 @@ import matplotlib as mpl
 from simulation2 import Monte_Carlo
 
 inteval = [0, 0.2]
-step = 1e-3
+step = 1e-2
 start = 0
 t = np.arange(inteval[0], inteval[1], step)
-n = 100000
+n = 10
 
 ## simulation results ###
 data = MC(n, t)
@@ -52,7 +52,7 @@ for i in range(5):
 	plt.xlabel('time')
 	plt.show()
 
-# ## Variances ###
+# # ## Variances ###
 for i in range(3):
 	plt.figure(6+i)
 	plt.title('Variance of ' + labels_var[i])

### 2017-05-12 Undergraduate Thesis/NumericalSimulation/simulation.py
update

@@ -91,10 +91,10 @@ def stat(data):
 	# Cov_u_b_im = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]+1j*data[3][:, i])[1] for i in range(col)])
 	# Cov_u_b_star_re = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i])[0] for i in range(col)])
 	# Cov_u_b_star_im = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i])[1] for i in range(col)])
-	Cov_u_u_star = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[0][:, i]-1j*data[1][:, i]) for i in range(col)], dtype=np.complex)
-	Cov_u_gamma = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[4][:, i]) for i in range(col)], dtype=np.complex)
-	Cov_u_b = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]+1j*data[3][:, i]) for i in range(col)], dtype=np.complex)
-	Cov_u_b_star = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i]) for i in range(col)], dtype=np.complex)
+	Cov_u_u_star = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[0][:, i]-1j*data[1][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_gamma = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[4][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_b = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]+1j*data[3][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_b_star = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i]) for i in range(col)], dtype=np.complex64)
[…]

### 2017-05-14 Undergraduate Thesis/NumericalSimulation/simulation.py
update

@@ -7,7 +7,8 @@ from simulation2 import kernel
 ############# Parameters ###############
 d = 1.5
 sigma = 0.1549
-omega = 1.78
+# omega = 1.78
+omega = 0
 gamma_b = 0.1*d
 sigma_gamma = 5*sigma
 sigma_b = 5*sigma
@@ -91,11 +92,24 @@ def stat(data):
 	# Cov_u_b_im = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]+1j*data[3][:, i])[1] for i in range(col)])
 	# Cov_u_b_star_re = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i])[0] for i in range(col)])
 	# Cov_u_b_star_im = np.asarray([cov(data[0][:, i]+1j*data[1][:, i], data[2][:, i]-1j*data[3][:, i])[1] for i in range(col)])
-	Cov_u_u_star = np.asarray([cov(data[0][:, i]+1.j*data[1][:, i], data[0][:, i]-1.j*data[1][:, i]) for i in range(col)], dtype=np.complex64)
-	Cov_u_gamma = np.asarray([cov(data[0][:, i]+1.j*data[1][:, i], data[4][:, i]) for i in range(col)], dtype=np.complex64)
-	Cov_u_b = np.asarray([cov(data[0][:, i]+1.j*data[1][:, i], data[2][:, i]+1.j*data[3][:, i]) for i in range(col)], dtype=np.complex64)
-	Cov_u_b_star = np.asarray([cov(data[0][:, i]+1.j*data[1][:, i], data[2][:, i]-1.j*data[3][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_u_star = np.asarray([cov_u_u_star(data[0][:, i]+1.j*data[1][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_gamma = np.asarray([cov_u_gamma(data[0][:, i]+1.j*data[1][:, i], data[4][:, i]) for i in range(col)], dtype=np.complex64)
+	Cov_u_b = np.asarray([cov_u_b(data[0][:, i]+1.j*data[1][:, i], data[2][:, i]+1.j*data[3][:, i]) for i in range(col)], dtype=np.complex64)
[…]

### 2017-05-14 Undergraduate Thesis/NumericalSimulation/demo_real.py
update

@@ -7,17 +7,14 @@ import matplotlib as mpl
 from simulation2 import Monte_Carlo
 
 inteval = [0, 0.2]
-step = 1e-2
+step = 1e-3
 start = 0
 t = np.arange(inteval[0], inteval[1], step)
-n = 100
+n = 100000
 
 ## simulation results ###
 data = MC(n, t)
 mean, var, cov = stat(data)
-[E_u_re_sim, E_u_im_sim, E_b_re_sim, E_b_im_sim, E_gamma_sim] = mean
-[Var_u_sim, Var_b_sim, gamma_sim] = var
-[Cov_u_u_star_re_sim, Cov_u_u_star_im_sim, Cov_u_u_star_re_sim, Cov_u_u_star_im_sim, Cov_u_b_re_sim, Cov_u_b_im_sim, Cov_u_b_star_re_sim, Cov_u_b_star_im_sim] = cov
 
 ## theoretical results ###
 E_u = [E_u(i) for i in t]
@@ -33,17 +30,17 @@ Cov_u_gamma = [Cov_u_gamma(i) for i in t]
 Cov_u_b = [Cov_u_b(i) for i in t]
 Cov_u_b_star = [Cov_u_b_star(i) for i in t]
 
-theo_mean = [real(E_u), imag(E_u), real(E_b), imag(E_b), E_gamma]
+theo_mean = [E_u, E_b, E_gamma]
 theo_var = [Var_u, Var_b, Var_gamma]
-theo_cov = [real(Cov_u_u_star), imag(Cov_u_u_star), real(Cov_u_gamma), imag(Cov_u_gamma), real(Cov_u_b), imag(Cov_u_b), real(Cov_u_b_star), imag(Cov_u_b_star)]
+theo_cov = [Cov_u_u_star, Cov_u_gamma, Cov_u_b, Cov_u_b_star]
 
-labels_mean = ['Re(u)', 'Im(u)', 'Re(b)', 'Im(b)', 'gamma']
+labels_mean = ['u', 'b', 'gamma']
 labels_var = ['u', 'b', 'gamma']
-labels_cov = ['Re(Cov(u, u*))', 'Im(Cov(u, u*))', 'Re(Cov(u, gamma))', 'Im(Cov(u, gamma))', 'Re(Cov(u, b))', 'Im(Cov(u, b))', 'Re(Cov(u, b*))', 'Im(Cov(u, b*))']
[…]

### 2017-05-25 Undergraduate Thesis/NumericalSimulation/plot.py
Ver 1.1

@@ -1,0 +1,22 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+labels_cov_save = ['Re(Cov(u, u_star))', 'Im(Cov(u, u_star))', 'Re(Cov(u, gamma))', 'Im(Cov(u, gamma))', 'Re(Cov(u, b))', 'Im(Cov(u, b))', 'Re(Cov(u, b_star))', 'Im(Cov(u, b_star))']
+labels_cov = ['Re(Cov(u, u*))', 'Im(Cov(u, u*))', 'Re(Cov(u, gamma))', 'Im(Cov(u, gamma))', 'Re(Cov(u, b))', 'Im(Cov(u, b))', 'Re(Cov(u, b*))', 'Im(Cov(u, b*))']
+
+x = np.linspace(0, 0.2, 200)
+for i in range(8):
+	plt.figure(i)
+	sim = np.load(labels_cov_save[i]+'_sim.npy')
+	theo = np.load(labels_cov_save[i]+'_theo.npy')
+	l1, = plt.plot(x, sim)
+	l2, = plt.plot(x, theo)
+	plt.title(labels_cov[i])
+	plt.ylabel(labels_cov[i])
+	plt.xlabel('time')
+	plt.legend((l1, l2), ('Simulation', 'Theoretical'))
+	if i in [0, 1, 2, 3]:
+		plt.ylim((-0.1, 0.05))
+	elif i in [5, 6, 7]:
+		plt.ylim((-0.01, 0.01))
+	plt.show()

### 2017-08-22 Graduate - Introduction to Analysis I/Homework20170822-1.tex
add assignment 1

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\labelenumi{\arabic{enumi}.}
\def\theenumi{\arabic{enumi}}
\def\labelenumii{(\alph{enumii})}
\def\theenumii{\alph{enumii}}
\def\p@enumii{\theenumi.}
\def\labelenumiii{\arabic{enumiii}.}
\def\theenumiii{\arabic{enumiii}}
\def\p@enumiii{(\theenumi)(\theenumii)}
\def\labelenumiv{\arabic{enumiv}.}
\def\theenumiv{\arabic{enumiv}}
\def\p@enumiv{\p@enumiii.\theenumiii}
\pagestyle{plain}
\setcounter{secnumdepth}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 1\\Tuesday, August 22, 2017}\bigskip
\end{center}

\noindent\textbf{Instructions}: You may submit this homework ``the old fashion'' way, i.e., using paper and pencil (or pen), but if you do so, please use at least one sheet of ($8\frac{1}{2}%
\times11$) paper per problem. Write your name at the top of each sheet you
use. Please write neatly. Staple the sheets together or use a paper clip.

However, I encourage you to do at least some of the problems using LaTeX.  As of the third assignment, you will have to submit your homework in LaTeX.

\noindent If you use results from books, Royden or others, please be explicit about what results you are using.

\begin{center}
\emph{Homework 1 is due by the start of class on Wednesday, September 6.}
\end{center} 
\medskip

\begin{enumerate}
\item \textbf{Problem 34, page 20}.  Show that the assertion of the Heine-Borel Theorem is equivalent to the Completeness Axiom for the real numbers.  Show that the assertion of the Nested Set Theorem is equivalent to the Completeness Axiom for the real numbers.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\begin{proof}

\end{proof}

\bigskip

\item \textbf{Problem 44, page 24}.  Let $p$ be a natural number greater than $1$, and $x$ a real number, $0<x<1$.  Show that there is a sequence $\{a_n\}$ of integers with $0\leq a_n < p$ for each $n$ such that \[
x = \sum_{n=1}^{\infty} \frac{a_n}{p^n} \]and that this sequence is unique except when $x$ is of the form $q/p^n$, in which case there are exactly two such sequences.  Show that, conversely, if $\{a_n\}$ is any sequence of integers with $0\leq a_n < p$, then the series \[\sum_{n=1}^{\infty} \frac{a_n}{p^n} \]converges to a real number $x$ with $0\leq x \leq 1$. (If $p = 10$, this series is called the \emph{decimal} expansion of $x$.  For $p = 2$ it is called the \emph{binary} expansion of $x$, and for $p = 3$, the \emph{tenary} expansion.)

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item \textbf{Problem 46, page 25}. Show that the assertion of the Bolzano-Weierstrass Theorem is equivalent to the Completeness Axiom of the real numbers.  Show that the assertion of the Monotone Convergence Theorem is equivalent to the Completeness Axiom for the real numbers.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item Let $\mathbb{F}$ be an ordered field with the property that if $[a,b]$ is any closed interval and if $f:[a,b]\rightarrow \mathbb{F}$ is any continuous function such that $f(a)>0$ and $f(b)<0$, then there is an $x$, $a < x < b$, such that $f(x)=0$.  Show that such a field $\mathbb{F}$ has the least upper bound property.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item Show that if $\mathbb{F}$ is an ordered field such that
\begin{enumerate}
\item the order for $\mathbb{F}$ satisfies the Archimedean property, and
\item every Cauchy sequence is convergent, 
\end{enumerate}
then $\mathbb{F}$ satisfies the Completeness Axiom. (There are examples of ordered fields that \emph{don't} have the Archimedean property and \emph{do} have the property that every Cauchy sequence is convergent.  Can you come up with such an example?)

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item Suppose that for $i = 1,2$, $\mathbb{F}_i$ is an ordered field satisfying the Completeness Axiom. Show that there is a unique isomorphism $\alpha$ from $\mathbb{F}_1$ onto $\mathbb{F}_2$. That is, $\alpha$ is a field isomorphism that preserves the order ($x \leq_1 y$ implies $\alpha(x) \leq_2 \alpha(y)$, where $\leq_i$ denotes ``less than or equal to'' in the field $\mathbb{F}_i$). Thus, there is at most \emph{one} field of ``real numbers''.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\end{enumerate}
\end{document}

### 2017-08-23 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

@@
 \begin{proof}
-
+\textbf{Completeness Axiom $\to$ Heine-Borel theorem} is shown in the proof of Heine-Borel theorem in Page 18.
+\\
+\textbf{Heine-Borel theorem $\to$ Nested Set theorem} is shown in Page 19. \\
+\textbf{Nested Set theorem $\to$ Completeness Axiom theorem:}\\
+Let $E$ be a nonempty and upper-bounded set of real numbers, and let $T$ is the set consists of all upper bounders of $E$. Pick $a_1\notin T$, and $b_1 \notin T$, then $a_1 < b_1$.
+If $\frac{a_1+b_1}{2} \in T$, then $[a_2, b_2] = \left[a_1, \frac{a_1+b_1}{2}\right]$; else $[a_2, b_2] = \left[\frac{a_1+b_1}{2}, b_1\right]$. 
+Construct $[a_3, b_3], \cdots$ as above, we can get a nested set series $\{[a_n, b_n]\}$, satisfying $a_n\notin T, b_n\in T$.
+With Nested Set theorem, there exist a real number $x$ belongs to all these close sets, and $\lim_{n\to\infty}a_n = \lim_{n\to\infty}b_n = x$.\\
+If $x\notin T$, then exists $y\in E$, s.t.
+$x < y$.
+So $b_n < x$ when $n$ is large enough.
+This makes a contradiction with $b_n\in T$, so $x\in T$.
+On the othe hand, if there exists $z\in T$, s.t.
+$z < x$, then $a_n > z$ when n is large enough.
+This makes a contradiction with $a_n\in E$.
+So $x$ is the supremum of $E$.
+\\
+To sum up, we have a logical circle like this: \\
+Completeness Axiom $\to$ Heine-Borel theorem $\to$ Nested Set theorem $\to$ Completeness Axiom. So these three theorems are equivalent.
 \end{proof}

### 2017-08-23 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update'

@@
 \bigskip
-\textbf{Collaborators:}\\
+\textbf{Collaborators:} Me \& One of my undergraduate classmate;
 \smallskip
@@
 \\
-\textbf{Heine-Borel theorem $\to$ Nested Set theorem} is shown in Page 19. \\
+\textbf{Heine-Borel theorem $\to$ Completeness Axiom:} \\
+Let $E$ be a nonempty and upper-bounded set of real numbers, and let $b$ be one of it's upper boundaries.
+Pick $a\in E$, then $[a, b]$ is a closed set.
+Let $U$ be the set of upper boundaries of $E$, and $T = E\bigcap [a, b]$.
+If the supremum does not exist, then $\forall x\in[a, b]$, either $\exists a_1\in E$, s.t.
+$a_1 > x$, or $\exists b_1\in T$, s.t.
+$b_1 < x$.
+If it is the former case, we define an open set $A_1 = (a-1, a_1)$; else we define an open set $B_1 = (b_1, b+1)$.
+Since we can define such an open set to cover every $x\in [a, b]$, there exists a open cover $\{A_i\}\bigcup\{B_i\}$.
+According to Heine-Borel theorem, there exists a finite cover $\{A\}_{i = 1}^{n_1}\bigcup\{B\}_{i = 1}^{n_2}$.
+If we denote $A_0 = \bigcup_{i=1}^{n_1}\{A_i\}, B_0 = \bigcup_{i=1}^{n_2}\{B_i\}$, then since $A_0$ consists of elements in $T$, while $B_0$ consists of elements of $E's$ upper bound, we have $A_0\bigcap B_0 = \emptyset$.
+Then there exists a number $\epsilon\in T$, s.t.
+$\epsilon\notin A_0\bigcup B_0$.
+It is contradictory to the assumption that $A_0\bigcup B_0$ is a cover of $[a, b]$.
+So $E$ has a supremum.
+\\
+\textbf{Completeness Axiom $\to$ Nested Set theorem:} \\
+Let $\{[a_i, b_i\}$ being a descending closed set series.
+Denote $A = \{a_i\}, B = \{b_i\}$, then $A$ has an upper bound $b_0$, and $B$ has an lower bound $a_0$.
+According to the Completeness Axiom, $A$ has a supremum, denoted by $x$, and B has a infimum, denoted by $y$.
+If $x > y$, then according to the definition of supremum and infimum, there exists $j_1, j_2$, s.t.
+$y \le b_{j_2} < \frac{x+y}{2} < a_{j_1} \le x$.
+It contradicts with that $a_i < b_j, \forall i, j$.
+so $x \le y$, which means $\bigcap \{[a_i, b_i]\} \ne \emptyset$.
+\\
+For the general case, it is the same using the similar skills.\\ 
 \textbf{Nested Set theorem $\to$ Completeness Axiom theorem:}\\
@@
 Construct $[a_3, b_3], \cdots$ as above, we can get a nested set series $\{[a_n, b_n]\}$, satisfying $a_n\notin T, b_n\in T$.
-With Nested Set theorem, there exist a real number $x$ belongs to all these close sets, and $\lim_{n\to\infty}a_n = \lim_{n\to\infty}b_n = x$.\\
+With Nested Set theorem, there exist a real number $x$ belongs to all these closed sets, and $\lim_{n\to\infty}a_n = \lim_{n\to\infty}b_n = x$.\\
 If $x\notin T$, then exists $y\in E$, s.t.
@@
 So $x$ is the supremum of $E$.
-\\
-To sum up, we have a logical circle like this: \\
-Completeness Axiom $\to$ Heine-Borel theorem $\to$ Nested Set theorem $\to$ Completeness Axiom. So these three theorems are equivalent.
 \end{proof}
@@
 x = \sum_{n=1}^{\infty} \frac{a_n}{p^n} \]and that this sequence is unique except when $x$ is of the form $q/p^n$, in which case there are exactly two such sequences.
-Show that, conversely, if $\{a_n\}$ is any sequence of integers with $0\leq a_n < p$, then the series \[\sum_{n=1}^{\infty} \frac{a_n}{p^n} \]converges to a real number $x$ with $0\leq x \leq 1$.
+Show that, conversely, if $\{a_n\}$ is any sequence of integers with $0\leq a_n < p$, then the sequence \[\sum_{n=1}^{\infty} \frac{a_n}{p^n} \]converges to a real number $x$ with $0\leq x \leq 1$.
 (If $p = 10$, this series is called the \emph{decimal} expansion of $x$.
@@
 \textbf{Solution:}
+\begin{proof}
+\textbf{Existance:} \\
+Let $a_1 = \lfloor px\rfloor$, $a_2 = \lfloor p^2x-a_1p\rfloor$, $\cdots$, $a_n = \lfloor p^nx - \Sum_{i=1}^{n-1}a_ip^{n-i}$.
+From this inductive construction we know that the subsum $S_n = \Sum_{i=1}^n\frac{a_i}{p^i}$ forms a increasing sequence, while it is upper bounded by $x$.
+According to the Monotone Convergence Criterion, this sequence has a limitation.
+Moreover, $|x - S_n| \le \frac{1}{p^{n-1}}$ for each n, so $\lim_{n\to\infty} |x-S_n|= 0$
+\end{proof}
 \bigskip

### 2017-08-24 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

@@
 \textbf{Completeness Axiom $\to$ Heine-Borel theorem} is shown in the proof of Heine-Borel theorem in Page 18.
-\\
+\\[5pt]
 \textbf{Heine-Borel theorem $\to$ Completeness Axiom:} \\
@@
 So $E$ has a supremum.
-\\
+\\[5pt]
 \textbf{Completeness Axiom $\to$ Nested Set theorem:} \\
@@
 \\
-For the general case, it is the same using the similar skills.\\ 
+For the general case, it is the same using the similar skills.\\[5pt]
 \textbf{Nested Set theorem $\to$ Completeness Axiom theorem:}\\
@@
 \textbf{Existance:} \\
-Let $a_1 = \lfloor px\rfloor$, $a_2 = \lfloor p^2x-a_1p\rfloor$, $\cdots$, $a_n = \lfloor p^nx - \Sum_{i=1}^{n-1}a_ip^{n-i}$.
-From this inductive construction we know that the subsum $S_n = \Sum_{i=1}^n\frac{a_i}{p^i}$ forms a increasing sequence, while it is upper bounded by $x$.
+Let $a_1 = \lfloor px\rfloor$, $a_2 = \lfloor p^2x-a_1p\rfloor$, $\cdots$, $a_n = \lfloor p^nx - \sum_{i=1}^{n-1}a_ip^{n-i}\rfloor=-$.
+From this inductive construction we know that the subsum $S_n = \sum_{i=1}^n\frac{a_i}{p^i}$ forms a increasing sequence, while it is upper bounded by $x$.
 According to the Monotone Convergence Criterion, this sequence has a limitation.
-Moreover, $|x - S_n| \le \frac{1}{p^{n-1}}$ for each n, so $\lim_{n\to\infty} |x-S_n|= 0$
+Moreover, $|x - S_n| \le \frac{1}{p^{n-1}}$ for each n, so $\lim_{n\to\infty} |x-S_n|= 0$, that means $x$ is a limitation of $\{S_n\}$.
+By the same criterion, we can know that $x$ is the only limitation of $\{S_n\}$, that means $x = \sum_{n=1}^{\infty}\frac{a_n}{p^n}$.
+\\[5pt]
+\textbf{Uniqueness:} \\
+First, we need to prove that $0$ can be represented in this way by two sequences if we may let $a_0 = -1$.
+The two sequences are trivial: the first one is $a_i = 0$, and the second one is $a_0 = -1, a_i = p-1$.
+If there exist a third sequence ${b_i}$, then if $b_0 \ge 0, b_j > 0$, then $\sum_{b_i} \ge \frac{1}{p^j} > 0$.
+If $b_0 \le -1, b_j < p-1$, the $\sum_{b_i} \le -\frac{1}{p^j} < 0$.
+So there only exists two sequences for $0$.
+When $x = \frac{q}{p^n}$, it is just the same as $x = 0$ since we only need to shuffle the point n times to the right.
+So there also exists two sequences for $x$.
+\\
+When $x \ne \frac{q}{p^n}$, assume there exists two sequences for representing $x$, denoted by $\{a_i\}$ and $\{b_i\}$.
+According to this assumption, there must exist a $j$, s.t.
+$a_j \ne 9$.
+Let $k$ be the first position of difference between these two sequences, then $|\sum{a_i}-\sum{b_i}| >= \frac{1}{p^k}-\sum_{i=k+1}^{\infty}\frac{|a_i-b_i|}{p^i} > \frac{1}{p^j}$.
+So this contradicts with our assumption, which means $x$ only has one sequence in this form.
 \end{proof}
@@
 \textbf{Solution:} 
+\begin{proof}
+\textbf{Completeness Axiom $\to$ Monotone Convergence Criterion is shown is the proof in Page 21.} \\
+\textbf{Monotone Convergence Criterion $\to$ Completeness Axiom:} \\
+Let $E$ be a upper bounded set, and $T$ be the set of upper bound of $E$.
+Pick $a_1 \in E, b_1 \in T$.
+If $\frac{a_1+b_1}{2}\in E$, we choose $a_2 = \frac{a_1+b_1}{2}, b_2 = b_1$; else we choose $a_2 = a_1, b_2 = \frac{a_1+b_1}{2}$.
+Similarly, we get two sequences $\{a_n\}, \{b_n\}$, and $\{a_n\}$ is a upper bounded monotone increasing sequence, $\{b_n\}$ is a lower bounded monotone decreasing sequence, and $b_n-a_n\to 0$.
+According to Monotone Convergence Criterion, there exists $\alpha$, s.t.
+$\alpha = \lim_{n\to\infty}a_n$.
+Next we prove $\alpha = \sup E$.
+\\
+First, $\forall \epsilon > 0, \exists N_\epsilon$, s.t.
+when $n > N_\epsilon$, $\alpha-\epsilon < a_n$.
+Since $a_n$ is not an upper bound of $E$, there exists $x_\epsilon \in E$, s.t.
+$\alpha-\epsilon < a_n < x_\epsilon$.
+On the other hand, if there exists $x_0\in E$, s.t.
+$x_0 > \alpha$, then $\lim_{n\to\infty}b_n = \lim_{n\to\infty}a_n+\lim_{n\to\infty}\frac{b_1-a_1}{2^n} = \alpha$.
+Thus $\exists n_0 > 0$, s.t.
+$x_0 > b_{n_0}$.
+It contradicts with the assumption that $b_i$ are upper bounds of $E$.
+So $\alpha = \sup E$.
+\\[5pt]
+Since \textbf{Nested Set theorem $\to$ Bolzano-Weierstarss theorem} has been proved in Page 21, and \textbf{Bolzano-Weierstarss theorem $\to$ Cauchy Convergence Criterion} has been proved in Page 22, and we have proved the Nested Set theorem is equavilent to Completeness Axiom, we only need to prove \textbf{Cauchy Convergence Criterion $\to$ Nested Set theorem}.
+\\
+Assume $\{[a_n, b_n\}$ is a sequence of closed sets, and $\lim_{n\to\infty}(b_n-a_n) = 0$.
+Then pick $m > n$, we have $0 \le a_m-a_n < b_n-a_n\to 0$.
+So $\{a_n\}$ is Cauchy, which means $\lim_{n\to\infty}a_n = \alpha$, and $\lim_{n\to\infty}b_n = \alpha$.
+Since $\{a_n\}$ is monotone increasing while $\{b_n\}$ is monotone decreasing, we know $\alpha$ is the only number belongs to every closed set.
+\end{proof}
 \bigskip
@@
 
-\textbf{Solution:}
+\textbf{Solution:} \\
+
 \bigskip

### 2017-08-25 Graduate - Introduction to Analysis I/Homework20170822-1.tex
local
Add a problem

@@
 \bigskip
-\textbf{Collaborators:} Me \& One of my undergraduate classmate;
+\textbf{Collaborators:} 
 \smallskip
@@
 According to this assumption, there must exist a $j$, s.t.
-$a_j \ne 9$.
+$a_j \ne q-1$.
 Let $k$ be the first position of difference between these two sequences, then $|\sum{a_i}-\sum{b_i}| >= \frac{1}{p^k}-\sum_{i=k+1}^{\infty}\frac{|a_i-b_i|}{p^i} > \frac{1}{p^j}$.
@@
 \textbf{Solution:}
+\begin{proof}
+Let $E$ be a upper-bounded set, and $T$ be the set of all upper bounds of $E$. Construct a function f like this: 
+$$
+f = \left\{
+\begin{aligned} 
+1, x\in E \\
+-1, x \in T
+\end{aligned}
+\right.
+$$
+We assume that $E$ has no supremum.
+That means $\forall x\in E, \forall \epsilon > 0$(We may assume $x$ is a inner point of $E$), we can find $x_1 > x \in E$, so $\forall x_2 \in (x-\delta, x_1), |f(x_1)-f(x)| = 0 < \epsilon$.
+So $f$ is continuous on $x$.
+With the arbitrariness of $x$, $f$ is continuous on $E$.
+Similarly, $f$ is continuous on $T$.
+Now we prove that $f$ is continuous on $E\bigcup T$.
+If not, assume $f$ is not continuous on $x_0$.
+If $x_0 \in E$, then $f$ should be discontinuous on the right side, which means $\exists \epsilon > 0, \forall \eta > 0, \exists x$, s.t.
+$|x_0 - x| < \eta, |f(x_0)-f(x)|>\epsilon$.
+That just means $x_0$ is the supremum of $E$, which makes a contradiction.
+If $x_0 \in T$, similarly $x_0$ is the supremum of $E$ according to definition.
+So $f$ is continuous on $E\bigcup T$.
+Using the property in the problem, for $a \in E, b\in T$, there must exist $x$, s.t.
+$f(x) = 0$.
+It contradicts with the construction of $f$.
+So E has a supremum, which means $\mathcal{F}$ has the least upper bound property.
+\end{proof}
 \bigskip
@@
 
-\textbf{Solution:} \\
+\textbf{Solution:}
 

### 2017-08-25 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

@@
 \textbf{Solution:} 
+\begin{proof}
+\textbf{Uniqueness:} \\
+Assume there exists two field isomorphisms $f_1, f_2$ from $\mathcal{F_1}$ onto $\mathcal{F_2}$.
+Let $E$ is an upper bounded set in $\mathcal{F_1}$, and according to the Completeness Axiom, it's supremum is $e$.
+Denote $E_1 = f_1(E)\in \mathcal{F_2}, E_2 = f_2(E)\in\mathcal{F_2}$.
+Then according to properties of isomorphism, $E_1, E_2$ are both upper bounded sets, so they both have supremums, denoted by $e_1, e_2$.
+Then since the isomorphism preserves the order, we have $f_1(e) = f_2(e) = e_1 = e_2$.
+Since for each $x\in \mathcal{F_1}$, we can construct a set with $x$ being it's supremum (for example, a sequence converge to $x$), we have $f_1(x) = f_2(x)$.
+Thus $f_1 = f_2$.
+\\[5pt]
+\textbf{Existence:} \\
+
+\end{proof}
 \bigskip

### 2017-08-25 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

--- 2017-08-25 Graduate - Introduction to Analysis I/Homework20170822-1.tex
@@
 \textbf{Solution:} 
+\begin{proof}
+\textbf{Uniqueness:} \\
+Assume there exists two field isomorphisms $f_1, f_2$ from $\mathcal{F}_1$ onto $\mathcal{F}_2$.
+Let $E$ is an upper bounded set in $\mathcal{F}_1$, and according to the Completeness Axiom, it's supremum is $e$.
+Denote $E_1 = f_1(E)\in \mathcal{F}_2, E_2 = f_2(E)\in\mathcal{F}_2$.
+Then according to properties of isomorphism, $E_1, E_2$ are both upper bounded sets, so they both have supremums, denoted by $e_1, e_2$.
+Then since the isomorphism preserves the order, we have $f_1(e) = f_2(e) = e_1 = e_2$.
+Since for each $x\in \mathcal{F}_1$, we can construct a set with $x$ being it's supremum (for example, a sequence converge to $x$), we have $f_1(x) = f_2(x)$.
+Thus $f_1 = f_2$.
+\\[5pt]
+\textbf{Existence:} \\
+
+\end{proof}
 \bigskip

### 2017-08-30 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

@@
 \textbf{Existence:} \\
+Since $\mathcal{F}_1, \mathcal{F}_2$ are fields, they close to multiplications.
+Let $I_1$ be the identity of $\mathcal{F}_1$, and $I_2$ be the identity of $\mathcal{F}_2$.
+Then since each non-zero element have an inverse, we can define rational numbers in $F_i$:
+$$
+q = (c_1I_i)\times (c_2I_i)^{-1},
+$$
+where $x^{-1}$ means the inverse in it's field. \\
+Now we construct the map like this: \\
+$$
+\begin{aligned}
+f: ~\mathcal{F}_1&\to\mathcal{F}_2 \\
+(c_1I_1)\times(c_2I_1)^{-1} &\mapsto (c_1I_2)\times(c_2I_2)^{-1}.
+\end{aligned}
+$$
+For $x \in \mathcal{F}_1$, if $x$ is not a rational number, we call it an irrational number.
+If $x$ is an irrational number, if we can construct two monotone sequences of rational numbers ${a_i}, {b_i}$, s.t.
+$a_{i+1}>a{i}$, $b{i+1} < b{i}$, and ${a_i}, {b_i} \to x$, then since the map preserves the order for rational numbers, we can define
+$$
+f(x) = \lim_{i\to\infty}f(a_i) = \lim_{i\to\infty}f(b_i).
+$$
+for irrational numbers. Then using the linear property of limit, it is trivial to prove that this function is a field isomorphism.
+
+First we prove that $\mathcal{F}$ has the Archimedean property.
+If not, suppose for $a, b\in \mathcal{F}$, there do not exist a natural number n, $n\cdot a > b$.
+Suppose $E$ is a bounded set, and $b \in E$, while $a \notin E$.
+According to the Completeness Axiom, $E$ has a supremum, denoted by $x_0$.
+
+suppose $E$ is a bounded set in $\mathcal{F}$, and with the completeness property, $E$ has a supremum, denoted by $x_0$. 
+According to properties of ordered field, there exists $a_0$,
 

### 2017-09-01 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

@@
 \textbf{Solution:}
-
+\begin{proof}
+Let $E$ be any upper bounded set in $\mathcal{F}$. Let $T$ be the set of all upper bounds of $E$. Select $x_1 \in E$, $y_1 \in T$, and we construct two sequences like this:
+$$
+x_2 = \left\{
+\begin{aligned}
+&x_1, ~\frac{x_1+y_1}{2}\in T, \\
+&\frac{x_1+y_1}{2}, ~\frac{x_1+y_1}{2}\in E
+\end{aligned}
+\right.
+$$
+$$
+y_2 = \left\{
+\begin{aligned}
+&\frac{x_1+y_1}{2}, ~\frac{x_1+y_1}{2}\in T \\
+&y_1, ~\frac{x_1+y_1}{2}\in E
+\end{aligned}
+\right.
+$$
+Let $\{z_n\} = \{x_1, y_1, y_2, x_2,\cdots\}$, let $\xi = y_1-x_1$, then according to Archimedean property, for $\forall \epsilon > 0$, there exists a $N > 0$, $\forall m, n > N$, $|z_m-z_n| < \frac{\xi}{2^N} < \epsilon$.
+Thus $\{z_n\}$ is a Cauchy sequence, so it convergent to $z$.
+\\
+Now we prove that $z$ is the supremum of $E$.
+First, we have $\{x_i\} \le z \le \{y_i\}$, or if there exists $n$, s.t.
+$x_n > z$, then with the monotoness of $\{x_i\}$, for $\forall m > n$, $|x_m - z| \le |x_n-z|$, which contradicts with that $\{x_n\}\subset\{z_n\}\to z$.
+In fact this already contains that $z$ is the minimal element of $T$, whichi means $z$ is the supremum of $E$.
+Thus we proved the Completeness Axiom.
+\end{proof}
 \bigskip
@@
 \textbf{Existence:} \\
+We construct the function like this: \\
+According to the properties of fields, there exists $0_1, 1_1\in \mathcal{F}_1,~ 0_2, 1_2\in \mathcal{F}_2$, 
 Since $\mathcal{F}_1, \mathcal{F}_2$ are fields, they close to multiplications.
@@
 If $x$ is an irrational number, if we can construct two monotone sequences of rational numbers ${a_i}, {b_i}$, s.t.
-$a_{i+1}>a{i}$, $b{i+1} < b{i}$, and ${a_i}, {b_i} \to x$, then since the map preserves the order for rational numbers, we can define
+$a_{i+1}>a_{i}$, $b_{i+1} < b_{i}$, and ${a_i}, {b_i} \to x$, then since the map preserves the order for rational numbers, we can define
 $$

### 2017-09-04 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\labelenumi{\arabic{enumi}.}
\def\theenumi{\arabic{enumi}}
\def\labelenumii{(\alph{enumii})}
\def\theenumii{\alph{enumii}}
\def\p@enumii{\theenumi.}
\def\labelenumiii{\arabic{enumiii}.}
\def\theenumiii{\arabic{enumiii}}
\def\p@enumiii{(\theenumi)(\theenumii)}
\def\labelenumiv{\arabic{enumiv}.}
\def\theenumiv{\arabic{enumiv}}
\def\p@enumiv{\p@enumiii.\theenumiii}
\pagestyle{plain}
\setcounter{secnumdepth}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 2\\Thursday, August 31, 2017}\bigskip
\end{center}

\noindent\textbf{Instructions}: You may submit this homework ``the old fashion'' way, i.e., using paper and pencil (or pen), but if you do so, please use at least one sheet of ($8\frac{1}{2}%
\times11$) paper per problem. Write your name at the top of each sheet you
use. Please write neatly. Staple the sheets together or use a paper clip.

However, I encourage you to do at least some of the problems using LaTeX.  As of the third assignment, you will have to submit your homework in LaTeX.

\noindent If you use results from books, Royden or others, please be explicit about what results you are using.

\begin{center}
\emph{Homework 2 is due by the start of class on Wednesday, September 13.}
\end{center} 
\medskip

\begin{enumerate}
\item Recall the unconventional terminology I introduced in class: If $J$ is an infinite set and $f:J\to \mathbb{R}$ is a real-valued function, then the symbol $\sum_{j\in J} f(j)$ is the series determined by $J$, with terms $f(j)$.  We say $\sum_{j\in J} f(j)$ \emph{converges to $S$ unconditionally} if for every $\epsilon > 0$ there is a finite subset $F_0 \subset J$ such that if $F$ is any finite subset of $J$ that contains $F_0$, then $|\sum_{j\in F} f(j) - S|< \epsilon$. Show that if $\sum_{j\in J} f(j)$ converges to some $S$ unconditionally, then $\{j\in J \mid f(j)\neq 0\}$ is countable.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\begin{proof} 
According to the assumption, $\forall \epsilon > 0$, there is a finite subset $F_0$, $\forall$ finite $F\supset F_0$, $-\epsilon-(\sum_{j\in F_0}f(j)-S) < \sum_{j\in F\setminus F_0}f(j) < \epsilon-(\sum_{j\in F_0}f(j)-S)$. Denote $\alpha = \epsilon-(\sum_{j\in F_0}f(j)-S)$. \\[2pt]
Suppose that $E$ = $\{j\in J|f(j)\ne 0\}$ is uncountable, denote $E_1 = \{j\in J|f(j) > 0\}$, $E_2 = \{j\in J|f(j) < 0\}$, then $E = E_1+E_2$. Then either $E_1$ or $E_2$ is uncountable, otherwise $E$ is countable. We may assume that $E_1$ is uncountable. We can construct a sequence of subsets $\{F_n\}$ like this: \\[2pt]
First, $F_1 = \{j\in J|f(j) > \alpha\}$ is countable, otherwise $F_1\setminus F_0$ is uncountable, which means we can find a finite set from $F_1\setminus F_0$, s.t. $\sum_{j\in F_1\setminus F_0}f(j) > \alpha$. Similarly, $F_{n+1} = \{j\in J|f(j) > \frac{\alpha}{2^n}\}$ are all countable, which means $G_n = E_1 - F_{n+1}$ is uncountable. However, since the countable sum of countable sequences is also countable, so $\lim_{n\to\infty}G_n = \{j\in J|f(j)\le 0\}$ is uncountable, and it contradicts to the assumption. So there must exist a $k > 0$, $F_k$ is uncountable, and thus $F_k \setminus F_0$ is uncountable. Thus we can select $2^k$ elements from $F_k$, and their sum is larger then $\alpha$, and it also contradicts with our assumption.
\end{proof}
\bigskip

\item Assume now that $J$ is countably infinite and show that the following assertions about a series $\sum_{j\in J} f(j)$ are equivalent:
\begin{enumerate}
\item The series $\sum_{j\in J} f(j)$ converges unconditionally.
\item For each bijection $\phi:\mathbb{N}\to J$, the series $\sum_{k = 1}^{\infty} f\circ(\phi(k))$ converges in the sense discussed in the text, and that the sum is the sum of $\sum_{j\in J} f(j)$.
\item The series of absolute values $\sum_{j\in J} |f(j)|$ converges.
\end{enumerate}

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\begin{proof}
Since $J$ is countably infinite, we may assume $J = \{j_i\}_{i=0}^{\infty}$. \\[2pt]
\textbf{(a) $\to$ (b):}
Since $\sum_{j\in J}f(j)$ converges unconditionally, $\forall \epsilon > 0$, $\exists$ a finite set $F_0$, $\forall F\supset F_0$,
$$
\left|\sum_{j\in F}f(j)-\sum_{i=1}^{\infty}f(j_i)\right|<\epsilon.
$$
Since $\phi$ is a bijection, there $\exists N > 0$, $\phi(\{1, 2, \cdots, N\})\supset F_0$. Denote $\phi(\{1, 2, \cdots, N\}) = F$, then
$$
\left|\sum_{i=1}^{N}f(\phi(i))-\sum_{i=1}^{\infty}f(j_i)\right| = \left|\sum_{i=1}^{N}f(\phi(i))-\sum_{i=1}^{\infty}f(\phi(j_i))\right| < \epsilon.
$$
Thus the series converges, and the sum is $\sum_{j\in J}f(j)$. \\[2pt]
\textbf{(b) $\to$ (c):}
Denote $A = \{i|f(j_i) > 0\}, B = \{i|f(j_i) < 0\}$. If $\#A < \infty$, then $S_1 = \sum_{i\in A} f(i) < \infty$. We can set the bijection as $\phi(i) = k\in A, ~1\le i \le \#A$, and make the rest part a bijection to $B$. Since the series converges, we can know that $\sum_{i\in B} f(i)$ converges. Thus $\sum|f(j)| \le S1+\sum_{i\in B}f(i)$ also converges. Similarly, if $\#B < \infty$ we can get the same result. If $\#A, \#B = \infty$, we can

\textbf{(c) $\to$ (a):}
If $\sum_{j\in J}|f(j)|$ converges, then $\forall \epsilon > 0$, there $\exists N > 0$, s.t. $\sum_{i= N}^{\infty} |f(j_i)| \le \epsilon$. Then for this $\epsilon$, we take $F_0 = \{a_1, a_2, \cdots, a_{N-1}\}$, then 
\end{proof}
\bigskip

\item \begin{enumerate}
\item Show that the series \[
\sum_{n\geq 1, n\neq m} \frac{1}{m^2 - n^2}\]is convergent and has sum equal to $-\frac{3}{4m^2}$ (decompose the rational fraction $1/(m^2 - x^2)$).
\item Let $u_{mn} = \frac{1}{m^2 - n^2}$ if $m\neq n$, and let $u_{nn} = 0$. Show that \[
\sum_{m=0}^{\infty}\left(\sum_{n=0}^{\infty} u_{mn}\right) = -\sum_{n=0}^{\infty}\left(\sum_{m=0}^{\infty} u_{mn}\right) \neq 0.\]
\item Explain what, if anything, the computations of parts a) and b) of this problem have to do with Problem 2.
\end{enumerate}

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\begin{proof}
\textbf{(a)} \\[2pt]

\end{proof}
\bigskip

\item (Problems 17, 18, and 19, page 43) These problems tie well together, so I thought I would make them one big problem.

\begin{enumerate}
\item Show that a set $E$ is measurable if and only if for each $\epsilon > 0$, there is a closed set $F$ and an open set $\mathcal{O}$ for which $F\subseteq E \subseteq \mathcal{O}$ and $m^*(\mathcal{O} \sim F)< \epsilon.$
\item Suppose $E$ is a set with finite outer measure. Show that there is a $G_{\delta}$ set $G$ such that $
 E \subseteq G \text{ and } m^*(E) = m(G).$  Show that $E$ is measurable if and only if there is an $F_{\sigma}$ set $F$ contained in $E$ such that $m(F) = m^*(E)$.
\item Suppose $E$ is a set with finite outer measure. Show that if $E$ is \emph{not} measurable then there is an open set $\mathcal{O}$ containing $E$ that has finite outer measure for which \[
m^*(\mathcal{O}\sim E) > m^*(\mathcal{O}) - m^*(E).                                                                                                                                                                                                
                                                                                                                                                                                               \]

\end{enumerate}

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item (Problem 28, Page 47) Show that continuity of measure together  with finite additivity of measure implies countable additivity of measure.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\end{enumerate}
\end{document}

### 2017-09-05 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update

@@
 \textbf{(b) $\to$ (c):}
-Denote $A = \{i|f(j_i) > 0\}, B = \{i|f(j_i) < 0\}$.
-If $\#A < \infty$, then $S_1 = \sum_{i\in A} f(i) < \infty$.
-We can set the bijection as $\phi(i) = k\in A, ~1\le i \le \#A$, and make the rest part a bijection to $B$.
-Since the series converges, we can know that $\sum_{i\in B} f(i)$ converges.
-Thus $\sum|f(j)| \le S1+\sum_{i\in B}f(i)$ also converges.
-Similarly, if $\#B < \infty$ we can get the same result.
-If $\#A, \#B = \infty$, we can
-
-\textbf{(c) $\to$ (a):}
-If $\sum_{j\in J}|f(j)|$ converges, then $\forall \epsilon > 0$, there $\exists N > 0$, s.t.
-$\sum_{i= N}^{\infty} |f(j_i)| \le \epsilon$.
-Then for this $\epsilon$, we take $F_0 = \{a_1, a_2, \cdots, a_{N-1}\}$, then
+According to (b) we have $\sum_{k=1}^{\infty}f(j_k)$ converges.
+Suppose $\sum_{j\in J}|f(j)|$ does not converge, we first prove that $\sum_{k=1}^{\infty}f(j_k)^+$ and $\sum_{k=1}^{\infty}f(j_k)^-$ do not converge, where $f(j_k)^+, f(j_k)^-$ means the absolute value of positive and negative terms in $f(j)$, seperately.
+\\[2pt]
+Suppose $\sum_{k=1}^{\infty}f(j_k)+$ converges, then since
+$$
+\sum_{k=1}^{\infty}f(j_k)^- = \sum_{k=1}^{\infty}f(j_k)^+-\sum_{k=1}^{\infty}f(j_k),
+$$
+we know that $\sum_{k=1}^{\infty}f(j_k)^-$ converges, which means
+$$
+\sum_{k=1}^{\infty}|f(k_j)| = \sum_{k=1}^{\infty}f(k_j)^++\sum_{k=1}^{\infty}f(k_j)^-
+$$
+also converges, which lead to a contradiction. \\[2pt]
+Thus we can rearrange the order of $\sum_{j\in J}f(j)$ like this: for each $f(a_i) > 0$, put enough $f(b_i) < 0$ after it, making $f(a_i) + \sum_{i}f(b_i) < 1$.
+The possibility of this map comes from that $\sum_{j}f(j)^-\to\infty$.
+Then we constructed a bijection from $\mathbb{N}\to J$.
+However, $\sum_{j}\phi(f(j)) < \sum_{j_i}-1\to -\infty$, which makes a contradiction.
+Thus $\sum_{j}|f(j)|$ converges.
+\\[2pt]
+\textbf{(c) $\to$ (a):} Since the series of absolute values $\sum_{j\in J}|f(j)|$ converges, we have the original series $\sum_{j\in J}|f(j)|$ converges, and mark that sum as $S$.
+Then according to the definition, for $\forall \epsilon > 0$, there $\exists N > 0$, $\sum_{i=N}^{\infty}|f(j_i)| < \epsilon$.
+If we take $F_0 = \{j_1, j_2, \cdots, j_{N-1}\}$, then $\forall$ finite $F\supset F_0$, $\sum_{j\in F\setminus F_0} f(j) \le \sum_{i=N}^{\infty}|f(j_i)|< \epsilon$.
+That means (a) holds.
 \end{proof}
@@
 \textbf{(a)} \\[2pt]
-
+$$
+\begin{aligned}
+\sum_{n\ne m}\frac{1}{m^2-n^2} &= -\frac{1}{2m}\sum_{n\ne m}\left(\frac{1}{n-m}-\frac{1}{n+m} \right)\\
+&=-\frac{1}{2m}(-\frac{1}{m-1}-\frac{1}{m+1}-\cdots-1-\frac{1}{2m-1}\\
+&\quad + 1-\frac{1}{2m+1}+\cdots+\frac{1}{m}-\frac{1}{3m}\\
+&\quad + \frac{1}{m+1}-\frac{1}{3m+1}+\cdots+\frac{1}{2m}-\frac{1}{4m}+\cdots) \\
+&= -\frac{1}{2m}\left(\lim_{n\to\infty}(-\sum_{i=-m}^{m}\frac{1}{n+i}) + \frac{1}{m} + \frac{1}{2m}\right) \\
+&= -\frac{3}{4m}.
+\end{aligned}
+$$
+\\
+\textbf{(b)} 
+According to (a),
+$$
+\sum_{n=0}^{\infty}u_{mn} = -\frac{3}{4m^2}+\frac{1}{m^2} = \frac{1}{4m^2}, ~\sum_{m=0}^{\infty}u_{mn} = -\frac{1}{4n^2}.
+$$
+Thus
+$$
+\sum_{m=0}^{\infty}\left(\sum_{n=0}^{\infty} u_{mn}\right) = -\sum_{n=0}^{\infty}\left(\sum_{m=0}^{\infty} u_{mn}\right) = \sum_{n=1}^{\infty}\frac{1}{4n^2}\ne 0.
+$$
+\\
+\textbf{(c)}
 \end{proof}

### 2017-09-05 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update
update assignment 1'

@@
 \bigskip
-\textbf{Collaborators:} 
+\textbf{Collaborators:} One of my undergraduate classmate;
 \smallskip
@@
 \textbf{Existance:} \\
-Let $a_1 = \lfloor px\rfloor$, $a_2 = \lfloor p^2x-a_1p\rfloor$, $\cdots$, $a_n = \lfloor p^nx - \sum_{i=1}^{n-1}a_ip^{n-i}\rfloor=-$.
+Let $a_1 = \lfloor px\rfloor$, $a_2 = \lfloor p^2x-a_1p\rfloor$, $\cdots$, $a_n = \lfloor p^nx - \sum_{i=1}^{n-1}a_ip^{n-i}\rfloor$.
 From this inductive construction we know that the subsum $S_n = \sum_{i=1}^n\frac{a_i}{p^i}$ forms a increasing sequence, while it is upper bounded by $x$.
@@
 For $x \in \mathcal{F}_1$, if $x$ is not a rational number, we call it an irrational number.
-If $x$ is an irrational number, if we can construct two monotone sequences of rational numbers ${a_i}, {b_i}$, s.t.
+Since $\mathcal{F}$ has the Archimedean property(WHICH I DIDN'T PROVE), the rational numbers are density in $\mathcal{F}$.
+So $\forall x\in \mathcal{F}$, if $x$ is an irrational number, we can construct two monotone sequences of rational numbers ${a_i}, {b_i}$, s.t.
 $a_{i+1}>a_{i}$, $b_{i+1} < b_{i}$, and ${a_i}, {b_i} \to x$, then since the map preserves the order for rational numbers, we can define
@@
 
-First we prove that $\mathcal{F}$ has the Archimedean property.
+% First we prove that $\mathcal{F}$ has the Archimedean property.
 If not, suppose for $a, b\in \mathcal{F}$, there do not exist a natural number n, $n\cdot a > b$.
@@
 
-suppose $E$ is a bounded set in $\mathcal{F}$, and with the completeness property, $E$ has a supremum, denoted by $x_0$. 
-According to properties of ordered field, there exists $a_0$,
+% suppose $E$ is a bounded set in $\mathcal{F}$, and with the completeness property, $E$ has a supremum, denoted by $x_0$. 
+% According to properties of ordered field, there exists $a_0$,
 

### 2017-09-06 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update assignment 1'
update
add problem 4.a, 4.b

@@
 \textbf{(c)}
+The computation of (b) has the same principle as (c)$\to$(b) in prob. 2.
 \end{proof}
@@
 \textbf{Solution:}
+\begin{proof}
+\textbf{(a):}\\[2pt]
+\textbf{Sufficiency:}
+For $\forall A\subset \mathbb{R}$, first we have $m^*(A) \le m^*(A\cap E) + m^*(A\cap E^c)$.
+So we only need to show that $m^*(A) \ge m^*(A\cap E) + m^*(A\cap E^c)$.
+According to assumption, $m^*(A\cap E) + m^*(A\cap E^c) \le m^*(A\cap O)+m^*(A\cap F^c) < m^*(A\cap O)+m^*(A\cap O^c)+\epsilon$.
+Since the open set $O$ is measurable, we have $m^*(A\cap )+m^*(A\cap O^c) = m^*(O)$.
+Thus by the arbitrariness of $\epsilon$, we know that $m^*(A) = m^*(A\cap E)+m^*(A\cap E^c)$.
+\\[2pt]
+
+\textbf{Necessity:} We first show that $\forall \epsilon > 0$, we can find an open set $O\supset E$, s.t. $m^*(O\setminus E) < \epsilon$. \\[2pt]
+First, if $m^*(E) <\infty$. Then according to definition of outer measure, $\forall\epsilon > 0$, there is an open cover $\{O_i\}$ of $E$, s.t. 
+$$
+\sum_{i}m^*(O_i) < m^*(E)+\epsilon.
+$$
+Let $O = \bigcup_{i}O_i$, then $m^*(O) < m^*(E)+\epsilon$, and $O$ is an open set. Thus 
+$$
+m^*(O\setminus E) = m^*(E)-m^*(E\cap O) = m^*(O)-m^*(E) < \epsilon.
+$$
+If $m^*(E) = \infty$, define $E_{n} = \{x\in E:|x|\le n\}$. Then $E_n$ is measurable with finite outer measure, the argument above shows that there is an open set $O_k\supset E_k$, s.t.
+$$
+m^*(O_k\setminus E_k) < \frac{\epsilon}{2^k}.
+$$
+Then $O = \bigcup_{k} O_k$ is an open set that contains $E$, and 
+$$
+m^*(O\setminus E) = m^*\left(\bigcup_{k}O_k\setminus E\right)\le\sum_{k}m^*(O_k\setminus E)\le\sum_{k}m^*(O_k\setminus E_k)<\epsilon.
+$$
+So there is an open set $O\supset E$, s.t.
+$m^*(O\setminus E) < \frac{\epsilon}{2}$.
+Meanwhile, since $E^c$ is measurable, there is an open set $G\supset E^c$, s.t.
+$m^*(G\setminus E^c)<\frac{\epsilon}{2}$.
+Thus we have a closed set $F = G^c$, and $O\supset E\supset F$,
+$$
+m^*(O\setminus F) \le m^*(O\setminus E)+m^*(E\setminus F) = m^*(O\setminus E)+m^*(G\setminus E^c) < \epsilon.
+$$
+\\[2pt]
+\textbf{(b):}
+From (a) we know that $\forall \epsilon > 0$, there exists an open set $G$ and a closed set $F$, s.t. $G\supset E\supset F$. So 
+$$
+m(G\setminus E) \le m(G\setminus F) < \epsilon, ~m(E\setminus F) \le m(G\setminus F) < \epsilon.
+$$
+Thus we can construct two series of sets $\{G_k\}$ and $\{F_k\}$:
+$$
+G_k\supset E\supset F_k, ~m(G_k\setminus E) < \frac{\epsilon}{2^k}, ~m(E\setminus F_k) < \frac{\epsilon}{2^k}.
+$$
+Thus $G = \bigcap G_k$ is a $G_\delta$ set, and $F = \bigcup F_k$ is a $F_\sigma$ set, and
+$$
+m(G) - m^*(E) \le m(G\setminus E) < \frac{\epsilon}{2^n}, ~m^*(E)-m(F)\le m(E\setminus F) < \frac{\epsilon}{2^n}.
+$$
+Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$. \\[2pt]
+\textbf{(c):}
+
+\end{proof}
 \bigskip

### 2017-09-06 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex

@@
 $$
-Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$. \\[2pt]
+Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$.
+
+On the other hand, suppose there exists a $F_\sigma$ set $F$ contained in $E$, s.t.
+$m(F) = m^*(E)$.
+Then similar to the process of (a), $\forall \epsilon > 0$, there is an open set $G\supset E$, s.t.
+$m^*(G\setminus E) < \epsilon$.
+Thus $m^*(G\setminus F) < m^*(G\setminus E) + m^*(E\setminus F) < \epsilon$.
+Then $E$ is a measurable set.
+
 \textbf{(c):}
-
+Fisrt there exist an open set $O\supset E$ which has finite outer measure.
+Suppose for each open set $O$ containing $E$ that has finite outer measure, 
+$$
+m^*(O\setminus E) \le m^*(O)-m^*(E).
+$$
+Then we have
+$$
+m^*(O\setminus E) = m^*(O)-m^*(E)
+$$
+according to the properties of outer measures. 
+So according to the definition of outer measures, $\forall \epsilon > 0$, there is an open set $O\supset E$, s.t.
+$m^*(O)-m^*(E) < \epsilon$.
+This leads to $m^*(O\setminus E) < epsilon$.
+Accoding to Theorem 11 on Page 40, $E$ is measurable, which makes an contradiction.
+% Denote $\{O_k\}$ to be the set of open sets containing $E$, then $O = \bigcap O_k$ is the smallest $G_\sigma$ set containing $E$, but 
 \end{proof}

### 2017-09-07 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update

@@
 \textbf{Solution:}
+\begin{proof}
+Let $\{A_k\}_{k=1}^\infty$ be a set of disjoint measurable sets. Denote $B_k = \bigcup_{i=1}^k A_i$, then $\{B_k\}$ is an ascending sequence of measurable sets, and 
+$$
+m(B_k) = \sum_{i=1}^k m(A_i).
+$$
+According to the continuity of measure, 
+$$
+m\left(\bigcup_{k=1}^{\infty}A_k \right) = m\left(\bigcup_{k=1}^\infty B_k\right) = \lim_{k\to\infty}m(B_k) = \lim_{k\to\infty}\sum_{n=1}^n m(A_k) = \sum_{k=1}^{\infty}m(A_k).
+$$
+It shows the countable additivity of measure.
+\end{proof}
 \bigskip

### 2017-09-13 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\labelenumi{\arabic{enumi}.}
\def\theenumi{\arabic{enumi}}
\def\labelenumii{(\alph{enumii})}
\def\theenumii{\alph{enumii}}
\def\p@enumii{\theenumi.}
\def\labelenumiii{\arabic{enumiii}.}
\def\theenumiii{\arabic{enumiii}}
\def\p@enumiii{(\theenumi)(\theenumii)}
\def\labelenumiv{\arabic{enumiv}.}
\def\theenumiv{\arabic{enumiv}}
\def\p@enumiv{\p@enumiii.\theenumiii}
\pagestyle{plain}
\setcounter{secnumdepth}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 3\\Monday, September 11, 2017}\bigskip
\end{center}

\noindent\textbf{Instructions}: This and all subsequent homeworks must be submitted written in \LaTeX.

\noindent If you use results from books, Royden or others, please be explicit about what results you are using.

\begin{center}
\emph{Homework 3 is due by midnight, Friday, September 22.}
\end{center} 
\medskip

\begin{enumerate}
\item  (Problem 34, Page 53) Show that there is a continuous, strictly increasing function on the interval $[0, 1]$ that maps a
set of positive measure onto a set of measure zero.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
Let $C$ be the Cantor set on $[0, 1]$, and $\varphi(x)$ be the Cantor function. Define
$$
\phi(x) = \varphi(x)+x, ~x\in C.
$$
We now show $\phi^{-1}(x)$, the inverse of $\phi(x)$, satisfies the properties in the problem.
First, since $\phi(x)$ is a continuous, strictly increasing function on $[0, 1]$, thus is continuous and strictly increasing on $C\subset [0, 1]$.

Denote $D = \phi(C)$, then according to theorems in the book, $m(D) = 1$. $\forall x_1 < x_2\in D$, if $\phi^{-1}(x_1) \ge \phi^{-1}(x_2)$, then since $\phi$ is strictly increasing, $\phi(\phi^{-1}(x_1)) = x_1+\phi^{-1}(x_1) \ge \phi(\phi^{-1}(x_2)) = x_2+\phi^{-1}(x_2)$, which means $\phi^{-1}(x_1) < \phi^{-1}(x_2)$, leading to a contradictory. Thus $\phi^{-1}$ is strictly increasing.

On the other hand, $\forall x_0 \in D, \forall \epsilon > 0$, since $\phi$ is continuous on $C$, then $\forall \delta > 0, ~\exists\epsilon_1 > 0, ~\forall y\in C, ~|y-\phi^{-1}(x_0)| < \epsilon_1, ~|\phi(y)-x_0| < \delta$. Denote $\epsilon_1 = \min(\epsilon_1, \epsilon)$, then $\forall y\in C, ~|y-\phi^{-1}(x_0)| < \epsilon_1, ~|\phi(y)-x_0| < \delta$. Thus according to properties of strictly increasing bijection, $\forall x\in D, ~|x-x_0| < \delta, ~|\phi^{-1}(x)-\phi^{-1}(x_0)| < \epsilon_1\le \epsilon$. It means that $\phi^{-1}$ is continuous on $D$.

Since $C$ is measure zero, we get a function satisfying the properties in the problem.
\bigskip

\item (Problem 37, Page 53) Let $f$ be a continuous function defined on $E$. Is it true that $f^{-1}(A)$ is always measurable if $A$ is measurable?

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}

\bigskip

\item  (Problem 39, Page 53) Let $F$ be the subset of $[0, 1]$ constructed in the same manner as the Cantor set except that
each of the intervals removed at the nth deletion stage has length $\alpha 3^{-n}$ with $0 < a < 1$. Show
that $F$ is a closed set, $[0, 1]\sim F$ dense in $[0,1]$, and $m(F) = 1- a$. Such a set F is called a \emph{generalized Cantor set}.

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item Let $C$ be the Cantor set and let $\varphi$ be the Cantor-Lebesgue function.
\begin{enumerate}
\item Show that $C$ consists of all $x\in [0,1]$ whose  ternary expansion has coefficients equal to $0$ or $2$, i.e., if $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0, 1, \text{or } 2$, then $x\in C$ if and only if $c_k = 0 \text{ or } 2$. 
\item Show that if $x\in C$ and $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0 \text{ or } 2$, then $\varphi(x) = \sum_{k\geq 1} (\frac{1}{2} c_k) 2^{-k}$.
\end{enumerate}
\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item  Construct a Cantor-type subset of $[0,1]$ by removing from each interval remaining at the $k^{\text{th}}$ stage, a subinterval of relative length $\theta_k$, $0 < \theta_k < 1$. Show that the remainder has measure zero if and only if $\sum_{k\geq 1} \theta_k = \infty$.  (Use the fact that for $a_k > 0$, the product $\Pi_{k = 1}^{\infty} a_k$ converges, in the sense that $\lim_{n\to \infty} \Pi_{k=1}^N a_k$ exists and  is not zero, if and only if $\sum_{k =1}^{\infty} \ln a_k$ converges.)

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item Let $Z$ be a set of measure zero in $\mathbb{R}$.  What is the measure of $\{x^2 \mid x\in Z\}$?

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
$X = \{x^2\mid x\in Z\}$ is also measure 0.

On one hand, we can define a map 
$$
\begin{aligned}
\phi: X &\to Z, \\
x&\mapsto \sqrt{x}, \quad\text{if}~ \sqrt{x}\in Z. \\
x&\mapsto -\sqrt{x}, \quad\text{if}~ \sqrt{x}\notin Z ~\text{and}~ -\sqrt{x}\in Z.
\end{aligned}
$$
Then it is a bijection from $X$ to a subset of $Z$.

On the other hand, the map
$$
\begin{aligned}
\varphi: Z &\to X
\end{aligned}
$$
\bigskip

\item  Let $0.\alpha_1 \alpha_2 \cdots$ be the dyadic development of any $x\in[0,1]$. Let $k_1,k_2,k_3,\ldots$ be a fixed permutation of the positive integers $1,2,\ldots$, and consider the transformation $T$ which sends $x = \alpha_1\alpha_2\alpha_3\cdots$ to $Tx: = \alpha_{k_1}\alpha_{k_2}\alpha_{k_3}\cdots$. Show that if $E$ is a measurable subset of $[0,1]$ then its image under $T$, $T(E)$, is also measurable and that $m(T(E))= m(E)$.  That is, show that $T$ is a measure preserving transformation of $[0,1]$. [Consider first the special case where $E$ is a dyadic interval of the form $(s2^{-k}, (s+1)2^{-k})$ and $s = 0,1,\ldots, 2k-1$.  Then think about open sets and note that each open set can be written as a countable union of non-overlapping half-open dyadic intervals.]

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\end{enumerate}
\end{document}

### 2017-09-14 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

@@
 
-On the other hand, $\forall x_0 \in D, \forall \epsilon > 0$, since $\phi$ is continuous on $C$, then $\forall \delta > 0, ~\exists\epsilon_1 > 0, ~\forall y\in C, ~|y-\phi^{-1}(x_0)| < \epsilon_1, ~|\phi(y)-x_0| < \delta$.
-Denote $\epsilon_1 = \min(\epsilon_1, \epsilon)$, then $\forall y\in C, ~|y-\phi^{-1}(x_0)| < \epsilon_1, ~|\phi(y)-x_0| < \delta$.
-Thus according to properties of strictly increasing bijection, $\forall x\in D, ~|x-x_0| < \delta, ~|\phi^{-1}(x)-\phi^{-1}(x_0)| < \epsilon_1\le \epsilon$.
-It means that $\phi^{-1}$ is continuous on $D$.
+On the other hand, $\forall x_0 \in D, \forall \epsilon > 0$, we need to show that $\exists\delta > 0, ~\forall x_1\in D, ~|x_1-x_{0}| < \delta$, then $|\phi^{-1}(x_1)-\phi^{-1}(x)| < \epsilon$.
+Denote $y_1 = \phi(\min\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\}), ~y_2 = \phi(\max\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\})$, then let $\delta = \min{y_1-x_0, y_2-x_0}$, we have $\forall |x-x_0|< \delta$, $|\phi^{-1}(x)-\phi^{-1}(x_0)| < \epsilon$.
+Thus $\phi^{-1}$ is continuous on $D$.
 
@@
 
-\textbf{Solution:}
+\textbf{Solution:} It is not true.
+
+We may consider the function $\psi(x)$ defined by Proposition 21 on Page 52.
+It is a strictly increasing continuous function, and it maps a measurable set $A\subset C$, onto a nonmeasurable set.
+Thus if we consider $\psi^{-1}(x)$, it has been proved as a strictly increasing continuous function in Problem 1.
+Then $\psi^{-1}(A)$ is nonmeasurable.
 
@@
 \textbf{Solution:}
+First, we denote $F_1 = \left[0, \frac{3-\alpha}{6}\right]\cup \left[1-\frac{3-\alpha}{6}, 1\right]$.
+With the same process of constructing the Cantor set, we have a collection of $F_n$.
+We define the generalized Cantor set as
+$$
+F = \bigcap_{k=1}^{\infty}F_n.
+$$
+Since each $F_n$ is a closed set, we have $F$ as well closed.
+Then $F_n$ is the disjoint of union of $2^n$ intervals, each of length $(1-\alpha)\frac{1}{2^n}+\frac{\alpha}{3^n}$.
+By the finite additivity of Lebesgue measure,
+$$
+m(F_k) = 1-\alpha + \left(\frac{2}{3}\right)^n\alpha.
+$$
+According to the continuity of measure, we have $m(F) = \lim_{k\to\infty}m(F_k) = 1-\alpha$.
+
+Let $x < y\in [0, 1]$.
+If $y\notin F_k$ for one of the $k$, then since $[0, 1]\setminus F$ is open, there exists $t < y$ in $N(y)$, s.t.
+$t\in [0, 1]\setminus F$.
+If $x\notin F_k$, it is the same case.
+Now we assume that $x, ~y \in F$.
+If $x, ~y$ are not in the same subset of $F_k$, then $\exists t\in [0, 1]\setminus F$.
+Then we can assume that $x, ~y$ always belong to the same subset.
+However, the subsets make a nested set with the limit of lower bound and the upper bound be the same.
+According to Nested Set Theorem, we have $x = y$.
+Then we have proved that $[0, 1]\setminus F$ is dense.
 \bigskip
@@
 \textbf{Solution:}
+\textbf{(a).} We show by induction that a number belongs to the intervals we removed in each step iff its ternary expasion has a coefficient 1.
+First, the interval removed at the first step can be represented as $(0.1, ~0.2)$.
+Thus $0.1 \notin F$, and $0.0, 0.2\in F$.
+Assume it holds in the first $n$ steps, then the intervals removed at the $n+1$ step has the representation $(0.a_1a_2\cdots a_n1, ~0.a_1a_2\cdots a_n2)$, in which $a_i\in\{0, 2\}$.
+Then each number in this interval has an expansion like
+$$
+0.a_1a_2\cdots a_n1a_{n+1}\cdots.
+$$
+Thus each number in $F$ has a coefficient 1 in its expansion.
+According to the construction process, we can also know that the reverse also holds. Thus the proposition holds.
+
+\textbf{(b)}. 
+According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step.
+Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
 \bigskip
@@
 \textbf{Solution:}
+Denote $F_n$ as the remained set after $n$ steps. Then according to the construction, we have 
+$$
+m(F_n) = \prod_{i=1}^{n}(1-\theta_i).
+$$
+First we have $\sum_{n=1}^{\infty}-\theta_n$ and $\sum_{n=1}^{\infty}\ln(1-\theta_n)$ be both negative-term series, and the necessity of their convergence is $\lim_{n\to\infty}\theta_n = 0$.
+On the other hand, when $\lim_{n\to\infty} \theta_n = 0$,
+$$
+\lim_{n\to\infty}\frac{\ln(1-\theta_n)}{-\theta_n} = 1,
+$$
+thus that $\sum{\ln(1-\theta_n)}$ converges is equivalent to the convergence of $\sum{-\theta_n}$.
+
+Then according to the continuity of measure,
+$$
+\begin{aligned}
+m(F) > 0 \Leftrightarrow m(\lim_{n\to\infty}F_n) > 0 \Leftrightarrow \prod_{i=1}^{\infty}(1-\theta_i) ~\text{converges} \Leftrightarrow \sum_{i=1}^{\infty} \ln(1-\theta_i) ~\text{converges} \\
+\Leftrightarrow \sum_{i=1}^{\infty}\theta_i ~\text{converges}.
+\end{aligned}
+$$
+Thus $m(F) = 0$ iff $\sum{\theta_i} = \infty$.
+
 \bigskip

### 2017-09-14 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
add prob 6

@@
 
-On one hand, we can define a map 
+First, if the set $Z$ is bounded, which means $Z\in [0, M]$.
+Since $m(Z) = 0$, $\forall \epsilon > 0$, there exists an open cover $\{O_i\} = \{(a_i, b_i)\}$, s.t.
+$m^*(\cup\{O_i\}\setminus Z) < \epsilon$.
+Thus $\{(a_i^2, b_i^2)\}$ is an open cover of $X$, and $m^*(\cup(a_i^2, b_i^2)\setminus X) \le M\sum(b_i-a_i) < M\epsilon$.
+Thus now $X$ is a measure-zero set.
+When $Z \in [-M, 0]$, with the same process above, we can know that $X$ is a measure-zero set.
+Then when $Z \in [-M, M]$, we know $X$ is also measure zero.
+
+Since $Z$ is measure zero, for $\forall \epsilon > 0$ and integer $n > 0$, we have $m(Z\cap [-n, n]) < 2^{-n}\epsilon$.
+Thus from the discussion above we have $m(X\cap [-n^2, n^2]) < 2^{-n}\epsilon$.
+Since
 $$
-\begin{aligned}
-\phi: X &\to Z, \\
-x&\mapsto \sqrt{x}, \quad\text{if}~ \sqrt{x}\in Z. \\
-x&\mapsto -\sqrt{x}, \quad\text{if}~ \sqrt{x}\notin Z ~\text{and}~ -\sqrt{x}\in Z.
-\end{aligned}
+X = \bigcup_{n=1}^{\infty}X\cap[-n, n],
 $$
-Then it is a bijection from $X$ to a subset of $Z$.
-
-On the other hand, the map
+with the addivity of measure, 
 $$
-\begin{aligned}
-\varphi: Z &\to X
-\end{aligned}
+m(X) < \sum_{n=1}^{\infty}2^{-n}\epsilon = \epsilon.
 $$
+With the arbitrariness of $\epsilon$, we have $m(X) = 0$.
 \bigskip
@@
 \textbf{Solution:}
+
 \bigskip

### 2017-09-14 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

@@
 \textbf{Solution:}
+Consider the intervals $E_k^i = [i\cdot2^-{k}, ~(i+1)2^{-k})$. Then
+$$
+T[E_k] = \bigcap_{i=1}^{2^k}F_{k_i},
+$$
+where 
+$$
+F_{k_i} = \left\{
+\begin{aligned}
+&[F_{k_{i-1}}.\text{left}, ~F_{k_{i-1}}.\text{mid}), ~\text{if}~ k_i = 0 \\
+&[F_{k_{i-1}}.\text{mid}, ~F_{k_{i-1}}.\text{right}), ~\text{if}~ k_i = 1.
+\end{aligned}
+\right.
+$$
+Then since the finite intersection of closed sets is measurable, we know that $T[E_k]$ is measurable, and we have $m(T(E_k)) = m(E_k)$ since the probability of the numbers with infinite length be seperated into the intervals.
+Then since each open interval can be written as a countable union of non-overlapping half-open dyadic intervals, we know from the discussion above that $T(E)$ is measurable, and $m(T(E)) = m(E)$.
 

### 2017-09-16 Graduate - Numerical Analysis/Assignment 4/main.m
Add assign 4

@@ -1,1 +1,53 @@
-f1 = 
+f1 = @(x)(exp(x)-3*x^2);
+df1 = @(x)(exp(x)-6*x);
+f2 = @(x)(x-1-0.3*cos(x));
+df2 = @(x)(1+0.3*sin(x));
+tol = 1e-6;
+format long;
+
+% f1: Prob 2(a); 
+% ONLY FOR THE NEGATIVE ROOT
+% bisection
+subplot(121);
+a = -1; b = 0;
+[root, index, iteration, error, count] = bisection(f1, a, b, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+hold on;
+% Newton
+x0 = -0.5;
+[root, index, iteration, error, count] = newton(f1, df1, x0, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+hold on;
+% Secant
+x0 = -1; x1 = 0;
+[root, index, iteration, error, count] = secant(f1, x0, x1, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+
+title('Error estimation for e^x-3x^2');
+legend('Bisection', 'Newton', 'Secant');
+
+% f2: Prob 2(d);
+% bisection
+subplot(122);
+a = 0; b = pi/2;
+[root, index, iteration, error, count] = bisection(f2, a, b, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+hold on;
+% Newton
+x0 = 0.5;
+[root, index, iteration, error, count] = newton(f2, df2, x0, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+hold on;
+% Secant
+x0 = 0; x1 = 1;
+[root, index, iteration, error, count] = secant(f2, x0, x1, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
+semilogy(index(1:count), error(1:count));
+
+title('Error estimation for x-1-0.3cos(x)');
+legend('Bisection', 'Newton', 'Secant');

### 2017-09-16 Graduate - Numerical Analysis/Assignment 4/newton.m

@@ -1,20 +1,17 @@
-function [root, index, iteration, error] = newton(f, df, x0, tol)
+function [root, index, iteration, error, count] = newton(f, df, x0, tol)
 % Newton's Method for root extraction;
 % f, df: function and it's derivative;
 % x0: initial point;
 % tol: tolerance;
-count = 1;
-iteration = zeros(100, 1);
-index = (0:1:100)';
-error = zeros(100, 1);
-iteration(1) = x0;
-error(1) = feval(f, x0);
+count = 1; index = (0:1:100)';
+iteration = zeros(100, 1); iteration(1) = x0;
+error = zeros(100, 1); error(1) = abs(x0);
 while(1)
     count = count + 1;
     x1 = x0 - feval(f, x0) / feval(df, x0);
     iteration(count) = x1;
-    error(count) = feval(f, x1);
-    if(abs(x1 - x0) < tol)
+    error(count) = abs(x1-x0);
+    if(abs(x1-x0) < tol)
         root = x1;
         return;
     elseif(count > 100)
@@ -22,5 +19,5 @@ while(1)
         root = x1;
         return;
     end
-    x0 =x1;
+    x0 = x1;
 end

### 2017-09-16 Graduate - Numerical Analysis/Assignment 4/secant.m

@@ -1,22 +1,25 @@
-function [root] = secant(f, x0, x1, tol)
+function [root, index, iteration, error, count] = secant(f, x0, x1, tol)
 % Secant Method for root extraction;
 % f: the function;
 % x0, x1: initial points;
 % tol: tolerance;
-count = 0;
+count = 2; index = (0:1:100)';
+iteration = zeros(100, 1); iteration(1) = x0; iteration(2) = x1;
+error = zeros(100, 1); error(1) = abs(x0); error(2) = abs(x1-x0);
 while(1)
     count = count + 1;
     f0 = feval(f, x0);
     f1 = feval(f, x1);
     x2 = x1 - (x1 - x0)/(f1 - f0) * f1;
-    if abs(x2 - x0) < tol
-        disp(count);
+    iteration(count) = x2;
+    error(count) = abs(x2-x1);
+    if(abs(x2 - x0) < tol)
         root = x2;
-        return
-    elseif count > 100
+        return;
+    elseif(count > 100)
         warning('Count over 100, may not be convergence');
         root = x2;
-        return
+        return;
     end
     x0 = x1;
     x1 = x2;

### 2017-09-18 Graduate - Numerical Analysis/Assignment 2/prob2revised2.m
update

@@ -1,0 +1,4 @@
+function res = prob2revised2(x)
+% prob 2;
+% using Taylor series;
+    res = (x/2+(x.^2)/8+(x.^3)/16)';

### 2017-09-18 Graduate - Numerical Analysis/Assignment 4/main.m

@@ -6,9 +6,9 @@ tol = 1e-6;
 format long;
 
 % f1: Prob 2(a); 
-% ONLY FOR THE NEGATIVE ROOT
+figure(1);
+% FOR THE NEGATIVE ROOT
 % bisection
-subplot(121);
 a = -1; b = 0;
 [root, index, iteration, error, count] = bisection(f1, a, b, tol);
 disp([index(1:count), iteration(1:count), error(1:count)]);
@@ -25,29 +25,71 @@ x0 = -1; x1 = 0;
 [root, index, iteration, error, count] = secant(f1, x0, x1, tol);
 disp([index(1:count), iteration(1:count), error(1:count)]);
 semilogy(index(1:count), error(1:count));
-
-title('Error estimation for e^x-3x^2');
+title('Error estimation for e^x-3x^2, the negative root');
 legend('Bisection', 'Newton', 'Secant');
-
-% f2: Prob 2(d);
+% for the smaller positive root
 % bisection
-subplot(122);
-a = 0; b = pi/2;
-[root, index, iteration, error, count] = bisection(f2, a, b, tol);
+figure(2);
+a = 0; b = 1;
+[root, index, iteration, error, count] = bisection(f1, a, b, tol);
 disp([index(1:count), iteration(1:count), error(1:count)]);
 semilogy(index(1:count), error(1:count));
 hold on;
 % Newton
 x0 = 0.5;
-[root, index, iteration, error, count] = newton(f2, df2, x0, tol);
+[root, index, iteration, error, count] = newton(f1, df1, x0, tol);
 disp([index(1:count), iteration(1:count), error(1:count)]);
 semilogy(index(1:count), error(1:count));
 hold on;
 % Secant
 x0 = 0; x1 = 1;
-[root, index, iteration, error, count] = secant(f2, x0, x1, tol);
+[root, index, iteration, error, count] = secant(f1, x0, x1, tol);
 disp([index(1:count), iteration(1:count), error(1:count)]);
 semilogy(index(1:count), error(1:count));
-
-title('Error estimation for x-1-0.3cos(x)');
+title('Error estimation for e^x-3x^2, the smaller positive root');
 legend('Bisection', 'Newton', 'Secant');
+% for the larger positive root
+% bisection
+figure(3);
+a = 1; b = 4;
+[root, index, iteration, error, count] = bisection(f1, a, b, tol);
+disp([index(1:count), iteration(1:count), error(1:count)]);
[…]

### 2017-09-20 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

@@
 \textbf{(b)}. 
-According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step.
+% According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step.
 Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
+First, assume $x\in O$.
+According to the construction of Cantor function, if $x = \sum_{k} c_k3^{-k}$ is the ternary expansion of $x$, and the first $1$ in the ternary expansion is in the $n_{th}$ place, then $\varphi(x) = \frac{1}{2^n} + \sum_{k < n}\frac{1}{2}c_k 2^{-k} $.
+
+If $x = \sum_{k}c_k3^{-k}\in C$, according to the extension of $\varphi(x)$, $\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} $.
+We can construct a sequence $\{t_i\} = \{\sum_{k} d_k3^{-k}\}$, s.t.
+$d_i = c_i, \forall i < m_{i+1} $, where $m_i $ is the position of $i_{th}~ 2~ \text{in}~ c_k $, and $d_{m_{i+1}} = 1$.
+Then $\{t_i\}$ is a strictly increasing sequence, and $\lim_{i\to\infty}t_{i} = x$.
+
+Since $\varphi(x)$ is a strictly increasing function in $O$, we know that
+$$
+\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} \ge \varphi(t_i) = \frac{1}{2^i}+\sum_{k<i}\frac{1}{2}d_k2^{-k}.
+$$ 
+Thus 
+$$
+\varphi(x) \ge \sum_{k}\frac{1}{2}c_k2^{-k} 
+$$
+when we let $i\to\infty$. On the other hand, $\forall \epsilon > 0$, $\exists i > 0$, $\frac{1}{2^i} < \epsilon$. Thus
+$$
+\varphi(t_i) > \sum_{k}\frac{1}{2}c_k2^{-k} - \epsilon.
+$$ 
+So 
+$$
+\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} = \frac{1}{2^i}+\sum_{k<i}\frac{1}{2}d_k2^{-k}.
+$$
 \bigskip

### 2017-09-22 Graduate - Numerical Analysis/Assignment 5/assignment.tex
update

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Numerical Analysis \\ Assignment 5}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 2.21, Page 121}
\solution{Solution}{
According to Theorem 2.7, we should choose $c$ so as to have $|g'(\alpha)| < 1$. Thus
$$
|g'(\alpha)| = |1+cf'(\alpha)| < 1.
$$
So $c$ satisfies $-2 < cf'(\alpha) < 0$. For a good rate of convergence, pick $c$ s.t. $cf'(\alpha) \sim 0$.
}

\problem{2}{Problem 2.24, Page 121}
\solution{Solution}{
\textbf{(a)} 
$$
g(x) = -16+6x+\frac{12}{x}.
$$
Thus $g'(2) = 3 > 1.$ So the iteration does not converge.

\textbf{(b)}
$$
g(x) = \frac{2}{3}x+\frac{1}{x^2}.
$$
Thus $g'(3^{\frac{1}{3}}) = \frac{2}{3}-2\alpha^{-3} = 0$. So the iteration converges. Since
$$
\begin{aligned}
\lim_{n\to\infty}\frac{\alpha-x_{n+1}}{(\alpha-x_n)^2} &= \lim_{n\to\infty}\frac{-2x_n^3+3\alpha x_n^2-3}{3x_n^2(\alpha-x_n)^2} = \lim_{x_n\to\alpha}\frac{-2x_n^3+3\alpha x_n^2-3}{3x_n^2(\alpha-x_n)^2}\\
&= \lim_{x_n\to\alpha}\frac{-6x_n^2+6\alpha x_n}{6x_n(\alpha-x_n)^2-6x_n^2(\alpha-x_n)} = \lim_{x_n\to\alpha}\frac{1}{\alpha-2x_n} \\
&= -\frac{1}{\alpha}.
\end{aligned}
$$
We know the iteration is second-order convergent.

\textbf{(c)}
$$
g(x) = \frac{12}{1+x}.
$$
Thus $g'(\alpha) = -\frac{3}{4}$, so the iteration converges. Since
$$
\lim_{n\to\infty}\frac{\alpha-x_{n+1}}{\alpha-x_n} = \frac{(1+x_n)\alpha-12}{(1+x_n)(\alpha-x_n)} = \frac{\alpha}{\alpha-2x_n-1} = -\frac{3}{4},
$$
We know the iteration is linear convergence, and the rate is $\frac{3}{4}$.
}

\problem{3}{Problem 2.28, Page 122}
\solution{Proof}{
Assume $f(x) = (x-\alpha)h(x), ~h(\alpha) \ne 0$. Then
$$
\begin{aligned}
g(x) &= x - \frac{f(x)}{D(x)} = x-\frac{(x-\alpha)^2h^2(x)}{(x-\alpha)(h(x)+1)h((x-\alpha)h(x)+x)-(x-\alpha)h(x)} \\
&= x - \frac{(x-\alpha)h^2(x)}{(h(x)+1)h((x-\alpha)h(x)+x)-h(x)}.
\end{aligned}
$$
Thus 
$$
\begin{aligned}
g'(\alpha) &= \left.1-\frac{(h^2(x)+2(x-\alpha)h(x)h'(x))((h(x)+1)h((x-\alpha)h(x)+x)-h(x)) - (x-\alpha)M}{((h(x)+1)h((x-\alpha)h(x)+x)-h(x))^2}\right|_{x=\alpha} \\
&= 1-\frac{h^4(\alpha)}{h^4(\alpha)} = 0.
\end{aligned}
$$
And we can know that $g''(\alpha)\ne 0$. Accoding to Theorem 2.8, this iteration is a second-order method.
}

\problem{4}{Problem 2.48, Page 126}
\solution{Proof}{
According to the continuity of $\lVert\cdot\rVert_{\infty}$, we can find an $\epsilon$ and a closed set $B(\alpha, \delta)$, s.t. $\forall x\in B(\alpha, \delta)$, $\lVert G(x)\rVert_{\infty} \le 1-\epsilon$. Then $\forall x_0 \in B = B(\alpha, \delta)$,
$$
\lVert \alpha-x_{n+1}\rVert = \lVert g(\alpha)-g(x_n)\rVert = \lVert G(\xi)\rVert \cdot \lVert \alpha-x_n\rVert \le (1-\epsilon) \lVert \alpha-x_n\rVert \le (1-\epsilon)^n \lVert \alpha-x_0\rVert.
$$
Thus $\lVert \alpha-x_{n+1}\rVert \to 0, ~t\to\infty$. So the iteration converges to $\alpha$. And since $g(B) \subset B$ according to that $\lVert\alpha-g(x)\rVert < \lVert\alpha-x\rVert$, and $\max \lVert G(x)\rVert < 1$, we know that it satisfies the condition of Theorem 2.9.
}

\problem{5}{Problem 2.50, Page 127}
\solution{Solution}{

}
\end{document}

### 2017-09-23 Graduate - Numerical Analysis/Assignment 5/assignment.tex
Add HW 5

@@
   morekeywords={*, factorial, sum, erlang},
+  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
 }
@@
 \solution{Solution}{
+The code and result are as follows;(In fact)
+}
+\lstinputlisting[language = MATLAB]{Newton.m}
+\lstinputlisting[language = MATLAB]{prob50.m}
+\begin{lstlisting}[language = MATLAB]
+>> prob50
+   1.600000000000000   1.200000000000000
+   1.581250000000000   1.225000000000000
+   1.581138833992095   1.224744897959184
+\end{lstlisting}
 
+\problem{6}{Problem 2.51, Page 127}
+\solution{Solution}{
+We just use the code of Newton's method from Problem 2.50, and the executive script is as follows;
 }
+\lstinputlisting[language = MATLAB]{prob51.m}
+\solution{Result}{
+The result is shown in the following table \ref{Table 1}, and the convergence speed shown in \ref{Graph 1}.
+From the result we know that different initial values may lead to convergence to different roots, while when the iteration comes to very close to the root, the convergence order is first-order.
+}
+\begin{table}[!htb]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Initial Point & Convergence & Result & Number of iterates \\
+\hline
+(1.2, 2.5) & Yes & (1.336355248159268, 1.754234729131226) & 11 \\
+\hline
+(-2, 2.5) & Yes & (1.336355247361990, 1.754234726236878) & 19 \\
+\hline
+(-1.2, -2.5) & Yes & (1.336355235838950, 1.754234684404958) & 24 \\
+\hline
+(2, -2.5) & Yes & (2.998365352785336, 0.148430977265564) & 9 \\
+\hline
+\end{tabular}
+\caption{The result of convergence and iteration count.}
+\label{Table 1}
+\end{table}
+
+\begin{figure}[!htb]
+\centering
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width = \textwidth]{res1.eps}
+\end{minipage}
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width = \textwidth]{res2.eps}
+\end{minipage} \\
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width = \textwidth]{res3.eps}
+\end{minipage}
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width = \textwidth]{res4.eps}
+\end{minipage}
+\caption{Convergence Order}
+\label{Figure 1}
+\end{figure}
 \end{document}

### 2017-09-23 Graduate - Numerical Analysis/Assignment 5/prob50.m

@@ -1,0 +1,8 @@
+format long;
+f = @(x)([x(1)^2+x(2)^2-4; x(1)^2-x(2)^2-1]);
+F = @(x)([2*x(1), 2*x(2); 2*x(1), -2*x(2)]);
+x0 = [1.6; 1.2];
+max_it = 100;
+tol = 1e-6;
+[x, error, count] = Newton(f, F, x0, max_it, tol);
+disp(x(1:count, 1:2));

### 2017-09-28 Draft/4-homework20170925.tex
update

--- 2017-09-14 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
@@
 \begin{center}
-\textbf{Introduction to Analysis $I$\\Homework 3\\Monday, September 11, 2017}\bigskip
+\textbf{Introduction to Analysis $I$\\Homework 4\\Wednesday, September 27, 2017}\bigskip
 \end{center}
@@
 \begin{center}
-\emph{Homework 3 is due by midnight, Friday, September 22.}
+\emph{Homework 4 is due by midnight, Saturday, October 7.}
 \end{center} 
@@
 \begin{enumerate}
-\item  (Problem 34, Page 53) Show that there is a continuous, strictly increasing function on the interval $[0, 1]$ that maps a
-set of positive measure onto a set of measure zero.
+\item  (Problem 18, Page 63) Let $I$ be a closed bounded interval and let $f$ be a bounded measurable function defined on $I$.
+Let $\epsilon > 0$.
+Show that there is a step function $h$ on $I$ and a measurable subset $F$ of $I$ for which \[
+|h-f|< \epsilon \text{ on } F \text{ and } m(I\sim F)< \epsilon .\]
 
@@
 \textbf{Solution:}
-Let $C$ be the Cantor set on $[0, 1]$, and $\varphi(x)$ be the Cantor function. Define
-$$
-\phi(x) = \varphi(x)+x, ~x\in C.
-$$
-We now show $\phi^{-1}(x)$, the inverse of $\phi(x)$, satisfies the properties in the problem.
-First, since $\phi(x)$ is a continuous, strictly increasing function on $[0, 1]$, thus is continuous and strictly increasing on $C\subset [0, 1]$.
-
-Denote $D = \phi(C)$, then according to theorems in the book, $m(D) = 1$.
-$\forall x_1 < x_2\in D$, if $\phi^{-1}(x_1) \ge \phi^{-1}(x_2)$, then since $\phi$ is strictly increasing, $\phi(\phi^{-1}(x_1)) = x_1+\phi^{-1}(x_1) \ge \phi(\phi^{-1}(x_2)) = x_2+\phi^{-1}(x_2)$, which means $\phi^{-1}(x_1) < \phi^{-1}(x_2)$, leading to a contradictory.
-Thus $\phi^{-1}$ is strictly increasing.
-
-On the other hand, $\forall x_0 \in D, \forall \epsilon > 0$, we need to show that $\exists\delta > 0, ~\forall x_1\in D, ~|x_1-x_{0}| < \delta$, then $|\phi^{-1}(x_1)-\phi^{-1}(x)| < \epsilon$.
-Denote $y_1 = \phi(\min\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\}), ~y_2 = \phi(\max\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\})$, then let $\delta = \min{y_1-x_0, y_2-x_0}$, we have $\forall |x-x_0|< \delta$, $|\phi^{-1}(x)-\phi^{-1}(x_0)| < \epsilon$.
-Thus $\phi^{-1}$ is continuous on $D$.
-
-Since $C$ is measure zero, we get a function satisfying the properties in the problem.
 \bigskip
 
-\item (Problem 37, Page 53) Let $f$ be a continuous function defined on $E$. Is it true that $f^{-1}(A)$ is always measurable if $A$ is measurable?
-
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
-
-\textbf{Solution:} It is not true.
-
-We may consider the function $\psi(x)$ defined by Proposition 21 on Page 52.
-It is a strictly increasing continuous function, and it maps a measurable set $A\subset C$, onto a nonmeasurable set.
-Thus if we consider $\psi^{-1}(x)$, it has been proved as a strictly increasing continuous function in Problem 1.
-Then $\psi^{-1}(A)$ is nonmeasurable.
-
-\bigskip
-
-\item  (Problem 39, Page 53) Let $F$ be the subset of $[0, 1]$ constructed in the same manner as the Cantor set except that
-each of the intervals removed at the nth deletion stage has length $\alpha 3^{-n}$ with $0 < a < 1$. Show
-that $F$ is a closed set, $[0, 1]\sim F$ dense in $[0,1]$, and $m(F) = 1- a$. Such a set F is called a \emph{generalized Cantor set}.
+\item (Problem 22, Page 64) (Dini's Theorem)  Let $\{f_n\}$ be an increasing sequence of continuous functions on $[a,b]$ which converges pointwise on $[a,b]$ to the continuous function $f$ on $[a,b]$.
+Show that the convergence is uniform on $[a,b]$.
 
@@
 \textbf{Solution:}
-First, we denote $F_1 = \left[0, \frac{3-\alpha}{6}\right]\cup \left[1-\frac{3-\alpha}{6}, 1\right]$.
-With the same process of constructing the Cantor set, we have a collection of $F_n$.
-We define the generalized Cantor set as
-$$
-F = \bigcap_{k=1}^{\infty}F_n.
-$$
-Since each $F_n$ is a closed set, we have $F$ as well closed.
-Then $F_n$ is the disjoint of union of $2^n$ intervals, each of length $(1-\alpha)\frac{1}{2^n}+\frac{\alpha}{3^n}$.
-By the finite additivity of Lebesgue measure,
-$$
-m(F_k) = 1-\alpha + \left(\frac{2}{3}\right)^n\alpha.
-$$
-According to the continuity of measure, we have $m(F) = \lim_{k\to\infty}m(F_k) = 1-\alpha$.
-
-Let $x < y\in [0, 1]$.
-If $y\notin F_k$ for one of the $k$, then since $[0, 1]\setminus F$ is open, there exists $t < y$ in $N(y)$, s.t.
-$t\in [0, 1]\setminus F$.
-If $x\notin F_k$, it is the same case.
-Now we assume that $x, ~y \in F$.
-If $x, ~y$ are not in the same subset of $F_k$, then $\exists t\in [0, 1]\setminus F$.
-Then we can assume that $x, ~y$ always belong to the same subset.
-However, the subsets make a nested set with the limit of lower bound and the upper bound be the same.
-According to Nested Set Theorem, we have $x = y$.
-Then we have proved that $[0, 1]\setminus F$ is dense.
 \bigskip
 
-\item Let $C$ be the Cantor set and let $\varphi$ be the Cantor-Lebesgue function.
-\begin{enumerate}
-\item Show that $C$ consists of all $x\in [0,1]$ whose  ternary expansion has coefficients equal to $0$ or $2$, i.e., if $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0, 1, \text{or } 2$, then $x\in C$ if and only if $c_k = 0 \text{ or } 2$.
-\item Show that if $x\in C$ and $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0 \text{ or } 2$, then $\varphi(x) = \sum_{k\geq 1} (\frac{1}{2} c_k) 2^{-k}$.
-\end{enumerate}
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
-
-\textbf{Solution:}
-\textbf{(a).} We show by induction that a number belongs to the intervals we removed in each step iff its ternary expasion has a coefficient 1.
-First, the interval removed at the first step can be represented as $(0.1, ~0.2)$.
-Thus $0.1 \notin F$, and $0.0, 0.2\in F$.
-Assume it holds in the first $n$ steps, then the intervals removed at the $n+1$ step has the representation $(0.a_1a_2\cdots a_n1, ~0.a_1a_2\cdots a_n2)$, in which $a_i\in\{0, 2\}$.
-Then each number in this interval has an expansion like
-$$
-0.a_1a_2\cdots a_n1a_{n+1}\cdots.
-$$
-Thus each number in $F$ has a coefficient 1 in its expansion.
-According to the construction process, we can also know that the reverse also holds. Thus the proposition holds.
-
-\textbf{(b)}. 
-According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step.
-Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
-\bigskip
-
-\item  Construct a Cantor-type subset of $[0,1]$ by removing from each interval remaining at the $k^{\text{th}}$ stage, a subinterval of relative length $\theta_k$, $0 < \theta_k < 1$.
-Show that the remainder has measure zero if and only if $\sum_{k\geq 1} \theta_k = \infty$.
-(Use the fact that for $a_k > 0$, the product $\Pi_{k = 1}^{\infty} a_k$ converges, in the sense that $\lim_{n\to \infty} \Pi_{k=1}^N a_k$ exists and  is not zero, if and only if $\sum_{k =1}^{\infty} \ln a_k$ converges.)
+\item  (Problem 5, Page 364) Show that an extended real-valued function $f$ on $X$ is measurable if and only if for each rational number $c$, $\{x\in X \mid f(x)< c\}$ is a  measurable set.
 
@@
 \textbf{Solution:}
-Denote $F_n$ as the remained set after $n$ steps. Then according to the construction, we have 
-$$
-m(F_n) = \prod_{i=1}^{n}(1-\theta_i).
-$$
-First we have $\sum_{n=1}^{\infty}-\theta_n$ and $\sum_{n=1}^{\infty}\ln(1-\theta_n)$ be both negative-term series, and the necessity of their convergence is $\lim_{n\to\infty}\theta_n = 0$.
-On the other hand, when $\lim_{n\to\infty} \theta_n = 0$,
-$$
-\lim_{n\to\infty}\frac{\ln(1-\theta_n)}{-\theta_n} = 1,
-$$
-thus that $\sum{\ln(1-\theta_n)}$ converges is equivalent to the convergence of $\sum{-\theta_n}$.
-
-Then according to the continuity of measure,
-$$
-\begin{aligned}
-m(F) > 0 \Leftrightarrow m(\lim_{n\to\infty}F_n) > 0 \Leftrightarrow \prod_{i=1}^{\infty}(1-\theta_i) ~\text{converges} \Leftrightarrow \sum_{i=1}^{\infty} \ln(1-\theta_i) ~\text{converges} \\
-\Leftrightarrow \sum_{i=1}^{\infty}\theta_i ~\text{converges}.
-\end{aligned}
-$$
-Thus $m(F) = 0$ iff $\sum{\theta_i} = \infty$.
-
 \bigskip
 
-\item Let $Z$ be a set of measure zero in $\mathbb{R}$.  What is the measure of $\{x^2 \mid x\in Z\}$?
+\item (Problem 13, Page 365) Let $\{f_n\}$ be a sequence of real-valued functions on $X$ such that for each natural number $n$, $\mu \{x\in X \mid |f_n (x) - f_{n+1}(x)|> 1/2^n\}<1/2^n$.
+Show that $\{f_n\}$ is pointwise convergent a.e.
+on $X$.
 
@@
 \textbf{Solution:}
-$X = \{x^2\mid x\in Z\}$ is also measure 0.
-
-First, if the set $Z$ is bounded, which means $Z\in [0, M]$.
-Since $m(Z) = 0$, $\forall \epsilon > 0$, there exists an open cover $\{O_i\} = \{(a_i, b_i)\}$, s.t.
-$m^*(\cup\{O_i\}\setminus Z) < \epsilon$.
-Thus $\{(a_i^2, b_i^2)\}$ is an open cover of $X$, and $m^*(\cup(a_i^2, b_i^2)\setminus X) \le M\sum(b_i-a_i) < M\epsilon$.
-Thus now $X$ is a measure-zero set.
-When $Z \in [-M, 0]$, with the same process above, we can know that $X$ is a measure-zero set.
-Then when $Z \in [-M, M]$, we know $X$ is also measure zero.
-
-Since $Z$ is measure zero, for $\forall \epsilon > 0$ and integer $n > 0$, we have $m(Z\cap [-n, n]) < 2^{-n}\epsilon$.
-Thus from the discussion above we have $m(X\cap [-n^2, n^2]) < 2^{-n}\epsilon$.
-Since
-$$
-X = \bigcup_{n=1}^{\infty}X\cap[-n, n],
-$$
-with the addivity of measure, 
-$$
-m(X) < \sum_{n=1}^{\infty}2^{-n}\epsilon = \epsilon.
-$$
-With the arbitrariness of $\epsilon$, we have $m(X) = 0$.
 \bigskip
 
-\item  Let $0.\alpha_1 \alpha_2 \cdots$ be the dyadic development of any $x\in[0,1]$.
-Let $k_1,k_2,k_3,\ldots$ be a fixed permutation of the positive integers $1,2,\ldots$, and consider the transformation $T$ which sends $x = \alpha_1\alpha_2\alpha_3\cdots$ to $Tx: = \alpha_{k_1}\alpha_{k_2}\alpha_{k_3}\cdots$.
-Show that if $E$ is a measurable subset of $[0,1]$ then its image under $T$, $T(E)$, is also measurable and that $m(T(E))= m(E)$.
-That is, show that $T$ is a measure preserving transformation of $[0,1]$.
-[Consider first the special case where $E$ is a dyadic interval of the form $(s2^{-k}, (s+1)2^{-k})$ and $s = 0,1,\ldots, 2k-1$.
-Then think about open sets and note that each open set can be written as a countable union of non-overlapping half-open dyadic intervals.]
+\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
+\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
+\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
+\begin{enumerate}
+\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
+\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
+\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.\end{enumerate}
+
+\item (Problem 16, Page 365) Assume $\mu (X) < \infty$.
+Show that $\{f_n\}$ converges to $f$ in measure if and only if each  subsequence of $\{f_n\}$ has a further subsequence that converges pointwise a.e.
+on $X$ to $f$.
+Use this to show that for two sequences that converge in measure, the product sequence also converges in measure to the product of the limits.
+
+\item Show that if $f$ is an lower semicontinuous (resp.
+upper semicontinuous) function on an interval $[a,b]$, then there is a family $\{f_{\alpha}\}$ of continuous functions on the interval $[a,b]$ such that $f(x) = \sup\{f_{\alpha}(x) \mid \alpha \in A \}$ (resp.
+$f(x) = \inf\{f_{\alpha}(x) \mid \alpha \in A \}$) for all $x \in [a,b]$.
 
@@
 \textbf{Solution:}
-
 \bigskip

### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
update

--- 2017-09-28 Draft/4-homework20170925.tex
@@
 \bigskip
-\textbf{Collaborators:}\\
+\textbf{Collaborators:} None
 \smallskip
@@
 \textbf{Solution:}
+For $\epsilon > 0$, according to Lusin's Theorem, there exists a closed subset $F$ of $I$, s.t. $m(I\setminus F) < \epsilon$, and $f$ is continuous on $F$.
+% Assume $\bigcup_{i=1}^\infty O_i$ is an open cover of $F$, in which $O_{i}$ are open intevals. Then since $F$ is closed there exists a finite open cover, denoted by $\bigcup_{i=1}^n O_i.$ Then
+% $$
+% F = \bigcup_{i=1}^n (O_i\cap F).
+% $$
+% Denote $F_{i} = O_{i}\cap F$, then 
+% Since $f$ is continuous on $F$, 
+Then for $x_0\in F$, for this $\epsilon > 0$, 
+$$
+\exists \sigma > 0, ~\forall x\in (x_0-\delta, ~x_0+\delta)\cap F, ~|f(x)-f(x_0)| < \epsilon.
+$$
+Since
+$$
+\bigcup_{x_0\in F} (x_0-\delta_i, ~x_0+\delta_i)
+$$
+is an open cover of the closed set $F$, it has a finite subcover, denoted by
+$$
+\bigcup_{i=1}^n (x_i-\delta_i, ~x_i+\delta_i).
+$$
+If we define
+$$
+h = \left\{
+\begin{aligned}
+&f(x_i), ~\text{for} ~x\in (x_i-\delta_i, ~x_i+\delta_i), \\
+&0, ~\text{others}
+\end{aligned}
+\right.
+$$
+then $h$ takes constant values in finite intervals, and $h = 0$ in other parts, we know $h$ is a step function. And from the construction above, on each interval $(x_i-\delta_i, x_i+\delta_i)\cap F$, 
+$$
+|h-f|< \epsilon ~\text{on}~ (x_i-\delta_i, x_i+\delta_i)\cap F.
+$$
+Thus $h$ is the step function needed.
+
 \bigskip

### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add problem 2

@@
 For $\epsilon > 0$, according to Lusin's Theorem, there exists a closed subset $F$ of $I$, s.t. $m(I\setminus F) < \epsilon$, and $f$ is continuous on $F$. 
-% Assume $\bigcup_{i=1}^\infty O_i$ is an open cover of $F$, in which $O_{i}$ are open intevals. Then since $F$ is closed there exists a finite open cover, denoted by $\bigcup_{i=1}^n O_i.$ Then
-% $$
-% F = \bigcup_{i=1}^n (O_i\cap F).
-% $$
-% Denote $F_{i} = O_{i}\cap F$, then 
-% Since $f$ is continuous on $F$, 
 Then for $x_0\in F$, for this $\epsilon > 0$, 
@@
 \textbf{Solution:}
+If the convergence is not uniform, then there $\exists \epsilon > 0, \forall N > 0, ~\exists n > N, ~\exists x\in [a, b], ~|f(x)-f_n(x)| > \epsilon $.
+
+We can construct a sequence $\{x_n\}$ like this:
+
+$$
+N = 1, ~\exists n_1 > 1, ~\exists x_1\in[a, b], ~|f_{n_1}(x_1)-f(x_1)| \geqslant \epsilon.
+$$
+$$
+N = n_1, ~\exists n_2 > n_1, ~\exists x_2\in[a, b], ~|f_{n_2}(x_2)-f(x_2)| \geqslant \epsilon.
+$$
+$$
+\cdots
+$$
+$$
+N = n_{k-1}, ~\exists n_k > n_{k-1}, ~\exists x_k\in[a, b], ~|f_{n_k}(x_k)-f(x_k)| \geqslant \epsilon.
+$$
+$$
+\cdots
+$$
+Then since $x_i\in [a, b]$, according to Bolzano-Weierstrass Theorem, there is a convergent subsequence in $\{x_i\}$, and we may denote it by $\{y_i\}$ for convinence.
+Assume $y_i\to y\in [a, b]$, then since
+$$
+\lim_{n\to\infty}f_n(y) = f(y),
+$$
+for this $\epsilon > 0, ~\exists N$, s.t.
+$$
+|f_N(y)-f(y)|<\epsilon.
+$$
+since $f_N$ is continuous, with $y_k\to y$, there $\exists K > 0$, 
+$$
+|f_N(y_k)-f(y_k)| < \epsilon
+$$
+holds for all $k > K$. Notice that $\{f_n\}$ is an increasing sequence, when $n > N ~\text{and}~ k > K$, 
+$$
+|f_n(y_k)-f(y_k)| \leqslant |f_N(y_k)-f(y_k)|<\epsilon.
+$$
+Since $n_k\to\infty$ when $k\to\infty$, when $k$ is sufficiently large we have $k > K, ~n_k > N$. Thus 
+$$
+|f_{n_k}(x_k)-f(x_k)| < \epsilon,
+$$ 
+which makes a contradiction with the assumption. Thus the convergence is uniform.
 \bigskip

### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add problem 3
Add problem 4

@@
 \textbf{Solution:}
+Notice that for each $r\in \mathbb{R}\supset\mathbb{Q}$, we have
+$$
+\{x\in X\mid f(x) < r\} = \bigcup_{\substack{c < r \\ c \in \mathbb{Q}}}\{x\in X\mid f(x) < c\}.
+$$
+Then since Lebesgue measurable sets make a $\sigma-$Algebra, we know $\{x\in X\mid f(x) < r\}$ is measurable.
+On the other hand, since each rational number is a real number, the other direction stands.
 \bigskip
@@
 \textbf{Solution:}
+Denote
+$$
+E_n = \{x\in X\mid |f_n(x)-f_{n+1}(x)|>\frac{1}{2^n}\},
+$$
+Then 
+$$
+\bigcup_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\frac{1}{2^n} = 1.
+$$
+According to Borel-Cantelli Lemma, $\exists E_0$, $\mu(E_0) = 0$, s.t.
+$\forall x\in X\setminus E_0$, $x$ belongs to at most finite number of $E_n$.
+That means, $\forall x\in X\setminus E_0$, $\exists N > 0$, $\forall n > N$, $x\in E_n$.
+So
+$$
+|f_n(x)-f_{n+1}(x)| < \frac{1}{2^n}.
+$$
+Thus 
+$$
+\forall m > n, |f_m(x)-f_{n}(x)| < \sum_{i=n}^{m-1}|f_{i+1}(x)-f_i(x)| < \frac{1}{2^{n-1}}.
+$$
+This means that $f_n(x)$ is a Cauchy sequence, then it converges. Thus $\{f_n\}$ is pointwise convergent on $X\setminus E_0$, and thus is pointwise convergent a.e. on $X$.
 \bigskip
@@
 \item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
-\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.\end{enumerate}
+\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.
+\end{enumerate}
+
+\bigskip
+\textbf{Collaborators:} None
+\smallskip
+
+\textbf{Solution:}
+
+\bigskip
 

### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add prob 5

@@
 \bigskip
-\textbf{Collaborators:} None
+\textbf{Collaborators:} None, but (b) and (c) checked a proof from my Real Analysis textbook in college (Written by Prof. Zhaobo Huang, Fudan University).
 \smallskip
@@
 \textbf{Solution:}
+\textbf{(a)} Since $\{f_n\}$ converges pointwise a.e. on $X$, there $\exists E_0, ~\mu(E_0) = 0$, s.t. $\lim\limits_{n\to\infty}f_n = f$ on $E_1 = X\setminus E_0$. Then $\forall \epsilon > 0$,
+$$
+E_1 = \bigcup_{k=1}^{\infty} \bigcap_{n=k}^{\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\} = \varliminf_{n\to\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}.
+$$
+Thus, according to the continuity of measure, 
+$$
+\mu(E_1) \le \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}).
+$$
+Since $\mu(X) < \infty$, we have
+$$
+\begin{aligned}
+\lim_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| &> \epsilon\}) \le \varlimsup_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| > \epsilon\}) \\
+&= \mu(X) - \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}) \le 0.
+\end{aligned}
+$$
+Thus $\{f_n\}$ converges to $f$ in measure.
 
+\textbf{(b)}
+Since $\{f_n\}$ converges to $f$ in measure, $\forall k \in \mathbb{N}$, $\exists n_k > n_{k-1} \in \mathbb{N}$, s.t. when $n \ge n_k$,
+$$
+\mu(\{x\in X\mid |f_n(x)-f(x)| \ge \frac{1}{2^k}\}) < \frac{1}{2^k}.
+$$
+Denote $E_{k} = \{x\in X\mid |f_{n_k}(x)-f(x)| \ge \frac{1}{2^k}\}$, then $\mu(E_k) < \frac{1}{2^k}$. Let 
+$$
+F_k = \bigcap_{i=k}^{\infty} (X\setminus 
+E_i) = \{x\in X\mid |f_{n_i}(x)-f(x)|\le \frac{1}{2^i}, i = k, k+1, \cdots\}
+$$
+then $\{f_{n_k}\}$ converges uniformly to $f$ on $F_k$, thus is convergent on $F = \bigcup\limits_{k=1}^{\infty}F_k$. On the other hand,
+$$
+X\setminus F = \bigcap_{k=1}^{\infty}(X\setminus F_k) = \bigcap_{k=1}^{\infty}\bigcup_{k=1}^{\infty}E_i = \varlimsup_{i\to\infty}E_i,
+$$
+and 
+$$
+\sum_{i=1}^{\infty}\mu(E_i) \le \sum_{i=1}^{\infty}\frac{1}{2^i} = 1, 
+$$
+thus $\mu(X\setminus F) = 0$, $\{f_{n_k}\}$ converges pointwise a.e. on $X$.
+
+\textbf{(c)} If $\{f_n\}$ is Cauchy in measure, then for each $n_i \in \mathbb{N}$, there $\exists n_{i+1} > n_{i}$, s.t. 
+$$
+\mu(\{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\})\le \frac{1}{2^i}.
+$$
+We can denote the subsequence $\{f_{n_i}\}$ as $\{g_i\}$, and $E_i = \{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\}$.
+Let $F_{k} = \bigcup\limits_{i = k}^{\infty}E_i $, then $\mu(F_k)\le \sum\limits_{i=k}^{\infty}\frac{1}{2^i}\le \frac{1}{2^{k-1}} $.
+Denote $F = \bigcap\limits_{i=1}^\infty F_i $, then $\mu(F) = 0$.
+
+If we choose $x\notin F_{k}$, and $i \ge j \ge k$, then 
+$$
+|g_i(x)-g_j(x)| \le \sum_{l = j}^{i-1}|g_{l+1}(x)-g_l(x)| \le \frac{1}{2^j},
+$$
+which means $g_i(x)$ is Cauchy respective to $i$ on $X\setminus F$, thus converges on $X\setminus F$. Thus we can construct a function $f$ like this: 
+$$
+f(x) = \left\{
+\begin{aligned}
+&0, ~x\in F \\
+&\lim_{i\to\infty}f_i(x), ~x\in X\setminus F.
+\end{aligned}
+\right.
+$$
+Then $\{g_i(x)\}$ converges to $f$ on $X\setminus F$, which means $\{g_i\}$ converges pointwise a.e. on $X$. Now we show $\{f_n\}$ converges to $f$ in measure. Notice
+$$
+\mu(\{x\in X\mid |f_n - f|\ge \xi\}) \le \mu(\{x\mid |f_n-g_m|\ge \frac{\xi}{2}\}) + \mu(\{x\mid |g_m-f|\ge \frac{\xi}{2}\}), ~m > n
+$$
+and when $n\to\infty$, the two terms in the right can be arbitrarily small, so 
+$$
+\lim_{n\to\infty}\mu(\{x\in X\mid |f_n - f|\ge \xi\}) = 0, ~\forall \xi > 0.
+$$
+The $\{f_{n}\}$ converges in measure.
 \bigskip

### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add Problem 6

@@
 
+\bigskip
+\textbf{Collaborators:} None
+\smallskip
+
+\textbf{Solution:}
+\textbf{(1)} Necessity: From $\{f_n\}$ converges to $f$ in measure and the property of convergence, we know that each subsequence of $\{f_n\}$ converges to $f$ in measure.
+From Problem 5(b) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_{j}}}\}$ converges pointwise a.e.
+on $X$ to $f$.
+
+Sufficiency: If each subsequence $\{f_{n_k}\}$ has a further subsequence $\{f_{n_{k_j}}\}$ converges pointwise a.e.
+on $X$ to $f$, then since $\mu(X) < \infty$, from Problem 5(a) we know $\{f_{n_k}\}$ converges in measure to $f$.
+If $\{f_n\}$ does not converge to $f$ in measure, then there $\exists \epsilon > 0$,
+$$
+\begin{aligned}
+&\text{for}~ n_1 = 1, ~\exists n_2 > n_1, ~\mu(\{x\mid |f_{n_2}-f| \ge \epsilon\}) \ge \epsilon, \\
+&\text{for}~ n_2, ~\exists n_3 > n_2, ~\mu(\{x\mid |f_{n_3}-f| \ge \epsilon\}) \ge \epsilon, \\
+&\cdots, \\
+&\text{for}~ n_k, ~\exists n_{k+1} > n_k, ~\mu(\{x\mid |f_{n_{k+1}}-f| \ge \epsilon\}) \ge \epsilon, \\
+&\cdots.
+\end{aligned}
+$$
+Then we get a subsequence $\{f_{n_k}\}$ which does not converge to $f$ in measure. It makes a contratiction.
+
+\textbf{(2)} Suppose $\{f_n\}$, $\{g_n\}$ are two sequences that converge in measure to respectively $f$ and $g$.
+For each subsequence $\{f_{n_k}g_{n_k}\}$ of $\{f_ng_n\}$, from (1) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_l}}\}$ converges pointwise a.e.
+to $f$, and $\{g_{n_{k_l}}\}$ has a subsequence $\{g_{n_{k_{l_j}}}\}$ converges pointwise a.e.
+to $g$.
+Since the union of two measure-zero sets is a measure-zero set, we know $\{f_{n_{k_{l_j}}}g_{n_{k_{l_j}}}\}$ converges pointwise a.e.
+to $fg$ according to the linear property of limits.
+Thus according to (1) we know $\{f_ng_n\}$ converges in measure to the product of limits.
+\bigskip
+
 \item Show that if $f$ is an lower semicontinuous (resp.

### 2017-10-01 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
Add problem 7

@@
 \bigskip
-\textbf{Collaborators:} None
+\textbf{Collaborators:} Checked https://people.math.gatech.edu/\~{}loss/16FALLTEA/NOTES/semicontinuity.pdf for help.
 \smallskip
@@
 \textbf{Solution:}
+We first show a lemma.
+\begin{lemma}
+If $\{f_\alpha(x)\}$ is a family of upper semi-continuous functions, then $\inf\limits_{\alpha\in I}f_\alpha(x)$ is also upper semi-continuous.
+Conversely, lower semi-continuous is preserved under monotone increasing limits.
+\end{lemma}
+\begin{proof}
+In fact, suppose $\{f_\alpha(x)\}_{\alpha\in I}$ is a family of upper semi-continuous functions, then 
+$$
+\{x\in [a, b]\mid f_\alpha(x)\ge t\} = \bigcap_{\alpha\in I}\{x\in [a, b]\mid f_\alpha(x)\ge t\}.
+$$
+With the continuity of $f_\alpha(x)$ and the compactness of $[a, b]$, we know $\{x\in [a, b]\mid f_\alpha(x) \ge t\}$ is closed, so $\{x\in [a, b]\mid f_\alpha(x)\ge t\}$ is also closed.
+Thus $\inf\limits_{\alpha\in I} f_\alpha(x)$ is upper semi-continuous.
+\end{proof}
 
+We just show the case when $f$ is a lower semicontinuous function. Let
+$$ 
+f_\epsilon(x) = \inf_{y\in [a, b]}\left(f(y) + \frac{|x-y|}{\epsilon}\right),
+$$
+and we show that $f_\epsilon(x) $ is continuous and converges pointwise to $f$ from below when $\epsilon \to 0^+$.
+
+First, we have $f_\epsilon(x) \le f(x)$ by setting $y = x$ instead of taking the infimum. For each fixed $y\in [a, b]$, the map
+$$
+x \mapsto f(y)+\frac{|x-y|}{\epsilon}
+$$
+is continuous, hence according to the lemma, $f_{\epsilon}(x)$ is an upper semi-continuous function.
+
+Since $[a, b]$ is conpact, $f$ is lower semicontinuous, and the map $y\mapsto |x-y|$ is continuous, the infimum is attained, and there exists $y(\epsilon, x) \in [a, b]$, s.t.
+$$
+f_\epsilon(x) = f(y(\epsilon, x)) + \frac{d(x, y(\epsilon, x))}{\epsilon}.
+$$
+Pick $\{x_n\}\to x$, then since $[a, b]$ is compact we may assume $y(\epsilon, x) \to y_{0}$. Then since $f_{\epsilon}(x)$ is upper semicontinuous, 
+$$
+f_\epsilon(x)\ge \varlimsup_{n\to\infty}f_\epsilon(x_n) = \varlimsup_{n\to\infty}f(y(\epsilon, x_n)) + \frac{|x-y_0|}{\epsilon} \ge f(y_0) +\frac{|x-y_0|}{\epsilon} \ge f_\epsilon(x)
+$$
+Thus $f_\epsilon(x) $ is continuous. When $\epsilon\to 0$, we know $y(\epsilon, x) \to x$, otherwise $\frac{d(x, y(\epsilon, x))}{\epsilon}\to\infty$. And we have
+$$
+f(x) \ge \varlimsup_{\epsilon \to 0}f_\epsilon(x) = \varlimsup_{\epsilon\to 0}\left(f(y(\epsilon, x))+\frac{d(x, y(\epsilon, x))}{\epsilon}\right) \ge f(x) + \varlimsup_{\epsilon\to 0}\frac{d(x, y(\epsilon, x))}{\epsilon}.
+$$
+Which means $$\frac{d(x, y(\epsilon, x))}{\epsilon}\to 0,$$
+and $f_\epsilon(x) \to f(x)$.
 \bigskip

### 2017-10-01 Graduate - Numerical Analysis/Assignment 6/assignment.tex
add assign 6

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Numerical Analysis \\ Assignment 6}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 3.1, Page 185}
\solution{(a)}{
If we expand $V_{n}(x)$ by the last row, then we can know
$$
V_n(x) = A_{n+1,n+1}x^n+A_{n+1, n}x^{n-1}+\cdots + A_{n, 1},
$$
where $A_{i, j}$ is the cofactors of $V$. Then $V_n(x)$ is a polynomial of degree $n$, thus it has $n$ roots. By replacing $x$ with $x_{i}, i = 0, 1, \cdots, n-1$, we can find $V_{n}(x_i) = 0$, thus $x = x_{i}$ are exactly roots of $V_{n}$. On the other hand, the coefficient of $x^{n}$ is just $V_{n-1}(x_{n-1}) $, thus
$$
V_n(x) = V_{n-1}(x_{n-1})\prod_{i=0}^{n-1}(x-x_i).
$$
}
\solution{(b)}{
With the definition of $X$ we know
$$
\begin{aligned}
\det(X) &= V_n(x_n) = V_{n-1}(x_{n-1})\prod_{i=0}^{n-1}(x_n-x_i) \\
&= V_{n-2}(x_{n-2})\prod_{i=0}^{n-1}(x_n-x_i)\prod_{i=0}^{n-2}(x_{n-1}-x_i)\\
&= \cdots \\ 
&= V_0(x_0)\prod_{k=0}^{n-1}\prod_{i=0}^{k-1}(x_{k+1}-x_i) = \prod_{0\le j<i\le n}(x_i-x_j).
\end{aligned}
$$
}

\problem{2}{Problem 3.6, Page 186}
\solution{Solution}{
We know from linear interpolation,
$$
|E(x)| = \frac{(x-x_0)(x_1-x)}{2}\cdot \sin(\xi), ~x_0 \le \xi \le x_1.
$$
Since $|f''(t)| = |sin(t)| \le 1$, we should take $h$, s.t. $\frac{h^2}{8} \le 1e^{-6}$. Thus we may take $h = 0.002$.

And we need a table entries of $7$ significant digits so as not to let the rounding error dominate the interpolation error.
}

\problem{3}{Problem 3.8, Page 187}
\solution{Solution}{
The Lagrange quadratic interpolation of $f$ at $x_i$ is
$$
L(x) = \frac{(x-x_1)(x-x_2)}{(x_0-x_1)(x_0-x_2)}f_0 + \frac{(x-x_0)(x-x_2)}{(x_1-x_0)(x_1-x_2)}f_1 + \frac{(x-x_0)(x-x_1)}{(x_2-x_0)(x_2-x_1)}f_2.
$$
Then the rounding error of quadratic interpolation is
$$
\begin{aligned}
R(x) &= \frac{(x-x_1)(x-x_2)}{(x_0-x_1)(x_0-x_2)}\epsilon_0 + \frac{(x-x_0)(x-x_2)}{(x_1-x_0)(x_1-x_2)}\epsilon_1 + \frac{(x-x_0)(x-x_1)}{(x_2-x_0)(x_2-x_1)}\epsilon_2 \\
&= \frac{1}{2h^2}((x-x_1)(x-x_2)\epsilon_0 - 2(x-x_0)(x-x_2)\epsilon_1 + (x-x_0)(x-x_1)\epsilon_2)
\end{aligned}
$$
Since the maximum of a quadratic function is at either endpoints or vertex, 
$$
\max|R(x)| \le \max\left(|\epsilon_0|, ~|\epsilon_2|, \frac{1}{2h^2}\left(\frac{h^2}{4}+2h^2 +\frac{h^2}{4} \right)|\epsilon|~\right) = 1.25|\epsilon|.
$$
}

\problem{4}{Problem 3.21, Page 189}
\solution{Solution}{
First notice $p(x)-1$ has three roots. So we may assume
$$
p(x) = q(x)x(x-1)(x+1)+1, ~q(x) = ax^2+bx+c.
$$
Then we replace $x$ with $-2, 2, 3$, we have
$$
\left\{
\begin{aligned}
&q(-2) = 1 = 4a-2b+c \\
&q(2) = 1 = 4a+2b+c \\
&q(3) = 1 = 9a+3b+c
\end{aligned}
\right.
$$
Then $q(x) = 1$ has at least three roots, which means $q(x) = 1$. Thus the degree of $p(x)$ is 3.
}

\problem{5}{Problem 3.24, Page 189}
\solution{Proof}{
With (3.2.12) we know
$$
|\Psi(x)| = \left|\frac{f^{(n)}(\xi)}{n!}\prod_{i=0}^n(x-x_i)\right| < \frac{1}{n!}h^{n+1}\times n! = h^{n+1}. 
$$
Then $\max|e^x-p_n(x)|\to 0$, when $n\to\infty$.
}
\end{document}

### 2017-10-06 Graduate - Numerical Analysis/Assignment 7/assignment.tex
add prob1, prob2

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Numerical Analysis \\ Assignment 7}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 3.28, Page 190.}
\solution{(a)}{
We know from the last two conditions (the first derivative),
$$
p'(x) = \frac{y_1'-y_0'}{x_1-x_0}(x-x_0)+y_0'.
$$
Integrate this polynomial we get
$$
p(x) = \frac{1}{2}\frac{y_1'-y_0'}{x_1-x_0}(x-x_0)^2+y_0'x+c.
$$
with boundary conditions we get $c = y_0-y_0'x_0$, then
$$
p(x) = y_0 + y_0'(x-x_0)\left(-\frac{(x-x_0)^2}{2(x_1-x_0)}+1\right)+y_1'\left(\frac{(x-x_0)^2}{2(x_1-x_0)}\right).
$$
}
\solution{(b)}{
We assume $p'(x_1) = y_1'$ is known. Then using Hermite interpolation we can get the fifth-order polynomial interpolation
$$
H(x) = \sum_{i=0}^{2}h_i(x) + \sum_{i=0}^{2}\tilde{h_i}(x),
$$
which satisfies
$$
\begin{aligned}
H(x_i) = y_i, ~0\le i\le 2, \\
H(x_i)' = y_i', ~0\le i\le 2.
\end{aligned}
$$
In order to get a fourth-order polynomial, we need to cancel out the coefficient of the fifth-order term, which means
$$
\sum_{i=0}^{2}(-2l_i'(x_i))\left(\frac{1}{\prod_{j\ne i}(x_i-x_j)}\right)^2y_i + \sum_{i=0}^{2}\left(\frac{1}{\prod_{j\ne i}(x_i-x_j)}\right)^2y_i' = 0.
$$
It shows
$$
\begin{aligned}
-2&\left(\frac{(x_0-x_1)+(x_0-x_2)}{(x_0-x_1)^3(x_0-x_2)^3}y_0+\frac{(x_1-x_0)+(x_1-x_2)}{(x_1-x_0)^3(x_1-x_2)^3}y_1+\frac{(x_2-x_0)+(x_2-x_1)}{(x_2-x_0)^3(x_2-x_1)^3}y_2\right) \\
+& \left(\frac{1}{(x_0-x_1)^2(x_0-x_2)^2}y_0'+\frac{1}{(x_1-x_0)^2(x_1-x_2)^2}y_1'+\frac{1}{(x_2-x_0)^2(x_2-x_1)^2}\right) = 0.
\end{aligned}
$$
with $x_i = x_0+ih$, this equation becomes
$$
y_1' = \frac{3}{4h}(y_2-y_0)-\frac{1}{4}(y_0'+y_2').
$$
Then the polynomial is 
$$
H(x) = \sum_{i=0}^{2}h_i(x) + \sum_{i=0}^{2}\tilde{h_i}(x),
$$
with
$$
\begin{aligned}
&h_i(x) = (1-2l_i'(x_i)(x-x_i))(l_i(x))^2, \\
&\tilde h_i(x) = (x-x_i)(l_i(x))^2,
\end{aligned}
$$
and $l_{i}(x)$ is the Lagrange basis.
}

\problem{2}{Problem 3.29, Page 190}
\solution{Solution}{
Assume the derivative of this quadratic polynomial is 
$$
p'(x) = a(x-x_1)+y_1'.
$$
Then integrate this we get
$$
p(x) = \frac{a}{2}(x-x_1)^2+y_1'x+c.
$$
with boundary conditions we know $a, c$ are the solutions of the linear equation system
$$
\left\{
\begin{aligned}
&\frac{(x_0-x_1)^2}{2}u+v = y_0-y_1'x_0 \\
&\frac{(x_2-x_1)^2}{2}u+v = y_0-y_1'x_2
\end{aligned}
\right.
$$
Thus the existence and uniqueness of this polynomial is equavilent to the existence and uniqueness of solution to the linear system.
Thus we know the matrix of coefficients is invertible, which means
$$
x_0 \ne x_2.
$$
Besides, in order to get a non-degenerated quadratic polynomial, the solution of $u \ne 0$. Thus
$$
y_1' \ne 0.
$$
}

\problem{3}{Problem 3.38, Page}

\end{document}

### 2017-10-07 Graduate - Numerical Analysis/Assignment 7/assignment.tex
add problem 3

@@
 $$
-H(x) = \sum_{i=0}^{2}h_i(x) + \sum_{i=0}^{2}\tilde{h_i}(x),
+H(x) = \sum_{i=0}^{2}h_i(x)y_i + \sum_{i=0}^{2}\tilde{h_i}(x)y'_i,
 $$
@@
 \problem{3}{Problem 3.38, Page}
+\solution{Solution}{
+Let $k(x) = \hat{s}(x)-g(x)$, then
+$$
+\begin{aligned}
+\int_{x_0}^{x_n}|g''(x)|^2dx &= \int_{x_0}^{x_n}|\hat{s}''(x)-k''(x)|^2dx \\
+&= \int_{x_0}^{x_n}|\hat{s}''(x)|^2dx-2\int_{x_0}^{x_n}\hat{s}''(x)k''(x)dx+\int_{x_0}^{x_n}|k''(x)|^2dx.
+\end{aligned}
+$$
+By integration by parts, 
+$$
+\left.\int_{x_0}^{x_n}\hat{s}''(x)k''(x)dx = \hat{s}''(x)k'(x)\right|_{x_0}^{x_n} - \int_{x_0}^{x_n}\hat{s}'''(x)k'(x)dx
+$$
+We know from the boundary conditions, 
+$$
+\hat{s}''(x_0) = \hat{s}''(x_n) = 0,
+$$
+thus the first term equals to $0$. Besides, since $\hat{s}(x)$ is a cubic polynomial, $\hat{s}'''(x)$ is a constant, denoted by $c$. Then 
+$$
+\left.\int_{x_0}^{x_n}\hat{s}'''(x)k'(x)dx = ck(x)\right|_{x_0}^{x_n} = c(k(x_n)-k(x_0)).
+$$
+We know from intepolation conditions that
+$$
+k(x_i) = \hat{s}(x_i) - g(x_i) = 0, ~0\le i\le n
+$$
+Thus the second term also equals to $0$. Then we know
+$$
+\int_{x_0}^{x_n}|g''(x)|^2dx = \int_{x_0}^{x_n}|\hat{s}''(x)|^2dx+\int_{x_0}^{x_n}|\hat{s}''(x)-g''(x)|^2dx \ge \int_{x_0}^{x_n}|\hat{s}''(x)|^2dx.
+$$
+}
 

### 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
add prob 2

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\labelenumi{\arabic{enumi}.}
\def\theenumi{\arabic{enumi}}
\def\labelenumii{(\alph{enumii})}
\def\theenumii{\alph{enumii}}
\def\p@enumii{\theenumi.}
\def\labelenumiii{\arabic{enumiii}.}
\def\theenumiii{\arabic{enumiii}}
\def\p@enumiii{(\theenumi)(\theenumii)}
\def\labelenumiv{\arabic{enumiv}.}
\def\theenumiv{\arabic{enumiv}}
\def\p@enumiv{\p@enumiii.\theenumiii}
\pagestyle{plain}
\setcounter{secnumdepth}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 5\\Sunday, October 8, 2017}\bigskip
\end{center}

\noindent\textbf{Instructions}: This and all subsequent homeworks must be submitted written in \LaTeX.

\noindent If you use results from books, Royden or others, please be explicit about what results you are using.

\begin{center}
\emph{Homework 5 is due by midnight, Saturday, October 21.}
\end{center} 
\medskip

\begin{enumerate}
\item  (Problem 24, Page 64) Let $I$ be an interval in $\mathbb{R}$ and let $f:I\to \mathbb{R}$ be increasing. Show that $f$ is measurable by first showing that, for each natural number $n$, the strictly increasing function $x\to f(x)+x/n$ is measurable, and then taking pointwise limits.

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
Denote $f_{n}(x) = f(x)+\frac{x}{n}$. Then since $f: I \to \mathbb{R}$ is increasing, $f_n(x)$ is strictly increasing on $I \in \{[a, b], [a, b), (a, b], (a, b)\}$.

For each fixed number $c$, if $\exists x_0\in I$, s.t. $f(x_0) = c$, then the set
$$
\{x\mid f(x) < c\} = (a, x_0),
$$
and the left side is the same as the set $I$, and it is an interval in $\mathbb{R}$, hence is measurable. Thus $f_{n}$ is measurable for every $n$.

For each $x\in I$, 
$$
\lim_{n\to\infty}f_n(x) = f(x)+\lim_{n\to\infty}\frac{x}{n} = f(x),
$$
hence $f_{n}$ converges to $f$ pointwise. Using Proposition 9, we know $f$ is measurable.
\bigskip

\item (Problem 8, Page 343)  Let $(X,\mathcal{M}, \mu)$ be a measure space.  The measure $\mu$ is said to be \textbf{semifinite} provided each measurable set of infinite measure contains measurable sets of arbitrarily large finite measure.
\begin{enumerate}
\item Show that each $\sigma$-finite measure is semifinite.
\item For $E\in \mathcal{M}$, define $\mu_1(E) = \mu(E)$, if $\mu(E)<\infty$, and if $\mu(E)=\infty$, define $\mu_1(E)=\infty$ if $E$ contains measurable sets of arbitrarily large finite measure and $\mu_1(E)= 0$ otherwise.  Show $\mu_1$ is a semifinite measure: it is called the semifinite part of $\mu$.
\item Find a measure $\mu_2$ on $\mathcal{M}$ that only takes the valures $0$ and $\infty$ and $\mu = \mu_1 + \mu_2$.
\end{enumerate}

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
\textbf{(a)} If $\mu$ is a $\sigma-$finite measure, then $X = \bigcup\limits_{n=1}^{\infty} X_i$, where $X_i$ has finite measure. Assume $E$ is a measurable set with infinite measure, then since $E\subset X$, $E = E\cap X = \bigcup\limits_{n=1}^{\infty} E\cap X_n$. For $\forall M > 0$, there must exist $N > 0$, s.t. $\mu\left(\bigcup\limits_{n=1}^{N}E\cap X_i\right) > M$, otherwise $\mu(E) \le \sum\limits_{n=1}^{\infty}\mu(E\cap X_n) < M_0$ for some $M_0 > 0$, which makes a contradiction with $\mu(E) = \infty$. Besides, we know from $\mu(X_i) < \infty$, that $\mu\left(\sum\limits_{n=1}^{N}(E\cap X_n)\right) < \infty$. Thus $\mu$ is semifinite.

\textbf{(b)} Suppose $E$ is a measurable set of infinite measure in the measure space $(X, \mathcal{M}, \mu_1)$. Then according to the definite of $\mu_1$, $E$ contains measurable sets of arbitrarily large finite measure. Thus $\mu_{1}$ is semifinite.

\textbf{(c)} Define $\mu_2$ like this: If $E$ can be represented as countable union of measurable sets with finite measure, then $\mu_2(E) = 0$. Otherwise $\mu_2(E) = \infty$.

First, we show that $\mu = \mu_1 + \mu_2$. If $\mu(E) < \infty$, then $E = \bigcup\limits_{n=1}^{\infty}E_n$, in which $E_n = \varnothing$ for $n \ge 2$. Thus $\mu_2(E) = 0 = \mu(E) - \mu_1(E)$. Now we assume $\mu(E) = \infty$. If $E$ can be represented as countable union of measurable sets with finite measure, that is, $E = \bigcup\limits_{n=1}^{\infty}E_n$ with $\mu(E_n) < \infty$, then with the continuity of measure, $\forall M > 0$, $\exists N > 0$, s.t. $\mu\left(\bigcup\limits_{n=1}^{N}E_n\right) > M$. Since $\mathcal{M}$ is a $\sigma-$algebra, it shows that $E$ contains measurable sets of arbitrarily large finite measure. Thus $\mu(E) = \infty = \mu_1(E) + 0 = \mu_1(E) + \mu_2(E)$. If $E$ can't be represented as countable union of measurable sets with finite measure, then $\mu(E) = \infty = \mu_1(E) +\mu_2(E)$.
% \textbf{(c)} First, when $\mu(E) < \infty$, $\mu_2(E) = \mu(E)-\mu_1(E) = 0$, and when $\mu(E) = \infty$ and $E$ does not contain measurable sets of arbitrarily large finite measure, $\mu_2(E) = \mu(E) - \mu_1(E) = \infty$. When $E$ contains measurable sets of arbitrarily large finite measure, define $\mu_2(E) = 0$. Hence $\mu = \mu_1 + \mu_2$.
% Now we consider the case when $\mu(E) = \infty$ and $E$ contains measurable sets with arbitrarily large finite measure.

% For $n = 1, 2, \cdots$, there is a measurable set $E_n \subset E$, s.t. $n \le \mu(E_n) < \infty$. Then with the Proposition of Continuity of Measure, 
% $$
% \mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \lim_{n\to\infty}\mu_2(E_n) = \infty.
% $$
% However, since each $E_n$ is a subset of $E$, we know $\bigcup\limits_{n=1}^{\infty}E_n $ is a subset of $E$. Then use the Monotocity property of measure, 
% $$
% \mu_2(E) \ge \mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \infty.
% $$
% Hence, when $\mu(E) = \infty$, $\mu_2(E) = \infty$. 
Now we show that $\mu_2$ is a measure. In fact, we only need to show that $\mu_2(\varnothing) = 0$, and $\mu_2$ is countably additive. First, from the definition we know $\mu(\varnothing) = 0 < \infty$, so $\mu_2(\varnothing) = 0$. Suppose $\{E_n\}_{n=1}^{\infty}$ is a sequence of disjoint measurable sets. If $\exists i$, s.t. $\mu_2(E_i) = \infty$. Then $E_i$ can't be represented as countable union of measurable sets with finite measure, thus $\bigcup\limits_{n=1}^{\infty}E_n $ can't be represented as countable union of measurable sets with finite measure. Then
$$
\mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \infty = \sum_{n=1}^{\infty}\mu_2(E_n).
$$
Now we suppose all $\mu_2(E_n) < \infty$. In this case, since $\mu_2$ takes value only in $\{0, \infty\}$, we have $\mu_2(E_n) = 0$. In this case, all $E_n$ is a countable union of measurable sets with finite measure, then $\bigcup\limits_{n=1}^{\infty}E_n $ is a countable union of measurable sets with finite measure. Thus
$$
\mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = 0 = \sum_{n=1}^{\infty}\mu_2(E_n).
$$
\bigskip

\item (Problem 9, Page 343) Prove Proposition 3, that is, show that $\mathcal{M}_0$ is a $\sigma$-algebra, $\mu_0$ is properly defined and $(X,\mathcal{M}_0, \mu_0)$ is complete.  In what sense is $\mathcal{M}_0$ minimal?

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item (Problem 10, Page 343) If $(X,\mathcal{M},\mu)$ is a measure space, we say that a subset $E$ of $X$ is \textbf{locally measurable} provided for each $B\in \mathcal{M}$ with $\mu(B)<\infty$, the intersection $E\cap B$ belongs to $\mathcal{M}$.  The measure $\mu$ is called \textbf{saturated} provided every locally measurable set is measurable.
\begin{enumerate}
\item Show that each $\sigma$-finite measure is saturated.
\item Show that the collection $\mathcal{C}$ of locally measurable sets is a $\sigma$-algebra.
\item Let $(X,\mathcal{M},\mu)$ be a measure space and $\mathcal{C}$ the $\sigma$ of locally measurable sets. For $E\in \mathcal{C}$, define $\overline{\mu}(E) = \mu(E)$ if $E\in \mathcal{M}$ and $\overline{\mu}(E) = \infty$ if $E\notin \mathcal{M}$.  Show that $(X,\mathcal{C},\overline{\mu})$ is a saturated measure space.
\item If $\mu$ is semifinite and $E\in \mathcal{C}$, set $\underline{\mu}(E)=\sup\{\mu(B)\mid B\in\mathcal{M},\, B\subseteq E \}$. Show that  $(X,\mathcal{C},\underline{\mu})$ is a saturated measure space and that $\underline{\mu}$ is an extension of $\mu$.  Give an example to show that $\overline{\mu}$ and $\underline{\mu}$ may be different.
\end{enumerate}

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

\item (Problem 18, Page 373)  Let $\{u_n\}$ be a sequence of nonnegative measurable functions on $X$.  For $x\in X$, define $f(x) = \sum_{n=1}^{\infty} u_n(x)$.  Show that \[
\int_X f \, d\mu = \sum_{n=1}^{\infty} \left[\int_X u_n \, d\mu \right].\]

\end{enumerate}
\end{document}

### 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
add prob 3

@@
 \textbf{Solution:}
+\textbf{(1)} We show $\mathcal{M}_0$ is a $\sigma-$algebra.
+\textbf{(1.1)} First, since $X\in \mathcal{M}, \emptyset\in\mathcal{M}$, and $X = X\cup\emptyset$, and $\mu(\emptyset) = 0$, we know $X\in\mathcal{M}_0$.
+\textbf{(1.2)} Suppose $E\in \mathcal{M}_0$, then $E = A\cup B$ where $B\in \mathcal{M}$ and $A\subset C$ for some $C\in\mathcal{M}$, and $\mu(C) = 0$.
+Then $E^c = A^c\cap B^c = (B^c\cap C^c)\cup(C\setminus A)$.
+Since $\mathcal{M}$ is a $\sigma-$algebra, we know $B^c, C^c, B^c\cup C^c \in \mathcal{M}$, and $C\setminus A \in \mathcal{M}$, and $(C\setminus A)\subset C$, with $\mu(C) = 0$.
+Hence $E^c\in\mathcal{M}_0 $.
+\textbf{(1.3)} Suppose $\{E_n\}$ is a sequence of sets in $\mathcal{M}_0$.
+We may assume $E_n = A_n\cup B_n$, where $B_n\in\mathcal{M}$, and $A_n\subset C_n$ for some $C_n\in\mathcal{M}$ with $\mu(C) = 0$.
+Then
+$$
+\bigcup\limits_{n=1}^{\infty}E_n = \left(\bigcup\limits_{n=1}^{\infty}A_n\right) \bigcup \left(\bigcup\limits_{n=1}^{\infty}B_n \right),
+$$
+and $\bigcup\limits_{n=1}^{\infty}B_n\in\mathcal{M} $.
+With the countable addivity of measure, $\bigcup\limits_{n=1}^{\infty}A_n\subset \bigcup\limits_{n=1}^{\infty}C_n\in\mathcal{M} $, and $\mu\left(\bigcup\limits_{n=1}^{\infty}C_n\right) = \sum\limits_{n=1}^{\infty}\mu(C_n) = 0$.
+Thus $\bigcup\limits_{n=1}^{\infty}E_n\in\mathcal{M} $.
+
+\textbf{(2)} We show $\mu_0$ is properly defined, which means $\mu_0$ satisfies the properties of measure.
+\textbf{(2.1)} First, for all $E\in\mathcal{M}_0$, suppose $E = A\cup B$ where $A\in\mathcal{M}$ and $B\subset C\in\mathcal{M}$ with $\mu(C) = 0$.
+Then $\mu_0(E) = \mu(A) \ge 0$.
+\textbf{(2.2)} Since $\emptyset\in\mathcal{M}$, and $\emptyset = \emptyset \cap \emptyset$ with $\mu(\emptyset) = 0$, we know $\mu_0(\emptyset) = \mu(\emptyset) = 0$.
+\textbf{(2.3)} Suppose $\{E_n\}$ is a countable collection of disjoint sets in $\mathcal{M}_0$, denote $E_n = A_n\cup B_n$, and $A_n\in\mathcal{M}$, $B_n\subset C_n\in\mathcal{M}$, with $\mu(C_n) = 0$.
+Then the same with \textbf{(1.3)}, we know
+$$
+\bigcup\limits_{n=1}^{\infty}E_n = \left(\bigcup\limits_{n=1}^{\infty}A_n\right) \bigcup \left(\bigcup\limits_{n=1}^{\infty}B_n \right),
+$$
+with $\bigcup\limits_{n=1}^{\infty}B_n\subset \bigcup\limits_{n=1}^{\infty}C_n\in\mathcal{M} $, and $\mu\left(\bigcup\limits_{n=1}^{\infty}C_n\right) = \sum\limits_{n=1}^{\infty}\mu(C_n) = 0$. Then
+$$
+\mu_0\left(\bigcup_{n=1}^{\infty}E_n\right) = \mu\left(\bigcup_{n=1}^{\infty}B_n\right) = \sum_{n=1}^{\infty}\mu(B_n) = \sum_{n=1}^{\infty}\mu_0(E_n).
+$$
+
+\textbf{(3)} We show $(X, \mathcal{M}_0, \mu_0)$ is complete.
+If $E\in\mathcal{M}_0$ and $\mu_0(E) = 0$, then $E = A\cup B$ where $A\in\mathcal{M}$ and $B\subset C\in \mathcal{M}$ and $\mu(C) = 0$, and $\mu(A) = \mu_0(E) = 0$.
+Then each subset $F\subset E$ has a form $E = \emptyset \cup F$, and $F\subset (A\cup C)$ where $\mu_0(A\cup C) = \mu(A)+\mu(C) = 0$, and $A\cup C, \emptyset \in \mathcal{M}$.
+Thus $F\in\mathcal{M}_0$.
+
 \bigskip

### 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
add prob 1

--- 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
@@
 \bigskip
-\textbf{Collaborators:} None
+\textbf{Collaborators:} None\\
 \smallskip
@@
 \bigskip
-\textbf{Collaborators:} None
+\textbf{Collaborators:}\\
 \smallskip
@@
 \textbf{Solution:}
-\textbf{(a)} If $\mu$ is a $\sigma-$finite measure, then $X = \bigcup\limits_{n=1}^{\infty} X_i$, where $X_i$ has finite measure.
-Assume $E$ is a measurable set with infinite measure, then since $E\subset X$, $E = E\cap X = \bigcup\limits_{n=1}^{\infty} E\cap X_n$.
-For $\forall M > 0$, there must exist $N > 0$, s.t.
-$\mu\left(\bigcup\limits_{n=1}^{N}E\cap X_i\right) > M$, otherwise $\mu(E) \le \sum\limits_{n=1}^{\infty}\mu(E\cap X_n) < M_0$ for some $M_0 > 0$, which makes a contradiction with $\mu(E) = \infty$.
-Besides, we know from $\mu(X_i) < \infty$, that $\mu\left(\sum\limits_{n=1}^{N}(E\cap X_n)\right) < \infty$.
-Thus $\mu$ is semifinite.
-
-\textbf{(b)} Suppose $E$ is a measurable set of infinite measure in the measure space $(X, \mathcal{M}, \mu_1)$.
-Then according to the definite of $\mu_1$, $E$ contains measurable sets of arbitrarily large finite measure.
-Thus $\mu_{1}$ is semifinite.
-
-\textbf{(c)} Define $\mu_2$ like this: If $E$ can be represented as countable union of measurable sets with finite measure, then $\mu_2(E) = 0$. Otherwise $\mu_2(E) = \infty$.
-
-First, we show that $\mu = \mu_1 + \mu_2$.
-If $\mu(E) < \infty$, then $E = \bigcup\limits_{n=1}^{\infty}E_n$, in which $E_n = \varnothing$ for $n \ge 2$.
-Thus $\mu_2(E) = 0 = \mu(E) - \mu_1(E)$.
-Now we assume $\mu(E) = \infty$.
-If $E$ can be represented as countable union of measurable sets with finite measure, that is, $E = \bigcup\limits_{n=1}^{\infty}E_n$ with $\mu(E_n) < \infty$, then with the continuity of measure, $\forall M > 0$, $\exists N > 0$, s.t.
-$\mu\left(\bigcup\limits_{n=1}^{N}E_n\right) > M$.
-Since $\mathcal{M}$ is a $\sigma-$algebra, it shows that $E$ contains measurable sets of arbitrarily large finite measure.
-Thus $\mu(E) = \infty = \mu_1(E) + 0 = \mu_1(E) + \mu_2(E)$.
-If $E$ can't be represented as countable union of measurable sets with finite measure, then $\mu(E) = \infty = \mu_1(E) +\mu_2(E)$.
-% \textbf{(c)} First, when $\mu(E) < \infty$, $\mu_2(E) = \mu(E)-\mu_1(E) = 0$, and when $\mu(E) = \infty$ and $E$ does not contain measurable sets of arbitrarily large finite measure, $\mu_2(E) = \mu(E) - \mu_1(E) = \infty$.
-When $E$ contains measurable sets of arbitrarily large finite measure, define $\mu_2(E) = 0$.
-Hence $\mu = \mu_1 + \mu_2$.
-% Now we consider the case when $\mu(E) = \infty$ and $E$ contains measurable sets with arbitrarily large finite measure.
-
-% For $n = 1, 2, \cdots$, there is a measurable set $E_n \subset E$, s.t. $n \le \mu(E_n) < \infty$. Then with the Proposition of Continuity of Measure, 
-% $$
-% \mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \lim_{n\to\infty}\mu_2(E_n) = \infty.
-% $$
-% However, since each $E_n$ is a subset of $E$, we know $\bigcup\limits_{n=1}^{\infty}E_n $ is a subset of $E$. Then use the Monotocity property of measure, 
-% $$
-% \mu_2(E) \ge \mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \infty.
-% $$
-% Hence, when $\mu(E) = \infty$, $\mu_2(E) = \infty$. 
-Now we show that $\mu_2$ is a measure.
-In fact, we only need to show that $\mu_2(\varnothing) = 0$, and $\mu_2$ is countably additive.
-First, from the definition we know $\mu(\varnothing) = 0 < \infty$, so $\mu_2(\varnothing) = 0$.
-Suppose $\{E_n\}_{n=1}^{\infty}$ is a sequence of disjoint measurable sets.
-If $\exists i$, s.t.
-$\mu_2(E_i) = \infty$.
-Then $E_i$ can't be represented as countable union of measurable sets with finite measure, thus $\bigcup\limits_{n=1}^{\infty}E_n $ can't be represented as countable union of measurable sets with finite measure.
-Then
-$$
-\mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = \infty = \sum_{n=1}^{\infty}\mu_2(E_n).
-$$
-Now we suppose all $\mu_2(E_n) < \infty$.
-In this case, since $\mu_2$ takes value only in $\{0, \infty\}$, we have $\mu_2(E_n) = 0$.
-In this case, all $E_n$ is a countable union of measurable sets with finite measure, then $\bigcup\limits_{n=1}^{\infty}E_n $ is a countable union of measurable sets with finite measure.
-Thus
-$$
-\mu_2\left(\bigcup_{n=1}^{\infty}E_n\right) = 0 = \sum_{n=1}^{\infty}\mu_2(E_n).
-$$
 \bigskip

### 2017-10-10 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
add prob 4

--- 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
@@
 \textbf{Solution:}
+\textbf{(a)} Suppose $\mu$ is a $\sigma-$finite measure.
+Then $X = \bigcup\limits_{n=1}^{\infty}X_n $ with $X_n$ measurable and $\mu(X_n) < \infty$.
+Suppose $E$ is a locally measurable set, then for all $X_n$, $E\cap X_n \in\mathcal{M}$.
+Thus $E = \bigcup\limits_{n=1}^{\infty}(E\cap X_n) \in\mathcal{M}$.
+
+\textbf{(b)} \textbf{(b.1)} First, for all $B\in\mathcal{M}$, $\mu(B) < \infty$, $X\cap B = B\in\mathcal{M}$. Hence $X\in \mathcal{C}$. 
+\textbf{(b.2)} Suppose $E\in\mathcal{C}$, then for each $B\in\mathcal{M}$ with $\mu(B) < \infty$, $E\cap B \in\mathcal{M}$. Then $E^c\cap B = B\setminus (E\cap B) \in\mathcal{M}$.
+\textbf{(b.3)} Suppose $\{E_n\}\in \mathcal{C}$ is a sequence of local measurable sets.
+Then for each $B\in\mathcal{M}$ and $\mu(B) < \infty$, for all $n$, $E_n\cap B\in\mathcal{M} $.
+Then fix $B$, we get
+$$
+\left(\bigcup_{n=1}^{\infty}E_n\right)\cap B = \bigcup_{n=1}^{\infty}(E_n\cap B)\in\mathcal{M}.
+$$
+Hence $\mathcal{C}$ is a $\sigma-$algebra.
+
+\textbf{(c)} \textbf{(c.1)} First we show $\overline\mu$ is a measure.
+First, $\overline\mu(E) \ge \mu(E)\ge 0$.
+As $\emptyset\in\mathcal{M}$, $\overline\mu(\emptyset) = \mu(\emptyset) = 0$.
+Suppose $\{E_n\}\in\mathcal{C}$ is a sequence of disjoint sets, then if $\exists i$, s.t.
+$E_i\notin\mathcal{M}$, then $\bigcup\limits_{n=1}^{\infty}E_n \notin\mathcal{M}$.
+Thus
+$$
+\overline\mu\left(\bigcup\limits_{n=1}^{\infty}E_n\right) = \infty = \sum_{n=1}^{\infty}\overline\mu(E_n).
+$$
+Now suppose $E_n\in\mathcal{M}$. Thus the countably additive property of $\overline\mu$ is the same as $\mu$.
+\textbf{(c.2)} Now suppose $B\in\mathcal{C}$ and $\overline\mu(B)< \infty$, then $B\in\mathcal{M}$, otherwise $\overline\mu(B) = \infty$.
+Suppose $E$ is a local measurable set, then $E\cap B\in\mathcal{C}$, thus according to the definition of $\mathcal{C}$, we know $E\in\mathcal{C}$.
+Thus $(X, \mathcal{C}, \overline\mu)$ is a saturated measure space.
+
+\textbf{(d)} \textbf{(d.1)} First we show $\underline{\mu}$ is a measure.
+$\underline{\mu}(E) \ge\mu(E)\ge 0$, $\underline{\mu}(\emptyset) = \sup\{\mu(B)\mid B\in\mathcal{M}, B\subset\emptyset\} = 0$.
+Suppose $\{E_n\}\in\mathcal{C}$ is a sequence of disjoint sets, then if all $E_n\in\mathcal{M}$, we have $\underline{\mu}(E_n) = \mu(E_n)$.
+Using the countable addivity of $\mu$ we can get the countable addivity of $\underline{\mu}$.
+Now suppose $E_n\notin\mathcal{M}$.
+Then using the countable addivity of $\mu$,
+$$
+\underline{\mu}\left(\bigcup_{n=1}^{\infty}E_n \right) = \sup\left\{\mu(B)\mid B\in\mathcal{M}, B\subset\bigcup_{n=1}^{\infty}E_n\right\} = \sum_{n=1}^{\infty} \sup\{\mu(B)\mid B\in\mathcal{M}, B\subset E_n\} = \sum_{n=1}^{\infty}\underline{\mu}(E_n).
+$$
+\textbf{(d.2)} In \textbf{(d.1)} we have shown $\underline{\mu}$ is an extension of $\mu$.
+Now we show $(X, \mathcal{C}, \underline{\mu})$ is a saturated measure space.
+Suppose $E$ is a locally measurable set, then for each $B\in\mathcal{C}$, $\underline\mu(B) < \infty$, $E\cap B\in\mathcal{C}$.
+For all $F\in\mathcal{F}$ with $\mu(F) < \infty$, we have $\underline{\mu}(F) = \mu(F) < \infty$.
+Thus $E\cap F\in\mathcal{C}$, and it means $E$ is measurable in $(X, \mathcal{C}, \underline{\mu})$.
+Hence, $(X, \mathcal{C}, \underline{\mu})$ is a saturated measure space.
+
+% If $B\in\mathcal{M}$, and if $\mu(B) = \infty$,  since $\mu$ is semifinite, $\forall M > 0, \exists B_M\subset B\in\mathcal{M} $, s.t.
+$\mu(B_M) > M$.
+Then $\underline{\mu}(B) = \infty$, which makes a contradiction.
+Thus $\mu(B) < \infty$.
+% then if $\exists n$, $\mu(E_n) = \infty$, then $\underline\mu(E_n) = \sup\{\mu(B)\mid B\in\mathcal{M}, B\subset E_n\}$.
+Since $\mu$ is semifinite, $\forall M > 0, \exists B\in\mathcal{M}$, s.t.
+$\mu(B_M) > M$.
+Thus $\underline{\mu}(E_n) = \infty$, and $B_{M}\subset\bigcup\limits_{n=1}^{\infty}E_n$.
+We have
+% $$
+% \underline{\mu}\left(\bigcup_{n=1}^{\infty}E_n \right) = \infty = \sum_{n=1}^{\infty}\underline{\mu}(E_n).
+% $$
+% If $\mu(E_n) < \infty$, 
 \bigskip

### 2017-10-28 Graduate - Numerical Analysis/Assignment 10/assignment.tex
add two probs

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Numerical Analysis \\ Assignment 9}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 4.16, Page 242}
\solution{Solution}{
For each $m < n$, by integration by parts, 
$$
\begin{aligned}
\int_{0}^{\infty}e^{-x} x^m \varphi_n(x)dx &= \frac{(-1)^n}{n!}\int_{0}^{\infty} x^m\frac{d^n}{dx^n}(x^ne^{-x})dx \\
&= \frac{(-1)^n}{n!}\left.\left(x^m\frac{d^{n-1}}{dx^{n-1}}(x^ne^{-x})\right|_{0}^{\infty}-\int_{0}^{\infty}mx^{m-1}\frac{d^{n-1}}{dx^{n-1}}(x^ne^{-x})dx \right)
\end{aligned}
$$
Since 
$$
x^m\frac{d^{n-1}}{dx^{n-1}}(x^ne^{-x}) = e^{-x}N(x),
$$
where $N(x)$ is a polynomial of degree $n-1+m$, by L'Hospital's Rule we know the first term in the integration is $0$. Then by induction we know
$$
\begin{aligned}
\int_{0}^{\infty}e^{-x} x^m \varphi_n(x)dx &= \frac{(-1)^{n+1}m}{n!}\int_{0}^{\infty}x^{m-1}\frac{d^{n-1}}{dx^{n-1}}(x^n e^{-x})dx \\ 
&= \frac{(-1)^{n+m}m!}{n!}\int_{0}^{\infty}\frac{d^{n-m}}{dx^{n-m}}(x^n e^{-x})dx \\
&= \frac{(-1)^{n+m}m!}{n!}\frac{d^{n-m}}{dx^{n-m}}\int_{0}^{\infty}x^n e^{-x}dx \\
&= \frac{(-1)^{n+m}m!}{n!}\frac{d^{n-m}}{dx^{n-m}} (n!) = 0.
\end{aligned}
$$
In the deduction we used the property that $f(x) = x^n e^{-x}$ is absolutely continuous. Since $\varphi_m(x)$ is a polynomial of degree $m < n$, we know 
$$
(\varphi_n(x), \varphi_m(x)) = 0, ~\text{and}~ (\varphi_n(x), \varphi_n(x)) \ne 0.
$$
Hence $\{\varphi_n(x)\}$ is a family of orthogonal polynomials.
}

\problem{2}{Problem 4.18, Page 242}
\solution{Solution}{
First, we derive $c_n$. Multiply both sides of (4.4.21) by $w(x)\varphi_{n-1}(x)$, and then integrate, we get
$$
\int w\varphi_{n+1}\varphi_{n-1}dx = \int a_n wx\varphi_n\varphi_{n-1} + \int b_nw\varphi_n\varphi_{n-1} - c_n\int w\varphi_{n-1}^2.
$$
Using the orthogonality of $\varphi_n$, the left side is 0, and the second term of right side is 0. Then 
$$
a_n\int wx\varphi_n\varphi_{n-1} = c_n\int w\varphi_{n-1}^2.
$$
Since
$$
a_n\int wx\varphi_n\varphi_{n-1} = a_n\int  w\varphi_n(A_{n-1}x^n+B_{n-1}x^{n-1}+\cdots) = a_n\int w\varphi_n A_{n-1}x^n = a_n \frac{A_{n-1}}{A_n}\int w\varphi_n^2,
$$
we have
$$
c_n = \frac{a_n A_{n-1}\gamma_n}{A_n\gamma_{n-1}} = \frac{A_{n+1}A_{n-1}\gamma_n}{A_n^2\gamma_{n-1}}.
$$
Now we consider $b_n$. Multiply both sides of (4.4.21) by $w(x)\varphi_n(x)$, then integrate both sides, we get
$$
\int w\varphi_{n+1}\varphi_n = \int a_n wx\varphi_n^2+ \int b_n w\varphi_n^2 - \int c_n w\varphi_{n-1}\varphi_n.
$$
Using orthogonality, we get
$$
\int a_n wx\varphi_n^2 + \int b_n w\varphi_n^2 = 0.
$$
The first term can be wrote as 
$$
\begin{aligned}
\int a_n wx\varphi_n^2 &= a_n\int w(A_n x^{n+1}+B_n x+\cdots)\varphi_n = a_n \int w (\frac{A_n}{A_{n+1}}\varphi_{n+1}- \frac{A_n B_{n+1}-A_{n+1}B_n}{A_{n+1}}x^n+\cdots)\varphi_n \\
&= a_n\int w(B_n -\frac{A_n}{A_{n+1}}B_{n+1})x^n\varphi_n = a_n\int w\frac{1}{A_n}(B_n -\frac{A_n}{A_{n+1}}B_{n+1})\varphi_n^2.
\end{aligned}
$$
Thus
$$
a_n (\frac{B_n}{A_n}-\frac{B_{n+1}}{A_{n+1}}) \gamma_n + b_n\gamma_n = 0,
$$
we know
$$
b_n = a_n (\frac{B_{n+1}}{A_{n+1}} - \frac{B_n}{A_n}).
$$
}

\problem{3}{Problem 4.21, Page 243}

\problem{4}{Problem 4.23, Page 243}

\end{document}

### 2017-10-28 Graduate - Numerical Analysis/Assignment 10/assignment.tex
add prob 3, 4

@@
 \problem{3}{Problem 4.21, Page 243}
+\solution{Proof}{
+Denote $\varphi_n(x) = A_n x^n+B_n x^{n-1}+\cdots $, and $A_n > 0$. Then by (4.4.21), 
+$$
+\varphi_{n+1}(x) = (a_n x+b_n)\varphi_n(x)-c_n\varphi_{n-1}(x).
+$$
+We add a $\varphi_0(x)$ to this series, and $\varphi_{0}(x) = A_0 > 0$.
+First, when $n = 1$, since
+$$
+\int_{a}^{b} w(x)\varphi_1(x)\varphi_0(x)dx = \int_{a}^{b}A_0w(x)\varphi_1(x)dx = 0 = A_0\varphi_1(\xi)\int_{a}^{b}w(x) dx,
+$$
+we know $\varphi_1(\xi) = 0, ~\xi\in (a, b)$. Then we show $\varphi_2(x)$ has two different roots in $(a, b)$. First,
+$$
+\varphi_2(\xi) = (a_1\xi+b_1)\varphi_1(\xi)-c_1\varphi_0(\xi) = -c_1\varphi_0(\xi) < 0.
+$$
+Suppose $\varphi_2(x)$ does not change sign in $(a, b)$, then
+$$
+\int w(x)\varphi_2(x)\varphi_0(x) = A_0\int w(x) \varphi_2(x) < 0.
+$$
+It makes a contradiction with orthogonality.
+Then there $\exists x_1\in(a, b) $, s.t.
+$\varphi_2(x_1) = 0$.
+Since $A_2 > 0$, $x_1$ cannot be a double root.
+If $\varphi_2(x)$ has only one root in $(a, b)$, then
+$$
+\varphi_2(x)(x-x_1) = q(x)(x-x_1)^2,
+$$
+integrate by $w(x)$, then since $(x-x_1)$ is of degree 1, left side is 0.
+But we know $q(x)$ has no root in $(a, b)$, it does not change sign in $(a, b)$, thus the integration is not 0.
+It makes a contradiction.
+Thus $\varphi_2(x)$ has two different roots in $(a, b)$, and with $\varphi_2(\xi) < 0$ and $A_2 > 0$, we know the two roots are in $(a, \xi)$ and $(\xi, b)$ seperately.
+Using the same method, we know that $\varphi_n(x)$ has $n$ different roots in $(a, b)$.
+
+Now we assume this proposition holds for $\varphi_m(x)$, $m \le n$. Denote roots of $\varphi_{n}(x)$ to be $x_i$, then since
+$$
+\varphi_{n+1}(x_i) = (a_n x_i+b_n)\varphi_n(x_i)-c_n\varphi_{n-1}(x_i) = -c_n\varphi_{n-1}(x_i),
+$$
+$$
+\varphi_{n+1}(x_{i+1}) = (a_n x_{i+1}+b_n)\varphi_n(x_{i+1})-c_n\varphi_{n-1}(x_{i+1}) = -c_n\varphi_{n-1}(x_{i+1}),
+$$
+from the assumption we know $\varphi_{n-1}(x_i) $ and $\varphi_{n-1}(x_{i+1}) $ has different signs, which means $\varphi_n(x) $ has a root in each of this intervals.
+Then from $\varphi_n $ has $n$ different roots in $(a, b)$, from induction we get the result.
+}
 
 \problem{4}{Problem 4.23, Page 243}
-
+\solution{Solution}{
+We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials:
+$$
+T_0(x) = 1, ~T_1(x) = x, ~T_2(x) = 2x^2-1.
+$$
+For any $p(x) = a_0+a_1x+a_2x^2 $ of degree 2 that minimizes the distance, we have
+$$
+a_j = (f, T_j), ~j = 0, 1, 2.
+$$
+Thus
+$$
+a_0 = (f, T_0) = \int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \int_{\pi}^{0}-ydy = \frac{\pi^2}{2},
+$$
+$$
+a_1 = (f, T_1) = \int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi} y\cos ydy = y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy = -2,
+$$
+$$
+a_2 = (f, T_2) = \int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi}y\cos 2ydy = \frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy = -\frac{1}{2}.
+$$
+Thus
+$$
+p_2(x) = -\frac{1}{2}x^2-2x+\frac{\pi^2}{2}.
+$$
+}
 \end{document}

### 2017-10-29 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
update

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Introduction to Analysis \\ Assignment 6}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 29, Section 4.4, Page 89}
\solution{Sol}{
Both are not true. We can construct a $f$ like this:
$$
f(x) = \left\{
\begin{aligned}
1+\frac{1}{n^2}, ~n \le x < n+\frac{1}{2}, ~\forall n\in\mathbb{N} \\
-1, ~n+\frac{1}{2} \le x < n+1, ~\forall n\in\mathbb{N}
\end{aligned}
\right.
$$
Then $f$ is measurable, and $f$ is bounded on any bounded set, and
$$
a_n = \int_{n}^{n+1}f = \frac{1}{2n^2}.
$$
Clearly the series $\sum\limits_{n=1}^{\infty}a_n = \sum\limits_{n=1}^{\infty}\frac{1}{2n^2} $ converges absolutely, but 
$$
\int_{1}^{\infty}|f| = \sum_{n=1}^{\infty}(1+\frac{1}{2n^2}) = \infty,
$$
which means $f$ is not integratable on $[1, \infty)$.
}

\problem{2}{Problem 33, Section 4.4, Page 90}
\solution{Proof}{
First,
$$
|f_n-f| \le |f| + |f_n|, ~\forall n.
$$
Then since $f$ is integratable on $E$, if $\lim\limits_{n\to\infty}\int_E |f_n| = \int_{E}|f| $, we know $|f_n|+|f|$ converges pointwise a.e. to $2|f|$, and
$$
\lim_{n\to\infty}\int_E(|f_n|+|f|) = 2\int_E |f| < \infty,
$$
with General Lebesgue Dominated Convergence Theorem, notice $|f_n-f| $ converges pointwise a.e. to 0,
$$
\lim_{n\to\infty}\int_E|f_n-f| = \int_E 0 = 0.
$$
On the other hand, notice
$$
|f_n|-|f| \le |f_n-f|, ~\forall n.
$$
with the same method, since $\int_E|f-f_n|\to 0 $, and $|f-f_n| $ converges pointwise to 0,
$$
\lim_{n\to\infty}\int_E |f_n-f| = \int_E 0 = 0,
$$
we know from $|f_n|-|f| $ converges pointwise a.e. to 0,
$$
\lim_{n\to\infty}\int_E |f_n|-|f| = \int_E 0 = 0.
$$
Hence
$$
\lim_{n\to\infty}\int_E|f_n| = \int_E |f|.
$$
}

\end{document}

### 2017-10-29 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
add prob 1-6

@@
 $$
-which means $f$ is not integratable on $[1, \infty)$.
+which means $f$ is not integrable on $[1, \infty)$.
 }
@@
 $$
-Then since $f$ is integratable on $E$, if $\lim\limits_{n\to\infty}\int_E |f_n| = \int_{E}|f| $, we know $|f_n|+|f|$ converges pointwise a.e. to $2|f|$, and
+Then since $f$ is integrable on $E$, if $\lim\limits_{n\to\infty}\int_E |f_n| = \int_{E}|f| $, we know $|f_n|+|f|$ converges pointwise a.e. to $2|f|$, and
 $$
@@
 
+\problem{3}{Problem 35, Section 4.4, Page 90}
+\solution{Proof}{
+Denote $f_n(x) = f(x, a_n) $, in which $\{a_n\}$ is any series which converges to 0.
+Then from the condition we know $f_n(x) $ converges pointwise to $f(x)$, and $|f_n(x)| \le g(x)$.
+Then using Lebesgue Dominated Convergence Theorem, since $g$ is integrable on $[0, 1]$, we have
+$$
+\lim_{n\to\infty} \int_{0}^{1}f_n(x)dx = \int_{0}^{1} f(x)dx.
+$$
+It shows that 
+$$
+\limsup_{y\to 0}\int_{0}^{1}f(x, y)dx = \liminf_{y\to 0}\int_{0}^{1}f(x, y)dx = \int_{0}^{1}f(x)dx, 
+$$
+whic means 
+$$
+\lim_{y\to 0}\int_{0}^{1}f(x, y) dx = \int_{0}^{1}f(x)dx.
+$$
+For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)|dx < \epsilon$.
+Since $f(x, y)$ is continuous in $y$ for each $x$, then for each fixed $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$.
+Then
+$$
+|h(y)-h(y_0)| = \left|\int_{0}^{1} f(x, y)dx - \int_{0}^{1} f(x, y_0)dx\right| \le \int_{0}^{1} |f(x, y)-f(x, y_0)|dx < \epsilon.
+$$
+We know the continuity of $h$ since we can pick $\delta = \delta_1 $.
+}
+
+\problem{4}{Problem 36, Section 4.4, Page 90}
+\solution{Proof}{
+For any fixed $y\in [0, 1]$, suppose $\{h_n\}$ is a sequence with $h_n\to 0 $. Let
+$$
+f_n(x) = \frac{f(x, y+h_n)-f(x, y)}{h_n}
+$$
+Since $\partial f/\partial y$ exists, 
+$$
+\lim_{n\to\infty}f_n(x) = \lim_{h\to 0}\frac{f(x, y+h)-f(x, y)}{h} = \frac{\partial f}{\partial y}(x, y).
+$$
+It means $f_n(x)$ converges pointwise to $\frac{\partial f}{\partial y}(x, y)$.
+Thus
+$$
+\exists N > 0, ~\forall n > N, \left|f_n(x) - \frac{\partial f}{\partial y}(x, y)\right| < 1.
+$$
+Since 
+$$
+\left|\frac{\partial f}{\partial y}(x, y)\right| \le g(x)
+$$
+we have
+$$
+|f_n(x)| \le g(x)+1,
+$$
+and $g(x)+1$ is integrable on $[0, 1]$. By Lebesgue Dominated Convergence Theorem,
+$$
+\int_{0}^{1}f_n(x)dx \to \int_{0}^{1}\frac{\partial f}{\partial y}(x, y)dx.
+$$
+Since $\{h_n\}$ is arbitrary, and $f_n$ is integrable, we know
+$$
+\limsup_{n\to\infty}\int_{0}^{1}f_n(x)dx = \liminf_{n\to\infty}\int_{0}^{1}f_n(x) dx = \lim_{h\to 0}\frac{1}{h}\left(\int_0^1 f(x, y+h)dx-\int_{0}^{1}f(x, y)dx\right) = \frac{d}{dy}\int_{0}^{1}f(x, y)dx.
+$$
+}
+
+\problem{5}{Problem 38, Section 4.5, Page 91}
+\solution{(i)}{
+$$
+\lim_{n\to\infty}\int_{0}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
+$$
+But
+$$
+\int_{1}^{\infty}f^+ = \sum_{m=1}^{\infty}\frac{1}{2m} = \infty,
+$$
+So $f$ is not integrable.
+}
+\solution{(ii)}{
+$$
+\lim_{n\to\infty}\int_{1}^{n}f = \int_{1}^{\infty}\frac{\sin x}{x}dx,
+$$
+with Dirichlet's Criterion, we know this integral converges. But
+$$
+\int_{1}^{\infty}|f| \ge \int_{1}^{\infty}\frac{1}{2x}dx - \int_{1}^{\infty}\frac{\cos 2x}{x}dx,
+$$
+and the second term converges with Dirichlet's Criterion, but the first term $\to\infty$, we know this integral diverges to $\infty$. Thus $f$ is not integrable.
+
+This two counterexamples do not contradict to the continuity: $f$ is not integrable over the whole set $E = [1, \infty)$.
+}
+
+\problem{9}{Problem 39, Section 4.5, Page 91}
+\solution{Proof (i)}{
+Denote 
+$$
+F_1 = E_1, ~F_n = E_n \setminus \bigcup_{m=1}^{n-1}E_m, ~n \ge 2.
+$$
+Then $\{F_i\}$ is a sequence of disjoint measurable subsets of $E$. Then using Theorem 20,
+$$
+\int_{\cup_{n=1}^{\infty}E_n} f = \sum_{n=1}^{\infty}\int_{F_n}f = \lim_{n\to\infty}\sum_{m=1}^{n}\int_{F_m}f = \lim_{n\to\infty}\int_{E_n}f.
+$$
+}
+\solution{Proof of (ii)}{
+Using the same method with (i), only changing $F$ to 
+$$
+F_1 = E_1, ~F_n = E_1 \setminus\bigcup_{m=1}^{n-1}E_m, ~n\ge 2.
+$$
+The other parts of proof is just the same.
+}
 \end{document}

### 2017-10-29 LeetCode/443. String Compression.cpp

@@ -1,0 +1,41 @@
+class Solution {
+public:
+    int compress(vector<char>& chars) {
+        if(!chars.size()) return 0;
+        int i = chars.size()-2, local = 1;
+        char last = chars.back();
+        while(i >= 0) {
+            if(chars[i] != last) {
+                if(local == 1) {
+                    last = chars[i];
+                    i--;
+                    local = 1;
+                    continue;
+                }
+                else {
+                    chars.erase(chars.begin()+i+2, chars.begin()+i+local+1);
+                    while(local) {
+                        char c = local%10 + '0';
+                        local /= 10;
+                        chars.insert(chars.begin()+i+2, c);
+                    }
+                }
+                last = chars[i];
+                local = 1;
+            }
+            else {
+                local++;
+            }
+            i--;
+        }
+        if(local != 1) {
+            chars.erase(chars.begin()+1, chars.begin()+local);
+            while(local) {
+                char c = local%10 + '0';
+                local /= 10;
+                chars.insert(chars.begin()+1, c);
+            }
+        }
+        return chars.size();
+    }
+};

### 2017-10-30 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex

@@
 
-\problem{9}{Problem 39, Section 4.5, Page 91}
+\problem{6}{Problem 39, Section 4.5, Page 91}
 \solution{Proof (i)}{
@@
 }
+
+\problem{7}{Problem 44, Section 4.6, Page 95}
+\solution{(i)}{
+First, when $f$ is nonnegative, from the definition of integrable functions we know for any $\epsilon > 0$, there is a bounded measurable function with finite support $0 \le h(x) \le f(x)$, s.t. 
+$$
+\int_{\mathbb{R}} (f-h) = \int_{\mathbb{R}}f - \int_{\mathbb{R}}h \le \frac{1}{2}\epsilon.
+$$
+Let the support set of $h$ be $M$ with $m(M) < \infty$.
+Then using Simple Approximation Theorem, there is a simple function $\eta$ on M, s.t.
+$0 \le h - \eta \le \frac{\epsilon}{2m(M)}$.
+Let $\eta = 0$ on $\mathbb{R}\setminus M$, then $\eta$ has finite support, and
+$$
+\int_{\mathbb{R}}|f-\eta| = \int_{\mathbb{R}}(f-h+h-\eta) = \int_{\mathbb{R}}f-h + \int_{M} h-\eta \le \frac{1}{2}\epsilon + m(M)\frac{\epsilon}{2m(M)} = \epsilon.
+$$
+When $f$ is an arbitrary integrable function, $f^+, ~f^- $ are nonnegative functions.
+Let $E_+ = \{x\mid f^+ > 0\}, ~E_- = \{x\mid f^- > 0\} $, then there exists nonnegative simple functions $\eta^+, ~\eta^- $, s.t.
+$\eta^+ = 0 $ on $\mathbb{R}\setminus E_+ $, and $\eta^+ $ has finite support on $E_+ $, $\eta^- = 0 $ on $\mathbb{R}\setminus E_- $, and $\eta^- $ has finite support on $E_- $, and they satisfies
+$$
+\int_{\mathbb{R}} |f^+-\eta^+| < \epsilon, ~\int_{\mathbb{R}} |f^--\eta^-| < \epsilon.
+$$
+Let
+$$
+\eta = \left\{
+\begin{aligned}
+\eta^+, ~x\in E_+ \\ 
+\eta^-, ~x\in E_-
+\end{aligned},
+\right.
+$$
+then $\eta = \eta^+-\eta^- $ is a simple function with finite support, and
+$$
+\int_{\mathbb{R}}|f-\eta| = \int_{\mathbb{R}} |f^+-f^--(\eta^+-\eta^-)| \le \int_{\mathbb{R}}|f^+-\eta^+| + \int_{\mathbb{R}}|f^--\eta^-| < 2\epsilon.
+$$
+}
+\solution{(ii)}{
+From (i) we know there is a simple function $\eta$ which has finite support (denoted as $E$) and $\int_{\mathbb{R}}|f-\eta| < \epsilon $.
+Since $E$ is a measurable set of finite measure, with Lemma 22, for any $\delta_1 > 0$, there is a $n > 0$,
+$$
+m(E\cap(\mathbb{R}\setminus [-n, n])) < \delta_1.
+$$
+Let $I = [-n, n]$, using the result of Problem 3.18, for any $\delta_2 > 0$, there is a step function $s$ on $I$, and a close set $F\subset I$, s.t.
+$|\eta - s| < \delta_2 $ on $F$, and $m(I\setminus F) < \delta_2 $.
+Set $s(x) = 0$ for $x$ outside $I$.
+
+With Proposition 23, for each $\epsilon > 0$, $\exists \delta > 0 $, if $m(A) < \delta$, then $\int_{A}|f| < \epsilon $. Let $\delta_1 = \delta$, $\delta_2 = \min(\delta, \frac{\epsilon}{2n}) $, then
+$$
+\begin{aligned}
+\int_{\mathbb{R}}|f-s| &\le \int_{\mathbb{R}}|f-\eta|+\int_{\mathbb{R}}|\eta-s| < \epsilon + \int_{F} |\eta-s|+ \int_{I\setminus F}|\eta-s| + \int_{\mathbb{R}\setminus I}|\eta-s| \\
+&< \epsilon + 2n\frac{\epsilon}{2n} + \epsilon + \epsilon = 4\epsilon.
+\end{aligned} 
+$$
+}
+\solution{(iii)}{
+Use Lusin's Theorem, the proof is the same with (ii), and we only need to change the step function to continuous function.
+}
+
+\problem{8}{Problem 25, Section 18.2, Page}
+
+\problem{9}{Problem 26, Section 18.2, Page}
+
+\problem{10}{Problem 27, Section 18.3, Page}
 \end{document}

### 2017-10-31 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
update

@@
 \problem{8}{Problem 25, Section 18.2, Page}
+\solution{Solution}{
+With $\eta$ being the counting measure, suppose nonnegative $f$ on $\mathbb{N}$, and let nonnegative $f_n(x)$ be
+$$
+f_n(k) = \left\{
+\begin{aligned}
+&f(k), ~0 \le k \le n \\
+&0, ~k > n
+\end{aligned}
+\right.
+$$
+then $f_n \to f$ pointwise on $\mathbb{N}$, and $\{f_n\}$ is increasing. So by Monotone Convergence Thm, 
+$$
+\lim_{n\to\infty}\int_{\mathbb{N}}f_n = \int_{\mathbb{N}}f.
+$$
+Since
+$$
+\int_{\mathbb{N}}f_n = \sum_{i = 1}^{n}\int_{\{i\}}f_n + \int_{\{i \ge n\}} f_n = \sum_{i=1}^{n}\int_{\{i\}}f_n = \sum_{i=1}^{n}f_n(i),
+$$
+we have
+$$
+\int_{\mathbb{N}}f = \sum_{n = 0}^{\infty}f(n) < \infty.
+$$
+}
 
 \problem{9}{Problem 26, Section 18.2, Page}
+\solution{Solution}{
+With the definition of Dirac measure, let $g\equiv f(x_0)$, then
+$$
+m(\{g = f\}) = m_{\delta_{x_0}}(\{x\in X\mid f(x) = g(x)\}) = 1 = m(X).
+$$
+Then $f = g$, a.e. on $X$.
+$$
+\int_{X}f(x)d\delta_{x_0} =\int_{X}gd\delta_{x_0} = f(x_0)\int_{X}1d\delta_{x_0} = f(x_0) < \infty.
+$$
+}
 
 \problem{10}{Problem 27, Section 18.3, Page}
+\solution{Solution}{
+a
+}
 \end{document}

### 2017-10-31 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
update
complete

@@
 \problem{10}{Problem 27, Section 18.3, Page}
-\solution{Solution}{
-a
+\solution{(i)}{
+First we show that if $f$ is integrable on $X$, then the set
+$$
+F = \{x\mid f(x) \ne 0\}
+$$
+is countable. Otherwise, since $f$ is integrable, it means $f^+ $ and $f^- $ are both integrable. We now assume $f$ is nonnegative, then
+$$
+F = \bigcup_{n = 1}^{\infty}\{x\mid f(x) \ge \frac{1}{n}\}.
+$$
+If $F$ is uncountable, then there must exist $n$, s.t. $F_n = \{x\mid f(x) \ge \frac{1}{n}\}$ is uncountable, and $m(F_n) = \infty$. Thus 
+$$
+\int_{X}fd\eta \ge \int_{F_n}fd\eta \ge \frac{1}{n}\times\infty = \infty,
+$$
+which makes a contradiction. In this case, suppose there is a bijection from $F$ to a subset of $\mathbb{N}$, then this problem is the same with Problem 8.
+}
+\solution{(ii)}{
+Since $x_0\in X$, and $\mathcal{M}$ is the $\sigma-$algebra of all subsets of $X$, then $\{x_0\}$ is measurable. For any simple function $h(x) \le |f(x)|$, suppose
+$$
+h(x) = \sum_{i=1}^{n}c_i1_{E_i},
+$$
+and $x_0 \in c_1$, then 
+$$
+\int_{X}h(x)d\mu_{x_0} = \sum_{i=1}^{n}c_im(E_i) = c_1 \le |f(x_0)|.
+$$
+Then according to the definition of integration, 
+$$
+\int_{X}|f(x)| \le |f(x_0)|.
+$$
+On the other hand, let
+$$
+h(x) = \left\{
+\begin{aligned}
+&|f(x_0)|, ~x = x_0 \\
+&0, ~x\ne x_0
+\end{aligned}
+\right.
+$$
+then 
+$$
+\int_{X}h(x) = \int_{\{x_0\}}h(x_0) = |f(x_0)|.
+$$
+Hence
+$$
+\int_{X}|f(x)|d\mu_{x_0} = |f(x_0)|.
+$$
+When $f$ is arbitrary real-valued function, define $f^+ $ and $f^- $ as in the textbook, then $f = f^+-f^- $, and
+$$
+\int_{X}f = \int_{X}f^+ -\int_{X}f^-.
+$$
 }

### 2017-10-31 Graduate - Numerical Analysis/Assignment 10/assignment.tex
update

@@
 \solution{Solution}{
-We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials:
+We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials (normalized):
 $$
-T_0(x) = 1, ~T_1(x) = x, ~T_2(x) = 2x^2-1.
+T_0(x) = \frac{1}{\pi}, ~T_1(x) = \frac{2}{\pi}x, ~T_2(x) = \frac{2}{\pi}(2x^2-1).
 $$
@@
 $$
-a_0 = (f, T_0) = \int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \int_{\pi}^{0}-ydy = \frac{\pi^2}{2},
+a_0 = (f, T_0) = \int_{-1}^{1} \frac{1}{\pi\sqrt{1-x^2}}\cos^{-1}xdx = \int_{\pi}^{0}-\frac{1}{\pi}ydy = \frac{\pi}{2},
 $$
 $$
-a_1 = (f, T_1) = \int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi} y\cos ydy = y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy = -2,
+a_1 = (f, T_1) = \frac{2}{\pi}\int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\frac{2}{\pi}\int_{0}^{\pi} y\cos ydy = \frac{2}{\pi} (y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy) = -\frac{4}{\pi},
 $$
 $$
-a_2 = (f, T_2) = \int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi}y\cos 2ydy = \frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy = -\frac{1}{2}.
+a_2 = (f, T_2) = \frac{2}{\pi}\int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \frac{2}{\pi}\left.\int_{0}^{\pi}y\cos 2ydy = \frac{2}{\pi}(\frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy) = 0,
 $$
@@
 $$
-p_2(x) = -\frac{1}{2}x^2-2x+\frac{\pi^2}{2}.
+p_2(x) = -\frac{4}{\pi}x+\frac{\pi}{2}.
 $$

### 2017-11-01 Graduate - Numerical Analysis/Assignment 10/assignment.tex
update

--- 2017-10-28 Graduate - Numerical Analysis/Assignment 10/assignment.tex
@@
 \solution{Solution}{
-We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials:
+We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials (normalized):
 $$
-T_0(x) = 1, ~T_1(x) = x, ~T_2(x) = 2x^2-1.
+T_0(x) = \frac{1}{\sqrt{\pi}}, ~T_1(x) = \sqrt{\frac{2}{\pi}}x, ~T_2(x) = \sqrt{\frac{2}{\pi}}(2x^2-1).
 $$
@@
 $$
-a_0 = (f, T_0) = \int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \int_{\pi}^{0}-ydy = \frac{\pi^2}{2},
+a_0 = (f, T_0) = \frac{1}{\sqrt{\pi}}\int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \frac{1}{\sqrt{\pi}}\int_{\pi}^{0}-ydy = \frac{(\pi)^{\frac{3}{2}}}{2},
 $$
 $$
-a_1 = (f, T_1) = \int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi} y\cos ydy = y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy = -2,
+a_1 = (f, T_1) = \sqrt{\frac{2}{\pi}}\int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\sqrt{\frac{2}{\pi}}\int_{0}^{\pi} y\cos ydy = \sqrt{\frac{2}{\pi}}(y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy) = -\sqrt{\frac{8}{\pi}},
 $$
 $$
-a_2 = (f, T_2) = \int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi}y\cos 2ydy = \frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy = -\frac{1}{2}.
+a_2 = (f, T_2) = \sqrt{\frac{2}{\pi}}\int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \sqrt{\frac{2}{\pi}}\left.\int_{0}^{\pi}y\cos 2ydy = \sqrt{\frac{2}{\pi}}(\frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy) = 0,
 $$

### 2017-11-08 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
update

--- 2017-10-09 Graduate - Introduction to Analysis I/Assignment 5/5-Homework20171008.tex
@@
 \begin{center}
-\textbf{Introduction to Analysis $I$\\Homework 5\\Sunday, October 8, 2017}\bigskip
+\textbf{Introduction to Analysis $I$\\Homework 7\\Wednesday, November  8, 
+2017}\bigskip
 \end{center}
@@
 
-\noindent If you use results from books, Royden or others, please be explicit about what results you are using.
+\noindent Since by now, you should all be sufficiently familiar with \LaTeX to 
+compose on your own, I will forgo the formalities of the previous assignments 
+and simply list the problems.  I will expect, however, that you will cite 
+relevant material in Royden or other sources properly and that you will 
+acknowledge your collaborators.
 
 \begin{center}
-\emph{Homework 5 is due by midnight, Saturday, October 21.}
+\emph{Homework 7 is due by midnight, Saturday, November 18.}
 \end{center} 
@@
 \begin{enumerate}
-\item  (Problem 24, Page 64) Let $I$ be an interval in $\mathbb{R}$ and let $f:I\to \mathbb{R}$ be increasing.
-Show that $f$ is measurable by first showing that, for each natural number $n$, the strictly increasing function $x\to f(x)+x/n$ is measurable, and then taking pointwise limits.
-
-\bigskip
-\textbf{Collaborators:} None\\
-\smallskip
-
-\textbf{Solution:}
-Denote $f_{n}(x) = f(x)+\frac{x}{n}$. Then since $f: I \to \mathbb{R}$ is increasing, $f_n(x)$ is strictly increasing on $I \in \{[a, b], [a, b), (a, b], (a, b)\}$.
-
-For each fixed number $c$, if $\exists x_0\in I$, s.t. $f(x_0) = c$, then the set
-$$
-\{x\mid f(x) < c\} = (a, x_0),
-$$
-and the left side is the same as the set $I$, and it is an interval in $\mathbb{R}$, hence is measurable. Thus $f_{n}$ is measurable for every $n$.
-
-For each $x\in I$, 
-$$
-\lim_{n\to\infty}f_n(x) = f(x)+\lim_{n\to\infty}\frac{x}{n} = f(x),
-$$
-hence $f_{n}$ converges to $f$ pointwise. Using Proposition 9, we know $f$ is measurable.
-\bigskip
-
-\item (Problem 8, Page 343)  Let $(X,\mathcal{M}, \mu)$ be a measure space.
-The measure $\mu$ is said to be \textbf{semifinite} provided each measurable set of infinite measure contains measurable sets of arbitrarily large finite measure.
-\begin{enumerate}
-\item Show that each $\sigma$-finite measure is semifinite.
-\item For $E\in \mathcal{M}$, define $\mu_1(E) = \mu(E)$, if $\mu(E)<\infty$, and if $\mu(E)=\infty$, define $\mu_1(E)=\infty$ if $E$ contains measurable sets of arbitrarily large finite measure and $\mu_1(E)= 0$ otherwise.
-Show $\mu_1$ is a semifinite measure: it is called the semifinite part of $\mu$.
-\item Find a measure $\mu_2$ on $\mathcal{M}$ that only takes the valures $0$ and $\infty$ and $\mu = \mu_1 + \mu_2$.
-\end{enumerate}
-
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
-
-\textbf{Solution:}
-\bigskip
-
-\item (Problem 9, Page 343) Prove Proposition 3, that is, show that $\mathcal{M}_0$ is a $\sigma$-algebra, $\mu_0$ is properly defined and $(X,\mathcal{M}_0, \mu_0)$ is complete.
-In what sense is $\mathcal{M}_0$ minimal?
-
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
-
-\textbf{Solution:}
-\bigskip
-
-\item (Problem 10, Page 343) If $(X,\mathcal{M},\mu)$ is a measure space, we say that a subset $E$ of $X$ is \textbf{locally measurable} provided for each $B\in \mathcal{M}$ with $\mu(B)<\infty$, the intersection $E\cap B$ belongs to $\mathcal{M}$.
-The measure $\mu$ is called \textbf{saturated} provided every locally measurable set is measurable.
-\begin{enumerate}
-\item Show that each $\sigma$-finite measure is saturated.
-\item Show that the collection $\mathcal{C}$ of locally measurable sets is a $\sigma$-algebra.
-\item Let $(X,\mathcal{M},\mu)$ be a measure space and $\mathcal{C}$ the $\sigma$ of locally measurable sets.
-For $E\in \mathcal{C}$, define $\overline{\mu}(E) = \mu(E)$ if $E\in \mathcal{M}$ and $\overline{\mu}(E) = \infty$ if $E\notin \mathcal{M}$.
-Show that $(X,\mathcal{C},\overline{\mu})$ is a saturated measure space.
-\item If $\mu$ is semifinite and $E\in \mathcal{C}$, set $\underline{\mu}(E)=\sup\{\mu(B)\mid B\in\mathcal{M},\, B\subseteq E \}$.
-Show that  $(X,\mathcal{C},\underline{\mu})$ is a saturated measure space and that $\underline{\mu}$ is an extension of $\mu$.
-Give an example to show that $\overline{\mu}$ and $\underline{\mu}$ may be different.
-\end{enumerate}
-
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
-
-\textbf{Solution:}
-\bigskip
-
-\item (Problem 18, Page 373)  Let $\{u_n\}$ be a sequence of nonnegative measurable functions on $X$.  For $x\in X$, define $f(x) = \sum_{n=1}^{\infty} u_n(x)$.  Show that \[
-\int_X f \, d\mu = \sum_{n=1}^{\infty} \left[\int_X u_n \, d\mu \right].\]
+\item  Problem 9,  Chapter 6
+\item  Problem 10, Chapter 6
+\item  Problem 13, Chapter 6
+\item  Problem 16, Chapter 6
+\item  Problem 26, Chapter 6
+\item  Problem 29, Chapter 6
+\item  Problem 35, Chapter 6
 

### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 4

@@
 \item  Problem 9,  Chapter 6
+
+\smallskip
+\textbf{Solution:}
+\smallskip
+
 \item  Problem 10, Chapter 6
@@
 \item  Problem 16, Chapter 6
+
+\smallskip
+\textbf{Solution:}
+\smallskip
+First, we show that if $f_1, ~f_2$ are differentiable functions, then $f = f_1+f_2$ is differentiable. In fact,
+$$
+\begin{aligned}
+\overline{D}f(x) &= \lim_{h\to 0}\sup_{0 < |t| < h}\frac{f(x+t)-f(x)}{t} = \lim_{h\to 0}\sup_{0 < |t| < h}(\frac{f_1(x+t)-f_1(x)}{t}+\frac{f_2(x+t)-f_2(x)}{t}) \\
+&\le \lim_{h\to 0}\sup_{0 < |t| < h}\frac{f_1(x+t)-f_1(x)}{t} + \lim_{h\to 0}\sup_{0 < |t| < h}\frac{f_2(x+t)-f_2(x)}{t}
+\end{aligned}
+$$
+$$
+\begin{aligned}
+\underline{D}f(x) &= \lim_{h\to 0}\inf_{0 < |t| < h}\frac{f(x+t)-f(x)}{t} = \lim_{h\to 0}\inf_{0 < |t| < h}(\frac{f_1(x+t)-f_1(x)}{t}+\frac{f_2(x+t)-f_2(x)}{t}) \\
+&\ge \lim_{h\to 0}\inf_{0 < |t| < h}\frac{f_1(x+t)-f_1(x)}{t} + \lim_{h\to 0}\inf_{0 < |t| < h}\frac{f_2(x+t)-f_2(x)}{t}
+\end{aligned}
+$$
+But since $f_1$ and $f_2$ are both differentiable, 
+$$
+\lim_{h\to 0}\inf_{0 < |t| < h}\frac{f_i(x+t)-f_i(x)}{t} = \lim_{h\to 0}\sup_{0 < |t| < h}\frac{f_i(x+t)-f_i(x)}{t}
+$$
+holds for $i = 1, 2$. Thus $\overline{D}f(x) = \underline{D}f(x)$, which means $f$ is differentiable.
+
+Let
+$$
+g^+ = \max\{g(x), ~0\}, ~g^- = \min\{g(x), ~0\},
+$$
+Then $g^+ \ge 0, ~g^- \le 0$, and $g(x) = g^+(x) + g^-(x)$. Define
+$$
+f_1(x) = \int_{a}^{x}g^+, ~f_2(x) = \int_{a}^{x}g^-,
+$$
+then $f_1, ~f_2$ are both monotone functions, using Lebesgue's Theorem, $f_1, ~f_2 $ are both differentiable a.e.
+on $(a, b)$, respectively differentiable on $(a, b)\setminus E_1 $ and $(a, b) \setminus E_2 $ where $m(E_1) = m(E_2) = 0$.
+Then using the conclusion above, $f = f_1 + f_2 $ is differentiable on $(a, b)\setminus (E_1\cup E_2)$, and hence differentiable a.e.
+on $(a, b)$.
+
 \item  Problem 26, Chapter 6

### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 3

@@
 \usepackage{amssymb}
+\usepackage{hyperref}
 
@@
 \item  Problem 13, Chapter 6
+
+\smallskip
+\textbf{Solution:}
+\smallskip
+First, we show that under the conditions of the Vitali Covering Lemma, $\mathcal{F}\setminus \bigcup\limits_{k=1}^n I_k $ is a Vitali covering of $E\setminus \bigcup\limits_{k=1}^n I_k$.
+In fact, if it is not true, then there $\exists x\in E\setminus\bigcup\limits_{k=1}^n I_k$ and $\epsilon > 0$, s.t.
+there does not exist an interval $I\in\mathcal{F}\setminus\bigcup\limits_{k=1}^n I_k$, s.t.
+$x\in I$, and $m(I) < \epsilon$.
+However, since $\mathcal{F}$ is a Vitali covering of $E$, then for $\epsilon_i = \frac{\epsilon}{2^i}, ~i = 1, 2, \cdots $, there exists $I_i'\in\mathcal{F} $, s.t.
+$x\in I_i' $ and $m(I_i') < \epsilon_i $.
+If there exists $i_0 $, s.t.
+$I_{i_0}\notin \{I_k\}_{k = 1}^{n} $, then $x\in I_{i_0} $ and $m(I_{i_0}) < \epsilon$, which makes a contradiction.
+Then $\{I_i'\} \in \{I_k\}_{k = 1}^{n}$, but it contradicts with $n < \infty$.
+Hence, our claim is proved.
+
+Then we show that if $\{I_k\}_{k=1}^{n} $ is a finite sequence of closed intervals, then we can find a pairwise disjoint subsequence $\{I_{k_j}\}$ s.t. 
+$$
+m(\bigcup_{j = 1}^{m} I_{k_j}) \ge m(\bigcup_{k=1}^{n}I_k).
+$$
+The proof of this proposition can be seen at \href{http://www.personal.psu.edu/t20/papers/vitali-l2h/node5.html}{http://www.personal.psu.edu/t20/papers/vitali-l2h/node5.html}
+
+Now we use these claims to construct a collection.
+Using Vitali Covering Lemma, for $\epsilon = \frac{3}{4}m(E)$, there exists a finite collection of disjoint intervals $\{I_k\}$, s.t.
+$m(E\setminus \bigcup I_k) < \epsilon$.
+Denote $A = \bigcup I_k $.
+
+Since $\mathcal{F}\setminus A$ is a Vitali covering of $E\setminus I_k $, there is a finite set of intervals $J_k $, s.t.
+$J_k\subset E\setminus A $ (Otherwise just follow the proof of Vitali Covering Lemma on the textbook), and
+$$
+m(E\setminus (A\cup\bigcup_{k=1}^m J_k)) < \frac{1}{12}m(E\setminus A).
+$$
+Then using claim 2, there is a pairwise disjoint subset $\{J_{k_i}\}$ s.t. 
+$$
+m(\bigcup J_{k_i}) \ge \frac{1}{3}m(\bigcup J_k).
+$$
+Then denote $B = \bigcup J_{k_i} $, and 
+$$
+m(E\setminus (A\cup B)) < \frac{2}{3}m(\bigcup J_k) +\frac{1}{12}m(E\setminus A) \le (\frac{2}{3}+\frac{1}{12})m(E\setminus A) = \frac{3}{4}m(E\setminus A).
+$$
+By constructing like above recursively, we can get a sequence of subsets $\{A_i\}$, s.t. 
+$$
+m(E\setminus \bigcup_{i=1}^n A_i) \le (\frac{3}{4})^n m(E).
+$$
+By countable addivity,
+$$
+m(E\setminus \bigcup_{i=1}^\infty A_i) = 0.
+$$
+
 \item  Problem 16, Chapter 6

### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
update

@@
 \smallskip
+Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
+$$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
+$$
+since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.
 
+By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then
+
+\bigskip
 \item  Problem 10, Chapter 6
@@
 
+\bigskip
 \item  Problem 16, Chapter 6

### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex

@@
 $$
-For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)|dx < \epsilon$.
-Since $f(x, y)$ is continuous in $y$ for each $x$, then for each fixed $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$.
+For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)dx| < \epsilon$.
+Since $f(x, y)$ is continuous in $y$ for each $x$ in a closed set, then $f(x, y)$ is uniformly bounded, then for each $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$.
 Then
@@
 $$
-\lim_{n\to\infty}\int_{0}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
+\lim_{n\to\infty}\int_{1}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
 $$

### 2017-11-09 Graduate - Numerical Analysis/Assignment 7/assignment.tex
update

@@
 
+\problem{4}{For $n = 1, \cdots, 10$, generate the Newton divided difference polynomials that interpolates $\cos(x) ~\text{for}~ x \in [0, 2\pi]$, at n equally spaced points. Create an error table.}
+\solution{Solution}{
+The code and result (the graph of error and table of Max error) is listed below.
+}
+\lstinputlisting[language = MATLAB]{newton_poly.m}
+\lstinputlisting[language = MATLAB]{prob4.m}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width = 0.5\textwidth]{prob4.eps}
+\caption{Error of interpolation with different order}
+\end{figure}
+\begin{lstlisting}[language = MATLAB]
+>> prob4
+   1.0e+03 *
+
+    0.0020
+    0.0020
+    0.0040
+    0.0045
+    0.0520
+    0.1047
+    0.2818
+    0.9745
+    1.0237
+    7.0735
+\end{lstlisting}
+
+\problem{5}{For $n = 1,\cdots, 5$, construct Hermite interpolant that interpolates $\cos(x) ~\text{for}~ x \in [0, 2\pi]$, at $n$ equally spaced points. Create an error table.
+}
+\solution{Solution}{
+The code and result is as below. It seems Hermite intepolation is more stable then Newton intepolation.
+}
+\lstinputlisting[language = MATLAB]{Hermite_poly.m}
+\lstinputlisting[language = MATLAB]{prob5.m}
+\begin{figure}[!htb]
+\centering
+\includegraphics[width = 0.5\textwidth]{prob5.eps}
+\caption{Error of Hermite interpolation with different order}
+\end{figure}
+\begin{lstlisting}[language = MATLAB]
+>> prob5
+    2.0000
+    4.0801
+    0.8723
+    0.0900
+    0.0056
+\end{lstlisting}
+
 \end{document}

### 2017-11-10 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add 1/2

--- 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
@@
 \smallskip
+Sufficiency. Suppose $m^*(E) = m > 0$. Since each point in $E$ belongs to infinitely many of the $I_k $, then there exists $N > 0$, s.t. 
+$$
+\bigcup_{k=1}^N I_k\supset E,
+$$
+otherwise there exists $x\in E$, for each $N$, $x\notin \bigcup\limits_{k=1}^N I_k $, and that means $x\notin \bigcup\limits_{k=1}^{\infty}I_k $, which leads to a contradiction.
+Suppose the smallest $N$ such that $E \subset \bigcup\limits_{k=1}^N I_k$ to be $N_1 $, then using the same method, there exists $N_2 > N_1 $, s.t.
+$E \subset \bigcup\limits_{k=N_1+1}^{N_2} I_k$.
+By inductively constructing such $N_j $, we get a sequence $\{N_j\}$, s.t.
+$E \subset \bigcup\limits_{k=N_j+1}^{N_{j+1}} I_k $.
+Then by the definition of outer measure and finite addivity for open sets,
+$$
+m = m^*(E) \le m^*(\bigcup\limits_{k=N_j+1}^{N_{j+1}}I_k) = \sum_{k = N_j+1}^{N_{j+1}}m(I_k).
+$$
+Then for each $M > 0$,
+$$
+\sum_{k=1}^{\infty}m(I_k) > Mm, 
+$$
+which makes a contradiction with $\sum_{k=1}^{\infty}m(I_k) < \infty$. Then $m^*(E) = 0$.
 
+Necessity.
+% Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
+% $$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
+% $$
+% since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.
+
+% By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then
+
+\bigskip
 \item  Problem 10, Chapter 6

### 2017-11-10 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 1

@@
 Necessity.
-% Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
-% $$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
-% $$
-% since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.
-
-% By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then
+With the definition of outer measure, for each $\epsilon_n = \epsilon{1}{2^n} $, there exist an open set $O_n = \bigcup\limits_{j=1}^{\infty}I_{n_j} $ being the construction of open intervals, s.t.
+$E\subset O_n $, and $m(O_n) = \sum\limits_{j=1}^{\infty}m(I_{n_j}) < \epsilon_n $.
+Let $\{I_n\} = \{I_{n_j}\}_{n, j} $, then for each $x\in E$, $x$ belongs to infinitely many of these open intervals, and $\sum\limits_{n=1}^{\infty}m(I_n) = \epsilon < \infty$.
+% Let $\mathcal{F} = \bigcup O_k $, where $O_k = \bigcup I_{k_j} $ is an open set covering $E$.
+Then since $E$ is a set of outer measure 0, for each $\epsilon > 0$, there exists $O_k $, s.t.
+$O_k \supset E $ and $m(O_k) < \epsilon$.
+Then for each $x\in E$, $x\in O_k \in \mathcal{F}$.
+This means $\mathcal{F}$ is a (general) Vitali cover of $E$.
+By Problem 6.6 (Gereral case of Vitali covering lemma), for $\epsilon_n = \frac{\epsilon}{2^n}$, there exists
 

### 2017-11-11 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 1
add prob 3

@@
 Let $\{I_n\} = \{I_{n_j}\}_{n, j} $, then for each $x\in E$, $x$ belongs to infinitely many of these open intervals, and $\sum\limits_{n=1}^{\infty}m(I_n) = \epsilon < \infty$.
-% Let $\mathcal{F} = \bigcup O_k $, where $O_k = \bigcup I_{k_j} $ is an open set covering $E$.
-Then since $E$ is a set of outer measure 0, for each $\epsilon > 0$, there exists $O_k $, s.t.
-$O_k \supset E $ and $m(O_k) < \epsilon$.
-Then for each $x\in E$, $x\in O_k \in \mathcal{F}$.
-This means $\mathcal{F}$ is a (general) Vitali cover of $E$.
-By Problem 6.6 (Gereral case of Vitali covering lemma), for $\epsilon_n = \frac{\epsilon}{2^n}$, there exists
 
@@
 \item  Problem 10, Chapter 6
+
+\smallskip
+\textbf{Solution:}
+\smallskip
+For $x_2 > x_1 $, 
+$$
+\begin{aligned}
+f(x_2) &= \sum_{k=1}^{\infty}l((c_k, d_k)\cap (-\infty, x_2)) = \sum_{k=1}^{\infty}l((c_k, d_k)\cap (-\infty, x_1)) + l((c_k, d_k)\cap (x_1, x_2)) \\
+&= f(x_1) + \sum_{k=1}^{\infty}l((c_k, d_k)\cap (x_1, x_2)).
+\end{aligned}
+$$
+Since $(c_k, d_k)$ is an open set, and $\exists k$, s.t. $x_1\in(c_k, d_k) $, thus $l((x_1, x_2)\cup (c_k, d_k)) > 0$. So $f(x_2) > f(x_1)$, which means $f$ is increasing.
+
+$\forall x\in E$, let $\{k_i\}$ be the infininte set where $x \in (c_{k_i}, d_{k_i})$.
+Let $f_k(x) = l((c_k, d_k) \cap (-\infty, x))$, then $f = \sum f_k $.
+Fix an $N > 0$, then since $x\in\bigcap\limits_{i=1}^{N}(c_{k_i}, d_{k_i}) $, and the intersection of finite open sets is also an open set, then there exists $t_N > 0 $, s.t.
+$x+t_N \in\bigcap\limits_{i=1}^{N}(c_{k_i}, d_{k_i}) $.
+Thus
+$$
+f_k(x+t_N)-f_k(x) = l(x, x+t_N) = t_N,
+$$
+for each $k = k_i, 1\le i\le N$.
+Thus since each $f_k$ is nondecreasing, $f(x+t_N) - f(x) \ge Nt_N$, we have $\overline{D}f(x) \ge N$.
+With the arbitrariness of $N > 0$, we know $\overline{D}f(x) = \infty$, which means $f$ is not differentiable at $x$.
+
+\bigskip
 \item  Problem 13, Chapter 6

### 2017-11-15 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add last 3 problems

@@
 \item  Problem 26, Chapter 6
+
+\smallskip
+\textbf{Solution:}
+No. In fact, let $\{x_i\}$ be the sequence of rational numbers in $[0, 1]$, then for each $i$, there is an irrational number $y_i $, s.t.
+$x_i < y_i < y_{i+1} $. Then
+$$
+TV(f) \ge \sum_{i=1}^{\infty}(|f(x_{i+1})-f(y_i)|+|f(y_i)-f(x_i)|) = \sum_{i=1}^{\infty}2 = \infty.
+$$
+Thus $f$ is not of bounded variation.
+
+\bigskip
 \item  Problem 29, Chapter 6
+
+\smallskip
+\textbf{Solution:}
+
+(a). No. In fact, consider the subinterval $[0, 1]$, let $x_i = \frac{1}{\sqrt{n\pi}} $, and $P_n = \{0, x_{2n+1}, x_{2n},\cdots, x_1\} $, then
+$$
+V(f, P_n) = \frac{1}{\pi}(1+\frac{2}{2n+1}+\frac{2}{2n}+\cdots+\frac{2}{2}+\frac{2}{1}-\cos(1)).
+$$
+Since the sum is a harmonic series, which diverges, we know $f $ is not of bounded variation.
+
+(b). Yes. Consider only the interval $[0, 1]$ since $g$ is an even function. Since $g\in\mathcal{C}^1 $ and is bounded on (0, 1), then 
+$$
+g'(x) = 2x\cos\frac{1}{x}+\sin\frac{1}{x},
+$$
+and $|g'(x)|\le 3 $, thus by the definition of Riemann integral, for any partition $P$,
+$$
+V(g, P) \le \int_{0}^{1}|g'|dx.
+$$
+Thus
+$$
+TV(g) \le\int_{0}^{1}|g'|dx \le 3.
+$$
+\bigskip
 \item  Problem 35, Chapter 6
 
+\smallskip
+\textbf{Solution:}
+First, we have
+$$
+f'(x) = \alpha x^{\alpha-1}\sin(\frac{1}{x^\beta})-\beta x^{\alpha-\beta-1}\cos(\frac{1}{x^\beta}).
+$$
+Since we know $f\in\mathcal{C}^1 $ and $|f|\le 1$ on $(0, 1)$, then according to the definition of Riemann integrals, for any partition $P$ of $[0, 1]$,
+$$
+V(f, P) \le\int_{0}^{1}|f'|dx \le \int_{0}^{1}\alpha x^{\alpha-1}+\beta x^{\alpha-\beta-1}dx.
+$$
+Since $\alpha > \beta > 0$, we have $\alpha-1 > -1$, $\alpha-\beta-1 > -1$, thus 
+$$
+TV(f) \le\int_{0}^{1}\alpha x^{\alpha-1}+\beta x^{\alpha-\beta-1}dx < \infty.
+$$
+When $\alpha \le \beta$, let $P_n = \{0, (\frac{n\pi}{2})^{-\beta}, \cdots, (\frac{\pi}{2})^{-\beta}\}$ be a partition of $[0, 1]$. Then
+$$
+V(f, P_n) = \sum_{i=1}^{n}(\frac{i\pi}{2})^{-\frac{\alpha}{\beta}} \ge \sum_{i=1}^{n}\frac{2}{i}\pi.
+$$
+Since this series is a harmonic series, thus it diverges, which means
+$$
+TV(f) = \infty.
+$$
 \end{enumerate}

### 2017-11-30 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
add prob 1.1

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

\begin{document}

\title{Introduction to Analysis \\ Assignment 8}
\date{\today}
\author{Chuan Lu}

\maketitle

\problem{1}{Problem 37, Page 123}
\solution{Sol}{
(i) Let
$$
f(x) = \left\{
\begin{aligned}
&x\sin(\frac{1}{x}), ~0 < x \le 1, \\
&0, ~x = 0
\end{aligned}
\right.
$$
Then $f$ is continuous on $(0, 1]$. Since $\lim\limits_{x\to 0^+}f(x) = 0 = f(0)$, $f$ is continuous on $[0, 1]$. For $x_1, x_2 \in [\epsilon, 1]$ where $\epsilon > 0$, 
$$
\begin{aligned}
|f(x_1)-f(x_2)| &= |x_1\sin\frac{1}{x_1}-x_2\sin\frac{1}{x_2}| = |(x_1-x_2)\sin\frac{1}{x_1}+x_2(\sin\frac{1}{x_1}-\sin\frac{1}{x_2})| \\
&\le |x_1-x_2|\sin\frac{1}{x_1} + 2x_2|\cos\frac{1}{2}(\frac{1}{x_1}+\frac{1}{x_2})\sin\frac{1}{2}(\frac{1}{x_1}-\frac{1}{x_2})| \\
&\le |x_1-x_2|\sin\frac{1}{x_1} + 2x_2|\sin\frac{x_2-x_1}{2x_1x_2}| \le |x_1-x_2|\sin\frac{1}{x_1}+2x_2|\frac{x_2-x_1}{2x_1x_2}| \\
&= |x_1-x_2|(\sin\frac{1}{x_1}+\frac{1}{x_1}) \le |x_1-x_2|(1+\frac{1}{\epsilon}).
\end{aligned}
$$ 
Thus $f$ is Lipschitz, with Proposition 7 we know $f$ is absolutely continuous.

However, with Problem 35 we know $f$ is not of bounded variation on $[0, 1]$, and with Remark on Page 122 we know $f$ is not absolutely continuous on $[0, 1]$.
}

\problem{2}{Problem 39, Page 123}

\problem{3}{Problem 41, Page 123}

\problem{4}{Problem 49, Page 128}

\problem{5}{Problem 56, Page 129}

\problem{6}{Problem 59, Page 129}

\end{document}

### 2017-12-01 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
update

@@
 However, with Problem 35 we know $f$ is not of bounded variation on $[0, 1]$, and with Remark on Page 122 we know $f$ is not absolutely continuous on $[0, 1]$.
+
+(ii) If not, then there is a $\epsilon > 0$, s.t.
+for each $\delta > 0$, there is a finite disjoint collection $\{(a_k, b_k)\}$ of open intervals satisfying $\sum\limits_{k=1}^{n}(b_k-a_k) < \delta $, s.t.
+$\sum\limits_{k=1}^{n}|f(b_k)-f(a_k)| \ge \epsilon $.
+As suggested in conditions, for each $c > 0$, $f$ is absolutely continuous on $[c, 1]$.
+Then these open intervals must lie in $[0, c]$ for every $c$.
+With the continuity of $f$ on $[0, 1]$, there exists $c > 0$, s.t.
+$0 < f(c) - f(0) <\epsilon$.
+If we take $\delta = c$, because $f$ is increasing, $\sum\limits_{k=1}^{n}(b_k-a_k) < f(c) - f(0) <\epsilon$.
+It contradicts with our assumption.
+Hence $f$ is absolutely continuous on $[0, 1]$.
+
+(iii) First we show $f$ is absolutely continuous by showing that it satisfies the condition in (ii). For each $c > 0$, since on $[c, 1]$ we have 
+$$ 
+\sqrt{x_1}-\sqrt{x_2}| = \frac{|x_1-x_2|}{\sqrt{x_1}+\sqrt{x_2}} \le \frac{|x_1-x_2|}{2\sqrt{c}},
+$$
+we know for each $\epsilon > 0$, pick $\delta = 2\sqrt{c}\epsilon$, then for each collection $\{(a_k, b_k)\}$ satisfying $\sum\limits_{k=0}^{n}|b_k-a_k| < \delta $,
+$$
+\sum_{k=1}^{n}|f(b_k)-f(a_k)| < \sum_{k=1}^{n}\frac{|x_1-x_2|}{2\sqrt{c}} < \epsilon.
+$$
+Hence $f$ is absolutely continuous on $[c, 1]$. Since $f$ is increasing, we know $f$ is absolutely continuous on $[0, 1]$.
+
+On the other hand, if there exists $\lambda > 0$, s.t. 
+$$
+|f(x_1)-f(x_2)| < \lambda|x_1-x_2|
+$$
+for each $x_1, x_2 $, then if we pick $\max(x_1, x_2) < \frac{1}{4\lambda^2}$, from the argument above we know
+$$
+|f(x_1)-f(x_2)| = \frac{|x_1-x_2|}{\sqrt{x_1}+\sqrt{x_2}} > \lambda|x_1-x_2|.
+$$
+Hence $f$ is not Lipschitz.
 }
@@
 \problem{2}{Problem 39, Page 123}
+\solution{Sol}{
+
+}
 

### 2017-12-01 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
update

@@
 \solution{Sol}{
+Suppose $E$ is a measurable set, then for each $\epsilon' > 0$, there exists an open set $O\supset E$, and $m(O\setminus E) < \epsilon'$.
+Let $O = \bigcup\limits_{k=1}^{\infty} (a_k, b_k)$ be the open decomposition of $O$, then $(a_i, b_i)$ are pairwise disjoint.
 
+If $f$ is absolutely continuous, by Problem 38, for each $\epsilon > 0$, there is a $\delta > 0$, for each $\{(a_k, b_k)\}$ satisfying $\sum\limits_{k=1}^{\infty}(b_k-a_k) < \delta$, $\sum\limits_{k=1}^{\infty}|f(b_k)-f(a_k)| < \epsilon $.
+In fact, if we take $\delta_1 < \delta - \epsilon'$, then since $f$ is increasing, $f(E) \in f(\cup\{(a_k, b_k)\})$ when $E \in \cup\{(a_k, b_k)\}$, thus
+$$
+m^*(f(E)) < m(f(\cup\{(a_k, b_k)\})) < \delta.
+$$
+
+On the other hand, since open sets are measurable, with Problem 39 we know the reverse holds.
 }
@@
 \problem{3}{Problem 41, Page 123}
+\solution{Sol}{
+(i) With the continuity of $f$ and the compactness of $[a, b]$, we know the maximum and minimum of $f$ on $[a, b]$ exists, thus $f$ maps $[a, b]$ to a closed set.
+Thus $f$ maps a $F_\sigma $ set to a $F_\sigma$ set.
+
+(ii) Problem 40 tells $f$ maps a set of measure zero to a set of measure zero.
+Since each measurable set could be represented as a union of a measure-zero set and a $F_\sigma $ set, we know $f$ maps a measurable set to a measurable set.
+}
 

### 2017-12-05 Graduate - Numerical Analysis/Assignment 14/product_trapezoidal.m
add prob 4

@@ -1,0 +1,14 @@
+function res = product_trapezoidal(f, b, n, alpha)
+% Product trapezoidal rule;
+% Compute integral of `f` on `[0, b]` with order `n`;
+
+phi1 = @(k) integral(@(u) u./(k-1+u).^alpha, 0, 1);
+phi2 = @(k) integral(@(u) (1-u)./(k-1+u).^alpha, 0, 1);
+
+h = b/n;
+x = 0:h:b;
+w = zeros(n+1, 1); w(1) = phi2(1); w(n+1) = phi1(n);
+for i = 2:n
+    w(i) = phi1(i-1)+phi2(i);
+end
+res = f(x)*w/(h^(alpha-1));

### 2017-12-06 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
add prob 4, 5.1 to 5.4

@@
 
+\newcommand{\df}{\text{Diff}}
 \problem{4}{Problem 49, Page 128}
+\solution{Sol}{
+Since $f$ is differentiable a.e.
+on $(a, b)$, we first show that $\{\df_{1/n}f\}$ converges pointwise a.e.
+to $f'$ on $(a, b)$.
+Suppose $f$ is differentiable on $E\in (a, b)$, with $m((a, b)\setminus E) = 0$.
+For $\forall x$ in $E$, we know for any $n > 0$, $\underline{D}f(x) \le \df_{1/n}f(x) \le \overline{D}f(x)$, so
+$$
+\underline{D}f(x) \le \lim_{n\to\infty}\df_{1/n}f(x) \le \overline{D}f(x).
+$$
+Since $\underline{D}f(x) = \overline{D}f(x)$, we know
+$$
+\lim_{n\to\infty}\df_{1/n}f(x) = f'(x), ~\forall x\in E.
+$$
+Thus
+$$
+\int_{a}^{b}\lim_{n\to\infty}\df_{1/n}f = \int_a^b f'.
+$$
+By fundamental theorem of integral (or by (29)), we know
+$$
+\lim_{n\to\infty}\int_a^b\df_{1/n}f = f(b)-f(a).
+$$
+Hence,
+$$
+\int_{a}^{b}\lim_{n\to\infty}\df_{1/n}f = \lim_{n\to\infty}\int_a^b\df_{1/n}f
+$$
+is equivlent to
+$$
+\int_{a}^{b} f' = f(b)-f(a).
+$$
+}
 
 \problem{5}{Problem 56, Page 129}
+\solution{(i)}{
+Since $O$ is an open set, let
+$$
+O = \bigcup_{n=1}^\infty (a_i, b_i)
+$$
+be its open decomposition, where $\{(a_i, b_i)\}$ are pairwise disjoint.
+Then since $g$ is absolutely continuous thus continuous, and $g$ is strictly increasing, $g$ maps an open interval to an open interval (in fact, this has been proved in a midterm exam).
+Hence, for any open interval $(a, b)$, by Corollary 12 we have
+$$
+\int_{a}^{b}g'(x) = g(b)-g(a) = m(g((a, b))).
+$$
+By countable addivity of measure and integral,
+$$
+\int_{O}g' = \sum_{i=1}^{\infty}\int_{a_i}^{b_i}g' = \sum_{i=1}^{\infty}m(g((a_i, b_i))) = m(g(O)).
+$$
+}
+\solution{(ii)}{
+We know that the intersection of two open sets is an open set, then by induction we know
+$$
+m(g(\cap_{i=1}^n O_i)) = \int_{\cap_{i=1}^n O_i}g', ~\forall n > 0.
+$$
+Let $E = \cap_{i=1}^{\infty}O_i $, then first we have
+$$
+m(g(E)) = m(g(\cap_{i=1}^{\infty} O_i)) \le m(g(\cap_{i=1}^{n} O_i)) = \int_{\cap_{i=1}^{n} O_i} g', ~\forall n.
+$$
+The left side of this inequity is independent of $n$, thus
+$$
+m(g(E)) \le \int_{\cap_{i=1}^{\infty} O_i} g' = \int_{E}g'.
+$$
+On the other hand, we know
+$$
+\int_{E} g' \le m(g(E))
+$$
+by the same arguments. Hence
+$$
+m(g(E)) = \int_{E}g'.
+$$
+}
+\solution{(iii)}{
+In a midterm exam we have proved that a strictly increasing and continuous function maps a null set to a null set, thus $m(g(E)) = 0$. By Theorem 10 we know $g'$ is integrable on $[a, b]$, then 
+$$
+\int_{E} g' = 0.
+$$
+}
+\solution{(iv)}{
+For any measurable subset $A$, by Theorem 11 of Chapter 2, there is a $G_\delta $ set $G \supset A$, and $m(G\setminus A) = 0$. Let $E = G\setminus A$, by (ii) and (iii), we have
+$$
+m(g(E)) = \int_{E} g', ~m(g(G)) = \int_{G}g'.
+$$
+Since $E\cap G = \emptyset$, by addivity of measure and integral,
+$$
+m(g(A)) = m(g(E)) + m(g(G)) = \int_{E\cup G}g' = \int_{A}g'.
+$$
+}
+\solution{(v)}{
+
+}
 

### 2017-12-06 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
add prob 5.5 to 5.6

@@
-%!TEX program = xelate
 \input{structure.tex}
@@
 \solution{(v)}{
+Since $\varphi$ is a simple function, assume $\varphi = \sum\limits_{k = 1}^{n}c_k1_{E_k} $.
+Since $E_k $ are measurable sets, we know $g((a, b)) \cap E_k $ are all measurable.
+Denote $D_k = g((a, b))\cap E_k $.
+Since $g$ is strictly increasing and continuous, we know $g^{-1}(D_k)$ is measurable, then by addivity of domain and (iv),
+$$
+\int_{a}^{b}\varphi(g(x))g'(x)dx = \sum_{k=1}^{n}\int_{g^{-1}(D_k)}c_kg'(x)dx = \sum_{k=1}^{n}c_km(g^{-1}(D_k)) = \int_{c}^{d}c_k1_{g^{-1}(D_k)} = \int_{c}^{d}\varphi(x)dx.
+$$
+}
+\solution{(vi)}{
+By Simple Approximation Lemma, for any $\epsilon > 0$, there are simple functions $\varphi$ and $\psi$, s.t. 
+$$
+0 \le \varphi \le f \le \psi, ~0\le\psi-\varphi < \epsilon.
+$$
+Since $g$ is strictly increasing and absolutely continuous, $g'$ exists a.e., integrable on $[a, b]$, and $g' > 0$. Then
+$$
+\int_a^b \varphi(g(x))g'(x)dx \le \int_a^b f(g(x))g'(x)dx \le \int_a^b\psi(g(x))g'(x)dx.
+$$
+By (v) we know
+$$
+\int_c^d \varphi(y)dy \le \int_a^b f(g(x))g'(x)dx \le \int_c^d \psi(y)dy,
+$$
+and by montonicity of integrals,
+$$
+\int_c^d \varphi(y)dy \le \int_c^d f(y)dy \le \int_c^d \psi(y)dy,
+$$
+and
+$$
+\int_c^d\psi(y)dy - \int_c^d\varphi(y)dy = \int_c^d(\psi - \varphi)dy \le \epsilon(d-c).
+$$
+By the arbitrariness of $\epsilon$,
+$$
+\int_c^d\psi(y)dy - \int_c^d\varphi(y)dy = 0.
+$$
+Hence
+$$
+\int_a^b f(g(x))g'(x)dx = \int_c^d f(y)dy.
+$$
+}
+
+\problem{6}{Problem 59, Page 129}
+\solution{Sol}{
 
@@
 
-\problem{6}{Problem 59, Page 129}
-
 \end{document}

### 2017-12-07 Graduate - Numerical Analysis/CS/assignment.tex
add cheatsheet

--- 2017-10-31 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
@@
 \begin{document}
-
-\title{Introduction to Analysis \\ Assignment 6}
-\date{\today}
-\author{Chuan Lu}
-
-\maketitle
-
-\problem{1}{Problem 29, Section 4.4, Page 89}
-\solution{Sol}{
-Both are not true. We can construct a $f$ like this:
-$$
-f(x) = \left\{
-\begin{aligned}
-1+\frac{1}{n^2}, ~n \le x < n+\frac{1}{2}, ~\forall n\in\mathbb{N} \\
--1, ~n+\frac{1}{2} \le x < n+1, ~\forall n\in\mathbb{N}
-\end{aligned}
-\right.
-$$
-Then $f$ is measurable, and $f$ is bounded on any bounded set, and
-$$
-a_n = \int_{n}^{n+1}f = \frac{1}{2n^2}.
-$$
-Clearly the series $\sum\limits_{n=1}^{\infty}a_n = \sum\limits_{n=1}^{\infty}\frac{1}{2n^2} $ converges absolutely, but 
-$$
-\int_{1}^{\infty}|f| = \sum_{n=1}^{\infty}(1+\frac{1}{2n^2}) = \infty,
-$$
-which means $f$ is not integrable on $[1, \infty)$.
-}
-
-\problem{2}{Problem 33, Section 4.4, Page 90}
-\solution{Proof}{
-First,
-$$
-|f_n-f| \le |f| + |f_n|, ~\forall n.
-$$
-Then since $f$ is integrable on $E$, if $\lim\limits_{n\to\infty}\int_E |f_n| = \int_{E}|f| $, we know $|f_n|+|f|$ converges pointwise a.e. to $2|f|$, and
-$$
-\lim_{n\to\infty}\int_E(|f_n|+|f|) = 2\int_E |f| < \infty,
-$$
-with General Lebesgue Dominated Convergence Theorem, notice $|f_n-f| $ converges pointwise a.e. to 0,
-$$
-\lim_{n\to\infty}\int_E|f_n-f| = \int_E 0 = 0.
-$$
-On the other hand, notice
-$$
-|f_n|-|f| \le |f_n-f|, ~\forall n.
-$$
-with the same method, since $\int_E|f-f_n|\to 0 $, and $|f-f_n| $ converges pointwise to 0,
-$$
-\lim_{n\to\infty}\int_E |f_n-f| = \int_E 0 = 0,
-$$
-we know from $|f_n|-|f| $ converges pointwise a.e. to 0,
-$$
-\lim_{n\to\infty}\int_E |f_n|-|f| = \int_E 0 = 0.
-$$
-Hence
-$$
-\lim_{n\to\infty}\int_E|f_n| = \int_E |f|.
-$$
-}
-
-\problem{3}{Problem 35, Section 4.4, Page 90}
-\solution{Proof}{
-Denote $f_n(x) = f(x, a_n) $, in which $\{a_n\}$ is any series which converges to 0.
-Then from the condition we know $f_n(x) $ converges pointwise to $f(x)$, and $|f_n(x)| \le g(x)$.
-Then using Lebesgue Dominated Convergence Theorem, since $g$ is integrable on $[0, 1]$, we have
-$$
-\lim_{n\to\infty} \int_{0}^{1}f_n(x)dx = \int_{0}^{1} f(x)dx.
-$$
-It shows that 
-$$
-\limsup_{y\to 0}\int_{0}^{1}f(x, y)dx = \liminf_{y\to 0}\int_{0}^{1}f(x, y)dx = \int_{0}^{1}f(x)dx, 
-$$
-whic means 
-$$
-\lim_{y\to 0}\int_{0}^{1}f(x, y) dx = \int_{0}^{1}f(x)dx.
-$$
-For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)|dx < \epsilon$.
-Since $f(x, y)$ is continuous in $y$ for each $x$, then for each fixed $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$.
-Then
-$$
-|h(y)-h(y_0)| = \left|\int_{0}^{1} f(x, y)dx - \int_{0}^{1} f(x, y_0)dx\right| \le \int_{0}^{1} |f(x, y)-f(x, y_0)|dx < \epsilon.
-$$
-We know the continuity of $h$ since we can pick $\delta = \delta_1 $.
-}
-
-\problem{4}{Problem 36, Section 4.4, Page 90}
-\solution{Proof}{
-For any fixed $y\in [0, 1]$, suppose $\{h_n\}$ is a sequence with $h_n\to 0 $. Let
-$$
-f_n(x) = \frac{f(x, y+h_n)-f(x, y)}{h_n}
-$$
-Since $\partial f/\partial y$ exists, 
-$$
-\lim_{n\to\infty}f_n(x) = \lim_{h\to 0}\frac{f(x, y+h)-f(x, y)}{h} = \frac{\partial f}{\partial y}(x, y).
-$$
-It means $f_n(x)$ converges pointwise to $\frac{\partial f}{\partial y}(x, y)$.
-Thus
-$$
-\exists N > 0, ~\forall n > N, \left|f_n(x) - \frac{\partial f}{\partial y}(x, y)\right| < 1.
-$$
-Since 
-$$
-\left|\frac{\partial f}{\partial y}(x, y)\right| \le g(x)
-$$
-we have
-$$
-|f_n(x)| \le g(x)+1,
-$$
-and $g(x)+1$ is integrable on $[0, 1]$. By Lebesgue Dominated Convergence Theorem,
-$$
-\int_{0}^{1}f_n(x)dx \to \int_{0}^{1}\frac{\partial f}{\partial y}(x, y)dx.
-$$
-Since $\{h_n\}$ is arbitrary, and $f_n$ is integrable, we know
-$$
-\limsup_{n\to\infty}\int_{0}^{1}f_n(x)dx = \liminf_{n\to\infty}\int_{0}^{1}f_n(x) dx = \lim_{h\to 0}\frac{1}{h}\left(\int_0^1 f(x, y+h)dx-\int_{0}^{1}f(x, y)dx\right) = \frac{d}{dy}\int_{0}^{1}f(x, y)dx.
-$$
-}
-
-\problem{5}{Problem 38, Section 4.5, Page 91}
-\solution{(i)}{
-$$
-\lim_{n\to\infty}\int_{0}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
-$$
-But
-$$
-\int_{1}^{\infty}f^+ = \sum_{m=1}^{\infty}\frac{1}{2m} = \infty,
-$$
-So $f$ is not integrable.
-}
-\solution{(ii)}{
-$$
-\lim_{n\to\infty}\int_{1}^{n}f = \int_{1}^{\infty}\frac{\sin x}{x}dx,
-$$
-with Dirichlet's Criterion, we know this integral converges. But
-$$
-\int_{1}^{\infty}|f| \ge \int_{1}^{\infty}\frac{1}{2x}dx - \int_{1}^{\infty}\frac{\cos 2x}{x}dx,
-$$
-and the second term converges with Dirichlet's Criterion, but the first term $\to\infty$, we know this integral diverges to $\infty$. Thus $f$ is not integrable.
-
-This two counterexamples do not contradict to the continuity: $f$ is not integrable over the whole set $E = [1, \infty)$.
-}
-
-\problem{6}{Problem 39, Section 4.5, Page 91}
-\solution{Proof (i)}{
-Denote 
-$$
-F_1 = E_1, ~F_n = E_n \setminus \bigcup_{m=1}^{n-1}E_m, ~n \ge 2.
-$$
-Then $\{F_i\}$ is a sequence of disjoint measurable subsets of $E$. Then using Theorem 20,
-$$
-\int_{\cup_{n=1}^{\infty}E_n} f = \sum_{n=1}^{\infty}\int_{F_n}f = \lim_{n\to\infty}\sum_{m=1}^{n}\int_{F_m}f = \lim_{n\to\infty}\int_{E_n}f.
-$$
-}
-\solution{Proof of (ii)}{
-Using the same method with (i), only changing $F$ to 
-$$
-F_1 = E_1, ~F_n = E_1 \setminus\bigcup_{m=1}^{n-1}E_m, ~n\ge 2.
-$$
-The other parts of proof is just the same.
-}
-
-\problem{7}{Problem 44, Section 4.6, Page 95}
-\solution{(i)}{
-First, when $f$ is nonnegative, from the definition of integrable functions we know for any $\epsilon > 0$, there is a bounded measurable function with finite support $0 \le h(x) \le f(x)$, s.t. 
-$$
-\int_{\mathbb{R}} (f-h) = \int_{\mathbb{R}}f - \int_{\mathbb{R}}h \le \frac{1}{2}\epsilon.
-$$
-Let the support set of $h$ be $M$ with $m(M) < \infty$.
-Then using Simple Approximation Theorem, there is a simple function $\eta$ on M, s.t.
-$0 \le h - \eta \le \frac{\epsilon}{2m(M)}$.
-Let $\eta = 0$ on $\mathbb{R}\setminus M$, then $\eta$ has finite support, and
-$$
-\int_{\mathbb{R}}|f-\eta| = \int_{\mathbb{R}}(f-h+h-\eta) = \int_{\mathbb{R}}f-h + \int_{M} h-\eta \le \frac{1}{2}\epsilon + m(M)\frac{\epsilon}{2m(M)} = \epsilon.
-$$
-When $f$ is an arbitrary integrable function, $f^+, ~f^- $ are nonnegative functions.
-Let $E_+ = \{x\mid f^+ > 0\}, ~E_- = \{x\mid f^- > 0\} $, then there exists nonnegative simple functions $\eta^+, ~\eta^- $, s.t.
-$\eta^+ = 0 $ on $\mathbb{R}\setminus E_+ $, and $\eta^+ $ has finite support on $E_+ $, $\eta^- = 0 $ on $\mathbb{R}\setminus E_- $, and $\eta^- $ has finite support on $E_- $, and they satisfies
-$$
-\int_{\mathbb{R}} |f^+-\eta^+| < \epsilon, ~\int_{\mathbb{R}} |f^--\eta^-| < \epsilon.
-$$
-Let
-$$
-\eta = \left\{
-\begin{aligned}
-\eta^+, ~x\in E_+ \\ 
-\eta^-, ~x\in E_-
-\end{aligned},
-\right.
-$$
-then $\eta = \eta^+-\eta^- $ is a simple function with finite support, and
-$$
-\int_{\mathbb{R}}|f-\eta| = \int_{\mathbb{R}} |f^+-f^--(\eta^+-\eta^-)| \le \int_{\mathbb{R}}|f^+-\eta^+| + \int_{\mathbb{R}}|f^--\eta^-| < 2\epsilon.
-$$
-}
-\solution{(ii)}{
-From (i) we know there is a simple function $\eta$ which has finite support (denoted as $E$) and $\int_{\mathbb{R}}|f-\eta| < \epsilon $.
-Since $E$ is a measurable set of finite measure, with Lemma 22, for any $\delta_1 > 0$, there is a $n > 0$,
-$$
-m(E\cap(\mathbb{R}\setminus [-n, n])) < \delta_1.
-$$
-Let $I = [-n, n]$, using the result of Problem 3.18, for any $\delta_2 > 0$, there is a step function $s$ on $I$, and a close set $F\subset I$, s.t.
-$|\eta - s| < \delta_2 $ on $F$, and $m(I\setminus F) < \delta_2 $.
-Set $s(x) = 0$ for $x$ outside $I$.
-
-With Proposition 23, for each $\epsilon > 0$, $\exists \delta > 0 $, if $m(A) < \delta$, then $\int_{A}|f| < \epsilon $. Let $\delta_1 = \delta$, $\delta_2 = \min(\delta, \frac{\epsilon}{2n}) $, then
-$$
-\begin{aligned}
-\int_{\mathbb{R}}|f-s| &\le \int_{\mathbb{R}}|f-\eta|+\int_{\mathbb{R}}|\eta-s| < \epsilon + \int_{F} |\eta-s|+ \int_{I\setminus F}|\eta-s| + \int_{\mathbb{R}\setminus I}|\eta-s| \\
-&< \epsilon + 2n\frac{\epsilon}{2n} + \epsilon + \epsilon = 4\epsilon.
-\end{aligned} 
-$$
-}
-\solution{(iii)}{
-Use Lusin's Theorem, the proof is the same with (ii), and we only need to change the step function to continuous function.
-}
-
-\problem{8}{Problem 25, Section 18.2, Page}
-\solution{Solution}{
-With $\eta$ being the counting measure, suppose nonnegative $f$ on $\mathbb{N}$, and let nonnegative $f_n(x)$ be
-$$
-f_n(k) = \left\{
-\begin{aligned}
-&f(k), ~0 \le k \le n \\
-&0, ~k > n
-\end{aligned}
-\right.
-$$
-then $f_n \to f$ pointwise on $\mathbb{N}$, and $\{f_n\}$ is increasing. So by Monotone Convergence Thm, 
-$$
-\lim_{n\to\infty}\int_{\mathbb{N}}f_n = \int_{\mathbb{N}}f.
-$$
-Since
-$$
-\int_{\mathbb{N}}f_n = \sum_{i = 1}^{n}\int_{\{i\}}f_n + \int_{\{i \ge n\}} f_n = \sum_{i=1}^{n}\int_{\{i\}}f_n = \sum_{i=1}^{n}f_n(i),
-$$
-we have
-$$
-\int_{\mathbb{N}}f = \sum_{n = 0}^{\infty}f(n) < \infty.
-$$
-}
-
-\problem{9}{Problem 26, Section 18.2, Page}
-\solution{Solution}{
-With the definition of Dirac measure, let $g\equiv f(x_0)$, then
-$$
-m(\{g = f\}) = m_{\delta_{x_0}}(\{x\in X\mid f(x) = g(x)\}) = 1 = m(X).
-$$
-Then $f = g$, a.e. on $X$.
-$$
-\int_{X}f(x)d\delta_{x_0} =\int_{X}gd\delta_{x_0} = f(x_0)\int_{X}1d\delta_{x_0} = f(x_0) < \infty.
-$$
-}
-
-\problem{10}{Problem 27, Section 18.3, Page}
-\solution{Solution}{
-a
-}
+Taylor: $R_{n+1}(x) = \frac{1}{n!}\int_{x_0}^{x}(x-t)^n $
 \end{document}

### 2017-12-09 Graduate - Numerical Analysis/CS/assignment.tex
update

@@
 
+\newcommand{\tb}{\textbf}
+
 \begin{document}
-Taylor: $R_{n+1}(x) = \frac{1}{n!}\int_{x_0}^{x}(x-t)^n $
+\tb{Taylor.} $\mathbf{R_{n+1}(x)} = \frac{1}{n!}\int_{x_0}^{x}(x-t)^nf^{(n+1)}(t)dt = \frac{(x-x_0)^{n+1}}{(n+1)!}f^{(n+1)}(\xi) $.
+~$\mathbf{\ln(1+x)} = \sum_{i=1}^{n}(-1)^{i-1}\frac{x^i}{i} $.
+~$\mathbf{\sin x} = \sum_{i=1}^{n-1}(-1)^{i-1}\frac{x^{2i-1}}{(2i-1)!}+(-1)^n\frac{x^{2n+1}}{(2n+1)}\cos\xi $.
+~$\mathbf{\cos x} = \sum_{i=0}^{n-1}(-1)^{i}\frac{x^{2i}}{(2i)!}+(-1)^n\frac{x^{2n}}{(2n)!}\cos\xi $.
+~$\mathbf{(1+x)^\alpha} = 1+C_{\alpha}^1x+C_{\alpha}^2x^2+\cdots+C_{\alpha}^nx^n+C_{\alpha}^{n+1}\frac{x^{n+1}}{(1+\xi)^{n+1-\alpha}}.
+~C_\alpha^i = \frac{\alpha(\alpha-1)\cdot(\alpha-i+1)}{i!} $.
+~$\tan^{-1}: $ Let $x = -u^2 $ in $\frac{1}{1-x}$.
+integrate.
+
+\tb{Mean value.} Diff: $f$ cont and diff; ~Int: $w > 0$ int, $f$ cont.
+
+\tb{float num.} $\sigma(0.a_1a_2\cdot a_t)\beta^e$. ~sig. digits: e.g. $0.02138, 0.02144$: 2; $0.333, 0.33$: 2; (minus 1).
+~loss of significance: solve by rationalize; (Or Taylor expansion)
+
+\tb{Conv Order:} 1: $|x-x_{n+1}|\le c|x-x_{n}|^p $ for some $c > 0$, $p \ge 1$. ~2: $\lim_{n\to\infty}\frac{|x-x_{n+1}|}{|x-x_n|^p} = c $
+
+\tb{Bisection:} cont. (intermediate value thm). ~Adv: 1: guaranteed to conv. 2: reasonal error bound; ~Disadv: 1: doesn't take adv of machine eps. 2: conv too slow.
+
+\tb{Newton:} $x_{n+1} = x_n-\frac{f(x_n)}{f'(x_n)} $, regarded as fixed-point iter $g(x) = x - \frac{f(x)}{f'(x)}$; ~Conv order and rate: Taylor expansion near $\alpha$, $\lim_{n\to\infty}\frac{\alpha-x_{n+1}}{(\alpha-x_n)^2} = -\frac{f''(\alpha)}{2f'(\alpha)} $ (Assumption: $f'(\alpha)\ne 0$, $f, f', f''$ cont, $x_0 $ sufficiently close to $\alpha$, s.t.
+$M = \frac{\max|f''|}{\min2|f'|})$, $M|\alpha-x_0| < 1$).
+~Error estimate: $\alpha-x_n = x_{n+1}-x_n $ (by mean value thm, let $f'(\xi) = f'(x_n)$); ~Adv: quick.
+~Disadv: 1: doesn't guaranteed to conv.
+2: need to know $f'$;
+
+\tb{Secant:} $x_{n+1} = x_n - \frac{x_n-x_{n-1}}{f(x_n)-f(x_{n-1})}f(x_n) $.
+~Error: $\alpha-x_{n+1} = -(\alpha-x_{n-1})(\alpha-x_n)\frac{f[x_{n-1}, x_n, \alpha]}{f[x_{n-1}, x_n]} = -()()\frac{f''(\xi_n)}{2f'(\eta_n)}$.
+~Conv: $p = \frac{\sqrt{5}+1}{2}$, assumption: $f\in C^2, f'(\alpha) \ne 0$, $\delta = \max\{M|e_0|, M|e_1|\} < 1$, let $I = [\alpha-\epsilon, \alpha+\epsilon]$, s.t.
+$f'\ne 0$ in $I$.
+Then $M|e_{n+1}|\le \delta^{q_{n+1}}, q_{n+1} = q_n+q_{n-1} $.
+
+\tb{Fixed point iter:} $x = g(x) \to x_{n+1}=g(x_n) $.
+~\tb{Exist:} assumption: $g$ cont, $g([a, b])\subset [a, b]$, then $x = g(x)$ has at least one sol in $[a, b]$ (pf: f = g(x)-x, intermediate val thm).
+~\tb{Unique:} (\tb{First case:} exist cond, $|g(x)-g(y)| \le \lambda|x-y|, 0<\lambda < 1$.
+$\to$ for any $x_0 $, $x_n\to\alpha$, $|\alpha - x_n| \le \frac{\lambda^n}{1-\lambda}|x_1-x_0|$) ~(\tb{2nd case:} exist cond, $g$ diff.
+$\lambda = \max|g'| < 1$ $\to$ 1st conclusion, and $\lim\frac{\alpha-x_{n+1}}{\alpha-x_n} = g'(\alpha)$).
+~(\tb{3rd case, local ver.} $g\in C^1 $ in neighbour of $\alpha, |g(\alpha)| < 1$, $x_0$ sufficiently close to $\alpha$.
+$\to$ 2nd conclusion)
+
+\tb{Higher order one-point:} $g\in C^{p}, p\ge 2 $ in neighbour of $\alpha$, $g'(\alpha) = \cdots = g^{(p-1)}(\alpha) = 0, g^{(p)}(\alpha)\ne 0 $, $x_0$ sufficiently close to $\alpha$; $\to$ order $p$, $\lim\frac{\alpha-x_{n+1}}{(\alpha-x_n)^p} = (-1)^{p-1}\frac{g^{(p)}(\alpha)}{p!} $.
+(pf: taylor expansion)
+
+\tb{Sys of nonlinear equs:} $f_1(x_1, x_2) = 0, f_2(x_1, x_2) = 0 $.
+fixed-point: $\alpha-x_{n+1} = G_n(\alpha-x_n), G_n $ is Jacobian of $g$, the iteration func (not f).
+~Thm: $D$ closed bounded convex, $g\in C^1 $, $g(D)\subset D$, $\lambda = \max\lVert G\rVert_\infty < 1.
+\to $ 1.
+any initial val $\to$ unique sol; 2.
+$\lVert \alpha-x_{n+1}\rVert_{\infty} \le (\lVert G\rVert_\infty +\epsilon_n)\lVert \alpha-x_{n}\rVert_{\infty}, \epsilon_n\to 0 $.
+~\tb{local ver:} in a neighbour of $\alpha$, if $\lVert G(\alpha)\rVert_{\infty} < 1$, then $x_n\to \alpha $.
+~($\lVert G\rVert_{\infty}$: maximum of row sums.) ~\tb{Newton:} $x_{n+1} = x_n-F(x_n)^{-1}f(x_n) $, $F$ is Jacobian of $(f_1, f_2) $.
+\\[5pt]
+
+\tb{Poly interpolation:} exist \& unique: 1. VA = y has unique sol (1.1: $\det V\ne 0$; 1.2: $VA=0$ only has zero-sol.) 2. Construct (Lagrange basis) - unique: $r(x)=p(x)-q(x)$, $r(x_i) = 0$;
+
+\tb{Lagrange:} $\Psi(x) = \prod_{i=0}^{n}(x-x_i)$, then $l_j(x) = \frac{\Psi(x)}{(x-x_j)\Psi'(x_j)}$.
+~Pf of res: $G(x) = E(x)-\frac{\Psi(x)}{\Psi(t)}E(t)$, then $G$ has $n+2$ zeros, use Rolle thm.
+~Rounding err: let $f_0 = f(x_0)-\epsilon,\cdots $, bound $E(x) = f(x) - L(f_i)(x)$ (use $f_i $ for interpolation)
+
+\tb{Newton:} $p_n(x) = f(x_0)+(x-x_0)f[x_0,x_1]+\cdots + (x-x_0)\cdots(x-x_{n-1})f[x_0,\cdots, x_n] $.
+~$f[x_0,\cdots, x_n] = \sum_{j=0}^{n}\frac{f(x_j)}{\Psi'(x_j)}$.
+~Pf of res: construct $p_{n+1}(x) $ by add a point $(t, f(t))$, then $p_{n+1}(t) = f(t) $.
+
+\tb{Residue} $f(t)- \sum_{j=0}^{n}f(x_j)l_j(t)  = \frac{(t-x_0)\cdots(t-x_n)}{(n+1)!}f^{(n+1)}(\xi) = f[x_0, \cdots, x_n, x]\prod_{i=0}^{n}(x-x_i)$.
+
+\tb{Algorithm of Newton and Lagrange!!!} \\[3pt]
+
+\tb{Interpolation basis:} 1.
+Monomial: $x^i $.
+adv: easy to write, matrix $A$ easy to compute and evaluate.
+disadv: $Ax=b$ expensive to solve, sys ill-cond; ~2.
+Lagrange: $l_i(x) $.
+adv: no need to solve equations, depend on $x_i $ not $y_i \to$ useful when many sets of $\{y_i\}$ on the same $\{x_i\}$.
+disadv: expensive to compute, hard to add new points; ~3.
+Newton: $\prod(x_i-x_j)$.
+adv: easy to compute, solve the matrix, bound error, add new points.
+
+\tb{Hermite:} use primes; $h_i(x) = (1-2l_i'(x_i)(x-x_i))l_i^2(x), \hat{h_i}(x) = (x-x_i)l_i^2(x) $, s.t.
+$h_i(x_j)=\hat{h_i'}(x_j) = \delta_{ij}, h_i'(x_j) = \hat{h_i}(x_j) = 0 $.
+~$H(x) = \sum y_ih_i(x)+\sum y_i'\hat{h_i}(x) $.
+~\tb{Res:} $E = f[x_1, x_1, \cdots, x_n, x_n, x]\prod(x-x_i)^2 = \Psi^2(x)\frac{f^{2n}(\xi)}{(2n)!}$, (let $p$ be interpolation on $\{x_i\}_{i=1}^{2n} $, let $x_{2i}\to x_{2i-1} $).
+
+\tb{Piecewise:} order $r$: poly order $< r$ in each interval; local cubic: lagrange/hermite;
+
+\tb{Spline:} Grid $a = x_0<\cdots<x_n = b $.
+$s$ is spline order $m$: 1.
+$s$ is poly order $<m$ on each $[x_{i-1}, x_i]$; 2.
+$s^{(r)} $ continuous, for $0\le r\le m-2$.
+then $s'$ is a spline of order $m-1$, etc.
+
+\tb{cubic spline:} $m=4$.
+cond: $s(x_i) = y_i, 0\le i\le n $.
+Case 1: $s'(x_0) = y_0', s'(x_n) = y_n' $, complete spline.
+~Case 2: $s''(x_0) = s''(x_n) = 0$, natural spline.
+\tb{Error:} $\max|f^{(j)}(x)-s^{j}(x)|\le c_jh^{4-j}\max|f^{(4)}(x)| $, $c_0 = \frac{5}{384}, c_1 = \frac{1}{24}, c_2 = \frac{3}{8}.
+$ ~$\int_{a}^{b}\lVert s''(x)\rVert^2dx\le\int_{a}^{b}\lVert g''(x)\rVert^2dx $, for any $g$ satisfying the conditions as $s$.
+In order to solve Runge ($\frac{1}{1+x^2}$), the other way is to interpolate at Chebyshev zeros (see chpt 4).
+
+\tb{Trigonometric:} for periodic functions. interpolate at $t_{j} = \frac{2\pi j}{2n+1}, j = 0, \pm 1,\cdots$. Use FFT. \\[5pt]
+
+\tb{Weierstrass appro.
+thm:} $f$ cont on $[a, b]$.
+for each $\epsilon$, there is a poly $p$, s.t.
+$|f-p|\le\epsilon$.
+(Motivation for best approx: more efficient than interpolation; low degree); Taylor: error increase when $|x|$ get large, and error not distributed evenly.
+(so could be better).
+
+\tb{Minimax:} minimax error $\rho_n(f) = \inf_{deg(q)\le n}\lVert f-q\rVert_{\infty} $ (compute: the max error gets at endpoints and some middle points.)
+
+\tb{Least square:} minimize $M_n(f) = \inf_{deg(r)\le n}\lVert f-r\rVert_2 $. (compute: derivative of coefficients = 0.)
+
+\tb{Weight func:} nonnegative, $\int_{a}^{b}|x|^nw(x) $ finite for all $n$; if $\int_{a}^{b}w(x)g(x) = 0 $ and $g$ nonnegative, then $g = 0$.
+
+\tb{Orthogonal poly:} $(f, g) = \int_{a}^{b}w(x)f(x)g(x)dx $; Gram-Schmidt: $|\varphi_0| = 1, ~\psi(x) = x^n+a_{n,n-1}\varphi_{n-1}(x)+\cdots+a_{n, 0}\varphi_0(x), ~a_{n, j} = -(x^n, \varphi_j), ~\varphi_n(x) = \frac{\psi_n(x)}{|\psi_n(x)|} $.
+~\tb{Legendre:} $w(x) = 1, \in[-1, 1]$, $P_n(x) = \frac{(-1)^n}{2^nn!}\frac{d^n}{dx^n}[(1-x^2)^n], P_0 = 1; ~(P_n, P_n) = \frac{2}{2n+1} $.
+~\tb{Chebyshev:} $w(x) = \frac{1}{\sqrt{1-x^2}}, \in[-1, 1]$, $T_n(x) = \cos(n\cos^{-1}x), T_{n+1} = 2xT_n(x)-T_{n-1}(x), ~(T_n, T_m) = \pi(n=m=0), 0(n\ne m), \pi/2(n=m>0) $.
+~If $deg(f) = m$, $f = \sum_{n=0}^{m}\frac{(f,\varphi_n)}{(\varphi_n, \varphi_n)}\varphi_n(x) $.
+~\tb{TRR:} $\varphi_{n+1}(x) = (a_nx+b_n)\varphi_n(x)-c_n\varphi_{n-1}(x) $, where $\varphi_n = A_nx^n+B_nx^{n-1}+\cdots, ~a_n = \frac{A_{n+1}}{A_n}, \gamma_n = (\varphi_n, \varphi_n), b_n = a_n(\frac{B_{n+1}}{A_{n+1}}-\frac{B_n}{A_n}), c_n = \frac{A_{n+1}A_{n-1}}{A_n^2}\frac{\gamma_n}{\gamma_{n-1}}$.
+
+\tb{General least square sol:} $\varphi$ be ort.
+poly with $w(x)$.
+$r(x) = \sum_{k=0}^{n}b_k\varphi_k(x) $, where $b_j = (f, \varphi_j) $.
+~\tb{Bessel \& Parseval:} $|r_n^*|_2^2 = \sum_{k=0}^{n}(f, \varphi_k)^2 \le |f|_2^2 = \sum_{k=0}^{\infty}(f, \varphi_k)^2 $;
+
+\tb{Minimax:} \tb{de la Vallee-Poussin:} $f$ cont, $deg(Q)\le n$, $f(x_j)-Q(x_j) = (-1)^je_j, 0\le j\le n+1, e_j\ne 0 $ of same sign, $a\le x_0 <\cdots < x_{n+1}\le b $, then $\min|e_j| \le \rho_n(f) \le |f-Q|_\infty $.
+~\tb{Equioscillation:} there is a unique poly $deg(q^*)\le n $, s.t.
+$\rho_n(f) = |f-q^*|_\infty $.
+and $q^* $ satisfy that there exists $a\le x_0 <\cdots < x_{n+1}\le b $, s.t.
+$f(x_j)-q^*(x_j) = \sigma(-1)^j\rho_n(f), \sigma = \pm 1 $.
+
+\tb{Near Minimax:} use chebyshev least square $C_n(x) = \sum_{j=0}^{n}c_jT_j(x), c_j = \frac{2}{\pi}\int_{-1}^{1}\frac{f(x)T_j(x)}{\sqrt{1-x^2}}dx, c_0 = c_0/2 $ as an approximation, then the error is nearly $c_{n+1}T_{n+1}(x)$, then err be nearly $0$ at roots of $T_{n+1}(x) \to x_j = \cos\frac{2j+1}{2n+2}\pi, 0\le j\le n $.
+Use interpolation on these nodes $I_n(x) $ as approx of $C_n $ and $q_n^*(x) $.
+
+\tb{Cheb. Poly:} $r_n = \inf_{deg(q)\le n-1}(\max_{-1\le x\le 1}|x^n+q(x)|) $, the minimum attained at $x^n+q(x) = \frac{1}{2^{n-1}}T_n(x), r_n = \frac{1}{2^{n-1}} $.
+
+\tb{Near minimax err:} $x_i = \cos\frac{i\pi}{n+1}, 0\le i\le n+1, ~\sum_{k=0}^{n}c_{n,k}T_k(x_i)+(-1)^iE_n =f(x_i), \sum = \sum' \to c_{n, j} = \frac{2}{n+1}\sum_{i=0}^{n+1}f(x_i)\cos(\frac{ij\pi}{n+1}), \sum = \sum'', E_n = \frac{1}{n+1}\sum_{i=0}^{n+1}(-1)^if(x_i), \sum = \sum'' $.
+~\tb{Notice:} $\sum_{k=1}^{n}kz^k = \frac{1-(n+1)z^n+nz^{n+1}}{(1-z)^2}z $
 \end{document}

### 2017-12-13 Graduate - Numerical Analysis/cheat sheet/cs.tex

--- 2017-12-09 Graduate - Numerical Analysis/CS/assignment.tex
@@
 ~C_\alpha^i = \frac{\alpha(\alpha-1)\cdot(\alpha-i+1)}{i!} $.
-~$\tan^{-1}: $ Let $x = -u^2 $ in $\frac{1}{1-x}$.
-integrate.
+~$\tan^{-1}(x) = x-\frac{1}{3}x^3+\frac{1}{5}x^5+\cdots + (-1)^n\frac{x^{2n+1}}{2n+1} $, ~$\frac{1}{1+x} = 1-x+x^2-\cdots+(-1)^nx^n $.
+~$\frac{1}{\sqrt{1+x}} = 1-\frac{1}{2}x+\frac{1*3}{2*4}x^2+\cdots +(-1)^n\frac{(2n-1)!!}{(2n)!!}x^n $.
 
-\tb{Mean value.} Diff: $f$ cont and diff; ~Int: $w > 0$ int, $f$ cont.
+\tb{Mean value.} Diff: $f$ cont and diff; $f(b)-f(a) = f'(\xi)(b-a)$; ~Int: $w > 0$ int, $f$ cont. $\int_a^bw(x)f(x)dx = f(\xi)\int_a^bw(x)dx $.
 
 \tb{float num.} $\sigma(0.a_1a_2\cdot a_t)\beta^e$. ~sig. digits: e.g. $0.02138, 0.02144$: 2; $0.333, 0.33$: 2; (minus 1).
-~loss of significance: solve by rationalize; (Or Taylor expansion)
+~\tb{loss of significance:} solve by rationalize; (Or Taylor expansion) ~\tb{Machine epsilon}: called unit roundoff, chop: $\beta^{-t+1} $, round: $\frac{1}{2}\beta^{-t+1} $.
+the smallest num s.t.
+$fl(1+\delta) > 1$.
 
-\tb{Conv Order:} 1: $|x-x_{n+1}|\le c|x-x_{n}|^p $ for some $c > 0$, $p \ge 1$. ~2: $\lim_{n\to\infty}\frac{|x-x_{n+1}|}{|x-x_n|^p} = c $
+\tb{Conv Order:} 1: $|x-x_{n+1}|\le c|x-x_{n}|^p $ for some $c > 0$, $p \ge 1$. ~2: $\lim_{n\to\infty}\frac{|x-x_{n+1}|}{|x-x_n|^p} = c $ (2 also called asymptotic rate);
 
@@
 $\lambda = \max|g'| < 1$ $\to$ 1st conclusion, and $\lim\frac{\alpha-x_{n+1}}{\alpha-x_n} = g'(\alpha)$).
-~(\tb{3rd case, local ver.} $g\in C^1 $ in neighbour of $\alpha, |g(\alpha)| < 1$, $x_0$ sufficiently close to $\alpha$.
+~(\tb{3rd case, local ver.} $g\in C^1 $ in neighbour of $\alpha, |g(\alpha)| < 1$, $x_0$ sufficiently close (s.t.
+$g'(x) < 1$ in this interval) to $\alpha$.
 $\to$ 2nd conclusion)
@@
 
-\tb{Algorithm of Newton and Lagrange!!!} \\[3pt]
-
 \tb{Interpolation basis:} 1.
@@
 
-\tb{cubic spline:} $m=4$.
+\tb{cubic spline:} order $m=4$.
 cond: $s(x_i) = y_i, 0\le i\le n $.
@@
 ~\tb{TRR:} $\varphi_{n+1}(x) = (a_nx+b_n)\varphi_n(x)-c_n\varphi_{n-1}(x) $, where $\varphi_n = A_nx^n+B_nx^{n-1}+\cdots, ~a_n = \frac{A_{n+1}}{A_n}, \gamma_n = (\varphi_n, \varphi_n), b_n = a_n(\frac{B_{n+1}}{A_{n+1}}-\frac{B_n}{A_n}), c_n = \frac{A_{n+1}A_{n-1}}{A_n^2}\frac{\gamma_n}{\gamma_{n-1}}$.
+~\tb{Laguerre:} $w(x) = e^{-x}, [0, \infty), L_n(x) = \frac{1}{n!e^{-x}}\frac{d^n}{dx^n}(x^ne^{-x}) $, $|L_n|_2 = 1 $ for all $n$.
 
-\tb{General least square sol:} $\varphi$ be ort.
+\tb{General least square sol:} $\varphi$ be (normalized) ort.
 poly with $w(x)$.
 $r(x) = \sum_{k=0}^{n}b_k\varphi_k(x) $, where $b_j = (f, \varphi_j) $.
-~\tb{Bessel \& Parseval:} $|r_n^*|_2^2 = \sum_{k=0}^{n}(f, \varphi_k)^2 \le |f|_2^2 = \sum_{k=0}^{\infty}(f, \varphi_k)^2 $;
+~\tb{Bessel \& Parseval:} $|r_n^*|_2^2 = \sum_{k=0}^{n}(f, \varphi_k)^2 \le |f|_2^2 = \sum_{k=0}^{\infty}(f, \varphi_k)^2 $; ~\tb{Lagendre:} $\varphi_0(x) = \frac{1}{\sqrt{2}}, ~\varphi_n(x) = \sqrt{\frac{2n+1}{2}}\frac{(-1)^n}{2^nn!}\frac{d^n}{dx^n}[(1-x^2)^n], (f, \varphi_j) = \int_{-1}^1f(x)\varphi_j(x)dx, r_n^*(x) = \sum_{j=0}^{n}(f, \varphi_j)\varphi_j(x) $.
+~\tb{Chebyshev:} $\varphi_0(x) = \frac{1}{\sqrt{\pi}}, \varphi_n(x) = \sqrt{\frac{2}{\pi}}T_n(x), (f, \varphi_j) = \int_{-1}^1\frac{f(x)\varphi_j(x)}{\sqrt{1-x^2}}dx $.
 
@@
 
-\tb{Near Minimax:} use chebyshev least square $C_n(x) = \sum_{j=0}^{n}c_jT_j(x), c_j = \frac{2}{\pi}\int_{-1}^{1}\frac{f(x)T_j(x)}{\sqrt{1-x^2}}dx, c_0 = c_0/2 $ as an approximation, then the error is nearly $c_{n+1}T_{n+1}(x)$, then err be nearly $0$ at roots of $T_{n+1}(x) \to x_j = \cos\frac{2j+1}{2n+2}\pi, 0\le j\le n $.
-Use interpolation on these nodes $I_n(x) $ as approx of $C_n $ and $q_n^*(x) $.
+\tb{Near Minimax:} use chebyshev least square $C_n(x) = \sum_{j=0}^{n}c_jT_j(x), c_j = \frac{2}{\pi}\int_{-1}^{1}\frac{f(x)T_j(x)}{\sqrt{1-x^2}}dx, c_0 = c_0/2 $ as an approximation, then since $f = \sum_{j=0}^{\infty}'c_jT_j(x) (f\in C[-1, 1])$, the error $f(x) - C_n(x) $ is nearly $c_{n+1}T_{n+1}(x)$.
+Since $T_{n+1}(x_j) = (-1)^j, x_j = \cos\frac{j\pi}{n+1}, 0\le j\le n+1 $, with Chebyshev Equio.
+thm, $C_n $ should be nearly equal to the minimax approx.
+~$|f-I_n|_\infty \le\frac{1}{(n+1)!2^n}|f^{(n+1)}|_\infty $
+
+\tb{Chebyshev zeros interpolation:} from Near minimax, the error is nearly $c_{n+1}T_{n+1}(x) $, thus err be nearly $0$ at roots of $T_{n+1}(x) \to x_j = \cos\frac{2j+1}{2n+2}\pi, 0\le j\le n $.
+Use interpolation of $f(x)$ on these nodes $I_n(x) $ as approx of $C_n $ and $q_n^*(x) $ ($I_n(x) = \sum f(x_j)l_j(x) = \sum C_n(x_j)l_j(x) + \sum (f(x_j)-C_n(x_j))l_j(x) = C_n(x) $)
 
@@
 
+\tb{Cheb. Poly of 2nd kind:} $S_n(x) = \frac{1}{n+1}T_{n+1}'(x), [-1, 1], w(x) = \sqrt{1-x^2} $, satisfy same TRR with $\{T_n\}$.
+
 \tb{Near minimax err:} $x_i = \cos\frac{i\pi}{n+1}, 0\le i\le n+1, ~\sum_{k=0}^{n}c_{n,k}T_k(x_i)+(-1)^iE_n =f(x_i), \sum = \sum' \to c_{n, j} = \frac{2}{n+1}\sum_{i=0}^{n+1}f(x_i)\cos(\frac{ij\pi}{n+1}), \sum = \sum'', E_n = \frac{1}{n+1}\sum_{i=0}^{n+1}(-1)^if(x_i), \sum = \sum'' $.
-~\tb{Notice:} $\sum_{k=1}^{n}kz^k = \frac{1-(n+1)z^n+nz^{n+1}}{(1-z)^2}z $
+~\tb{Notice:} $\sum_{k=1}^{n}kz^k = \frac{1-(n+1)z^n+nz^{n+1}}{(1-z)^2}z $ \\[5pt]
+
+\tb{Integration:} $I_n(f) = \int_{a}^{b}f_n(x)dx = I(f_n) = \sum_{j=1}^{n}w_{j, n}f(x_{j, n}) $, use $\{f_n\}$ to approx. $f$, s.t. $|f-f_n|_\infty\to 0 $.
+
+\tb{Ways of deriving $w_{i}$:} 1. compute the integral of interpolation; 2. write down a series of equations.
+
+\tb{Asy. err:} $E_n $ exact; $\hat E_n $ estimate; $\lim_{n\to\infty}\frac{\hat{E_n}}{E_n} = 1 $. Corrected: $CT = I + \hat E$.
+
+\tb{trapezoidal:} $E_1(f) = \int_{a}^{b}(x-a)(x-b)f[a,b,x]dx = -\frac{(b-a)^3}{12}f''(\eta)$ (use mean value thm).
+~\tb{composite:} $E_n(f) = -\frac{h^3n}{12}\frac{1}{n}\sum_{j=1}^{n}f''(\eta_j) = -\frac{(b-a)h^2}{12}f''(\eta) $.
+~\tb{Asy err:} $\lim_{n\to\infty}\frac{E_n(f)}{h^2} = -\frac{1}{12}\int_{a}^{b}f''(x)dx $.
+
+\tb{Simpson:} $I_2 = \frac{h}{3}(1,4,1), h = \frac{b-a}{2}$.
+$E_2 = \int_{a}^{b}(x-a)(x-b)(x-c)f[a,b,c,x]dx = \int_{a}^{b}w'(x)f[a,b,c,x] dx = -\frac{h^5}{90}f^{(4)}(\eta).
+$ (integrate by parts; $w(x) = \int_{a}^{x}(t-a)(t-b)(t-c)dt, w(a)=w(b)=0, w(x)>0 \in (a, b) $.
+) ~\tb{composite:} $h = (b-a)/n, I_n = \frac{h}{3}(1,4,2,4,2\cdots, 2,4,1) $.
+$E_n = -\frac{h^4(b-a)}{180}f^{(4)}(\eta) $.
+
+\tb{Peano Kernel:} $f = p_1+R_2 $, $R_2 = \int_{a}^{x}(x-t)f''(t)dt $.
+compute $E_1(R_2) $ use $\int_{a}^{b}\int_{a}^{x}G(x, t)dtdx = \int_a^b\int_t^bG(x, t)dxdt $, get $E_n(f) = \int_{a}^{b}K(t)f''(t)dt $.
+
+\tb{N-C:} use lag.
+poly to approx $f$.
+\tb{Err:} 1.
+$n$ even, $f\in C^{n+2} $.
+$E_n(f) = C_nh^{n+3}f^{(n+2)}(\eta), ~C_n = \frac{1}{(n+2)!}\int_{0}^{n}u^2(u-1)\cdots (u-n)du $; 2.
+$n$ odd, $f\in C^{n+1} $.
+$E_n(f) = C_nh^{n+2}f^{(n+1)}(\eta), ~C_n = \frac{1}{(n+1)!}\int_0^n u(u-1)\cdots (u-n)du $.
+~\tb{Precision:} $m$ if $I = \hat{I}$ for all poly deg $\le m$.
+
+\tb{Conv NC:} $I_n(f)\to I(f) \iff $ 1. $I_n(f)\to I(f) $ for all $f\in\mathcal{F}$ dense in poly; 2. $B = \sup_{n}\sum_{j=0}^{n}|w_{j, n}| < \infty $.
+
+\tb{Midpoint:} $E_n(f) = \frac{h^2(b-a)}{24}f''(\eta) $. \\[5pt]
+
+\tb{Gaussian:} Regard $I_n(f) = \sum_{j=1}^{n}w_{j,n}f(x_{j,n}) = \int_{a}^{b}w(x)f(x)dx $.
+Use Orthogonal poly: (construct with Hermite).
+$w_i = \int_{a}^{b}w(x)l_i(x)dx $, $E_n(f) = \frac{f^{(2n)}(\eta)}{(2n)!}\int_{a}^{b}w(x)\frac{\varphi_n(x)^2}{A_n^2}dx $, $x_i $ be roots of $\varphi_n(x) $ w.r.t.
+$w(x)$.
+~\tb{Err:}  $|E_n(f)|\le 2\rho_{2n-1}(f)\int_a^bw(x)dx $.
+
+\tb{G-Legendre:} $w(x) = 1, \in [-1, 1]$, $w_i = -\frac{2}{(n+1)P_n'(x_i)P_{n+1}(x_i)}$, $E_n(f) = \frac{2^{2n+1}(n!)^4}{(2n+1)((2n)!)^2}\frac{f^{2n}(\eta)}{(2n)!} $.
+
+\tb{Comments:} roots of $I_n $ are diff. from $I_m $; can handle near-singular integrals.
+
+\tb{Asymptotic Err:} Euler-MacLaurin: err in trapezoidal: $E_n(f) = \int_a^bf(x)dx - h\sum_{j=0}^{n}''f(x_j)  = -\sum_{i=1}^{m}\frac{B_{2i}}{(2i)!}h^{2i}(f^{(2i-1)}(b) - f^{(2i-1)}(a)) + \frac{h^{2m+2}}{(2m+2)!}\int_a^b \bar{B}_{2m+2}(\frac{x-a}{h})f^{(2m+2)}(x)dx $, where $\frac{t(e^{xt}-1)}{e^t-1} = \sum_{j=1}^{\infty}B_j(x)\frac{t^{j}}{j!}, ~\frac{t}{e^t-1} = \sum_{j=0}^{\infty}B_j\frac{t^j}{j!}, \bar{B_j}(x)$ be periodic extension of $B_j(x) $ w./ pero.
+1.
+(PF: consider $n=1$, then $n \ge 1$ be composite form of $n=1$).
+\tb{Trapezoidal:} for periodic functions, order of conv.
+of tra.
+is greater than any power of $h$.
+
+\tb{Richardson:} $I - I_n = \frac{d_2}{n^2}+\frac{d_4}{n^4}+\cdots $, $I-I_{n/2} = \frac{4d_2}{n^2}+\frac{16d_4}{n^4}+\cdots $.
+Then $I = \frac{4I_n-I_{n/2}}{3} - \frac{4d_4}{n^4}-\cdots$.
+$I_n^{(k)} = \frac{4^kI_n^{(k-1)}-I_{n/2}^{(k-1)}}{4^k-1} $.
+(less computing, low order conv cmp to Gaussian).
+
+\tb{Romberg:} $I_k(f) = I_{2^k}^{(k)}(f) $.
+
+\tb{Singular:} In function/in interval; sol: \tb{1.
+change variable}(singularity happens in func and derivatives/interval): $u = x^\alpha ,u = \frac{1}{x^\alpha}$; EXP: $I = \int_{1}^\infty\frac{f}{x^p}dx, x = \frac{1}{u^\alpha}, I = \alpha\int_0^1u^{(p-1)\alpha-1}f(\frac{1}{u^\alpha})du $, pick $(p-1)\alpha-1$ larger to max smoothness on $x = 0$.
+2.
+for $I = \int_{a}^{b}$ has endpoint singularity, let $\psi(t) = \exp(\frac{-c}{1-t^2}), \varphi(t) = a + \frac{b-a}{\gamma}\int_{-1}^t\psi(u)du, -1\le t\le 1, \gamma  = \int_{-1}^1\psi(u)du $.
+Let $x = \varphi(t), I = \int_{-1}^1f(\varphi(t))\varphi'(t)dt $ ~\tb{2.
+Gaussian Quad:} EXP: $I = \int_{0}^{\infty}g(x)dx = \int_{0}^{\infty}e^{-x}f(x)dx $.
+Use Gauss-Laguerre ($w(x) = e^{-x}, L_n(x) = \frac{1}{n!e^{-x}}\frac{d^n}{dx^n}{x^ne^{-x}} $).
+~EXP: $I = \int_{-1}^1\frac{f(x)}{\sqrt{1-x^2}}dx$, use Chebyshev, $x_{j, n} = \cos\frac{2j-1}{2n}\pi, 1\le j\le n, w_{j, n} = \frac{\pi}{n} $.
+~\tb{Analytic:} $I = \int_{0}^{b}f(x)\log(x)dx = \int_0^\epsilon+\int_\epsilon^b  = I_1+I_2 $.
+Take the first terms of Taylor series of $f$ in $I_1 $.
+~\tb{4.
+Product Integration:} $I(f) = \int_a^bw(x)f(x) $, let all singularity in $w$.
+Produce $\{f_n\}$, $|f-f_n|_{\infty}\to 0 $, $I_n(f) = I(f_n)  $ easily computed, then $|I(f)-I_n(f) |\le |f-f_n|_\infty \int_a^b|w(x)|dx $.
+EXP: product trapezoidal for $I(f) = \int_0^bf(x)\log(x)dx, x_j = jh$.
+For $x_{j-1}\le x\le x_j, f_n(x) = \frac{1}{h}((x_j-x)f(x_{j-1})+(x-x_{j-1})f(x_j)) $, then $|f-f_n|\le \frac{h^2}{8}|f''|$.
+
+\tb{Diff:} 0.
+Definition.
+1.
+use poly.
+interpolation.
+$f'(x) = p_n'(x) = \sum_{j=0}^{n}f(x_j)l_j'(x) $, error = $\Psi_n'(x)\frac{f^{(n+1)}(\xi_1)}{(n+1)!}+\Psi_n(x)\frac{f^{(n+2)}(\xi_2)}{(n+2)!} = O(h^n)$ (when $\Psi_n'(x)\ne 0 $) and $= O(h^{n+1})$ (when $\Psi_n'(x) = 0 $).
+(So choose nodes to have $\Psi_n'(x) = 0 $) $\to$ if $n$ odd, nodes symmetrically about $x$.
+~\tb{2.
+Method of Undetermined Coeff.} EXP: $f''(x) = Af(x+h)+Bf(x)+Cf(x-h)$, use Taylor expansion of $f(x), f(x\pm h)$.
+Notice: error dominates the result when $h$ gets very small.
+\\[5pt]
+
+\tb{Some Formulas:} $\sum_{k=1}^{n}kz^k = \frac{1-(n+1)z^n+nz^{n+1}}{(1-z)^2}z $ ~$\int_{0}^1x^n\ln(x)dx = -\frac{1}{(n+1)^2} $.
 \end{document}

### 2018-01-23 Graduate - PDE/Assignment 1/u.m
UPDATE

@@ -1,0 +1,3 @@
+function y = u(x, t)
+    p = x*exp(-t);
+    y = exp(-2*(p-2).^2);

### 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
add problem 1-3

--- 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
@@
 \documentclass{article}%
+
 \usepackage{amsmath}
+
 \usepackage{graphicx}
+
 \usepackage{amsfonts}%
+
 \usepackage{amssymb}
@@
 \setlength{\topmargin}{-0.75in}
+
 \setlength{\textheight}{9.25in}
+
 \setlength{\oddsidemargin}{0.0in}
+
 \setlength{\evensidemargin}{0.0in}
+
 \setlength{\textwidth}{6.5in}
+
 \def\labelenumi{\arabic{enumi}.}
+
 \def\theenumi{\arabic{enumi}}
+
 \def\labelenumii{(\alph{enumii})}
+
 \def\theenumii{\alph{enumii}}
+
 \def\p@enumii{\theenumi.}
+
 \def\labelenumiii{\arabic{enumiii}.}
+
 \def\theenumiii{\arabic{enumiii}}
+
 \def\p@enumiii{(\theenumi)(\theenumii)}
+
 \def\labelenumiv{\arabic{enumiv}.}
+
 \def\theenumiv{\arabic{enumiv}}
+
 \def\p@enumiv{\p@enumiii.\theenumiii}
+
 \pagestyle{plain}
+
 \setcounter{secnumdepth}{0}
+
 \newtheorem{theorem}{Theorem}
+
 \newtheorem{acknowledgement}[theorem]{Acknowledgement}
+
 \newtheorem{algorithm}[theorem]{Algorithm}
+
 \newtheorem{axiom}[theorem]{Axiom}
+
 \newtheorem{case}[theorem]{Case}
+
 \newtheorem{claim}[theorem]{Claim}
+
 \newtheorem{conclusion}[theorem]{Conclusion}
+
 \newtheorem{condition}[theorem]{Condition}
+
 \newtheorem{conjecture}[theorem]{Conjecture}
+
 \newtheorem{corollary}[theorem]{Corollary}
+
 \newtheorem{criterion}[theorem]{Criterion}
+
 \newtheorem{definition}[theorem]{Definition}
+
 \newtheorem{example}[theorem]{Example}
+
 \newtheorem{exercise}[theorem]{Exercise}
+
 \newtheorem{lemma}[theorem]{Lemma}
+
 \newtheorem{notation}[theorem]{Notation}
+
 \newtheorem{problem}[theorem]{Problem}
+
 \newtheorem{proposition}[theorem]{Proposition}
+
 \newtheorem{remark}[theorem]{Remark}
+
 \newtheorem{solution}[theorem]{Solution}
+
 \newtheorem{summary}[theorem]{Summary}
+
 \newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
@@
 \begin{center}
-\textbf{Introduction to Analysis $I$\\Homework 4\\Wednesday, September 27, 2017}\bigskip
+
+\textbf{Homework 1}\bigskip
+
 \end{center}
 
-\noindent\textbf{Instructions}: This and all subsequent homeworks must be submitted written in \LaTeX.
+\noindent\textbf{Instructions}:
 
-\noindent If you use results from books, Royden or others, please be explicit about what results you are using.
+\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip
+
+\noindent If you use results from books including Conway's, please be explicit about what results you are using.
 
 \begin{center}
-\emph{Homework 4 is due by midnight, Saturday, October 7.}
+
+\emph{Homework 1 is due on Dropbox on Monday, February  5.}
+
 \end{center}
+
 \medskip
@@
 \begin{enumerate}
-\item  (Problem 18, Page 63) Let $I$ be a closed bounded interval and let $f$ be a bounded measurable function defined on $I$.
-Let $\epsilon > 0$.
-Show that there is a step function $h$ on $I$ and a measurable subset $F$ of $I$ for which \[
-|h-f|< \epsilon \text{ on } F \text{ and } m(I\sim F)< \epsilon .\]
 
-\bigskip
-\textbf{Collaborators:} None
-\smallskip
+\item Show that $\lim_{n\to \infty}{n^{\frac{1}{n}}} = 1$ without using logarithms.
 
-\textbf{Solution:}
-For $\epsilon > 0$, according to Lusin's Theorem, there exists a closed subset $F$ of $I$, s.t. $m(I\setminus F) < \epsilon$, and $f$ is continuous on $F$. 
-Then for $x_0\in F$, for this $\epsilon > 0$, 
+\textbf{Proof.} Let $n^{1/n} = 1+y_n $. First we know $n^{1/n} > 1^{1/n} = 1 $, so $y_{n} > 0$. Then 
 $$
-\exists \sigma > 0, ~\forall x\in (x_0-\delta, ~x_0+\delta)\cap F, ~|f(x)-f(x_0)| < \epsilon.
+n = (1+y_n)^n = 1+ny_n+\frac{n(n-1)}{2}y_n^2+\cdots+y_n^n > 1+\frac{n(n-1)}{2}y_n^2.
 $$
-Since
+Thus $\frac{n(n-1)}{2}y_n^2 < n-1 $, which means $y_n < \sqrt{2/n}.
+$ Hence $\lim\limits_{n\to\infty} y_n \le \lim\limits_{n\to\infty}\sqrt{2/n} = 0$, which means $y_n\to 0 $, and thus $n^{1/n}\to 1 $.
+
+\item Given a power series, $\sum_{n=0}^{n=\infty} a_n(z - a)^n$, show that its radius of convergence $R$ satisfies the inequalities$$(\limsup{\vert \frac{a_{n+1}}{a_n} \vert})^{-1} \leq R \leq \limsup{\vert \frac{a_{n}}{a_{n+1}} \vert}.$$
+
+\textbf{Proof.} We only proof the right inequality since it is just the same for the left one.
+If $R > r > \limsup|\frac{a_n}{a_{n+1}}| = \alpha $, then there is an $N > 0$ s.t.
+$r > |a_n/a_{n+1}| $ for all $n \ge N$.
+Let $B = |a_N|r^N $, then $|a_{N+1}|r^{N+1} = |a_{N+1}|rr^{N} > B $.
+Hence for all $n > N$ we have $|a_n|r^n > B $, which gives $|a_nz^n| \ge B |z|^n/|r|^n $ when $n > N$.
+But $|z|/|r| > 1$, which makes $|z|^n/|r|^n \to\infty $ when $n\to\infty$.
+Hence $\sum a_nz^n $ diverges, so $R \le \alpha$.
+
+\item Problem III.1.6.
+
+\textbf{(a).} By Theorem 1.3, 
 $$
-\bigcup_{x_0\in F} (x_0-\delta_i, ~x_0+\delta_i)
+\limsup |a_n|^{1/n} = \limsup |a^n|^{1/n} = |a|,
 $$
-is an open cover of the closed set $F$, it has a finite subcover, denoted by
+thus $R = \frac{1}{|a|}$.
+
+\textbf{(b).} By Theorem 1.3,
 $$
-\bigcup_{i=1}^n (x_i-\delta_i, ~x_i+\delta_i).
-$$
-If we define
-$$
-h = \left\{
+\limsup |a_n|^{1/n} = \limsup |a^{n^2}|^{1/n} = \limsup |a^n| = \left\{
 \begin{aligned} 
-&f(x_i), ~\text{for} ~x\in (x_i-\delta_i, ~x_i+\delta_i), \\
-&0, ~\text{others}
+&0, |a| < 1, \\
+&1, |a| = 1, \\
+&\infty, |a| > 1.
 \end{aligned}
@@
 $$
-then $h$ takes constant values in finite intervals, and $h = 0$ in other parts, we know $h$ is a step function. And from the construction above, on each interval $(x_i-\delta_i, x_i+\delta_i)\cap F$, 
-$$
-|h-f|< \epsilon ~\text{on}~ (x_i-\delta_i, x_i+\delta_i)\cap F.
-$$
-Thus $h$ is the step function needed.
-
-\bigskip
-
-\item (Problem 22, Page 64) (Dini's Theorem)  Let $\{f_n\}$ be an increasing sequence of continuous functions on $[a,b]$ which converges pointwise on $[a,b]$ to the continuous function $f$ on $[a,b]$.
-Show that the convergence is uniform on $[a,b]$.
-
-\bigskip
-\textbf{Collaborators:} None
-\smallskip
-
-\textbf{Solution:}
-If the convergence is not uniform, then there $\exists \epsilon > 0, \forall N > 0, ~\exists n > N, ~\exists x\in [a, b], ~|f(x)-f_n(x)| > \epsilon $.
-
-We can construct a sequence $\{x_n\}$ like this:
-
-$$
-N = 1, ~\exists n_1 > 1, ~\exists x_1\in[a, b], ~|f_{n_1}(x_1)-f(x_1)| \geqslant \epsilon.
-$$
-$$
-N = n_1, ~\exists n_2 > n_1, ~\exists x_2\in[a, b], ~|f_{n_2}(x_2)-f(x_2)| \geqslant \epsilon.
-$$
-$$
-\cdots
-$$
-$$
-N = n_{k-1}, ~\exists n_k > n_{k-1}, ~\exists x_k\in[a, b], ~|f_{n_k}(x_k)-f(x_k)| \geqslant \epsilon.
-$$
-$$
-\cdots
-$$
-Then since $x_i\in [a, b]$, according to Bolzano-Weierstrass Theorem, there is a convergent subsequence in $\{x_i\}$, and we may denote it by $\{y_i\}$ for convinence.
-Assume $y_i\to y\in [a, b]$, then since
-$$
-\lim_{n\to\infty}f_n(y) = f(y),
-$$
-for this $\epsilon > 0, ~\exists N$, s.t.
-$$
-|f_N(y)-f(y)|<\epsilon.
-$$
-since $f_N$ is continuous, with $y_k\to y$, there $\exists K > 0$, 
-$$
-|f_N(y_k)-f(y_k)| < \epsilon
-$$
-holds for all $k > K$. Notice that $\{f_n\}$ is an increasing sequence, when $n > N ~\text{and}~ k > K$, 
-$$
-|f_n(y_k)-f(y_k)| \leqslant |f_N(y_k)-f(y_k)|<\epsilon.
-$$
-Since $n_k\to\infty$ when $k\to\infty$, when $k$ is sufficiently large we have $k > K, ~n_k > N$. Thus 
-$$
-|f_{n_k}(x_k)-f(x_k)| < \epsilon,
-$$ 
-which makes a contradiction with the assumption. Thus the convergence is uniform.
-\bigskip
-
-\item  (Problem 5, Page 364) Show that an extended real-valued function $f$ on $X$ is measurable if and only if for each rational number $c$, $\{x\in X \mid f(x)< c\}$ is a  measurable set.
-
-\bigskip
-\textbf{Collaborators:} None
-\smallskip
-
-\textbf{Solution:}
-Notice that for each $r\in \mathbb{R}\supset\mathbb{Q}$, we have
-$$
-\{x\in X\mid f(x) < r\} = \bigcup_{\substack{c < r \\ c \in \mathbb{Q}}}\{x\in X\mid f(x) < c\}.
-$$
-Then since Lebesgue measurable sets make a $\sigma-$Algebra, we know $\{x\in X\mid f(x) < r\}$ is measurable.
-On the other hand, since each rational number is a real number, the other direction stands.
-\bigskip
-
-\item (Problem 13, Page 365) Let $\{f_n\}$ be a sequence of real-valued functions on $X$ such that for each natural number $n$, $\mu \{x\in X \mid |f_n (x) - f_{n+1}(x)|> 1/2^n\}<1/2^n$.
-Show that $\{f_n\}$ is pointwise convergent a.e.
-on $X$.
-
-\bigskip
-\textbf{Collaborators:} None
-\smallskip
-
-\textbf{Solution:}
-Denote
-$$
-E_n = \{x\in X\mid |f_n(x)-f_{n+1}(x)|>\frac{1}{2^n}\},
-$$
-Then 
-$$
-\bigcup_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\frac{1}{2^n} = 1.
-$$
-According to Borel-Cantelli Lemma, $\exists E_0$, $\mu(E_0) = 0$, s.t.
-$\forall x\in X\setminus E_0$, $x$ belongs to at most finite number of $E_n$.
-That means, $\forall x\in X\setminus E_0$, $\exists N > 0$, $\forall n > N$, $x\in E_n$.
-So
-$$
-|f_n(x)-f_{n+1}(x)| < \frac{1}{2^n}.
-$$
 Thus 
 $$
-\forall m > n, |f_m(x)-f_{n}(x)| < \sum_{i=n}^{m-1}|f_{i+1}(x)-f_i(x)| < \frac{1}{2^{n-1}}.
-$$
-This means that $f_n(x)$ is a Cauchy sequence, then it converges. Thus $\{f_n\}$ is pointwise convergent on $X\setminus E_0$, and thus is pointwise convergent a.e. on $X$.
-\bigskip
-
-\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
-\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
-\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
-\begin{enumerate}
-\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
-\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
-\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.
-\end{enumerate}
-
-\bigskip
-\textbf{Collaborators:} None, but (b) and (c) checked a proof from my Real Analysis textbook in college (Written by Prof. Zhaobo Huang, Fudan University).
-\smallskip
-
-\textbf{Solution:}
-\textbf{(a)} Since $\{f_n\}$ converges pointwise a.e. on $X$, there $\exists E_0, ~\mu(E_0) = 0$, s.t. $\lim\limits_{n\to\infty}f_n = f$ on $E_1 = X\setminus E_0$. Then $\forall \epsilon > 0$,
-$$
-E_1 = \bigcup_{k=1}^{\infty} \bigcap_{n=k}^{\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\} = \varliminf_{n\to\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}.
-$$
-Thus, according to the continuity of measure, 
-$$
-\mu(E_1) \le \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}).
-$$
-Since $\mu(X) < \infty$, we have
-$$
+R = \left\{
 \begin{aligned}
-\lim_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| &> \epsilon\}) \le \varlimsup_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| > \epsilon\}) \\
-&= \mu(X) - \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}) \le 0.
-\end{aligned}
-$$
-Thus $\{f_n\}$ converges to $f$ in measure.
-
-\textbf{(b)}
-Since $\{f_n\}$ converges to $f$ in measure, $\forall k \in \mathbb{N}$, $\exists n_k > n_{k-1} \in \mathbb{N}$, s.t. when $n \ge n_k$,
-$$
-\mu(\{x\in X\mid |f_n(x)-f(x)| \ge \frac{1}{2^k}\}) < \frac{1}{2^k}.
-$$
-Denote $E_{k} = \{x\in X\mid |f_{n_k}(x)-f(x)| \ge \frac{1}{2^k}\}$, then $\mu(E_k) < \frac{1}{2^k}$. Let 
-$$
-F_k = \bigcap_{i=k}^{\infty} (X\setminus 
-E_i) = \{x\in X\mid |f_{n_i}(x)-f(x)|\le \frac{1}{2^i}, i = k, k+1, \cdots\}
-$$
-then $\{f_{n_k}\}$ converges uniformly to $f$ on $F_k$, thus is convergent on $F = \bigcup\limits_{k=1}^{\infty}F_k$. On the other hand,
-$$
-X\setminus F = \bigcap_{k=1}^{\infty}(X\setminus F_k) = \bigcap_{k=1}^{\infty}\bigcup_{k=1}^{\infty}E_i = \varlimsup_{i\to\infty}E_i,
-$$
-and 
-$$
-\sum_{i=1}^{\infty}\mu(E_i) \le \sum_{i=1}^{\infty}\frac{1}{2^i} = 1, 
-$$
-thus $\mu(X\setminus F) = 0$, $\{f_{n_k}\}$ converges pointwise a.e. on $X$.
-
-\textbf{(c)} If $\{f_n\}$ is Cauchy in measure, then for each $n_i \in \mathbb{N}$, there $\exists n_{i+1} > n_{i}$, s.t. 
-$$
-\mu(\{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\})\le \frac{1}{2^i}.
-$$
-We can denote the subsequence $\{f_{n_i}\}$ as $\{g_i\}$, and $E_i = \{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\}$.
-Let $F_{k} = \bigcup\limits_{i = k}^{\infty}E_i $, then $\mu(F_k)\le \sum\limits_{i=k}^{\infty}\frac{1}{2^i}\le \frac{1}{2^{k-1}} $.
-Denote $F = \bigcap\limits_{i=1}^\infty F_i $, then $\mu(F) = 0$.
-
-If we choose $x\notin F_{k}$, and $i \ge j \ge k$, then 
-$$
-|g_i(x)-g_j(x)| \le \sum_{l = j}^{i-1}|g_{l+1}(x)-g_l(x)| \le \frac{1}{2^j},
-$$
-which means $g_i(x)$ is Cauchy respective to $i$ on $X\setminus F$, thus converges on $X\setminus F$. Thus we can construct a function $f$ like this: 
-$$
-f(x) = \left\{
-\begin{aligned}
-&0, ~x\in F \\
-&\lim_{i\to\infty}f_i(x), ~x\in X\setminus F.
+&\infty, |a| < 1,\\
+&1, |a| = 1,\\
+&0, |a| > 1.
 \end{aligned}
@@
 $$
-Then $\{g_i(x)\}$ converges to $f$ on $X\setminus F$, which means $\{g_i\}$ converges pointwise a.e. on $X$. Now we show $\{f_n\}$ converges to $f$ in measure. Notice
+
+\textbf{(c).} By Theorem 1.3,
 $$
-\mu(\{x\in X\mid |f_n - f|\ge \xi\}) \le \mu(\{x\mid |f_n-g_m|\ge \frac{\xi}{2}\}) + \mu(\{x\mid |g_m-f|\ge \frac{\xi}{2}\}), ~m > n
+\limsup |a_n|^{1/n} = \limsup |k^n|^{1/n} = k,
 $$
-and when $n\to\infty$, the two terms in the right can be arbitrarily small, so 
+thus $R = \frac{1}{k}$.
+
+\textbf{(d).} Since 
 $$
-\lim_{n\to\infty}\mu(\{x\in X\mid |f_n - f|\ge \xi\}) = 0, ~\forall \xi > 0.
+\sum_{n=0}^{\infty}|z|^{n!} < \sum_{n=0}^{\infty}|z|,
 $$
-The $\{f_{n}\}$ converges in measure.
-\bigskip
+and the convergence radius of the latter series is $R' = 1$, we know $R\ge 1$.
+On the other hand, if $R > 1$, pick $1 < |z| = r < R$, then $|z|^{n!} = r^{n!}\to\infty $ when $n\to\infty$, hence the series diverges.
+Thus $R = 1$.
 
-\item (Problem 16, Page 365) Assume $\mu (X) < \infty$.
-Show that $\{f_n\}$ converges to $f$ in measure if and only if each  subsequence of $\{f_n\}$ has a further subsequence that converges pointwise a.e.
-on $X$ to $f$.
-Use this to show that for two sequences that converge in measure, the product sequence also converges in measure to the product of the limits.
+\item Problem III.1.7
 
-\item Show that if $f$ is an lower semicontinuous (resp.
-upper semicontinuous) function on an interval $[a,b]$, then there is a family $\{f_{\alpha}\}$ of continuous functions on the interval $[a,b]$ such that $f(x) = \sup\{f_{\alpha}(x) \mid \alpha \in A \}$ (resp.
-$f(x) = \inf\{f_{\alpha}(x) \mid \alpha \in A \}$) for all $x \in [a,b]$.
+\item Problem III.2.6
 
-\bigskip
-\textbf{Collaborators:}\\
-\smallskip
+\item Problem III.2.7
 
-\textbf{Solution:}
-\bigskip
+\item Problem III.2.9.
+
+\item Problem III.2.13
+
+\item Problem III.2.20
 
 \end{enumerate}
+
 \end{document}

### 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
add prob 4-5

@@
 
+\textbf{Proof.} On one hand, 
+$$
+\sum_{n=1}^{\infty} |a_n| |z^{n(n+1)}| \le \sum_{n=1}^{\infty}|a_n||z^n|,
+$$
+thus $R \ge R' = \lim|a_n/a_{n+1}| = \lim \frac{n+1}{n} = 1 $.
+On the other hand, if $R > 1$, pick $1 < r < R$, then $|a_n|z^{n(n+1)} = \frac{1}{n}r^{n(n+1)} = \frac{1}{n}(1+\delta)^{n(n+1)} > \frac{1}{n} (1+n\delta)^{n+1} > \frac{1}{n}(1+n(n+1)\delta) > (n+1)\delta.
+$ But the last term $\to\infty$ as $n\to\infty$, hence the series diverges.
+Thus $R = 1$.
+
+When $z = 1$, the series becomes $\sum_{n=1}^{\infty}\frac{(-1)^n}{n}$, it is a Leibniz series, thus converges.
+When $z = -1$, since $n(n+1)$ is a even number, it is the same with $z = 1$, thus converges.
+When $z = i$, the series becomes
+$$
+\begin{aligned}
+&\sum_{n=0}^{\infty} -\left(\frac{(-1)^{4n+1}}{(4n+1)}+\frac{(-1)^{4n+2}}{4n+2}\right)+\left(\frac{(-1)^{4n+3}}{(4n+3)}+\frac{(-1)^{4n+4}}{4n+4}\right) = \sum_{n=0}^{\infty}\frac{1}{4n+1}-\frac{1}{4n+2}-\frac{1}{4n+3}+\frac{1}{4n+4} \\
+&= \sum_{n=0}^{\infty}(-1)^n (\frac{1}{2n+1}-\frac{1}{2n+2}) = \sum_{n=0}^{\infty}\frac{(-1)^n}{(2n+1)(2n+2)}.
+\end{aligned}
+$$
+It is also a Leibniz series, so converges.
+
 \item Problem III.2.6
+
+\textbf{(i)} $z = x+iy$, then $e^z = e^x(\cos y+i\sin y) = i \to x = 0, y = 2k\pi + \frac{\pi}{2}$. Thus $z = i(2k\pi+\frac{\pi}{2}), k \in \mathbb{Z}$.
+
+\textbf{(ii)} $e^x(\cos y+i\sin y) = -1 \to x = 0, y = 2k\pi+\pi $. Thus $z = i(2k\pi+\pi), k \in \mathbb{Z}$.
+
+\textbf{(iii)} $e^x(\cos y+i\sin y) = -i \to x = 0, y = 2k\pi + \frac{3\pi}{2}$. Thus $z = i(2k\pi+\frac{3\pi}{2}), k \in \mathbb{Z}$.
+
+\textbf{(iv)} $\frac{1}{2}(e^{iz}+e^{-iz}) = 0 \to e^{-y}(\cos x+i\sin x)+e^y(\cos x-i\sin x) = 0 \to \cos x = 0, e^{-y} = e^y \to y = 0, x = k\pi+\frac{\pi}{2}.
+$ Thus $z = k\pi+\frac{\pi}{2}, k\in\mathbb{Z} $.
+
+\textbf{(v)} $\frac{1}{2i}(e^{iz}-e^{-iz}) = 0 \to e^{-y}(\cos x+i\sin x)-e^y(\cos x-i\sin x) = 0 \to -y = y, \sin x = 0 \to y = 0, x = k\pi $. Thus $z = k\pi, k\in\mathbb{Z}$.
 

### 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
add problem 6-9

@@
 \item Problem III.2.7
+$$
+\cos z\cos w = \frac{1}{4}(e^{iz}+e^{-iz})(e^{iw}+e^{-iw}) = \frac{1}{4}(e^{i(z+w)}+e^{-i(z+w)}+e^{i(z-w)}+e^{i(w-z)}),
+$$
+$$
+\sin z\sin w = -\frac{1}{4}(e^{iz}-e^{-iz})(e^{iw}-e^{-iw}) = \frac{1}{4}(-e^{i(z+w)}-e^{-i(z+w)}+e^{i(z-w)}+e^{i(w-z)})
+$$
+$$
+\cos z\sin w = \frac{1}{4i}(e^{iz}+e^{-iz})(e^{iw}-e^{-iw}) = \frac{1}{4i}(e^{i(z+w)}-e^{i(z-w)}+e^{i(w-z)}-e^{-i(z+w)})
+$$
+$$
+\sin z\cos w = \frac{1}{4i}(e^{iz}-e^{-iz})(e^{iw}+e^{-iw}) = \frac{1}{4i}(e^{i(z+w)}+e^{i(z-w)}-e^{i(w-z)}-e^{i(z+w)})
+$$
+Hence, 
+$$
+\cos(z+w) = \frac{1}{2}(e^{i(z+w)}+e^{-i(z+w)}) = \cos z\cos w-\sin z\sin w.
+$$
+$$
+\sin(z+w) = \frac{1}{2i}(e^{i(z+w)}-e^{-i(z+w)}) = \cos z\sin w+\sin z\cos w.
+$$
 
@@
 
+\textbf{Proof.} 
+$$
+\begin{aligned}
+|z_n-z| &= |r_ne^{i\theta_n}-re^{i\theta}| = |r_n\cos(\theta_n)-r\cos(\theta) + i(r_n\sin(\theta_n)-r\sin(\theta))| \\
+&= \sqrt{(r_n\cos(\theta_n)-r\cos(\theta))^2+(r_n\sin(\theta_n)-r\sin(\theta))^2} \\
+&= \sqrt{r_n^2+r^2-2r_nr\cos(\theta_n-\theta)}.
+\end{aligned}
+$$
+If $\theta_n \nrightarrow \theta $, then there exists $\epsilon > 0$
+$$
+|z_n-z| \ge \sqrt{2r_nr(1-\cos(\theta_n-\theta))} > \epsilon,
+$$
+which contradicts with $z_n\to z $. Hence $\theta_n\to \theta $. So
+$$
+|z_n-z| \to |r_n-r|.
+$$
+Thus $r_n\to r $.
+
 \item Problem III.2.13
 
+$z = f(z)^n \to f(z) = z^{1/n} $, take a branch. Thus
+$$
+f(z) = z^{1/n} = e^{\frac{1}{n}\log z} = e^{\frac{1}{n} (\log |z| + iArg z+ i2k\pi)} = |z|^{1/n}e^{\frac{i}{n}(Argz+2k\pi)}.
+$$
+Pick any $k\in\mathbb{Z}$ and we can get a function satisfying the conditions.
+
 \item Problem III.2.20
+
+$$
+\log(z_1\cdots z_n) = \log|z_1\cdots z_n|+ Arg(z_1\cdots z_n).
+$$
+We need to show that ($Arg$ is the principle branch.)
+$$
+Arg(z_1\cdots z_n) = \sum Arg(z_i).
+$$
+and
+$$
+\log|z_1\cdots z_n| = \sum\log|z_i|.
+$$
+The second term is trivial from logarithm of real numbers.
+For the first term, we use induction.
+Let $z_j = r_je^{i\theta_j} $, then from the condition we know $-\frac{\pi}{2} < \theta_j < \frac{\pi}{2}$ (*).
+
+First, when $k = 2$, from the condition we know $2k\pi-\frac{\pi}{2} < \theta_1 + \theta_2 < 2k\pi+\frac{\pi}{2}$.
+But from (*) we know $-\pi < \theta_1 + \theta_2 <\pi $, thus $-\frac{\pi}{2} <\theta_1 + \theta_2 < \frac{\pi}{2}$.
+Hence $Arg(z_1z_2) = Arg(z_1)+Arg(z_2)$.
+
+Suppose it holds when $\le n-1$.
+Then from induction we know $-\frac{\pi}{2} <\sum\limits_{j=1}^{n-1}\theta_j < \frac{\pi}{2}$, and using the same deduction with $k = 2$, we can know $-\frac{\pi}{2} <\sum\limits_{j=1}^{n}\theta_j < \frac{\pi}{2}$.
+Hence $Arg(\prod z_i) = \sum Arg(z_i)$.
+
+If the restrictions are removed, the formula is not valid.
+For example, $z_1 = e^{i\pi}, z_2 = e^{i\frac{3\pi}{2}} $, then $\log(z_1z_2) = i\frac{\pi}{2}$, while $\log(z_1)+\log(z_2) = i\frac{5\pi}{2}$.
 

### 2018-01-29 Graduate - Introduction to Analysis II/HW2/2HW20180127-2.tex
add hw 1-6

\documentclass{article}%

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage{amsfonts}%

\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}

\setlength{\textheight}{9.25in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textwidth}{6.5in}

\def\labelenumi{\arabic{enumi}.}

\def\theenumi{\arabic{enumi}}

\def\labelenumii{(\alph{enumii})}

\def\theenumii{\alph{enumii}}

\def\p@enumii{\theenumi.}

\def\labelenumiii{\arabic{enumiii}.}

\def\theenumiii{\arabic{enumiii}}

\def\p@enumiii{(\theenumi)(\theenumii)}

\def\labelenumiv{\arabic{enumiv}.}

\def\theenumiv{\arabic{enumiv}}

\def\p@enumiv{\p@enumiii.\theenumiii}

\pagestyle{plain}

\setcounter{secnumdepth}{0}

\newtheorem{theorem}{Theorem}

\newtheorem{acknowledgement}[theorem]{Acknowledgement}

\newtheorem{algorithm}[theorem]{Algorithm}

\newtheorem{axiom}[theorem]{Axiom}

\newtheorem{case}[theorem]{Case}

\newtheorem{claim}[theorem]{Claim}

\newtheorem{conclusion}[theorem]{Conclusion}

\newtheorem{condition}[theorem]{Condition}

\newtheorem{conjecture}[theorem]{Conjecture}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{criterion}[theorem]{Criterion}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{example}[theorem]{Example}

\newtheorem{exercise}[theorem]{Exercise}

\newtheorem{lemma}[theorem]{Lemma}

\newtheorem{notation}[theorem]{Notation}

\newtheorem{problem}[theorem]{Problem}

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{solution}[theorem]{Solution}

\newtheorem{summary}[theorem]{Summary}

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}

\textbf{Homework 2}\bigskip

\end{center}

\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

\noindent If you use results from books including Conway's, please be explicit about what results you are using.

\begin{center}

\emph{Homework 2 is due on ICON by Midnight, February  11.}

\end{center}

\medskip

\begin{enumerate}

\item Problem IV.1.5

\textbf{Sol.} By Proposition 1.3, 
$$
\begin{aligned}
V(\gamma) &= \int_{0}^{1}|\gamma'(t)|dt = \int_0^1 |\frac{1-i}{t^2}e^{\frac{-1+i}{t}}|dt = \int_{0}^{1} |\frac{1-i}{t^2}e^{-\frac{1}{t}}(\cos\frac{1}{t}+i\sin\frac{1}{t})|dt \\
&= \int_0^1\frac{e^{-\frac{1}{t}}}{t^2}\sqrt{(\cos\frac{1}{t}+\sin\frac{1}{t})^2+(\sin\frac{1}{t}-\cos\frac{1}{t})^2}dt = \int_0^1\sqrt{2}\frac{e^{-\frac{1}{t}}}{t^2}dt \\
&= \left.\sqrt{2}e^{-\frac{1}{t}}\right\arrowvert_{0}^{1} = \sqrt{2}e^{-1}.
\end{aligned}
$$
Hence $\gamma$ is rectifiable. The trace looks like the graph below:
\begin{figure}[!htb] \centering
\includegraphics[width = 5cm]{prob1.jpg}
\end{figure}

\item Problem IV.1.9

\textbf{Sol.}
$$
\int_\gamma \frac{1}{z}dz = \int_{0}^{2\pi} e^{-int}ine^{int}dt = 2\pi in.
$$

\item Problem IV.1.12

\textbf{Sol.}
$$
I(r) = \int_{\gamma} \frac{e^{iz}}{z}dz = \int_{0}^{2\pi}\frac{e^{ire^{it}}}{re^{it}}ire^{it}dt = \int_{0}^{2\pi}ie^{ire^{it}}dt = \int_{0}^{2\pi}ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))dt.
$$
Then 
$$
|I(r)| \le \int_{0}^{2\pi}|ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))|dt = \int_0^{2\pi}e^{-r\sin t}dt = \int_{0}^{\pi}+\int_{\pi}^{2\pi}e^{-r\sin t}dt.
$$
Pick an arbitrary $\epsilon > 0$, the first term
$$
\int_{0}^{\pi}e^{-r\sin t}dt = \int_0^\epsilon + \int_\epsilon^{\pi-\epsilon} + \int_{\pi-\epsilon}^{\pi}e^{-r\sin t}dt \le 2\epsilon + (\pi-2\epsilon)e^{-r\sin\epsilon}.
$$
Then when $r \to \infty$,
$$
\int_{0}^{\pi}e^{-r\sin t}dt \le 2\epsilon.
$$
By the arbitrariness of $\epsilon$, $\int_{0}^{\pi}e^{-r\sin t}dt \to 0$ when $r\to \infty$. It is the same for the second term $\int_{\pi}^{2\pi} $. Hence $\lim\limits_{r\to\infty}I(r) = 0 $.

\item Problem IV.1.13

\textbf{Sol (a).} 
$$
\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{0}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{0}^{\pi} = 2i-2.
$$
\textbf{(b).}
$$
\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{2\pi}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{2\pi}^{\pi} = 2i+2.
$$

\item Problem IV.1.14

\textbf{Proof.} First, assume $\varphi$ is one-one. Then if $\varphi$ is not strictly increasing, suppose there exists $x < y \in [a, b]$, s.t. $\varphi(x) \ge \varphi(y)$. If $\varphi(x) = \varphi(y)$, it contradicts with that $\varphi$ is one-one. So $\varphi(x) > \varphi(y)$. Since $\varphi(x) > c$ (otherwise $\varphi(y) < c$ contradicts with $\varphi([a, b]) \ge c$), by continuity of $\varphi$, $\exists z \in [a, x]$, s.t. $\varphi(z) = \varphi(y)$, which makes a contradiction. Thus $\varphi$ is strictly increasing.

Now assume $\varphi$ is strictly increasing, then $\varphi$ is an injection. Besides, for each $y\in [c, d]$, by continuity of $\varphi$, there is a $x\in[a, b]$, s.t. $\varphi(x) = y$. Hence $\varphi$ is a bijection.

\item Problem IV.1.20

\textbf{Sol.} 
$$
\int_{\gamma}\frac{1}{z^2-1}dz = \int_{0}^{2\pi}\frac{1}{(e^{it}+1)^2-1}ie^{it}dt = \left.\int_{0}^{2\pi}\frac{i}{2+e^{it}}dt = \frac{1}{2}i(t+i\ln(2+e^{it}))\right\arrowvert_{0}^{2\pi} = \pi i
$$

\item Problem IV.2.1

\item Problem IV.2.2  (Please note.  This problem will be used a number of places in the theory we will develop.)

\item Problem IV.2.3

\end{enumerate}

\end{document}

### 2018-01-30 Graduate - Introduction to Analysis II/HW2/2HW20180127-2.tex
add prob 7
add prob 8, 9

@@
 
+\textbf{Proof.} We need to show that $g$ is continuous at each $t_0\in[c, d] $.
+In fact, $\forall \epsilon > 0$, since $\varphi$ is continuous, $\exists \delta > 0$, when $|t_1-t_0| < \delta $, we have $|\varphi(s, t_1)-\varphi(s, t_0)| < \frac{\epsilon}{b-a}$.
+Thus when $|t_1-t_0| < \delta $,
+$$
+|g(t_1)-g(t_0)| \le \int_{a}^{b}|\varphi(s, t_1)-\varphi(s, t_2)|ds < \int_{a}^{b}\frac{\epsilon}{b-a}ds = \epsilon.
+$$
+Hence $g$ is continuous at $t_0 $.
+
 \item Problem IV.2.2  (Please note.  This problem will be used a number of places in the theory we will develop.)
 
+\textbf{Proof.} 
+First, by the same deduction of last problem, we can show $g$ is continuous. Thus, if we prove that $g$ is differentiable with $g'$ given by 
+$$
+g'(z) = \int_{\gamma}\frac{\partial\varphi}{\partial z}(w, z)dz,
+$$
+then $g'$ is continuous since $\frac{\partial \varphi}{\partial z}$ is continuous. Hence we only need to prove the formula for $g'$.
+
+For a fixed point $z_0 $ in G, let $\epsilon > 0$.
+Denote $\frac{\partial \varphi}{\partial z}$ by $\phi$.
+Pick a closed set $F\subset G$ s.t.
+$z_0\in F $, then since $\gamma $ is rectifiable, $\phi$ is uniformly continuous on $\gamma\times F$.
+Thus, there is a $\delta > 0$ s.t.
+$|\phi(w', z')-\phi(w, z)| < \epsilon$ when $(w-w')^2+(z-z')^2<\delta^2 $.
+In particular,
+$$
+|\phi(w, z)-\phi(w, z_0)| < \epsilon
+$$
+when $|z-z_0| < \delta$. Hence,
+$$
+|\int_{z_0}^{z}\phi(w, z)-\phi(w, z_0)dw| \le \epsilon|z-z_0|.
+$$
+For a fixed $w\in\gamma$, $\Phi(z) = \varphi(w, z)-z\phi(w, z_0)$ is a primitive of $\phi(w, z)-\phi(w, z_0)$. By Fundamental Thm of Calculus, 
+$$
+|\varphi(w, z)-\varphi(w, z_0)-(z-z_0)\phi(w, z_0)|\le \epsilon |z-z_0|
+$$
+for each $w$ when $|z-z_0|< \delta$. Hence
+$$
+|\frac{g(z)-g(z_0)}{z-z_0}-\int_{\gamma}\phi(w, z_0)dw|\le \epsilon\int_{\gamma}1ds.
+$$
+when $0 < |z-z_0| < \delta $. Hence by arbitrariness of $\epsilon$ we proved the proposition.
+
 \item Problem IV.2.3
+
+\textbf{Proof.} Let $\phi = \frac{\varphi(w)}{w-z}$, then $\frac{\partial \phi}{\partial z} = (w-z)^{-2}\varphi(w) $ is continuous on $\mathbb{C}-\{\gamma\}$.
+Thus by exercise 2 we know $g$ is analytic, and
+$$
+g'(z) = \int_{\gamma}\varphi(w)(w-z)^{-2}dw.
+$$
+Now suppose for $k \le n$,
+$$
+g^{(k)}(z) = n!\int_{\gamma}\varphi(w)(w-z)^{-(n+1)}dw,
+$$
+then
+$$
+g^{(n+1)}(z) = (n+1)n!\int_{\gamma}\varphi(w)(w-z)^{-(n+2)}dw = (n+1)!\int_{\gamma}\varphi(w)(w-z)^{-(n+2)}dw.
+$$
+By induction we know the result is correct.
 

### 2018-02-05 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
add prob 1, 2

--- 2018-01-29 Graduate - Introduction to Analysis II/HW2/2HW20180127-2.tex
@@
 
-\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip
+\noindent\textbf{Instructions}:References such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip
 
@@
 
+\noindent \textbf{Reminder: Exam I will be from 6:30 to 10:30 on Thursday, February 15 in Room 40 of Schaeffer Hall.}
+
 \begin{center}
 
-\emph{Homework 2 is due on ICON by Midnight, February  11.}
+\emph{Homework 3 is due in your Dropbox folder by 11:59, Sunday , February 19.}
 
@@
 
+\noindent Working on this homework will help you with Exam I, so please don't put it off until after the exam.
+
 \begin{enumerate}
 
-\item Problem IV.1.5
+\item Problem IV.2.4
 
-\textbf{Sol.} By Proposition 1.3, 
+\textbf{(a)}
+By Abel's transform, let $\{a_n\}, \{b_n\}$ be two sequences, and $B_k = \sum\limits_{i=1}^{k}b_i $. Then
 $$
-\begin{aligned}
-V(\gamma) &= \int_{0}^{1}|\gamma'(t)|dt = \int_0^1 |\frac{1-i}{t^2}e^{\frac{-1+i}{t}}|dt = \int_{0}^{1} |\frac{1-i}{t^2}e^{-\frac{1}{t}}(\cos\frac{1}{t}+i\sin\frac{1}{t})|dt \\
-&= \int_0^1\frac{e^{-\frac{1}{t}}}{t^2}\sqrt{(\cos\frac{1}{t}+\sin\frac{1}{t})^2+(\sin\frac{1}{t}-\cos\frac{1}{t})^2}dt = \int_0^1\sqrt{2}\frac{e^{-\frac{1}{t}}}{t^2}dt \\
-&= \left.\sqrt{2}e^{-\frac{1}{t}}\right\arrowvert_{0}^{1} = \sqrt{2}e^{-1}.
-\end{aligned}
+\sum_{k=1}^{n}a_kb_k = a_nB_n - \sum_{k=1}^{n-1}(a_{k+1}-a_k)B_k.
 $$
-Hence $\gamma$ is rectifiable. The trace looks like the graph below:
-\begin{figure}[!htb] \centering
-\includegraphics[width = 5cm]{prob1.jpg}
-\end{figure}
-
-\item Problem IV.1.9
-
-\textbf{Sol.}
+Hence for each fixed $n$, denote $\sum\limits_{k=1}^{n}a_k $ by $A_n $
 $$
-\int_\gamma \frac{1}{z}dz = \int_{0}^{2\pi} e^{-int}ine^{int}dt = 2\pi in.
+C_n = \lim_{r\to1^-}\sum_{k=1}^{n}a_kr^k = r^nA_n - \sum_{k=1}^{n-1}r^k(r-1)A_k.
+$$
+Since $\sum a_n(z-a)^n $ have radius of convergence 1,
+$$
+\lim_{r\to 1^-} \sum_{n=1}^{\infty}a_nr^n < \infty,
+$$
+then we can change the order of limits:
+$$
+\lim_{r\to 1^-}\lim_{n\to\infty}\sum_{k=1}^{n}a_kr^k = \lim_{n\to\infty}\lim_{r\to 1^-}\sum_{k=1}^{n}a_kr^k = \lim_{n\to\infty} A_n
+$$
+since each $A_k $ is a finite number, which comes from $\sum a_n $ converges to $A$. Hence,
+$$
+\lim_{r\to 1^-}\sum_{n=1}^{\infty}a_nr^n = \lim_{n\to\infty} A_n = A.
 $$
 
-\item Problem IV.1.12
+\textbf{(b)}
+Consider $a_n = \frac{(-1)^{n+1}}{n} $, then by Proposition III.1.4,
+$$
+\lim_{n\to\infty}\left|\frac{a_n}{a_{n+1}}\right| = \lim\frac{n+1}{n} = 1.
+$$
+Hence the series $\sum a_n(z-a)^n $ have radius of convergence 1. Since the series $\sum a_n $ is a Leibniz series, then it converges to $A < \infty$.
 
-\textbf{Sol.}
+Now consider the function $f(z) = \log z$, it is analytic on $|z-1| < 1$, and it has power series expansion
 $$
-I(r) = \int_{\gamma} \frac{e^{iz}}{z}dz = \int_{0}^{2\pi}\frac{e^{ire^{it}}}{re^{it}}ire^{it}dt = \int_{0}^{2\pi}ie^{ire^{it}}dt = \int_{0}^{2\pi}ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))dt.
+f(z) = \sum_{n=0}^{\infty}b_n (z-1)^n,
 $$
-Then 
+where $b_n = \frac{1}{n!}f^{(n)}(1) = \frac{(-1)^{n-1}}{n} (n \ge 1), $ and $b_0 = 0 $. By this we can find $a_i = b_i $ for each $i \ge 0$, thus
 $$
-|I(r)| \le \int_{0}^{2\pi}|ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))|dt = \int_0^{2\pi}e^{-r\sin t}dt = \int_{0}^{\pi}+\int_{\pi}^{2\pi}e^{-r\sin t}dt.
-$$
-Pick an arbitrary $\epsilon > 0$, the first term
-$$
-\int_{0}^{\pi}e^{-r\sin t}dt = \int_0^\epsilon + \int_\epsilon^{\pi-\epsilon} + \int_{\pi-\epsilon}^{\pi}e^{-r\sin t}dt \le 2\epsilon + (\pi-2\epsilon)e^{-r\sin\epsilon}.
-$$
-Then when $r \to \infty$,
-$$
-\int_{0}^{\pi}e^{-r\sin t}dt \le 2\epsilon.
-$$
-By the arbitrariness of $\epsilon$, $\int_{0}^{\pi}e^{-r\sin t}dt \to 0$ when $r\to \infty$. It is the same for the second term $\int_{\pi}^{2\pi} $. Hence $\lim\limits_{r\to\infty}I(r) = 0 $.
-
-\item Problem IV.1.13
-
-\textbf{Sol (a).} 
-$$
-\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{0}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{0}^{\pi} = 2i-2.
-$$
-\textbf{(b).}
-$$
-\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{2\pi}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{2\pi}^{\pi} = 2i+2.
+\sum a_n = f(2) = \log 2
 $$
 
-\item Problem IV.1.14
+\item Problem IV.2.6
 
-\textbf{Proof.} First, assume $\varphi$ is one-one.
-Then if $\varphi$ is not strictly increasing, suppose there exists $x < y \in [a, b]$, s.t.
-$\varphi(x) \ge \varphi(y)$.
-If $\varphi(x) = \varphi(y)$, it contradicts with that $\varphi$ is one-one.
-So $\varphi(x) > \varphi(y)$.
-Since $\varphi(x) > c$ (otherwise $\varphi(y) < c$ contradicts with $\varphi([a, b]) \ge c$), by continuity of $\varphi$, $\exists z \in [a, x]$, s.t.
-$\varphi(z) = \varphi(y)$, which makes a contradiction.
-Thus $\varphi$ is strictly increasing.
+\textbf{Sol.} In the region where $f(z) = \sqrt{z}$ is analytic, 
+$$
+f(z) = \sum_{n=0}^{\infty}a_n(z-1)^n,
+$$
+where
+$$
+a_n = \frac{1}{n!}f^{(n)}(1) = \frac{(-1)^{(n-1)}}{n!}\frac{(2n-3)!!}{2^{n}} (n \ge 1), ~a_0 = 1.
+$$
+and since
+$$
+\lim_{n\to\infty}\left|\frac{a_n}{a_{n+1}}\right| = \lim_{n\to\infty} \frac{2n+2}{2n-1} = 1,
+$$
+we know the radius of convergence is 1.
 
-Now assume $\varphi$ is strictly increasing, then $\varphi$ is an injection.
-Besides, for each $y\in [c, d]$, by continuity of $\varphi$, there is a $x\in[a, b]$, s.t.
-$\varphi(x) = y$.
-Hence $\varphi$ is a bijection.
+\item Problem IV.2.9
 
-\item Problem IV.1.20
+\item Problem IV.2.11
 
-\textbf{Sol.} 
-$$
-\int_{\gamma}\frac{1}{z^2-1}dz = \int_{0}^{2\pi}\frac{1}{(e^{it}+1)^2-1}ie^{it}dt = \left.\int_{0}^{2\pi}\frac{i}{2+e^{it}}dt = \frac{1}{2}i(t+i\ln(2+e^{it}))\right\arrowvert_{0}^{2\pi} = \pi i
-$$
+\item Problem IV.3.3
 
-\item Problem IV.2.1
+\item Problem IV.3.6
 
-\item Problem IV.2.2  (Please note.  This problem will be used a number of places in the theory we will develop.)
+\item Problem IV.3.14
 
-\item Problem IV.2.3
+\item Problem IV.4. 2
+
+\item Problem IV. 4.3
+
+\item Problem IV.5.7
+
+\item Problem IV.5.9
 

### 2018-02-05 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
add prob 3

@@
 
+\textbf{(a)}
+Let $f(z) = e^{z}-e^{-z} $, then by Corollary 2.13,
+$$
+f^{(n-1)}(0) = \frac{(n-1)!}{2\pi i}\int_{\gamma}\frac{e^z-e^{-z}}{z^n}dz = 1+(-1)^{n}.
+$$
+Thus
+$$
+\int_{\gamma}\frac{e^z-e^{-z}}{z^n}dz = \frac{2\pi i}{(n-1)!}(1+(-1)^n).
+$$
+
+\textbf{(b)}
+Let $f(z) = 1$, then 
+$$
+f^{(n-1)}(\frac{1}{2}) = \frac{(n-1)!}{2\pi i}\int_{\gamma}\frac{1}{(z-\frac{1}{2})^n} dz = \left\{
+\begin{aligned}
+& 1, n = 1 \\
+& 0, n \ge 2
+\end{aligned}
+\right.
+$$
+Thus
+$$
+\int_{\gamma}\frac{1}{(z-\frac{1}{2})^n} dz = \left\{
+\begin{aligned}
+& 2\pi i, n = 1 \\
+& 0, n \ge 2
+\end{aligned}
+\right.
+$$
+
+\textbf{(c)}
+First, we have
+$$
+\frac{1}{z^2+1} = \frac{1}{2i}(\frac{1}{z-i}-\frac{1}{z+i}).
+$$
+Then let $f(z) = 1 = g(z)$, then
+$$
+1 = f(i) = \frac{1}{2\pi i}\int_{\gamma}\frac{1}{z-i}dz = g(-i) = \frac{1}{2\pi i}\int_{\gamma}\frac{1}{z+i}dz.
+$$
+Hence 
+$$
+\int_{\gamma}\frac{1}{z^2+1}dz = \frac{1}{2i}(\int_\gamma\frac{dz}{z-i}-\int_\gamma\frac{dz}{z+i}) = 0.
+$$
+
+\textbf{(d)}
+Let $f(z) = \sin z$, then $f$ is analytic on $\mathbb{C}$.
+$$
+f(0) = \frac{1}{2\pi i}\int_{\gamma}\frac{\sin z}{z}dz = 0.
+$$
+Hence
+$$
+\int_\gamma \frac{\sin z}{z}dz = 0.
+$$
+
+\textbf{(e)}
+Let $f(z) = z^{1/m} $, then
+$$
+f^{(m-1)}(1) = \frac{(m-1)!}{2\pi i}\int_{\gamma}\frac{z^{1/m}}{(z-1)^m}dz = \prod_{i=0}^{m-1}(\frac{1}{m}-i).
+$$
+Hence
+$$
+\int_{\gamma}\frac{z^{1/m}}{(z-1)^m}dz  = \frac{2\pi i}{(m-1)!}\prod_{i=0}^{m-1}(\frac{1}{m}-i).
+$$
+
 \item Problem IV.2.11
+
+First, 
+$$
+f(z) = \frac{1}{2i}\log(\frac{1+iz}{1-iz}) = \frac{1}{2i}(\log(1+iz)-\log(1-iz)).
+$$
+We know $\log(z)$ is analytic on $\mathbb{C}\setminus l$, where $l$ is a line starting from the origin.
+Thus $f$ is analytic on $\mathbb{C}\setminus l\{z_1, z_2\}$, where $z_1 = -i, ~z_2 = i $.
+Hence $l: Re(z) = 0 $.
+
+On a branch of $f$, 
+$$
+\tan f(z) = \frac{1}{i}\frac{e^{if(z)}-e^{-if(z)}}{e^{if(z)}+e^{-if(z)}}.
+$$
+Since
+$$
+e^{if(z)} = e^{\frac{1}{2}\log(\frac{1+iz}{1-iz})} = (\frac{1+iz}{1-iz})^{1/2},
+$$
+we have
+$$
+\tan f(z) = \frac{1}{i}\frac{(\frac{1+iz}{1-iz})^{1/2}-(\frac{1+iz}{1-iz})^{-1/2}}{(\frac{1+iz}{1-iz})^{1/2}+(\frac{1+iz}{1-iz})^{-1/2}} = \frac{1}{i}\frac{2iz}{2} = z.
+$$
+By exercise III.3.19(d),
+$$
+f(z) = \frac{1}{2i}(\log\frac{1+iz}{1-iz}) = \frac{1}{2i}(\log\frac{z-i}{z+i}+\log i-\log (-i)) = -\frac{1}{2}\int_{-1}^{1}\frac{dt}{z-it} - \frac{\pi}{2}
+$$
 

### 2018-02-14 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
..
add prob 4-6

@@
 $$
-By exercise III.3.19(d),
+When $|z| < 1$, $f(z)$ is analytic. Hence by Theorem 2.8, 
 $$
-f(z) = \frac{1}{2i}(\log\frac{1+iz}{1-iz}) = \frac{1}{2i}(\log\frac{z-i}{z+i}+\log i-\log (-i)) = -\frac{1}{2}\int_{-1}^{1}\frac{dt}{z-it} - \frac{\pi}{2}
+\begin{aligned}
+\log(1+iz) - \log(1-iz) &= \sum_{n=1}^{\infty}(-1)^{n-1}\frac{((1+iz)-1)^n}{n}-\sum_{n=1}^{\infty}(-1)^{n-1}\frac{((1-iz)-1)^n}{n} \\
+&= \sum_{n=1}^{\infty}(-1)^{n-1}\frac{(iz)^n}{n}-\sum_{n=1}^{\infty}(-1)^{n-1}\frac{(-iz)^n}{n} = 2i\sum_{n=0}^{\infty}(-1)^n\frac{z^{2n+1}}{2n+1}.
+\end{aligned}
 $$
+Hence $f(z) = \sum\limits_{n=0}^{\infty}(-1)^n\frac{z^{2n+1}}{2n+1} $.
 
@@
 
+\textbf{Sol.}
+The only function is $f(z) = \exp(z)$.
+
+First, it is clear that $f(z) = \exp(z)$ is a solution.
+Now suppose there is another function $g$, s.t.
+$g(x) = \exp(x), \forall x\in\mathbb{R}$, then for each point $x_0\in\mathbb{R} $, let $\{x_n\} = \{x_0 + \frac{1}{n}\}$, then $f(x_i) = g(x_i)$ for each $i$, and $\{x_n\}\to x_0 $.
+Hence, $x_0 $ is a limit point of the set $\{f = g\}$, thus by Corollary 3.8, $f = g$ on $\mathbb{C}$.
+
 \item Problem IV.3.6
 
-\item Problem IV.3.14
+\textbf{Proof.} If $f(a) = 0$, then the proposition holds.
+Now suppose $f(a) \ne 0$, hence $|f(a)| > 0$.
+Let $g(z) = \frac{1}{f(z)}$, then since $f$ is analytic, $g$ is analytic in $G$.
+Hence $|g(a)| = \left|\frac{1}{f(a)}\right| = \frac{1}{|f(a)|} \ge |g(z)|$ for each $z\in G$.
+Then by Maximum Modulus Thm, $g$ is constant, which means $f$ is constant.
 

### 2018-02-17 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
add prob 7, 8

@@
 
-\item Problem IV.4. 2
+\item Problem IV.4.2
 
-\item Problem IV. 4.3
+\textbf{Sol.} Checked https://math.stackexchange.com/questions/2422165/finding-a-closed-rectifiable-curve-with-prescribed-winding-numbers/2422214
+
+Let $\gamma$: $[0, 1] \to \mathbb{C}$ be a union of circles:
+$$
+\gamma([\frac{1}{2}-\frac{1}{2^n}, \frac{1}{2}-\frac{1}{2^{n+1}}]) = \gamma_1 = B(\frac{1}{2^n}, \frac{1}{2^n}), ~n\ge 1,
+$$
+and
+$$
+\gamma([1-\frac{1}{2^n}, 1-\frac{1}{2^{n+1}}]) = \gamma_2 = B(-\frac{1}{2^n}, \frac{1}{2^n}), n \ge 1.
+$$
+And the direction of $\gamma_1 $ is counterclockwise and $\gamma_2 $ is clockwise.
+
+Then $\gamma$ is rectifiable since length of $\gamma$ is $2\sum_{n=1}^{\infty}2\pi\frac{1}{2^n} = 4\pi$.
+Now we show that $\gamma$ is continuous.
+In fact, we only need to show that $\gamma$ is continuous at the point $t = \frac{1}{2}$ and $t = 1$ since circles are continuous.
+First we know $\lim_{t\to 1}\gamma(t) = 0 $, hence $\gamma $ is closed.
+For $\forall \epsilon > 0$, pick $n$, s.t.
+$\frac{1}{2^n} < \frac{\epsilon}{2}$, then $d(\gamma(t), 0) < 2\times\frac{1}{2^n} < \epsilon$ for all $t\in [1-\frac{1}{2^n}, 1]$.
+Hence $\gamma$ is continuous at $t = 1$, and similarly, $\gamma$ is continuous at $t = \frac{1}{2}$.
+
+For any integer $k$, if $k > 0$, pick a point $a$ inside the $k^{th} $ largest circle and outside the $(k+1)^{th} $ circle of $\gamma_1 $, then by Proposition 4.1, $n(\gamma; a) = k$.
+If $k = 0$, pick $a$ outside the largest circle of both $\gamma_1 $ and $\gamma_2 $, then $n(\gamma; a) = 0$.
+ If $k < 0$, then pick $a$ inside the $k^{th} $ largest circle and outside the $(k+1)^{th} $ circle of $\gamma_2 $, by Prop 4.1 and Prop 4.3 $n(\gamma; a) = k$.
+
+\item Problem IV.4.3
+
+\textbf{Proof.} By Corollary 3.6, since $p$ is a polynomial of degree $n$, we know
+$$
+p(z) = c(z-z_1)(z-z_2)\cdots(z-z_n),
+$$
+where $z_i $ are roots of $p$ and $z_i $ could equal to $z_j $. Then
+$$
+\frac{p'(z)}{p(z)} = \frac{a\sum_{i=1}^{n}\prod_{j\ne i}^{n}(z-z_j)}{a\prod_{i=1}^{n}(z-z_j)} = \sum_{i=1}^{n}\frac{1}{z-z_i},
+$$
+with $z_i \in B(0, R) $.
+Hence,
+$$
+\int_{\gamma}\frac{p'(z)}{p(z)}dz = \int_{\gamma}\sum_{i=1}^{n}\frac{1}{z-z_i}dz = \sum_{i=1}^{n}
+\int_\gamma\frac{1}{z-z_i}dz = \sum_{i=1}^{n}2\pi i = 2\pi in
+$$
+by Prop 4.3 and Thm 4.4.
 

### 2018-02-20 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex

@@
 
-\textbf{Homework 2}\bigskip
+\textbf{Homework 3}\bigskip
 
@@
 
+\textbf{Sol.}
+Let $f(z) = z^n $. Then by Corollary 5.9,
+$$
+\int_{\gamma}\frac{z^n}{(z-1)^n}dz = \int_{\gamma}\frac{f(z)}{(z-1)^n}dz = \frac{2\pi i}{(n-1)!}f^{(n-1)}(1)n(\gamma; 1) = 2\pi in \times n(\gamma; 1) = 2\pi in.
+$$
+
 \item Problem IV.5.9
+
+\textbf{Proof.} 
+With Morera's Theorem, we need to show for each triangular $T$ in $\mathbb{C}$, the integral of $f$ on $T$ is 0. We separate it into three cases, and use $A, B, C$ to denote the vertices of $T$.
+
+1) $T$ does not intersect $[-1, 1]$. Then by Cauchy's Theorem, since $f$ is analytic on $\mathbb{C}\setminus [-1, 1]$, we know $\int_{T}f = 0 $.
+
+2) $T$ intersects $[-1, 1]$ on one point $x_0 $.
+Then $f$ must intersect the x-axis on another point $x_1 $.
+Without loss of generality, assume $A$ is on the upper half plane and $B, C$ are on lower half plane.
+Then
+$$
+\int_{T}f = \int_{A\to x_0}+\int_{x_0\to B}+\int_{B\to C}+\int_{C\to x_1}+\int_{x_1\to A}+\int_{x_0\to x_1}+\int_{x_1\to x_0}f = \int_{Ax_0x_1A}f + \int_{x_0BCx_1 x_0}f.
+$$
+Since $f$ is continuous, we know $f$ is uniformly continuous in the closed region with $T$ being its border.
+Then $\forall \epsilon > 0$, $\exists \delta > 0$, $\forall |z_1-z_2| < \delta $, $|f(z_1)-f(z_2)| < \epsilon$.
+And $f$ is bounded inside the region, suppose $|f(z)| \le M$.
+
+Pick $z_0 $ on $T_{A\to x_0} $ and $z_1 $ on $T_{x_1\to A} $, s.t.
+$Im(z_0) = Im(z_1)$, and $|z_0-x_0| < \delta, |z_1-x_1| < \delta $.
+Let $y_0 = Re(z_0), y_1 = Re(z_1) $, then $|x_0-y_0| < \delta, |x_1-y_1| < \delta$, and $Im(z_0) = Im(z_1) < \delta$.
+Denote $g(x) = f(x + Im(z_0)), x\in\mathbb{R}$,
+then
+$$
+\left|\int_{x_0}^{x_1} f - \int_{z_0}^{z_1}f\right| = \left|\int_{x_0}^{y_0}+\int_{y_0}^{y_1}+\int_{y_1}^{x_1}f - \int_{y_0}^{y_1}g\right| < 2\delta M + \left|\int_{y_0}^{y_1}(f-g)\right| < 2\delta M + \epsilon|y_1-y_0|.
+$$
+Hence
+$$
+\left|\int_{Ax_0x_1A}f\right| = \left|\int_{Az_0z_1A}f +\int_{z_0}^{x_0}+\int_{x_0}^{x_1}+\int_{x_1}^{z_1}+\int_{z_1}^{z_0}f\right| < 2\delta M + 2\delta M + \epsilon|y_1-y_0|.
+$$
+With the arbitrariness of $\epsilon$ and corrosponding $\delta$(we can make $\delta$ arbitrarily small), we know
+$$
+\int_{Ax_0x_1A}f = 0.
+$$
+Similarly, 
+$$
+\int_{T}f = \int_{Ax_0x_1A} + \int_{x_0BCx_1 x_0}f = 0.
+$$
+
+3) An edge of $T$ overlaps with $[-1, 1]$. In fact, from the discussion in 2), we know
+$$
+\int_{T} f = 0.
+$$
+Hence, $f$ is analytic on $\mathbb{C}$, which means $f$ is entire.
 

### 2018-03-02 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add prob 1, 2

--- 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
@@
 
-\textbf{Homework 1}\bigskip
+\textbf{Homework 4}\bigskip
 
@@
 \noindent\textbf{Instructions}:
-
-\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip
+\noindent In problems the problems below, references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip
 
@@
 
-\emph{Homework 1 is due on Dropbox on Monday, February  5.}
+\emph{Homework 4 is due in class at Midnight March 9.}
 
@@
 
+Do the following problems:
+
 \begin{enumerate}
 
-\item Show that $\lim_{n\to \infty}{n^{\frac{1}{n}}} = 1$ without using logarithms.
+\item IV.7.1
 
-\textbf{Proof.} Let $n^{1/n} = 1+y_n $. First we know $n^{1/n} > 1^{1/n} = 1 $, so $y_{n} > 0$. Then 
+\textbf{Sol.
+(Discussed with a college classmate)} In fact, I don't think that this proposition is correct.
+For example, pick $G$ the unit disk $B(0, 1)$, and $\gamma = \gamma(t): [0, 1] \to B$, s.t.
+$\gamma(t) = t$ for $0\le t < 1$, and $\gamma(1) = 0$.
+Then $\gamma$ is closed, and by simple calculation we know $V(\gamma) = 2$, which shows $\gamma$ is rectifiable.
+
+Let $f = \frac{1}{z-1}$, then $f$ is analytic in $B(0, 1)$. But when $t \to 1$, $f\circ \gamma(t)\to\infty$, hence it is not rectifiable.
+
+\item IV.7.2
+
+\textbf{(a)} Let $f(z) = z$, pick any $z_0 \in \{z\mid d(z,\partial G) < \frac{1}{2}r\} $, then since there is only one point $z = z_0 $ satisfies $f(z) = z_0 $, by Thm 7.2,
 $$
-n = (1+y_n)^n = 1+ny_n+\frac{n(n-1)}{2}y_n^2+\cdots+y_n^n > 1+\frac{n(n-1)}{2}y_n^2.
+n(\gamma; z_0) = \frac{1}{2\pi i}\int_{\gamma}\frac{1}{z-z_0}dz
 $$
-Thus $\frac{n(n-1)}{2}y_n^2 < n-1 $, which means $y_n < \sqrt{2/n}.
-$ Hence $\lim\limits_{n\to\infty} y_n \le \lim\limits_{n\to\infty}\sqrt{2/n} = 0$, which means $y_n\to 0 $, and thus $n^{1/n}\to 1 $.
+Since $\frac{1}{z-z_0}$ is analytic on $\{z\mid d(z, \partial G) < \frac{1}{2}r\}$, by Prop 2.15, we know the integral is $0$. Hence $\{z\mid d(z,\partial G) < \frac{1}{2}r\} \subset H$.
 
-\item Given a power series, $\sum_{n=0}^{n=\infty} a_n(z - a)^n$, show that its radius of convergence $R$ satisfies the inequalities$$(\limsup{\vert \frac{a_{n+1}}{a_n} \vert})^{-1} \leq R \leq \limsup{\vert \frac{a_{n}}{a_{n+1}} \vert}.$$
+\item V.1.1
 
-\textbf{Proof.} We only proof the right inequality since it is just the same for the left one.
-If $R > r > \limsup|\frac{a_n}{a_{n+1}}| = \alpha $, then there is an $N > 0$ s.t.
-$r > |a_n/a_{n+1}| $ for all $n \ge N$.
-Let $B = |a_N|r^N $, then $|a_{N+1}|r^{N+1} = |a_{N+1}|rr^{N} > B $.
-Hence for all $n > N$ we have $|a_n|r^n > B $, which gives $|a_nz^n| \ge B |z|^n/|r|^n $ when $n > N$.
-But $|z|/|r| > 1$, which makes $|z|^n/|r|^n \to\infty $ when $n\to\infty$.
-Hence $\sum a_nz^n $ diverges, so $R \le \alpha$.
+\item V.1.4
 
-\item Problem III.1.6.
+\item V.1.12
 
-\textbf{(a).} By Theorem 1.3, 
-$$
-\limsup |a_n|^{1/n} = \limsup |a^n|^{1/n} = |a|,
-$$
-thus $R = \frac{1}{|a|}$.
+\item V.1.13
 
-\textbf{(b).} By Theorem 1.3,
-$$
-\limsup |a_n|^{1/n} = \limsup |a^{n^2}|^{1/n} = \limsup |a^n| = \left\{
-\begin{aligned} 
-&0, |a| < 1, \\
-&1, |a| = 1, \\
-&\infty, |a| > 1.
-\end{aligned}
-\right.
-$$
-Thus 
-$$
-R = \left\{
-\begin{aligned}
-&\infty, |a| < 1,\\
-&1, |a| = 1,\\
-&0, |a| > 1.
-\end{aligned}
-\right.
-$$
+\item V.1.17
 
-\textbf{(c).} By Theorem 1.3,
-$$
-\limsup |a_n|^{1/n} = \limsup |k^n|^{1/n} = k,
-$$
-thus $R = \frac{1}{k}$.
+\item V.2.1
 
-\textbf{(d).} Since 
-$$
-\sum_{n=0}^{\infty}|z|^{n!} < \sum_{n=0}^{\infty}|z|,
-$$
-and the convergence radius of the latter series is $R' = 1$, we know $R\ge 1$.
-On the other hand, if $R > 1$, pick $1 < |z| = r < R$, then $|z|^{n!} = r^{n!}\to\infty $ when $n\to\infty$, hence the series diverges.
-Thus $R = 1$.
+\item V.2.2
 
-\item Problem III.1.7
+\item V.2.3
 
-\item Problem III.2.6
+\item V.2.4
 
-\item Problem III.2.7
-
-\item Problem III.2.9.
-
-\item Problem III.2.13
-
-\item Problem III.2.20
+\item V.2.5
 

### 2018-03-02 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add prob 3

@@
 
+\textbf{(a)} Around $z = 0$,
+$$
+\lim_{z\to 0}|zf(z)| = \lim_{z\to 0}|\sin(z)| =\frac{1}{2}\lim_{z\to 0}|e^{iz}-e^{-iz}| \le \lim_{z\to 0}|z| = 0.
+$$
+Hence by Thm 1.2, $z = 0$ is removable, and $f(0) = 1$ by power series expansion.
+
+\textbf{(b)} At $z = 0$, $g(z) = \cos(z)$ is analytic, and $\cos(0) = 1$. Thus by Prop 1.4, $z = 0$ is a pole, and the singular part is $\frac{1}{z}$.
+
+\textbf{(c)} At $z = 0$, $\lim_{z \to 0} zf(z) = \lim_{z\to 0}\cos z-1 = 0 $, then by Thm 1.2, $0$ is removable, and $f(0) = 0$ by power series expansion.
+
+\textbf{(d)} At $z = 0$, 
+$$
+f(z) = \sum_{n=0}^{-\infty}\frac{1}{(-n)!}z^{n} ,
+$$
+hence $0$ is an essential singularity, and $f(0<|z|<\delta) = \{z\mid |z| > exp(\frac{1}{\delta})\} $.
+
+\textbf{(e)} At $z = 0$,
+$$
+f(z) = \frac{1}{z^2}\sum_{n=1}^{\infty}(-1)^{n-1}\frac{z^n}{n} = \frac{1}{z}+\sum_{n=0}^{\infty}\frac{(-1)^{n+1}}{n+2}z^n.
+$$
+Hence $0$ is a pole, and the singularity part is $\frac{1}{z}$.
+
+\textbf{(f)} At $z = 0$, 
+$$
+f(z) = z\sum_{n=0}^{\infty}(-1)^n\frac{z^{-2n}}{n!} = z+\sum_{n=-1}^{-\infty} (-1)^{-n}\frac{z^{2n+1}}{(-n)!}
+$$
+Hence $0$ is an essential singularity, and $f(0<|z|<\delta) = \mathbb{C}$.
+
+\textbf{(g)} Around $z = 0$, notice $\frac{z^2+1}{z-1}$ is analytic, hence $0$ is a pole. Since $|z| < 1$,
+$$
+f(z) = 1-\frac{1}{z}+\frac{2}{z-1} = 1-\frac{1}{z}-2\sum_{n=0}^{\infty}z^n,
+$$
+we know the singular part is $-\frac{1}{z}$.
+
+\textbf{(h)} For any $n > 0$, 
+$$
+\lim_{z\to 0}z^nf(z) = \lim_{z\to 0}z^n\frac{1}{\sum_{n=1}^{\infty}\frac{1}{n!}z^n} = \infty,
+$$
+hence $0$ is an essential singularity, and $f(0<|z|<\delta) = \{z\mid |z| > \frac{1}{1-e^{\delta}}\} $.
+
+\textbf{(i)} 
+$$
+f(z) = z\sum_{n=0}^{\infty}(-1)^n\frac{z^{-(2n+1)}}{(2n+1)!} = 1+\sum_{n=-1}^{-\infty}(-1)^{-n}\frac{z^{2n-1}}{(-2n+1)!},
+$$
+hence $0$ is an essential singularity, and $f(0<|z|<\delta) = \{z\mid |z| < \delta\} $.
+
+\textbf{(j)} Same with (i), 0 is an essential singularity, and $f(0<|z|<\delta) = \{z\mid |z| < \delta^n\}$.
+
 \item V.1.4

### 2018-03-02 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add prob 5

@@
 
+\textbf{(a)} 
+$$
+f(z) = \frac{1}{z}(\frac{1}{1-z}-\frac{1}{2(1-z/2)}) = \frac{1}{z}(\sum_{n=0}^{\infty}z^n-\frac{1}{2}\sum_{n=0}^{\infty}(\frac{z}{2})^n) = \frac{1}{2z} + \sum_{n=0}^{\infty}(1-\frac{1}{2^{n+2}})z^n
+$$
+
+\textbf{(b)} 
+% $$
+% f(z) = \frac{1}{z-1}\frac{-1}{2}(\frac{1}{1-(z-1)}+\frac{1}{1+(z-1)}) = -\frac{1}{2}\frac{1}{z-1}(\sum_{n=0}^{\infty}(z-1)^n + \sum_{n=0}^\infty(-1)^n(z-1)^n) = -\frac{1}{z-1}-\sum_{n=0}^{\infty}(z-1)^{2n+1}.
+% $$
+$$
+f(z) = \frac{1}{z}(\frac{1}{z-2}-\frac{1}{z-1}) = \frac{1}{z}(-\frac{1}{2}\frac{1}{1-\frac{z}{2}} - \frac{1}{z}\frac{1}{1-\frac{1}{z}}) = \frac{1}{z}(-\sum_{n=0}^{\infty}\frac{z^n}{2^{n+1}} -\sum_{n=0}^{\infty}z^{-n-1}) = -\sum_{n=-1}^{\infty}\frac{z^n}{2^{n+2}}-\sum_{n=-\infty}^{-2}z^n
+$$
+
+\textbf{(c)}
+$$
+f(z) = \frac{1}{z}(\frac{\frac{1}{z}}{1-\frac{2}{z}}-\frac{\frac{1}{z}}{1-\frac{1}{z}}) = \frac{1}{z}(\sum_{n=0}^{\infty}(\frac{2}{z})^n-\sum_{n=0}^{\infty}\frac{1}{z^n}) = \sum_{n=-\infty}^{-1}(2^{-(n+1)}-1)z^n.
+$$
+
 \item V.1.12
+
+\textbf{Proof.}
+By (1.11), 
+$$
+a_n = \frac{1}{2\pi i}\int_{\gamma}\frac{\exp(\frac{1}{2}\lambda(z+\frac{1}{z}) )}{z^{n+1}}dz
+$$
+pick $\gamma = \exp(it)$, the unit circle, then
+$$
+a_n = \frac{1}{2\pi }\int_{0}^{2\pi}e^{\lambda\cos t}e^{-int}dt = \frac{1}{2\pi}\int_{0}^{2\pi}e^{\lambda\cos t}(\cos nt -i\sin nt)dt
+$$
+
+$$
+b_n = \frac{1}{2\pi i}\int_{\gamma}\frac{\exp(\frac{1}{2}\lambda(z-\frac{1}{z}))}{z^{n+1}}dz
+$$
+pick $\gamma = \exp(it)$,
+$$
+b_n = \frac{1}{2\pi}\int_{0}^{2\pi}e^{\lambda i \sin t}e^{-int}dt = \frac{1}{2\pi}\int_{0}^{2\pi} \cos(nt-\lambda \sin t) -i\sin(nt - \lambda \sin t) dt.
+$$
 

### 2018-03-03 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
update

@@
 \textbf{Proof.}
-By (1.11), 
+By (1.11), since $f$ is analytic on $0 < |z| < \infty$,
 $$
@@
 $$
-a_n = \frac{1}{2\pi }\int_{0}^{2\pi}e^{\lambda\cos t}e^{-int}dt = \frac{1}{2\pi}\int_{0}^{2\pi}e^{\lambda\cos t}(\cos nt -i\sin nt)dt
+a_n = \frac{1}{2\pi }\int_{0}^{2\pi}e^{\lambda\cos t}e^{-int}dt = \frac{1}{2\pi}\int_{0}^{2\pi}e^{\lambda\cos t}(\cos nt -i\sin nt)dt,
 $$
+the real part is
+$$
+\frac{1}{2\pi}\int_{0}^{2\pi}e^{\lambda\cos t}\cos ntdt = \frac{1}{2\pi}\left(\int_{0}^{\pi}e^{\lambda\cos t}\cos ntdt -\int_{\pi}^{0}e^{\lambda \cos(2\pi -s)}\cos(2\pi-s)ds\right) = \frac{1}{\pi}\int_{0}^{\pi}e^{\lambda\cos t}\cos ntdt.
+$$
+and the imaginary part is 
+$$
+-\frac{i}{2\pi}\int_{0}^{2\pi}e^{\lambda\cos t}\sin ntdt = -\frac{i}{2\pi} \left(\int_{0}^{\pi}e^{\lambda\cos t}\sin ntdt + \int_{\pi}^{0}e^{\lambda\cos(2\pi -s)}\sin(2\pi-s)ds\right) = 0.
+$$
+Hence $a_n = \frac{1}{\pi}\int_{0}^{\pi}e^{\lambda\cos t}\cos ntdt $.
 
@@
 $$
+The real part is
+$$
+\begin{aligned}
+\frac{1}{2\pi}\int_{0}^{2\pi} &\cos(nt-\lambda \sin t)dt = \frac{1}{2\pi}\left(\int_{0}^{\pi}\cos(nt-\lambda \sin t)dt - \int_{\pi}^{0}\cos(n(2\pi -s)-\lambda\sin(2\pi-s))ds\right) \\
+&= \frac{1}{2\pi}\left(\int_{0}^{\pi}\cos(nt-\lambda \sin t)dt +\int_{0}^{\pi}\cos(-ns+\lambda \sin s)ds\right) = \frac{1}{\pi}\int_{0}^{\pi}\cos(nt -\lambda \sin t)dt.
+\end{aligned}
+$$
+and the imaginary part is
+$$
+\begin{aligned}
+-\frac{i}{2\pi}\int_{0}^{2\pi}&\sin(nt-\lambda \sin t)dt = -\frac{i}{2\pi} \left(\int_{0}^{\pi}\sin(nt-\lambda\sin t)dt -\int_{\pi}^{0}\sin(n(2\pi-s) -\lambda\sin(2\pi-s))ds\right) \\
+&= -\frac{i}{2\pi} \left(\int_{0}^{\pi}\sin(nt-\lambda\sin t)dt-\int_{0}^{\pi}\sin(-ns+\lambda \sin s)ds\right) = 0.
+\end{aligned}
+$$
+Hence $b_n = \frac{1}{\pi}\int_{0}^{\pi}\cos(nt -\lambda\sin t )dt $.
 
@@
 
+\textbf{(a)} Suppose $f$ is entire and has a removable singularity at $\infty$, then $g(z) = f(\frac{1}{z})$ has a removable singularity at $z = 0$, thus we can define $g(0) = a < \infty$, which means $f$ is bounded in the neighbourhood of $\infty$.
+Hence by Liouville Thm, $f$ is constant.
+
+\textbf{(b)} By assumption, $g(z) = f(\frac{1}{z}) = \frac{1}{z^m}h(z)$, where $h(z)$ is analytic at $z = 0$.
+Since $f(z) = z^{m}h(\frac{1}{z})$ is entire, it means at $z = 0$, $h$ has a definition or has a removable singularity, and $h$ is entire.
+Hence, by (1) we know $h$ is a constant, which means $f$ is a polynomial of degree m.
+
+\textbf{(c)} Let $f(z) = \frac{\prod (z-u_i)}{\prod (z-v_i)}$, then 
+$$
+g(z) = f(\frac{1}{z}) = \frac{\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (\frac{1}{z}-v_i)}
+$$
+has a removable singularity at $z = 0$, which means $\lim_{z\to 0}g(z) $ exists and is not $\infty$. Notice
+$$
+\lim_{z \to 0}g(z) = \lim_{z\to 0}\frac{z^m\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (1-v_iz)},
+$$
+if $m < n$, then $\lim_{z\to 0} g(z) = \infty$, which makes a contradiction.
+If $m \ge n$, then the limit is well-defined.
+Hence $f = \frac{p(z)}{q(z)}$, where $p, q$ are polynomials, and $\deg(p) \le \deg(q)$.
+
+\textbf{(d)} Let $f(z) = \frac{\prod (z-u_i)}{\prod (z-v_i)}$, then 
+$$
+g(z) = f(\frac{1}{z}) = \frac{\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{k} (\frac{1}{z}-v_i)}
+$$
+has a pole of order m at $z = 0$, which means $g(z) = \frac{h(z)}{z^m}$, where $h(z)$ is analytic at $z = 0$. Then
+$$
+z^mg(z) = \frac{z^m\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{k} (\frac{1}{z}-v_i)} = \frac{z^{m+k}\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (1-v_iz)},
+$$
+and we have $m+k = n$, otherwise the order of pole is not $m$. Hence $f = \frac{p}{q}$, and $\deg(p)-\deg(q) = m$.
+
 \item V.1.17
+
+\textbf{Proof.} If not, first suppose $f$ has a pole of order $m$ at $a$. Then $f(z) = \frac{g(z)}{(z-a)^m}$, and $g$ is analytic on $G$.
+
+i) If $g(a) = 0$, then $f(z) = 0$, and we can define $f(a) = 0$, thus $a$ is a removable singularity.
+
+ii) If $g(a)\ne 0$, then according to the isolation of zeros, $\exists r > 0$, s.t.
+$g(z) \ne 0$ in $B(a, 2r)$.
+Consider $H = B(a, r)$, by max modulus theorem, $\min_{H}|g| = \min_{\partial H}|g|$, denote is as $c \ne 0$.
+Hence
+$$
+\begin{aligned}
+\int\int_{H}|f(x+iy)|^2 dxdy = \int\int_{H}\frac{|g(x+iy)|^2}{|x+iy-a|^{2m}}dxdy \ge \int\int_{H}\frac{c^2}{|x+iy-a|^2}dxdy.
+\end{aligned}
+$$
+Let $x = Re(a)+s\cos t, y = Im(a)+s\sin t $, then
+$$
+\int\int_{H}|f(x+iy)|^2 dxdy \ge \int_{0}^{r}\int_{0}^{2\pi}\frac{c^2}{s^{2m}}sdsdt = 2\pi c^2\int_{0}^{r}s^{1-2m}ds.
+$$
+If $m = 1$, then the integral becomes
+$$
+\left.\int_{0}^{r} s^{-1}ds = \ln(s)\right\arrowvert_{0}^{r} = \infty.
+$$
+If $m > 1$, then the integral is
+$$
+\left.\int_{0}^{r} s^{1-2m} ds = \frac{1}{2-2m}s^{2-2m}\right\arrowvert_{0}^r = \infty.
+$$
+Since the integrand is nonnegative,
+$$
+\int_{G} |f|^2 \ge \int_{H} |f|^2 = \infty,
+$$
+which makes a contradiction. With the same method, we know $a$ is not an essential singularity. Hence $a$ is a removable one.
+
+By the deduction we know, if $0 < p < 2$, $a$ could be a removable singularity or a pole of order $m$, which satisfies $pm < 2$. If $p \ge 2$, then $a$ is a removable singularity.
 
@@
 
+\textbf{(a)} Notice $(x^4+x^2+1)(x^2-1) = x^6-1 $, so $f(z) = \frac{z^2}{z^4+z^2+1}$ has four poles of order 1, and they are sixth roots of $1$, which are $a_i = e^{i\theta_i} $ where
+$$
+\theta = \frac{\pi}{3}, \frac{2\pi}{3}, \frac{4\pi}{3}, \frac{5\pi}{3}.
+$$
+Consider the two poles in the upper-half plane $a_1, a_2 $, then
+$$
+Res(f, a_1) = \lim_{z\to a_1}(z-a_1)f(z) = a_1^2(a_1-a_2)^{-1}(a_1-a_3)^{-1}(a_1-a_4)^{-1} = \frac{1}{2\sqrt{3}i}e^{\frac{\pi}{3}i},
+$$
+$$
+Res(f, a_2) = \lim_{z\to a_2}(z-a_2)f(z) = a_2^2(a_2-a_1)^{-1}(a_2-a_3)^{-1}(a_2-a_4)^{-1} = -\frac{1}{2\sqrt{3}i}e^{\frac{2\pi}{3}i}.
+$$
+Let $\gamma$ be the closed path which is the boundary of upper half of disk of radius $R > 1$ with center 0, in counter-clockwise direction. Then by Residue Theorem, 
+$$
+\frac{1}{2\pi i}\int_{\gamma}f =  Res(f, a_1)+Res(f, a_2) = \frac{1}{2\sqrt{3}i}
+$$
+And
+$$
+\int_{\gamma}f = \int_{-R}^{R}\frac{x^2}{x^4+x^2+1}dx + i\int_{0}^{\pi}\frac{R^3e^{i3t}}{R^4e^{i4t}+R^2e^{i2t}+1}dt.
+$$
+Notice $|R^4e^{i4t}+R^2e^{i2t}+1| \ge R^4-R^2=1 $ when $R$ is sufficiently large, so
+$$
+\left|i\int_{0}^{\pi}\frac{R^3e^{i3t}}{R^4e^{i4t}+R^2e^{i2t}+1}dt\right| \le \frac{\pi R^3}{R^4-R^2-1} \to 0 ~\text{as}~ R\to\infty.
+$$
+Since $\frac{x^2}{x^4+x^2+1} \ge 0, \forall x\in\mathbb{R}$, we know
+$$
+\int_{0}^{\infty}\frac{x^2}{x^4+x^2+1}dx = \frac{1}{2}\int_{-\infty}^{\infty}\frac{x^2}{x^4+x^2+1} = \frac{1}{2}\lim_{R\to\infty}\int_{-R}^{R}\frac{x^2}{x^4+x^2+1}dx = \frac{\pi}{\sqrt{3}}.
+$$
+
+For the followsing problems, I will not write all the steps since I don't have enough time to do so. I will only write the key points.
+
+% \textbf{(b)} $f$ has a removable singularity at $z = 0$. Hence $Res(f, a) = 0$. Let $\gamma$ be the curve in Example 2.7, then
+% $$
+% 0 = \int_{r}^{R}+\int_{-R}^{-r}\frac{\cos x-1}{x^2}dx + \int_{\gamma_r}+\int_{\gamma_R}\frac{\cos z-1}{z^2}dz = 2\int_{r}^{R}\frac{\cos x-1}{x^2}dx + \int_{\gamma_r}+\int_{\gamma_R}\frac{\cos z-1}{z^2}dz.
+% $$
+% Since
+% $$
+% \left|\int_{\gamma_R}\frac{\cos z-1}{z^2}dz\right| \le \int_{\gamma_R}\left|\frac{\cos z-1}{z^2}dz\right| \le \int_{\gamma_R}\frac{2}{|z|^2}dz \to 0 ~\text{as}~ R\to \infty,
+% $$
+% and
+% $$
+% \int_{\gamma_r}\frac{\cos z-1}{z^2}dz = \int_{\gamma_r}\frac{\cos z}{z^2}dz -\int_{\gamma_r}\frac{1}{z^2}dz
+% = \int_{0}^{\pi}\frac{\exp(ire^{it})+\exp(-ire^{it})}{2re^{it}}dt 
+% $$
+
+\textbf{(b)} We know 
+$$
+\int_{r}^{R}\frac{\cos x-1}{x^2}dx = \frac{1}{2}\left(\int_{r}^{R}+\int_{-R}^{-r}\frac{e^{ix}-1}{x^2}dx\right)
+$$
+Consider $f = \frac{e^{iz}-1}{z^2}$, then $f$ has a simple pole at $z = 0$. Let $\gamma$ be the curve in Example 2.7, then
+$$
+0 = \int_{r}^{R}+\int_{-R}^{-r}\frac{e^{ix}-1}{x^2}dx + \int_{\gamma_r}+\int_{\gamma_R}\frac{e^{iz}-1}{z^2}dz
+$$
+Since 
+$$
+\left|\int_{\gamma_R}\frac{e^{iz}-1}{z^2}dz\right| = \left|\int_{0}^{\pi}\frac{\exp(iRe^{it})-1}{Re^{it}}dt\right| \le \frac{1}{R}\int_{0}^{\pi}\exp(-R\sin t)dt,
+$$
+and by Example 2.7 we know the integral $\to 0$ as $R\to \infty$. And since $\frac{e^{iz}-1-iz}{z^2}$ has a removable singularity at $z = 0$, by Example 2.7 we know
+$$
+\lim_{\gamma\to 0}\left|\int_{\gamma_r}\frac{e^{iz}-1-iz}{z^2}dz\right| = 0, 
+$$
+but $\int_{\gamma}\frac{i}{z}dz = \pi$, hence 
+$$
+\lim_{\gamma\to 0}\left|\int_{\gamma_r}\frac{e^{iz}-1}{z^2}dz\right| = \pi.
+$$
+Hence
+$$
+\int_{0}^{\infty}\frac{\cos x-1}{x^2}dx = \lim_{r\to 0, R\to\infty}\int_{r}^{R}\frac{\cos x-1}{x^2}dx = -\frac{\pi}{2}.
+$$
+
+\textbf{(c)} The same with Example 2.9, let $z = e^{i\theta} $, then
+$$
+\int_{0}^{\pi}\frac{\cos 2\theta}{1-2a\cos\theta +a^2}d\theta = -\frac{i}{4}\int_{\gamma}\frac{z^4+2z^2+1}{-az^2+(a^2+1)z-a}dz,
+$$
+where $\gamma = \{|z| = 1\}$. By residue theorem, 
+$$
+\int_{\gamma}\frac{z^4+2z^2+1}{-az^2+(a^2+1)z-a}dz = 2\pi iRes(f, a) = 2\pi i\frac{(a^2+1)^2}{1-a^2}.
+$$
+Hence
+$$
+\int_{0}^{\pi}\frac{\cos 2\theta}{1-2a\cos\theta +a^2}d\theta = \frac{\pi}{2}\frac{(a^2+1)^2}{1-a^2}.
+$$
+
+\textbf{(d)} Same with (c), let $z = e^{i\theta} $, then
+$$
+\int_{0}^{\pi}\frac{d\theta}{(a+\cos\theta)^2} = -2i\int_{\gamma}\frac{z}{(z^2+2az+1)^2}dz,
+$$
+where $\gamma = \{|z| = 1\}$. By residue theorem, 
+$$
+\int_{\gamma}\frac{z}{(z^2+2az+1)^2}dz = \frac{1}{2}\pi i a(a^2-1)^{-\frac{3}{2}}.
+$$
+Hence
+$$
+\int_{0}^{\pi}\frac{d\theta}{(a+\cos\theta)^2} = \pi a(a^2-1)^{-\frac{3}{2}}.
+$$
+
 \item V.2.2
+
+\textbf{(a)}
+$$
+\int_{0}^{\infty}\frac{dx}{(x^2+a^2)^2} = \frac{1}{2}\int_{-\infty}^{\infty}\frac{dx}{(x^2+a^2)^2}.
+$$
+Consider $R > a$, let $\gamma = \{|z| = R, Im(z) > 0 \}$, then by residue thm, since $f$ has a pole of order 2, $z = ai$,
+$$
+\int_{\gamma} +\int_{-R}^{R} \frac{dz}{(z^2+a^2)^2} = 2\pi i Res(f, ai) = \frac{\pi}{2a^3}.
+$$
+But
+$$
+\left|\int_{\gamma}\frac{dz}{(z^2+a^2)^2}\right| \le \int_{\gamma}\left|\frac{dz}{(z^2+a^2)^2}\right| \le \int_{0}^{\pi}\frac{1}{|R^2-a^2|^2}dt \le \frac{\pi}{|R^2-a^2|^2} \to 0, ~\text{as}~ R\to\infty.
+$$
+Hence
+$$
+\int_{0}^{\infty}\frac{dx}{(x^2+a^2)^2} = \frac{\pi}{4a^3}.
+$$
+
+\textbf{(b)} Define $G, l(z), \gamma$ as in Example 2.10, using the same method of Example 2.10, we can show
+$$
+\int_{0}^{\infty}\frac{(\log x)^2}{1+z^2}dz = 0.
+$$
+$$
+\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = \int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{0}^{\pi}\frac{(\log R+i\theta)^3}{1+R^2e^{2i\theta}}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx + \int_{\pi}^{0}\frac{(\log r+i\theta)^3}{1+r^2e^{2i\theta}}ire^{i\theta}d\theta
+$$
+by residue thm,
+$$
+\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = 2\pi i Res(f, i) = -\frac{1}{8}\pi^4 i.
+$$
+And
+$$
+\int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx = 
+$$
 
@@
 
+\textbf{Sol.} We have proved that $f$ has an essential singularity at $z = 0$. Denote $G$ be the region surrounded by $\gamma$.
+
+i) If $0\notin G$, then by Cauchy's Thm, $\int_\gamma f = 0 $.
+
+ii) If $0\in G$, then by Laurent expansion, $Res(f, 0) = 1$.
+But by a problem in last homework, we can construct a $\gamma$, for each $n\in\mathbb{N}$, $n(\gamma, 0) = n$.
+Hence $\int_{\gamma}f = 2\pi ni, n\in\mathbb{N} $.
+
 \item V.2.4
 
+\textbf{Sol.} In fact, in a neighbourhood of $a$, $f = \frac{c_{-1}}{z-a}+\sum_{n=0}^\infty c_n(z-a)^n $, and $g = \sum_{n=0}^{\infty}d_n (z-a)^n $. Hence by definition, 
+$$
+Res(fg, a) = c_{-1}d_{0} = Res(f, a)g(a).
+$$
+
 \item V.2.5
+
+\textbf{Sol.} Notice in the last problem, each simple pole of $f$ is a simple pole of $fg$. By residue thm, 
+$$
+\frac{1}{2\pi i}\int_{\gamma}fg = \sum_{k=1}^{n}n(\gamma, a_k)Res(fg, a_k) = \sum_{k=1}^{n}n(\gamma, a_k)Res(f, a_k)g(a_k).
+$$
 

### 2018-03-03 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add prob 5

--- 2018-03-02 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
@@
 $$
+The real part is
+$$
+\begin{aligned}
+\frac{1}{2\pi}\int_{0}^{2\pi} &\cos(nt-\lambda \sin t)dt = \frac{1}{2\pi}\left(\int_{0}^{\pi}\cos(nt-\lambda \sin t)dt - \int_{\pi}^{0}\cos(n(2\pi -s)-\lambda\sin(2\pi-s))ds\right) \\
+&= \frac{1}{2\pi}\left(\int_{0}^{\pi}\cos(nt-\lambda \sin t)dt +\int_{0}^{\pi}\cos(-ns+\lambda \sin s)ds\right) = \frac{1}{\pi}\int_{0}^{\pi}\cos(nt -\lambda \sin t)dt.
+\end{aligned}
+$$
+and the imaginary part is
+$$
+\begin{aligned}
+-\frac{i}{2\pi}\int_{0}^{2\pi}&\sin(nt-\lambda \sin t)dt = -\frac{i}{2\pi} \left(\int_{0}^{\pi}\sin(nt-\lambda\sin t)dt -\int_{\pi}^{0}\sin(n(2\pi-s) -\lambda\sin(2\pi-s))ds\right) \\
+&= -\frac{i}{2\pi} \left(\int_{0}^{\pi}\sin(nt-\lambda\sin t)dt-\int_{0}^{\pi}\sin(-ns+\lambda \sin s)ds\right) = 0.
+\end{aligned}
+$$
+Hence $b_n = \frac{1}{\pi}\int_{0}^{\pi}\cos(nt -\lambda\sin t )dt $.
 
 \item V.1.13
+
+\textbf{(a)}
 

### 2018-03-03 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add prob 6-7

@@
 
-\textbf{(a)}
+\textbf{(a)} Suppose $f$ is entire and has a removable singularity at $\infty$, then $g(z) = f(\frac{1}{z})$ has a removable singularity at $z = 0$, thus we can define $g(0) = a < \infty$, which means $f$ is bounded in the neighbourhood of $\infty$.
+Hence by Liouville Thm, $f$ is constant.
+
+\textbf{(b)} By assumption, $g(z) = f(\frac{1}{z}) = \frac{1}{z^m}h(z)$, where $h(z)$ is analytic at $z = 0$.
+Since $f(z) = z^{m}h(\frac{1}{z})$ is entire, it means at $z = 0$, $h$ has a definition or has a removable singularity, and $h$ is entire.
+Hence, by (1) we know $h$ is a constant, which means $f$ is a polynomial of degree m.
+
+\textbf{(c)} Let $f(z) = \frac{\prod (z-u_i)}{\prod (z-v_i)}$, then 
+$$
+g(z) = f(\frac{1}{z}) = \frac{\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (\frac{1}{z}-v_i)}
+$$
+has a removable singularity at $z = 0$, which means $\lim_{z\to 0}g(z) $ exists and is not $\infty$. Notice
+$$
+\lim_{z \to 0}g(z) = \lim_{z\to 0}\frac{z^m\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (1-v_iz)},
+$$
+if $m < n$, then $\lim_{z\to 0} g(z) = \infty$, which makes a contradiction.
+If $m \ge n$, then the limit is well-defined.
+Hence $f = \frac{p(z)}{q(z)}$, where $p, q$ are polynomials, and $\deg(p) \le \deg(q)$.
+
+\textbf{(d)} Let $f(z) = \frac{\prod (z-u_i)}{\prod (z-v_i)}$, then 
+$$
+g(z) = f(\frac{1}{z}) = \frac{\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{k} (\frac{1}{z}-v_i)}
+$$
+has a pole of order m at $z = 0$, which means $g(z) = \frac{h(z)}{z^m}$, where $h(z)$ is analytic at $z = 0$. Then
+$$
+z^mg(z) = \frac{z^m\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{k} (\frac{1}{z}-v_i)} = \frac{z^{m+k}\prod_{i=1}^{n} (\frac{1}{z}-u_i)}{\prod_{i=1}^{m} (1-v_iz)},
+$$
+and we have $m+k = n$, otherwise the order of pole is not $m$. Hence $f = \frac{p}{q}$, and $\deg(p)-\deg(q) = m$.
 
 \item V.1.17
+
+\textbf{Proof.} If not, first suppose $f$ has a pole of order $m$ at $a$. Then $f(z) = \frac{g(z)}{(z-a)^m}$, and $g$ is analytic on $G$.
+
+i) If $g(a) = 0$, then $f(z) = 0$, and we can define $f(a) = 0$, thus $a$ is a removable singularity.
+
+ii) If $g(a)\ne 0$, then according to the isolation of zeros, $\exists r > 0$, s.t.
+$g(z) \ne 0$ in $B(a, 2r)$.
+Consider $H = B(a, r)$, by max modulus theorem, $\min_{H}|g| = \min_{\partial H}|g|$, denote is as $c \ne 0$.
+Hence
+$$
+\begin{aligned}
+\int\int_{H}|f(x+iy)|^2 dxdy = \int\int_{H}\frac{|g(x+iy)|^2}{|x+iy-a|^{2m}}dxdy \ge \int\int_{H}\frac{c^2}{|x+iy-a|^2}dxdy.
+\end{aligned}
+$$
+Let $x = Re(a)+s\cos t, y = Im(a)+s\sin t $, then
+$$
+\int\int_{H}|f(x+iy)|^2 dxdy \ge \int_{0}^{r}\int_{0}^{2\pi}\frac{c^2}{s^{2m}}sdsdt = 2\pi c^2\int_{0}^{r}s^{1-2m}ds.
+$$
+If $m = 1$, then the integral becomes
+$$
+\left.\int_{0}^{r} s^{-1}ds = \ln(s)\right\arrowvert_{0}^{r} = \infty.
+$$
+If $m > 1$, then the integral is
+$$
+\left.\int_{0}^{r} s^{1-2m} ds = \frac{1}{2-2m}s^{2-2m}\right\arrowvert_{0}^r = \infty.
+$$
+Since the integrand is nonnegative,
+$$
+\int_{G} |f|^2 \ge \int_{H} |f|^2 = \infty,
+$$
+which makes a contradiction. With the same method, we know $a$ is not an essential singularity. Hence $a$ is a removable one.
+
+By the deduction we know, if $0 < p < 2$, $a$ could be a removable singularity or a pole of order $m$, which satisfies $pm < 2$. If $p \ge 2$, then $a$ is a removable singularity.
 

### 2018-03-20 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add 5.2.2 b, c

--- 2018-03-03 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
@@
 
-\textbf{(b)} Define $G, l(z), \gamma$ as in Example 2.10, using the same method of Example 2.10, we can show
-$$
-\int_{0}^{\infty}\frac{(\log x)^2}{1+z^2}dz = 0.
-$$
+\textbf{(b)} Define $G, l(z), \gamma$ as in Example 2.10, then
 $$
@@
 $$
-\int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx = 
+\begin{aligned}
+\int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx &+ \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx = \int_{r}^{R}\frac{(\log x)^3+(\log x+\pi i)^3}{1+x^2}dx \\
+&= 2\int_{r}^{R}\frac{(\log x)^3}{1+x^2} + 3\pi i\int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx -3\pi^2\int_{r}^{R}\frac{\log x}{1+x^2}dx -\pi^3 i\int_{r}^{R}\frac{1}{1+x^2}dx
+\end{aligned}
 $$
+we know from example 2.10, as $r\to 0, R\to \infty$, the third term is 0, and the last term is
+$$
+-\pi^3 i\int_{0}^{\infty}\frac{1}{1+x^2}dx = -\frac{1}{2}\pi^4i.
+$$
+Now we consider the second term. Using the same notation $G, l(z), \gamma$,
+$$
+\int_{\gamma}\frac{(l(z))^2}{1+z^2}dz = \int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx + \int_{0}^{\pi}\frac{(\log R+i\theta)^2}{1+R^2e^{2i\theta}}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^2}{1+x^2}dx + \int_{\pi}^{0}\frac{(\log r+i\theta)^2}{1+r^2e^{2i\theta}}ire^{i\theta}d\theta
+$$
+by residue theorem,
+$$
+\int_{\gamma}\frac{(l(z))^2}{1+z^2}dz = 2\pi i Res(f, i) = -\frac{1}{4}\pi^3.
+$$
+And
+$$
+\begin{aligned}
+\int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx &+ \int_{-R}^{-r}\frac{(\log |x|+\pi i)^2}{1+x^2}dx = \int_{r}^{R}\frac{(\log x)^2+(\log x+\pi i)^2}{1+x^2}dx \\
+&= 2\int_{r}^{R}\frac{(\log x)^2}{1+x^2} + 2\pi i\int_{r}^{R}\frac{\log x}{1+x^2}dx -\pi^2\int_{r}^{R}\frac{1}{1+x^2}dx
+\end{aligned}
+$$
+when $r\to 0, R\to \infty$, the second term is 0, and the last term is
+$$
+-\pi^2\int_{0}^{\infty}\frac{1}{1+x^2}dx = -\frac{1}{2}\pi^3.
+$$
+Also, if $\rho > 0$ then
+$$
+\begin{aligned}
+\left|\rho\int_{0}^{\pi}\frac{(\log \rho+i\theta)^2}{1+\rho^2e^{2i\theta}}e^{i\theta}d\theta\right| &\le \rho\frac{|\log\rho|^2}{|1-\rho^2|}\int_{0}^{\pi}d\theta +2\rho\frac{|\log\rho|}{|1-\rho^2|}\int_{0}^{\pi}\theta d\theta +\frac{\rho}{|1-\rho^2|}\int_{0}^{\pi}\theta^2 d\theta \\
+&= \rho\frac{|\log\rho|^2}{|1-\rho^2|}\pi + \rho\frac{|\log\rho|}{|1-\rho^2|}\pi^2 + \frac{\rho}{|1-\rho^2|}\frac{\pi^3}{3}
+\end{aligned}
+$$
+let $\rho\to 0^+ $ or $\rho\to\infty$, these terms will be 0. It is just the same for the three-order case, thus
+$$
+\int_{0}^{\infty}\frac{(\log x)^2}{1+x^2}dx = \frac{1}{8}\pi^3,
+$$
+hence
+$$
+\int_{0}^{\infty}\frac{(\log x)^3}{1+x^2}dx = 0.
+$$
+
+\textbf{(c)}
+First,
+$$
+\int_{0}^{\infty}\frac{\cos ax}{(1+x^2)^2}dx = \frac{1}{2}\int_{-\infty}^{\infty}\frac{e^{iax}}{(1+x^2)^2}dx.
+$$
+Let $\gamma = \{|z|=R, Im(z) > 0\} \cup [-R, R]$, then by residue theorem,
+$$
+\int_{\gamma}\frac{e^{iaz}}{(1+z^2)^2}dz = 2\pi iRes(f, i) = \frac{(a+1)e^{-a}\pi}{2}.
+$$
+And
+$$
+\begin{aligned}
+\left|\int_{\gamma_R}\frac{e^{iaz}}{(1+z^2)^2}dz\right| &= \left|\int_{0}^{\pi}\frac{e^{-aR\sin\theta}(\cos(aR\cos\theta)+i\sin(aR\cos\theta))}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta\right| \\
+&\le \left|\int_{0}^{\pi}\frac{R}{|1-R^2|^2}d\theta\right| \to 0, ~\text{when} ~R\to\infty.
+\end{aligned}
+$$
+Hence
+$$
+\int_{0}^{\infty}\frac{\cos ax}{(1+x^2)^2}dx = \frac{(a+1)e^{-a}\pi}{4}.
+$$
+
+\textbf{(d)}
 

### 2018-03-20 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add 5.2.2 d, e

@@
 \textbf{(d)}
+If $z = e^{2i\theta} $ then $\bar{z} = \frac{1}{z}$ and so
+$$
+a+\sin^2\theta = a-\frac{1}{4}(e^{2i\theta}+e^{-2i\theta}-2) = a-\frac{1}{4}(z+\bar{z}-2) = -\frac{z^2-(4a+2)z+1}{4z}.
+$$
+Hence
+$$
+\int_{0}^{\pi/2}\frac{d\theta}{a+\sin^2\theta} = \frac{1}{2}\int_{0}^{\pi}\frac{d\theta}{a+\sin^2\theta} = i\int_{\gamma}\frac{1}{z^2-(4a+2)z+1}dz,
+$$
+where $\gamma = \{|z| = 1\}$.
+But $z^2-(4a+2)z+1 = (z-z_1)(z-z_2) $ where $z_1 = (1+2a)+2\sqrt{a^2+a}, ~z_2 = (1+2a)-2\sqrt{a^2+a} $.
+Since $a > 0$ we know $|z_1| > 1 $ and $|z_2| < 1$, by residue theorem,
+$$
+\int_{\gamma}\frac{1}{z^2-(4a+2)z+1}dz = 2\pi iRes(f, z_1) = \frac{\pi i}{-2\sqrt{a^2+a}}.
+$$
+Hence
+$$
+\int_{0}^{\pi/2}\frac{d\theta}{a+\sin^2\theta} = \frac{\pi}{2\sqrt{a^2+a}}.
+$$
+
+\textbf{(e)}
+Define $G, l(z), \gamma$ as in Example 2.10, then
+$$
+\int_{\gamma}\frac{l(z)}{(1+z^2)^2}dz = \int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx +\int_{0}^{\pi}\frac{\log R +i\theta}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{\log |x|+\pi i}{(1+x^2)^2}dx + \int_{\pi}^{0}\frac{\log r +i\theta}{(1+r^2e^{2i\theta})^2}ire^{i\theta}d\theta
+$$
+by residue theorem,
+$$
+\int_{\gamma}\frac{l(z)}{(1+z^2)^2}dz = \frac{(\pi+2i)\pi i}{4}.
+$$
+First,
+$$
+\int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx + \int_{-R}^{-r}\frac{\log |x|+\pi i}{(1+x^2)^2}dx = 2\int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx + \frac{\pi i}{2}\left(\frac{R}{R^2+1}-\frac{r}{r^2+1}+\arctan R-\arctan r\right)
+$$
+and
+$$
+\left|\int_{0}^{\pi}\frac{\log R +i\theta}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta\right| \le \frac{R|\log R|}{|1-R^2|^2}\int_{0}^{\pi}d\theta + \frac{R}{|1-R^2|^2}\int_{0}^{\pi}\theta d\theta \to 0,
+$$
+as $R\to \infty$. Also, we know $r\log r\to 0$ as $r\to 0^+ $, hence
+$$
+\left| \int_{\pi}^{0}\frac{\log r +i\theta}{(1+r^2e^{2i\theta})^2}ire^{i\theta}d\theta\right| \to 0.
+$$
+Hence,
+$$
+\int_{0}^{\infty}\frac{\log z}{(1+x^2)^2}dx = \frac{1}{2}\left(\frac{(\pi+2i)\pi i}{4}-\frac{\pi i}{2}\frac{\pi}{2}\right) = -\frac{\pi}{4}.
+$$
 

### 2018-03-25 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
add hw 5

\documentclass{article}%

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage{amsfonts}%

\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}

\setlength{\textheight}{9.25in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textwidth}{6.5in}

\def\labelenumi{\arabic{enumi}.}

\def\theenumi{\arabic{enumi}}

\def\labelenumii{(\alph{enumii})}

\def\theenumii{\alph{enumii}}

\def\p@enumii{\theenumi.}

\def\labelenumiii{\arabic{enumiii}.}

\def\theenumiii{\arabic{enumiii}}

\def\p@enumiii{(\theenumi)(\theenumii)}

\def\labelenumiv{\arabic{enumiv}.}

\def\theenumiv{\arabic{enumiv}}

\def\p@enumiv{\p@enumiii.\theenumiii}

\pagestyle{plain}

\setcounter{secnumdepth}{0}

\newtheorem{theorem}{Theorem}

\newtheorem{acknowledgement}[theorem]{Acknowledgement}

\newtheorem{algorithm}[theorem]{Algorithm}

\newtheorem{axiom}[theorem]{Axiom}

\newtheorem{case}[theorem]{Case}

\newtheorem{claim}[theorem]{Claim}

\newtheorem{conclusion}[theorem]{Conclusion}

\newtheorem{condition}[theorem]{Condition}

\newtheorem{conjecture}[theorem]{Conjecture}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{criterion}[theorem]{Criterion}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{example}[theorem]{Example}

\newtheorem{exercise}[theorem]{Exercise}

\newtheorem{lemma}[theorem]{Lemma}

\newtheorem{notation}[theorem]{Notation}

\newtheorem{problem}[theorem]{Problem}

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{solution}[theorem]{Solution}

\newtheorem{summary}[theorem]{Summary}

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}

\textbf{Homework 5}\bigskip

\end{center}

\noindent\textbf{Instructions}:
\noindent In problems the problems below, references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

\noindent If you use results from books including Conway's, please be explicit about what results you are using.

\begin{center}

\emph{Homework 5 is due in class at Midnight Monday, March 26.}

\end{center}

\medskip

Do the following problems:

\begin{enumerate}

\item V.3.1

\textbf{Proof}
From (3.1), (3.2) we know for a zero $z = a$ of $f$,
$$
\frac{f'(z)}{f(z)}g(z) = \frac{m}{z-a}g(z) + \frac{h'(z)}{h(z)}g(z),
$$
where $f(z) = (z-a)^mh(z) $ and $h$ is analytical around $a$ and $h(a)\ne 0$. Similarly, for a pole $z = a$ of $f$,
$$
\frac{f'(z)}{f(z)}g(z) = \frac{-m}{z-a}g(z)+\frac{h'(z)}{h(z)}g(z),
$$
where $f(z) = (z-a)^{-m}h(z)$ and $h$ is analytical and $h(a)\ne 0$. In both cases, since $g$ is analytic in $G$, it has no poles in $G$, so $\frac{h'(z)}{h(z)}g(z)$ is analytic. Hence, 
$$
\frac{f'(z)}{f(z)}g(z) = \sum_{k=1}^{n}\frac{g(a_k)}{z-a_k} -\sum_{j = 1}^{m}\frac{g(p_j)}{z-p_j}+\frac{h'(z)}{h(z)},
$$
and hence by Cauchy's theorem,
$$
\frac{1}{2\pi i}\int_{\gamma}\frac{f'(z)}{f(z)}dz = \sum_{i=1}^{n}g(z_i)n(\gamma; z_i)-\sum_{j=1}^{m}g(p_j)n(\gamma; p_j).
$$

\item V.3.2

\textbf{Sol.} Let $h(z) = f(z) - z^n $, $g(z) = z^n $, then by assumptions, on $\{|z| = 1\}$,
$$
|h(z)+g(z)| = |f(z)| < 1 = |g(z)|,
$$
hence by Rouche's theorem,
$$
Z_h-P_h = Z_g-P_g.
$$
Since $h, g$ are analytic on $\bar{B}(0, 1)$, $P_h = P_g = 0 $. Hence
$$
Z_h = Z_g = 1,
$$
which means the equation has one solution.

\item V.3.3 Hint: Think about the expansion\[
 \frac{1}{f(z)-w} = \frac{1}{f(z)} + \frac{w}{[f(z)]^2} + \cdots + \frac{w^n}{[f(t)]^{n+1}}+\cdots .                                       
                                       \]The hypotheses allow you to integrate this series termwise in $z$.

\textbf{Proof.} Since $f$ is analytic in $\bar{B}(0, R)$, it has no poles and according to assumptions, one zeros in it. Hence

\item V.3.5

\textbf{Proof.}
First we show it is true for the poles. Since $f$ is meromorphic in $G$, if $z_0 $ is a limit point of poles, then $f$ is either analytic in a neighbourhood of $z_0 $ or has an isolated singularity at $z_0 $. If $f$ is analytic at $z_0 $, then $f$ is analytic at some $B(z_0, r)$. But since $z_0 $ is a limit point of poles, there must be a pole $z_1\in B(z_0, r)$, which makes a contradiction. If $z_0 $ is an isolated singularity, then there is some $r > 0$, $f$ is analytic in $B(z_0, r)\setminus\{z_0\}$. By the same reason, there is a pole $z_1\in B(z_0, r)\setminus\{z_0\}$, which makes a contradiction. Hence it is true for poles.

For the zeros: suppose $z_0 $ is a limit point of zeros. First we claim that $z_0 $ cannot be a pole. Otherwise, since poles cannot have a limit points as we have shown above, $f$ has a Laurent expansion in some $B(z_0, r)\setminus\{z_0\}$:
$$
f(z) = \sum_{n=-m}^{\infty}a_n(z-z_0)^n.
$$
Then pick $r < 1$, we know
$$
\left|\sum_{n=0}^{\infty}a_n (z-z_0)^n\right| < \sum_{n=0}^{\infty}|a_n|r^n < M
$$
for some $M > 0$. However, we can pick a $\epsilon > 0$, s.t. 
$$
\sum_{n=-m}^{-1}a_n\epsilon^n > M.
$$
Hence for each $z\in B(z_0, \epsilon)$, $f(z)\ne 0$, which makes a contradiction with that $z_0 $ is a limit point of zeros. Thus, since poles cannot have a limit points, we can pick a $r > 0$, s.t. there is no pole in $B(z_0, r)$, which means $f$ is analytic in $B(z_0, r)$. By Theorem 4.3.7, zeros has no limit points in $B(z_0, r)$, which contradicts with that $z_0 $ is a limit point.

Hence, the proposition holds.

\item V.3.6

\item V.3.7

\textbf{Sol.}

\item V.3.10

\textbf{Proof.} In fact, by problem 2 we know there is an unique $z$ s.t. $|z| < 1$ and $f(z) = z$. When $|f(z)| \le 1$ on $|z| = 1$, we will show it is not true.

i) pick $f(z) \equiv 1$, then $f(z) = z$ has no solution in $|z| < 1$.

ii) pick $|f(z)| < 1$ on $|z| = 1$, then it has one solution in $|z| < 1$.

iii) pick $f(z) = z$, then is has infinity number of solutions.

Now we proof the only situations are as above, i.e., if a function $f$ is analytic in the unit dist $D$, and $f(D)\subset D$, then $f$ has one fixed point in $D$, except for the identity function.

In fact, suppose there are two fixed points $z_1, z_2 $. If $z_1 = 0$, then by Schwarz's lemma, there is a constant $|c| = 1$, s.t. $f(z) = cz$ for all $z$ in $D$. Hence, $f(z_2) = cz_2 = z_2 $, which means $c = 1$.

Now suppose $z_1, z_2\ne 0 $. Let $z_1 = re^{i\theta} $, consider $\varphi(z) = e^{i\theta}\frac{z+r}{rz+1}$, then $\varphi$ maps $D$ onto itself, and $\varphi(0) = z_1 $. Hence the function $g = \varphi^{-1} \circ f\circ\varphi$ maps $D$ to a subset of $D$ with two fixed points $t_1 = \varphi^{-1}(z_1) = 0 $, and $t_2 = \varphi^{-1}(z_1) \ne 0 $. By the first case, $g$ is the identity function, so $f$ is also the identity function.

\end{enumerate}

\end{document}

### 2018-03-25 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
add problem 3

@@
 \textbf{Proof.} Since $f$ is analytic in $\bar{B}(0, R)$, it has no poles and according to assumptions, one zeros in it. Hence
+$$
+g(w) = \frac{1}{2\pi i}\int_{\gamma}\frac{zf'(z)}{f(z)-w}dz = \frac{1}{2\pi i}\int_{\gamma}\sum_{n=1}^{\infty}\frac{w^{n-1}}{f(z)^n}zf'(z)dz.
+$$
+Let $f(z) = zh(z)$, by assumption we know $h(0)\ne 0$, hence
+$$
+\left|\frac{w^{n}}{f(z)^{n+1}}zf'(z)\right| = \left|\frac{w^{n}}{z^nh(z)^{n+1}}zf'(z)\right| = \left|\left(\frac{w}{z}\right)^n\frac{f'(z)}{h(z)^n}\right| \le \frac{|w|^n}{R^n}\frac{R^n|f'(z)|}{|f(z)|^n} = \left|\frac{w}{f(z)}\right|^n|f'(z)|.
+$$
+By assumption we know $|w| \le |f(z)|$, hence for $f(z)\ne w$ (and since the domain is $B(0; \rho)$ which means the inequality is strict), the series
+$$
+\sum_{n=0}^{\infty}\frac{|w|^n}{|f(z)|^n}f'(z)
+$$
+converges, thus by Weierstrass theorem, the series
+$$
+\sum_{n=1}^{\infty}\frac{w^{n-1}}{f(z)^n}zf'(z)dz
+$$
+converges uniformly, hence we can switch the infinity sum with the integral:
+$$
+g(w) = \frac{1}{2\pi i}\sum_{n=0}^{\infty} \int_{\gamma}\left(\frac{w}{z}\right)^n\frac{f'(z)}{h(z)^n}dz
+$$
 

### 2018-03-25 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
update prob 3

@@
 $$
-g(w) = \frac{1}{2\pi i}\sum_{n=0}^{\infty} \int_{\gamma}\left(\frac{w}{z}\right)^n\frac{f'(z)}{h(z)^n}dz
+g(w) = \frac{1}{2\pi i}\sum_{n=0}^{\infty} \int_{\gamma}\left(\frac{w}{z}\right)^n\frac{f'(z)}{h(z)^n}dz.
 $$
+For an arbitrary triangle path $T$ in $B(0,\rho)$, since $w^n $ is analytic for every $n \ge 0$,
+$$
+\int_{T}g(w)dw = \frac{1}{2\pi i}\int_{T}\sum_{n=0}^{\infty}\int_{\gamma}\left(\frac{w}{z}\right)^n\frac{f'(z)}{h(z)^n}dz = \frac{1}{2\pi i}\sum_{n=0}^{\infty}\int_{\gamma}\frac{1}{z^n}\frac{f'(z)}{h(z)^n}dz\int_{T}w^ndw = 0.
+$$
+Hence by Morera's theorem, $g$ is analytic.
 

### 2018-03-25 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
update problem 6

@@
 
+Properties: first, by Theorem 3.6, notice $f$ has one zero $z = 0$ and no poles,
+$$
+g(0) = \frac{1}{2\pi i}\int_{\gamma}\frac{zf'(z)}{f(z)}dz = \sum_{i=1}^{n}z_i n(\gamma; z_i) - \sum_{j=1}^{m}p_i n(\gamma, p_j) = 0.
+$$
+
 \item V.3.5
@@
 
-\textbf{Sol.}
+\textbf{Sol.} A very trivial version is: change $\gamma$ to any closed rectifiable curve in G where $f, g$ are meromorphic in a neighbourhood of $G$ with no zeros or poles in $\gamma$.
+In this case we do not need to modify the proof.
 

### 2018-03-26 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
finish hw 5

@@
 
+First, it is trivial that $H(G)$ is a commutative group under addition.
+Besides, if $f, g\in H(G)$, then $fg$ is also analytic, $fg = gf$, and $(fg)h = f(gh)$.
+Hence $H(G)$ is a commutative ring.
+If there is a zeros divisor $f\ne 0$, then there is $g\ne 0\in H(G)$, s.t.
+$fg = 0$.
+Let $\{z_i\}$ be zeros of $f$, then since $f$ is analytic, the zeros are isolated, which means if there are at most countable number of zeros in $G$, otherwise there is a limit point of zeros, which against the property of analytic functions.
+It is the same for $g$, hence $fg = 0$ only at countable number of points in $G$, which makes a contradiction.
+
+With the same arguments, we can show $M(G)$ is a commutative ring with 0 and 1, which are $f\equiv 0$ and $f\equiv 1$.
+Let $f\in M(G)$, and we only need to show that $\frac{1}{f}\in M(G)$.
+In fact, if $f\in M(G)$, then $f$ has countable number of zeros, hence $\frac{1}{f}$ has countable number of poles, and the order of each pole is finite.
+Hence $\frac{1}{f}\in M(G)$.
+
 \item V.3.7

### 2018-04-14 Graduate - Introduction to Analysis II/HW6/6HW20180406.tex
add hw 6

\documentclass{article}%

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage{amsfonts}%

\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}

\setlength{\textheight}{9.25in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textwidth}{6.5in}

\def\labelenumi{\arabic{enumi}.}

\def\theenumi{\arabic{enumi}}

\def\labelenumii{(\alph{enumii})}

\def\theenumii{\alph{enumii}}

\def\p@enumii{\theenumi.}

\def\labelenumiii{\arabic{enumiii}.}

\def\theenumiii{\arabic{enumiii}}

\def\p@enumiii{(\theenumi)(\theenumii)}

\def\labelenumiv{\arabic{enumiv}.}

\def\theenumiv{\arabic{enumiv}}

\def\p@enumiv{\p@enumiii.\theenumiii}

\pagestyle{plain}

\setcounter{secnumdepth}{0}

\newtheorem{theorem}{Theorem}

\newtheorem{acknowledgement}[theorem]{Acknowledgement}

\newtheorem{algorithm}[theorem]{Algorithm}

\newtheorem{axiom}[theorem]{Axiom}

\newtheorem{case}[theorem]{Case}

\newtheorem{claim}[theorem]{Claim}

\newtheorem{conclusion}[theorem]{Conclusion}

\newtheorem{condition}[theorem]{Condition}

\newtheorem{conjecture}[theorem]{Conjecture}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{criterion}[theorem]{Criterion}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{example}[theorem]{Example}

\newtheorem{exercise}[theorem]{Exercise}

\newtheorem{lemma}[theorem]{Lemma}

\newtheorem{notation}[theorem]{Notation}

\newtheorem{problem}[theorem]{Problem}

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{solution}[theorem]{Solution}

\newtheorem{summary}[theorem]{Summary}

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}

\textbf{Homework 6}\bigskip

\end{center}

\noindent\textbf{Instructions}:
\noindent In problems the problems below, references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

\noindent If you use results from books including Conway's, please be explicit about what results you are using.

\begin{center}

\emph{Homework 6 is due in class at Midnight Monday, April 23.}

\end{center}

\medskip

Do the following problems:

\begin{enumerate}

\item VI.1.4  Notice that this is related to a problem on the second midterm.

\textbf{Proof.}
If not, suppose for each $\epsilon > 0$, there is a polynomial $p(z)$, s.t. $\sup\{|p(z) - z^{-1}| : z\in A\} < \epsilon$. We claim that $|p(z) - z^{-1}| \le \epsilon$ for all $z\in A$. Otherwise, by the continuity of $|p(z)|$, $\exists z_0\in O(z, r)\cap A $, s.t. $|p(z_0)-z^{-1}| > \epsilon$, which makes a contradiction.

Now pick $\epsilon = \frac{1}{2R}$, then in $A$, $|p(z)-\frac{1}{z}| \le \frac{1}{2R}$, which means
$$
|zp(z)-1|\le \frac{|z|}{|2R|} \le \frac{1}{2}
$$
on $A$, hence on $\{|z| = R\}\subset\partial A$. Hence, by Maximum Modulus Thm, since $g(z) = zp(z)-1$ is analytic in $O(0, R)$, we know for each $z\in O(0, R)$, $|g(z)| < \max|g(\partial A)| \le \frac{1}{2}$. However, $|g(0)| = 1 > \frac{1}{2}$, which makes a contradiction.

\item VI.1.5

\textbf{Proof.}
Let $\{z_k\}_{k=1}^n $ be zeros of $f$ in $B(0, \frac{1}{3}R)$, and 
$$
g(z) = \frac{\prod_{k=1}^{n}z_k}{\prod_{k=1}^{n}(z-z_k)}f(z),
$$
then $g(z)$ is analytic in $B(0, R)$, and $g(0) = f(0) = a$. Hence by Max Modulus Thm,
$$
a = |g(0)| \le \left| \frac{\prod_{k=1}^{n}z_k}{\prod_{k=1}^{n}(z-z_k)}f(z)\right|_{z\in\{|z| = R\}} \le \frac{(\frac{1}{3}R)^n}{(\frac{2}{3}R)^n}M = \frac{1}{2^n}M.
$$
Then $n \le \frac{\log (M/a)}{\log 2}$.

\item VI.1.6

Let $h(z) = \frac{f(z)}{g(z)}$, then since $f, g$ never vanish in $B(0, R)$, $h$ and $H = \frac{1}{h}$ are both analytic in $B(0, R)$. Then by M.M.T,
$$
|h(z)| \le \left|\frac{f(z)}{g(z)}\right|_{|z| = 1} = 1, 
$$
and
$$
|H(z)| = \left|\frac{1}{h(z)}\right| \le \left|\frac{g(z)}{f(z)}\right|_{|z| = 1} = 1,
$$
we know $|h(z)| \equiv 1$ in $B(0, R)$, and by M.M.T, $h(z)$ is a constant $\lambda$, and $|\lambda| = 1$.

\item VI.2.5

\textbf{(a)}
Consider 
$$
\varphi(z) = \varphi_{z_1}(z)\cdots\varphi_{z_n}(z),
$$
where $\varphi_{z_k}(z) $ is the Mobius transformation 
$$
\varphi_{z_k}(z) = \frac{z-z_k}{1-\bar{z_k}z}.
$$
Then 
$$
g(z) = \frac{f(z)}{\varphi(z)}
$$
is analytic in $D$. Now we only need to show that $|g| \le M$ in $D$. If not, assume there is a point $z_0\in D $ , s.t. $|g(z_0)| = M_0 > M $. Then for any $|z_0| < r < 1$, by max modulus thm, 
$$
\max_{|z| = r}|h(z)| \ge M_0.
$$
Hence there is some $z_r\in \{|z| = r\}$, s.t.
$$
M \ge |f(z_r)| \ge M_0\varphi(z_r).
$$
Let $r\to 1^- $, take limit on both side, we get
$$
M \ge M_0\lim_{r\to 1^-}\varphi(z_r) = M_0
$$
as $|\varphi| = 1$ on $\partial D$, which leads to a contradiction. Hence, $|f| \le M|\varphi|$.

\textbf{(b)}
With the same notation as (a), we notice
$$
h(0) = \frac{f(0)}{\varphi(0)} = (-1)^{n}M,
$$
which means $|h(0)| = M$. But we have shown $|h(z)| \le M$ on $D$, hence by M.M.T., 
$$
h(z) \equiv (-1)^nM, \forall z\in D.
$$
Hence
$$
f(z) = h(z)\varphi(z) = (-1)^nM\varphi(z).
$$

\item VI.2.8

\textbf{Sol.}
Let $g(z) = \varphi_{\frac{1}{2}}\circ f(z) $, then 
$$
g(0) = 0, ~g'(0) = \frac{-f(0)f'(0)+\frac{5}{4}f'(0)}{(1-\frac{1}{2}f(0))^2} = 1,
$$
and $g$ is analytic in $D$. Hence by Schwarz's Thm, there is some $|c| = 1$,
$$
g(z) = cz = \varphi_{\frac{1}{2}}\circ f(z),
$$ 
which means
$$
f(z) = \varphi_{-\frac{1}{2}}(cz),
$$
where $|c| = 1$. Thus the solution is not unique.

\item VII.2.1

\textbf{Proof.} 
If $f_n\to f $, then since $\gamma$ is compact, we know $f_n\to f $ uniformly on $\gamma$.

Conversely, for each $z\in G$, let $\gamma$ be a circle $C(z, r)\subset G$, then by Cauchy's theorem,
$$
f_n(z) = \frac{1}{2\pi i}\int_{\gamma}\frac{f_n(w)}{w-z}dw,
$$
hence
$$
|f(z)-f_n(z)| = \frac{1}{2\pi}\left|\int_{\gamma}\frac{f_n(w)-f(w)}{w-z}dw\right| \le 2\sup_{w\in\gamma}\{|f(w)-f_n(w)|\}
$$
For each $\epsilon > 0$, since $f_n\to f $ uniformly on $\gamma$, there is a $N > 0$, for each $n \ge N$ and each $w\in\gamma$, $|f_n(w) - f(w)| < \frac{1}{2}\epsilon$. Hence, 
$$
|f_n(z) - f(z)| < \epsilon.
$$
Thus $f_n \to f$ on every $z\in G$.

\item VII.2.4

\textbf{Proof.}
Since $\{f_n\}$ is locally bounded, we know by Montel's theorem that $\{f_n\}$ is normal. Then each subsequence of $\{f_n\}$ has a subsequence that converges to an analytic function, and these functions are equal in $A$ which has a limit point. Hence these limit functions are equal in $G$, which means $f_n\to f $.

\item VII.2.5

\textbf{(b) to (a)} In fact it is trivial since uniform boundness leads to local boundness.

\textbf{(a) to (b)} I don't think it is right. For example, let $f_n(z) = nz^n $ and $G$ be the unit disk $D$, then of course $\{f_n\}$ is locally bounded by Lemma 2.8. Hence by Montel's theorem, $\{f_n\}$ is normal. However, since 
$$
\lim_{z\to \partial D} |f_n(z)| = n,
$$
for each $\epsilon > 0$ and each $c > 0$, we can pick some $n$ large enough and $z$ sufficiently close to $\partial D$, and $|cf_n(z)| > \epsilon$.

\end{enumerate}

\end{document}

### 2018-05-29 Graduate - Introduction to Analysis II/HW7/7HW20180422.tex
update

\documentclass{article}%

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage{amsfonts}%

\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}

\setlength{\textheight}{9.25in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textwidth}{6.5in}

\def\labelenumi{\arabic{enumi}.}

\def\theenumi{\arabic{enumi}}

\def\labelenumii{(\alph{enumii})}

\def\theenumii{\alph{enumii}}

\def\p@enumii{\theenumi.}

\def\labelenumiii{\arabic{enumiii}.}

\def\theenumiii{\arabic{enumiii}}

\def\p@enumiii{(\theenumi)(\theenumii)}

\def\labelenumiv{\arabic{enumiv}.}

\def\theenumiv{\arabic{enumiv}}

\def\p@enumiv{\p@enumiii.\theenumiii}

\pagestyle{plain}

\setcounter{secnumdepth}{0}

\newtheorem{theorem}{Theorem}

\newtheorem{acknowledgement}[theorem]{Acknowledgement}

\newtheorem{algorithm}[theorem]{Algorithm}

\newtheorem{axiom}[theorem]{Axiom}

\newtheorem{case}[theorem]{Case}

\newtheorem{claim}[theorem]{Claim}

\newtheorem{conclusion}[theorem]{Conclusion}

\newtheorem{condition}[theorem]{Condition}

\newtheorem{conjecture}[theorem]{Conjecture}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{criterion}[theorem]{Criterion}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{example}[theorem]{Example}

\newtheorem{exercise}[theorem]{Exercise}

\newtheorem{lemma}[theorem]{Lemma}

\newtheorem{notation}[theorem]{Notation}

\newtheorem{problem}[theorem]{Problem}

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{solution}[theorem]{Solution}

\newtheorem{summary}[theorem]{Summary}

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\begin{center}

\textbf{Homework 7}\bigskip

\end{center}

\noindent\textbf{Instructions}:
\noindent In problems the problems below, references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

\noindent If you use results from books including Conway's, please be explicit about what results you are using.

\begin{center}

\emph{Homework 7 is due at Midnight Wednesday, May 2.}

\end{center}

\medskip

Do the following problems:

\begin{enumerate}

\item Let $ F$ be the map that takes nonzero vectors in $ \mathbb{C}^2$ to vectors in $ \mathbb{R}^3$ by the following formula:
\[ F(z_{1},z_{2}) := \left(
\frac{z_{1}\bar{z}_{2} + \bar{z}_{1} z_{2}}{{z}_{1}\bar{z}_{1}+\bar{z}_2 z_2},\frac{z_{1}\bar{z}_{2} - \bar{z}_{1} z_{2}}{i({z}_{1}\bar{z}_{1}+\bar{z}_2 z_2)}, \frac{z_{1}\bar{z}_{1} - \bar{z}_{2} z_{2}}{{z}_{1}\bar{z}_{1}+\bar{z}_2 z_2}
\right) .
\]
Show that:

\begin{enumerate}

\item $ F$ defines a bijection between $ \mathbb{P}^1(\mathbb{C})$ and the unit sphere in $ \mathbb{R}^3$, and
\item if $S$ denotes stereographic projection from $\mathbb{C}_{\infty}-{\{(0,0,1)\}}$ to $\mathbb{C}$, then if $[z_1:z_2] \neq [1:0]$ , \[
S(F([z_1:z_2])) = z_1/z_2.
\]  
\end{enumerate}

\textbf{Proof.}
(a)
Let $z_1 = r_1e^{it_1}, z_2 = r_2e^{it_2} $, then $F$ maps $(r_1e^{it_1}, r_2e^{it_2})$ to
$$
\left(
2\frac{r_1r_2}{r_1^2+r_2^2}\cos(t_1-t_2), ~2\frac{r_1r_2}{r_1^2+r_2^2}\sin(t_1-t_2), ~\frac{r_1^2-r_2^2}{r_1^2+r_2^2}
\right)
$$
Hence if $F$ maps two vectors $(r_1e^{it_1}, r_2e^{it_2})$ and $(r_1'e^{it_1'}, r_2'e^{it_2'})$ to a same point in $\mathbb{R}^3 $, then $\tan(t_1-t_2) = \tan(t_1'-t_2')$, hence $t_1-t_2 = t_1'-t_2' $. Besides, if we denote $p_1 = \frac{r_1}{r_2}, p_1' = \frac{r_1'}{r_2'} $, then
$$
\frac{1-p_1^2}{p_1} = \frac{1-p_1'^2}{p_1'}, 
$$
and
$$
\frac{1+p_1^2}{p_1} = \frac{1+p_1'^2}{p_1'},
$$
when we add this two equations we get $p_1 = p_2 $. Hence by considering the first term we know $r_1 = r_2 $. Hence $F$ is an injection, and since $\lVert F(z) \rVert = 1$ we know $F$ is an injection from $\mathbb{P}^1(\mathbb{C}) $ to unit sphere.

On the other hand, for each $(\sin\varphi\cos\theta, ~\sin\varphi\sin\theta, ~\cos\theta)$ in unit sphere, we can find $r_1, r_2, t_1, t_2 $, s.t.
$$
\frac{r_1r_2}{r_1^2+r_2^2} = \frac{1}{2}\sin\varphi, ~t_1-t_2 = \theta.
$$
Hence $F$ is a bijection.

\textbf{(b)}

\item III.3.8

\textbf{Proof.}
First, if we choose $a, b, c, d$ to be real, then for each $x\in\mathbb{R}$, we can pick
$$
z = \frac{dx-b}{-cx+a}\in\mathbb{R}_{\infty}
$$
then $Tz = x$. For $x = \infty$, if $c = 0$, then by $ad-bc\ne 0$ we know $d\ne 0$, hence we can pick $z = \infty$ and $Tz = x$. If $c\ne 0$, let $z = \frac{a}{c}$ then $Tz = x$.

On the other hand, if $T(\mathbb{R}_\infty) = \mathbb{R}_\infty $, then there are $x_1, x_2, x_3\in\mathbb{R}_\infty $, s.t. $T(x_1) = 1, T(x_2) = 0, T(x_3) = \infty$. Then by Proposition 3.8,
$$
\frac{z-x_2}{z-x_3}/\frac{x_1-x_2}{x_1-x_3} = T(z) = \frac{(x_1-x_3)z - (x_1-x_3)x_2}{(x_1-x_2)z-(x_1-x_2)x_3},
$$
which means $a, b, c, d$ are all real.

\item III.3.11

\textbf{Proof.}
Let $T_1 $ be the Mobius transformation which maps $(z_1, z_2, z_3)$ to $(1, 0, \infty)$, and $T_2 $ maps $(w_1, w_2, w_3)$ to $(1, 0, \infty)$. Let $T = T_2T_1^{-1} $, then $T$ maps $\mathbb{R}_\infty $ onto $\mathbb{R}_\infty $, and hence by Exercise 8, 
$$
T(z) = \frac{az+b}{cz+d}
$$
where $a, b, c, d\in\mathbb{R}$. Hence 
$$
T(z)^* = T(z).
$$
Then for $z, z^* $ satisfying $T_1(z^*) = T_1(z)^* $, $T_2(z^*) = T_2(T_1^{-1}(T_1(z^*))) = T(T_1(z^*)) = T(T_1(z)^*) = T_2(z)^* $.

\item III.3.13

\textbf{Sol.}
We may consider the function
$$
f(z) = \frac{z^2+1}{2z}
$$
using the same process in Page 45.

First it is not a bijection, thus is not a conformal map.

\item III.3.14

\textbf{Sol.}
First, consider $T = \frac{1}{z-a}$, it maps $G$ onto a region between two parallel lines, denoted by $H$. Then we can use a rotation and translation $f$ to map $H$ onto the set $I = \{z: 0 < Im(z) < \frac{\pi}{2}\}$. Then $\exp(I) = \{z: Re(z) > 0\} = J$. At this stage we can use another Mobius transformation $g(z) = \frac{z-1}{z+1}$ to map $J$ to open unit disk. Hence
$$
\varphi(z) = g\circ \exp\circ f\circ T
$$
is what we need, and it is a conformal map.

\item III.3.15

\textbf{Sol.} In fact, as we have learned in Chapter 6.2, for any $|a| < 1$, 
$$
\varphi_a(z) = \frac{z-a}{1-\bar{a}z}
$$
is what we want.

\item III.3.16

\textbf{Sol.} First, $f(z) = \frac{z+1}{z-1}$ maps $G$ to $H = \mathbb{C} - (\{z: z\le 0\} \cup \{z = 1\})$. Then $g(z) = z^{1/2} $ maps $H$ to $I = \{z: Re(z) > 0\} - \{z = 1\}$. Then $h(z) = \frac{1-z}{1+z}$ maps $I$ to $J = D-\{z=0\}$ where $D$ is the open unit disk. By Problem 3.3.15 we know $\varphi(z) = \exp(\frac{z+1}{z-1})$ maps $D$ to $J$ conformally, hence $\varphi^{-1} $ maps $J$ to $D$ conformally. Hence, 
$$
\phi = \varphi^{-1}\circ h\circ g\circ f
$$
is what we want, and since the four functions are all analytic and one to one in their domains, $\phi$ is an analytic function and is also 1-1.

\item III.3.17

\textbf{Proof.}
In fact this is trivial by Open Mapping Theorem, since a subset of a circle cannot be open.

\end{enumerate}

\end{document}

### 2018-05-29 LeetCode/200. Number of Islands.cpp

@@ -1,0 +1,22 @@
+class Solution {
+public:
+    int numIslands(vector<vector<char>>& grid) {
+        int res = 0;
+        for(int i = 0; i < grid.size(); i++) {
+            for(int j = 0; j < grid[0].size(); j++) {
+                if(grid[i][j] == '1') res++;
+                dfs(grid, i, j);
+            }
+        }
+        return res;
+    }
+    
+    void dfs(vector<vector<char>>& grid, int i, int j) {
+        if(i < 0 || j < 0 || i >= grid.size() || j >= grid[0].size() || grid[i][j] == '0') return;
+        grid[i][j] = '0';
+        dfs(grid, i-1, j);
+        dfs(grid, i+1, j);
+        dfs(grid, i, j-1);
+        dfs(grid, i, j+1);
+    }
+};

### 2018-05-29 LeetCode/202. Happy Number.cpp

@@ -1,0 +1,23 @@
+class Solution {
+public:
+    bool isHappy(int n) {
+        unordered_set<int> process; process.insert(n);
+        int next;
+        while(1) {
+            next = happy(n);
+            if(next == 1) return true;
+            else if(process.find(next) != process.end()) return false;
+            process.insert(next);
+            n = next;
+        }
+    }
+    
+    int happy(int n) {
+        int count = 0;
+        while(n) {
+            count += (n%10)*(n%10);
+            n /= 10;
+        }
+        return count;
+    }
+};

### 2018-05-29 LeetCode/205. Isomorphic Strings.cpp

@@ -1,0 +1,14 @@
+class Solution {
+public:
+    bool isIsomorphic(string s, string t) {
+        if(s.size() != t.size()) return false;
+        unordered_map<char, char> mp1, mp2;
+        for(int i = 0; i < s.size(); i++) {
+            if(mp1.find(s[i]) != mp1.end() && mp1[s[i]] != t[i]) return false;
+            if(mp2.find(t[i]) != mp2.end() && mp2[t[i]] != s[i]) return false;
+            mp1[s[i]] = t[i];
+            mp2[t[i]] = s[i];
+        }
+        return true;
+    }
+};

### 2018-05-29 LeetCode/208. Implement Trie (Prefix Tree).cpp

@@ -1,0 +1,58 @@
+class Node {
+public:
+    Node* child[26];
+    bool is_key;
+    
+    Node(bool word = false) {
+        memset(child, 0, sizeof(child));
+        is_key = word;
+    }
+};
+
+class Trie {
+public:
+    Node* root;
+    /** Initialize your data structure here. */
+    Trie() {
+        root = new Node();
+    }
+    
+    /** Inserts a word into the trie. */
+    void insert(string word) {
+        Node* p = root;
+        for(int i = 0; i < word.size(); i++) {
+            if(!p->child[word[i] - 'a']) p->child[word[i] - 'a'] = new Node();
+            p = p->child[word[i] - 'a'];
+        }
+        p->is_key = true;
+    }
+    
+    /** Returns if the word is in the trie. */
+    bool search(string word) {
+        Node* p = root;
+        for(int i = 0; i < word.size(); i++) {
+            if(!p->child[word[i] - 'a']) return false;
+            p = p->child[word[i] - 'a'];
+        }
+        if(!p->is_key) return false;
+        return true;
+    }
+    
+    /** Returns if there is any word in the trie that starts with the given prefix. */
+    bool startsWith(string prefix) {
+        Node* p = root;
+        for(int i = 0; i < prefix.size(); i++) {
+            if(!p->child[prefix[i] - 'a']) return false;
+            p = p->child[prefix[i] - 'a'];
+        }
+        return true;
+    }
+};
+
+/**
+ * Your Trie object will be instantiated and called as such:
+ * Trie obj = new Trie();
+ * obj.insert(word);
+ * bool param_2 = obj.search(word);
+ * bool param_3 = obj.startsWith(prefix);
+ */

### 2018-05-29 LeetCode/236. Lowest Common Ancestor of a Binary Tree.cpp

@@ -1,0 +1,18 @@
+/**
+ * Definition for a binary tree node.
+ * struct TreeNode {
+ *     int val;
+ *     TreeNode *left;
+ *     TreeNode *right;
+ *     TreeNode(int x) : val(x), left(NULL), right(NULL) {}
+ * };
+ */
+class Solution {
+public:
+    TreeNode* lowestCommonAncestor(TreeNode* root, TreeNode* p, TreeNode* q) {
+        if(!root || root == p || root == q) return root;
+        TreeNode* left = lowestCommonAncestor(root->left, p, q);
+        TreeNode* right = lowestCommonAncestor(root->right, p, q);
+        return !left? right : (!right? left : root);
+    }
+};

### 2018-05-29 LeetCode/279. Perfect Squares.cpp

@@ -1,0 +1,32 @@
+class Solution {
+public:
+    int numSquares(int n) {
+        int sqroot = sqrt(n);
+        if(sqroot*sqroot == n) return 1;
+        
+        while(n % 4 == 0) n /= 4;
+        if(n % 8 == 7) return 4;
+        
+        for(int i = 1; i <= sqroot; i++) {
+            int remain = n - i*i;
+            int sqremain = sqrt(remain);
+            if(sqremain*sqremain == remain) return 2;
+        }
+        return 3;
+    }
+    
+};
+
+class Solution {
+public:
+    int numSquares(int n) {
+        if(n <= 0) return 0;
+        static vector<int> num({0});
+        while(num.size() <= n) {
+            int m = num.size(), minSquare = INT_MAX;
+            for(int i = 1; i*i <= m; i++) minSquare = min(minSquare, num[m - i*i]+1);
+            num.push_back(minSquare);
+        }
+        return num[n];
+    }
+};

### 2018-05-29 LeetCode/299. Bulls and Cows.cpp

@@ -1,0 +1,19 @@
+class Solution {
+public:
+    string getHint(string secret, string guess) {
+        int ds[10], dg[10];
+        memset(ds, 0, sizeof(ds)); 
+        memset(dg, 0, sizeof(dg));
+        int bull = 0, cow = 0;
+        for(int i = 0; i < secret.size(); i++) {
+            if(secret[i] == guess[i]) bull++;
+            ds[secret[i]-'0']++;
+            dg[guess[i]-'0']++;
+        }
+        for(int i = 0; i < 10; i++) {
+            cow += min(ds[i], dg[i]);
+        }
+        cow -= bull;
+        return ""+to_string(bull)+"A"+to_string(cow)+"B";
+    }
+};

### 2018-05-29 LeetCode/303. Range Sum Query - Immutable.cpp

@@ -1,0 +1,21 @@
+class NumArray {
+    vector<int> presum;
+public:
+    NumArray(vector<int> nums) {
+        presum.resize(nums.size()+1);
+        presum[0] = 0;
+        for(int i = 1; i <= nums.size(); i++) {
+            presum[i] = presum[i-1] + nums[i-1];
+        }
+    }
+    
+    int sumRange(int i, int j) {
+        return presum[j+1]-presum[i];
+    }
+};
+
+/**
+ * Your NumArray object will be instantiated and called as such:
+ * NumArray obj = new NumArray(nums);
+ * int param_1 = obj.sumRange(i,j);
+ */

### 2018-05-29 LeetCode/306. Additive Number.cpp

@@ -1,0 +1,33 @@
+class Solution {
+public:
+    bool isAdditiveNumber(string num) {
+        for(int i = 1; i <= num.size()/2; i++) {
+            for(int j = 1; j <= (num.size()-i)/2; j++) {
+                if(isAdditive(num.substr(0, i), num.substr(i, j), num.substr(i+j))) return true;
+            }
+        }
+        return false;
+    }
+    
+    bool isAdditive(string a, string b, string c) {
+        if((a.size() > 1 && a[0] == '0') || (b.size() > 1 && b[0] == '0')) return false;
+        string s = add(a, b);
+        if(s == c) return true;
+        else if(c.size() <= s.size()) return false;
+        else if(c.substr(0, s.size()) != s) return false;
+        return isAdditive(b, s, c.substr(s.size()));
+    }
+    
+    string add(string a, string b) {
+        string res;
+        int i = a.size()-1, j = b.size()-1, carry = 0;
+        while(i >= 0 || j >= 0) {
+            int sum = (i >= 0? a[i--]-'0': 0) + (j >= 0? b[j--]-'0': 0) + carry;
+            res += (sum%10 + '0');
+            carry = sum/10;
+        }
+        if(carry) res += carry + '0';
+        reverse(res.begin(), res.end());
+        return res;
+    }
+};

### 2018-05-29 LeetCode/332. Reconstruct Itinerary.cpp

@@ -1,0 +1,26 @@
+class Solution {
+public:
+    vector<string> findItinerary(vector<pair<string, string>> tickets) {
+        unordered_map<string, multiset<string> > graph;
+        unordered_map<string, unordered_map<string, int> > vis;
+        for(auto p: tickets) graph[p.first].insert(p.second);
+        
+        // for(auto p: graph) vis[p.first] = unordered_set<string>();
+        for(auto p: graph) for(auto n: p.second) vis[p.first][n]++;
+        
+        vector<string> s;
+        euler(graph, vis, s, "JFK"); s.push_back("JFK");
+        vector<string> res(s.rbegin(), s.rend());
+        return res;
+    }
+    
+    void euler(unordered_map<string, multiset<string> >& graph, unordered_map<string, unordered_map<string, int> >& vis, vector<string>& res, string u) {
+        for(auto v: graph[u]) {
+            if(vis[u][v]) {
+                vis[u][v]--;
+                euler(graph, vis, res, v);
+                res.push_back(v);
+            }
+        }
+    }
+};

### 2018-05-29 LeetCode/34. Search for a Range.cpp

@@ -1,0 +1,29 @@
+class Solution {
+public:
+    vector<int> searchRange(vector<int>& nums, int target) {
+        int left = 0, right = nums.size()-1, pos = -1;
+        while(left <= right) {
+            int mid = (left+right)/2;
+            if(nums[mid] == target) {
+                pos = mid; break;
+            }
+            else if(nums[mid] < target) left = mid+1;
+            else right = mid-1;
+        }
+        vector<int> res;
+        if(pos == -1) {
+            res.push_back(-1); res.push_back(-1); return res;
+        }
+        left = right = pos;
+        while(--left >= 0) {
+            if(nums[left] == nums[pos]) ;
+            else break;
+        }
+        while(++right < nums.size()) {
+            if(nums[right] == nums[pos]) ;
+            else break;
+        }
+        res.push_back(left+1); res.push_back(right-1);
+        return res;
+    }
+};

### 2018-05-29 LeetCode/342. Power of Four.cpp

@@ -1,0 +1,13 @@
+class Solution {
+public:
+    bool isPowerOfFour(int num) {
+        return 1 << (int)log2(num) == num && (int)log2(num) % 2 == 0;
+    }
+};
+
+class Solution {
+public:
+    bool isPowerOfFour(int num) {
+        return (num & (num-1)) == 0 && (num & 0x55555555) != 0;
+    }
+};

### 2018-05-29 LeetCode/372. Super Pow.cpp

@@ -1,0 +1,24 @@
+class Solution {
+public:
+    int superPow(int a, vector<int>& b) {
+        // using Euler's-theorem, phi(1337) = phi(7*191) = 1140;
+        // so a^{1140} == 1(mod 1337);
+        // Let b = 1140*p+q, then a^b == a^q(mod 1337); 
+        int q = 0;
+        for(int i = 0; i < b.size(); i++) q = (q*10+b[i])%1140;
+        a = a%1337;
+        return quickpow(a, q);
+    }
+    
+    int quickpow(int a, int q) {
+        if(q == 0) return 1;
+        if(q&1) {
+            int half = quickpow(a, (q-1)/2)%1337;
+            return (a*half*half)%1337;
+        }
+        else {
+            int half = quickpow(a, q/2)%1337;
+            return (half*half)%1337;
+        }
+    }
+};

### 2018-05-29 LeetCode/376. Wiggle Subsequence.cpp

@@ -1,0 +1,22 @@
+class Solution {
+public:
+    int wiggleMaxLength(vector<int>& nums) {
+        if(nums.size() <= 1) return nums.size();
+        int up[nums.size()] = {1}, down[nums.size()] = {1};
+        for(int i = 1; i < nums.size(); i++) {
+            if(nums[i] > nums[i-1]) {
+                up[i] = down[i-1]+1;
+                down[i] = down[i-1];
+            }
+            else if(nums[i] < nums[i-1]) {
+                up[i] = up[i-1];
+                down[i] = up[i-1]+1;
+            }
+            else {
+                up[i] = up[i-1];
+                down[i] = down[i-1];
+            }
+        }
+        return max(down[nums.size()-1], up[nums.size()-1]);
+    }
+};

### 2018-05-29 LeetCode/385. Mini Parser.cpp

@@ -1,0 +1,64 @@
+/**
+ * // This is the interface that allows for creating nested lists.
+ * // You should not implement it, or speculate about its implementation
+ * class NestedInteger {
+ *   public:
+ *     // Constructor initializes an empty nested list.
+ *     NestedInteger();
+ *
+ *     // Constructor initializes a single integer.
+ *     NestedInteger(int value);
+ *
+ *     // Return true if this NestedInteger holds a single integer, rather than a nested list.
+ *     bool isInteger() const;
+ *
+ *     // Return the single integer that this NestedInteger holds, if it holds a single integer
+ *     // The result is undefined if this NestedInteger holds a nested list
+ *     int getInteger() const;
+ *
+ *     // Set this NestedInteger to hold a single integer.
+ *     void setInteger(int value);
+ *
+ *     // Set this NestedInteger to hold a nested list and adds a nested integer to it.
+ *     void add(const NestedInteger &ni);
+ *
+ *     // Return the nested list that this NestedInteger holds, if it holds a nested list
+ *     // The result is undefined if this NestedInteger holds a single integer
+ *     const vector<NestedInteger> &getList() const;
+ * };
+ */
+class Solution {
+public:
+    NestedInteger deserialize(string s) {
+        stack<NestedInteger> st; st.push(NestedInteger());
+        for(int i = 0; i < s.size(); i++) {
+            if(isNum(s[i])) {
+                int num = 0, sgn = 1;
+                if(s[i] == '-') {
+                    sgn = -1;
+                    i++;
+                }
+                while(isNum(s[i])) {
+                    num = num*10+s[i]-'0';
+                    i++;
+                }
+                num *= sgn;
+                st.top().add(NestedInteger(num));
+                i--;
+            }
+            else {
+                if(s[i] == '[') st.push(NestedInteger());
+                else if(s[i] == ']') {
+                    NestedInteger tmp = st.top(); st.pop();
+                    st.top().add(tmp);
+                }
+            }
+        }
+        NestedInteger res = st.top().getList().front();
+        return res;
+    }
+    
+    bool isNum(char c) {
+        return c == '-' || isdigit(c);
+    }
+};

### 2018-05-29 LeetCode/386. Lexicographical Numbers.cpp

@@ -1,0 +1,17 @@
+class Solution {
+public:
+    vector<int> lexicalOrder(int n) {
+        vector<int> res(n);
+        int now = 1;
+        for(int i = 0; i < n; i++) {
+            res[i] = now;
+            if(now*10 <= n) now *= 10;
+            else {
+                if(now >= n) now /= 10;
+                now += 1;
+                while(now % 10 == 0) now /= 10;
+            }
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/39. Combination Sum.cpp

@@ -1,0 +1,24 @@
+class Solution {
+public:
+    vector<vector<int>> combinationSum(vector<int>& candidates, int target) {
+        sort(candidates.begin(), candidates.end());
+        vector<vector<int> > res; vector<int> now;
+        dfs(res, now, candidates, 0, 0, target);
+        return res;
+    }
+    
+    void dfs(vector<vector<int> >& res, vector<int>& now, vector<int>& candidates, int sum, int index, int target) {
+        if(sum == target) {
+            res.push_back(now);
+            return;
+        }
+        for(int j = index; j < candidates.size(); j++) {
+            if(sum + candidates[j] <= target) {
+                now.push_back(candidates[j]);
+                dfs(res, now, candidates, sum+candidates[j], j, target);
+                now.pop_back();
+            }
+            else break;
+        }
+    }
+};

### 2018-05-29 LeetCode/40. Combination Sum II.cpp

@@ -1,0 +1,25 @@
+class Solution {
+public:
+    vector<vector<int>> combinationSum2(vector<int>& candidates, int target) {
+        sort(candidates.begin(), candidates.end());
+        vector<vector<int> > res; vector<int> now;
+        dfs(res, now, candidates, 0, 0, target);
+        return res;
+    }
+    
+    void dfs(vector<vector<int> >& res, vector<int>& now, vector<int>& candidates, int sum, int index, int target) {
+        if(sum == target) {
+            res.push_back(now);
+            return;
+        }
+        for(int j = index; j < candidates.size(); j++) {
+            if(j && candidates[j] == candidates[j-1] && j > index) continue;
+            if(sum + candidates[j] <= target) {
+                now.push_back(candidates[j]);
+                dfs(res, now, candidates, sum+candidates[j], j+1, target);
+                now.pop_back();
+            }
+            else break;
+        }
+    }
+};

### 2018-05-29 LeetCode/438. Find All Anagrams in a String.cpp

@@ -1,0 +1,24 @@
+class Solution {
+public:
+    vector<int> findAnagrams(string s, string p) {
+        int sv[26] = {0}, pv[26] = {0};
+        if(!p.size() || !s.size() || s.size() < p.size()) return vector<int>();
+        for(int i = 0; i < p.size(); i++) {
+            sv[s[i]-'a']++; pv[p[i]-'a']++;
+        }
+        vector<int> res;
+        if(equal(sv, pv)) res.push_back(0);
+        for(int i = p.size(); i < s.size(); i++) {
+            sv[s[i]-'a']++; sv[s[i-p.size()]-'a']--;
+            if(equal(sv, pv)) res.push_back(i-p.size()+1);
+        }
+        return res;
+    }
+    
+    bool equal(int* s, int* p) {
+        for(int i = 0; i < 26; i++) {
+            if(s[i] != p[i]) return false;
+        }
+        return true;
+    }
+};

### 2018-05-29 LeetCode/456. 132 Pattern.cpp

@@ -1,0 +1,15 @@
+class Solution {
+public:
+    bool find132pattern(vector<int>& nums) {
+        stack<int> s;
+        int s3 = INT_MIN;
+        for(int i = nums.size()-1; i >= 0; i--) {
+            if(nums[i] < s3) return true;
+            else while(!s.empty() && nums[i] > s.top()) {
+                s3 = s.top(); s.pop();
+            }
+            s.push(nums[i]);
+        }
+        return false;
+    }
+};

### 2018-05-29 LeetCode/459. Repeated Substring Pattern.cpp

@@ -1,0 +1,18 @@
+class Solution {
+public:
+    bool repeatedSubstringPattern(string s) {
+        int n = s.size();
+        vector<int> factors;
+        for(int i = 1; i <= n/2; i++) if(n%i == 0) factors.push_back(i);
+        for(int factor: factors) {
+            bool flag = true;
+            string sub = s.substr(0, factor);
+            for(int i = 1; i < n/factor; i++) if(s.substr(i*factor, factor) != sub) {
+                flag = false;
+                break;
+            }
+            if(flag) return true;
+        }
+        return false;
+    }
+};

### 2018-05-29 LeetCode/473. Matchsticks to Square.cpp

@@ -1,0 +1,31 @@
+class Solution {
+public:
+    bool makesquare(vector<int>& nums) {
+        int count = 0;
+        for(int i: nums) count += i;
+        if(count%4 || count == 0) return false;
+        
+        sort(nums.begin(), nums.end(), cmp);
+        vector<int> sides(4, 0);
+        
+        return dfs(nums, sides, 0, count/4);
+    }
+    
+    static bool cmp(int x, int y) { return x>y; }
+    
+    bool dfs(vector<int>& nums, vector<int>& sides, int index, int target) {
+        if(index == nums.size()) {
+            if(sides[0] == target && sides[1] == target && sides[2] == target && sides[3] == target) return true;
+            else return false;
+        }
+        for(int i = 0; i < 4; i++) {
+            if(sides[i] + nums[index] > target) continue;
+            sides[i] += nums[index];
+            if(dfs(nums, sides, index+1, target)) return true;
+            sides[i] -= nums[index];
+        }
+        return false;
+    }
+    
+
+};

### 2018-05-29 LeetCode/482. License Key Formatting.cpp

@@ -1,0 +1,21 @@
+class Solution {
+public:
+    string licenseKeyFormatting(string S, int K) {
+        reverse(S.begin(), S.end());
+        string res = ""; 
+        int count = 0;
+        for(int i = 0; i < S.size(); i++) {
+            if(count == K) {
+                res += '-'; count = 0;
+            }
+            if(S[i] >= 'a' && S[i] <= 'z') {
+                count++; res += S[i] - 32;
+            }
+            else if((S[i] >= 'A' && S[i] <= 'Z') || S[i] >= '0' && S[i] <= '9') {
+                count++; res += S[i];
+            }
+        }
+        reverse(res.begin(), res.end());
+        return res[0] == '-'? res.substr(1, res.size()-1):res;
+    }
+};

### 2018-05-29 LeetCode/491. Increasing Subsequences.cpp

@@ -1,0 +1,23 @@
+class Solution {
+public:
+    vector<vector<int>> findSubsequences(vector<int>& nums) {
+        vector<vector<int>> res;
+        vector<int> now;
+        dfs(nums, res, now, 0);
+        return res;
+    }
+    
+    void dfs(vector<int>& nums, vector<vector<int>>& res, vector<int> now, int n) {
+        if(now.size() >= 2) res.push_back(now);
+        unordered_map<int, int> used;
+        for(int i = n; i < nums.size(); i++) {
+            if(used[nums[i]]) continue;
+            if(now.size() == 0 || now.back() <= nums[i]) {
+                used[nums[i]] = 1;
+                now.push_back(nums[i]);
+                dfs(nums, res, now, i+1);
+                now.pop_back();
+            }
+        }
+    } 
+};

### 2018-05-29 LeetCode/494. Target Sum.cpp

@@ -1,0 +1,19 @@
+class Solution {
+public:
+    int findTargetSumWays(vector<int>& nums, int S) {
+        int res = 0, sum = 0;
+        dfs(nums, res, sum, S, 0);
+        return res;
+    }
+    
+    void dfs(vector<int>& nums, int& res, int sum, int S, int n) {
+        if(n == nums.size()) {
+            if(sum == S) res++;
+            return;
+        };
+        
+        dfs(nums, res, sum+nums[n], S, n+1);
+        dfs(nums, res, sum-nums[n], S, n+1);
+    }
+};
+

### 2018-05-29 LeetCode/504. Base 7.cpp

@@ -1,0 +1,19 @@
+class Solution {
+public:
+    string convertToBase7(int num) {
+        if(!num) return "0";
+        string res; bool neg = false;
+        if(num < 0) {
+            neg = true;
+            num = -num;
+        }
+        while(num) {
+            int remainder = num%7;
+            num /= 7;
+            res += to_string(remainder);
+        }
+        if(neg) res += '-';
+        reverse(res.begin(), res.end());
+        return res;
+    }
+};

### 2018-05-29 LeetCode/537. Complex Number Multiplication.cpp

@@ -1,0 +1,24 @@
+class Solution {
+public:
+    string complexNumberMultiply(string a, string b) {
+        int aReal = 0, bReal = 0, aImag = 0, bImag = 0;
+        int index = 0; while(a[index++] != '+') ;
+        getDigit(a, 0, index-1, aReal); getDigit(a, index, a.size(), aImag);
+        index = 0; while(b[index++] != '+') ;
+        getDigit(b, 0, index-1, bReal); getDigit(b, index, b.size(), bImag);
+        int real = aReal*bReal - aImag*bImag, imag = aReal*bImag + aImag*bReal;
+        return to_string(real)+'+'+to_string(imag)+'i';
+    }
+        
+    void getDigit(string& a, int left, int right, int& num) {
+        int sgn = 1, index = left;
+        if(a[index] == '-') {
+            sgn = -1;
+            index++;
+        }
+        for(int i = index; i < right; i++) {
+            if(a[i] != 'i') num = num*10 + a[i] - '0';
+        }
+        num *= sgn;
+    }
+};

### 2018-05-29 LeetCode/547. Friend Circles.cpp

@@ -1,0 +1,23 @@
+class Solution {
+public:
+    int findCircleNum(vector<vector<int>>& M) {
+        int res = 0;
+        vector<int> vis(M.size(), 0);
+        for(int i = 0; i < M.size(); i++) {
+            if(!vis[i]) {
+                dfs(M, vis, i);
+                res++;
+            }
+        }
+        return res;
+    }
+    
+    void dfs(vector<vector<int>>& M, vector<int>& vis, int i) {
+        for(int j = 0; j < M.size(); j++) {
+            if(!vis[j] && M[i][j]) {
+                vis[j] = 1;
+                dfs(M, vis, j);
+            }
+        }
+    }
+};

### 2018-05-29 LeetCode/576. Out of Boundary Paths.cpp

@@ -1,0 +1,39 @@
+class Solution {
+public:
+    int findPaths(int m, int n, int N, int i, int j) {
+        long count = 0;
+        dfs(m, n, N, 0, count, i, j);
+        return count%(1000000007);
+    }
+    
+    void dfs(int m, int n, int N, int num, long& count, int i, int j) {
+        if(i >= m || j >= n || i < 0 || j < 0) {
+            count++;
+            return;
+        }
+        for(int k = 0; k < 4; k++) {
+            if(num < N) dfs(m, n, N, num+1, count, i+dir[k][0], j+dir[k][1]);
+        }
+    }
+    
+private:
+    int dir[4][2] = {{-1, 0}, {1, 0}, {0, -1}, {0, 1}};
+};
+
+class Solution {
+public:
+    int findPaths(int m, int n, int N, int i, int j) {
+        long dp[51][51][51] = {0};
+        for(int Ni = 1; Ni <= N; Ni++) {
+            for(int mi = 0; mi < m; mi++) {
+                for(int ni = 0; ni < n; ni++) {
+                    dp[mi][ni][Ni] = ((mi == 0? 1:dp[mi-1][ni][Ni-1])
+                                + (mi == (m-1)? 1:dp[mi+1][ni][Ni-1])
+                                + (ni == 0? 1:dp[mi][ni-1][Ni-1])
+                                + (ni == (n-1)? 1:dp[mi][ni+1][Ni-1]))%1000000007;
+                }
+            }
+        }
+        return dp[i][j][N];
+    }
+};

### 2018-05-29 LeetCode/59. Spiral Matrix II.cpp

@@ -1,0 +1,19 @@
+class Solution {
+public:
+    vector<vector<int>> generateMatrix(int n) {
+        vector<vector<int> > res(n, vector<int>(n));
+        int count = 1, i = 0;
+        while(count <= n*n) {
+            int j = i;
+            while(j < n-i) res[i][j++] = count++;
+            j = i+1;
+            while(j < n-i) res[j++][n-i-1] = count++;
+            j = n-i-2;
+            while(j > i) res[n-i-1][j--] = count++;
+            j = n-i-1;
+            while(j>i) res[j--][i] = count++;
+            i++;
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/60. Permutation Sequence.cpp

@@ -1,0 +1,16 @@
+class Solution {
+public:
+    string getPermutation(int n, int k) {
+        int factorials[] = {1, 1, 2, 6, 24, 120, 720, 5040, 40320, 362880};
+        vector<int> nums;
+        for(int i = 1; i <= n; i++) nums.push_back(i);
+        string res = "";
+        for(int i = 1; i <= n; i++) {
+            int index = (k-1)/factorials[n-i];
+            res += to_string(nums[index]);
+            nums.erase(nums.begin()+index);
+            k -= index*factorials[n-i];
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/628. Maximum Product of Three Numbers.cpp

@@ -1,0 +1,9 @@
+class Solution {
+public:
+    int maximumProduct(vector<int>& nums) {
+        sort(nums.begin(), nums.end());
+        int a = nums[0]*nums[1]*nums[nums.size()-1];
+        int b = nums[nums.size()-1]*nums[nums.size()-2]*nums[nums.size()-3];
+        return max(a, b);
+    }
+};

### 2018-05-29 LeetCode/643. Maximum Average Subarray I.cpp

@@ -1,0 +1,13 @@
+class Solution {
+public:
+    double findMaxAverage(vector<int>& nums, int k) {
+        double sum = 0, maxsum;
+        for(int i = 0; i < k; i++) sum += nums[i];
+        maxsum = sum;
+        for(int i = k; i < nums.size(); i++) {
+            sum += nums[i]-nums[i-k];
+            if(sum > maxsum) maxsum = sum; 
+        }
+        return maxsum/k;
+    }
+};

### 2018-05-29 LeetCode/68. Text Justification.cpp

@@ -1,0 +1,24 @@
+class Solution {
+public:
+    vector<string> fullJustify(vector<string>& words, int maxWidth) {
+        vector<string> res;
+        int i = 0;
+        while(i < words.size()) {
+            int len = 0, j = 0;
+            while(i+j < words.size() && len + words[i+j].size() <= maxWidth - j) {
+                len += words[i+(j++)].size();
+            }
+            j--;
+            string tmp = words[i];
+            for(int k = 0; k < j; k++) {
+                if(i+j >= words.size()-1) tmp += " ";
+                else tmp += string((maxWidth-len)/j + (k < (maxWidth-len)%j), ' ');
+                tmp += words[i+k+1];
+            }
+            tmp += string(maxWidth - tmp.size(), ' ');
+            res.push_back(tmp);
+            i += (j+1);
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/687. Longest Univalue Path.cpp

@@ -1,0 +1,40 @@
+/**
+ * Definition for a binary tree node.
+ * struct TreeNode {
+ *     int val;
+ *     TreeNode *left;
+ *     TreeNode *right;
+ *     TreeNode(int x) : val(x), left(NULL), right(NULL) {}
+ * };
+ */
+class Solution {
+public:
+    int longestUnivaluePath(TreeNode* root) {
+        if(!root) return 0;
+        vector<int> res = dfs(root);
+        return max(res[0], res[1])-1;
+    }
+    
+    vector<int> dfs(TreeNode* root) {
+        if(!root) return vector<int>(2, 0);
+        vector<int> res(2, 1);
+        vector<int> left = dfs(root->left), right = dfs(root->right);
+        if(root->left && root->right && root->val == root->left->val && root->val == root->right->val) {
+            res[0] = max(left[0], right[0])+1;
+            res[1] = max(max(left[1], right[1]), left[0]+right[0]+1);
+        }
+        else if(root->left && root->val == root->left->val) {
+            res[0] = left[0]+1;
+            res[1] = max(left[1], right[1]);
+        }
+        else if(root->right && root->val == root->right->val) {
+            res[0] = right[0]+1;
+            res[1] = max(left[1], right[1]);
+        }
+        else {
+            res[0] = 1;
+            res[1] = max(max(left[1], right[1]), max(left[0], right[0]));
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/694. Number of Distinct Islands.cpp

@@ -1,0 +1,63 @@
+class Solution {
+public:
+    int numDistinctIslands(vector<vector<int>>& grid) {
+        int count = 0; 
+        vector<vector<pair<int, int>>> s;
+        for(int i = 0; i < grid.size(); i++) {
+            for(int j = 0; j < grid[0].size(); j++) {
+                vector<pair<int, int>> local;
+                if(grid[i][j] == 1) {
+                    dfs(grid, local, i, j, i, j);
+//                     sort(local.begin(), local.end(), cmp);
+//                     bool flag = true;
+//                     for(auto v: s) {
+//                         if(isEqual(v, local)) {
+//                             flag = false;
+//                             break;
+//                         }
+                    
+//                     cout << flag << endl;
+//                     if(flag) {
+//                         s.push_back(local);
+//                         count++;
+//                     }
+                    if(find(s.begin(), s.end(), local) == s.end()) {
+                        s.push_back(local);
+                        count++;
+                    }
+                } 
+                // if(find(s.begin(), s.end(), local) == s.end()) {
+                //     s.push_back(local);
+                //     count++;
+                // }
+            }
+        }
+        return count;
+    }
+    
+    void dfs(vector<vector<int>>& grid, vector<pair<int, int>>& local, int i, int j, int i0, int j0) {
+        if(i < 0 || j < 0 || i >= grid.size() || j >= grid[0].size() || grid[i][j] == 0) return;
+        local.push_back(make_pair(i-i0, j-j0));
+        grid[i][j] = 0;
+        dfs(grid, local, i-1, j, i0, j0);
+        dfs(grid, local, i+1, j, i0, j0);
+        dfs(grid, local, i, j-1, i0, j0);
+        dfs(grid, local, i, j+1, i0, j0);
+    }
+    
+    static bool cmp(pair<int, int> a, pair<int, int> b) {
+        return a.first > b.first || (a.first == b.first && a.second > b.second);
+    }
+    
+    bool isEqual(vector<pair<int, int>>& a, vector<pair<int, int>>& b) {
+        if(a.size() != b.size()) return false;
+        for(int i = 0; i < a.size(); i++) {
+            cout << a[i].first << b[i].first << endl;
+            cout << a[i].second << b[i].second << endl;
+            if(a[i].first != b[i].first || a[i].second != b[i].second) {
+                return false;
+            }
+        }
+        return true;
+    }
+};

### 2018-05-29 LeetCode/696. Count Binary Substrings.cpp

@@ -1,0 +1,25 @@
+class Solution {
+public:
+    int countBinarySubstrings(string s) {
+        int count = 0;
+        for(int i = 0; i < s.size()-1; i++) {
+            count += search(s, i);
+        }
+        return count;
+    }
+    
+    int search(string s, int index) {
+        int count = (s[index] == '0'? -1: 1), flag = 0, last = s[index];
+        for(int i = index+1; i < s.size(); i++) {
+            if(count == 0) return 1;
+            if(s[i] != last && flag == 1) return 0;
+            if(s[i] != last) {
+                flag = 1;
+                last = s[i];
+            }
+            count += (s[i] == '0'?-1:1);
+        }
+        return count == 0;
+    }
+    
+};

### 2018-05-29 LeetCode/71. Simplify Path.cpp

@@ -1,0 +1,15 @@
+class Solution {
+public:
+    string simplifyPath(string path) {
+        vector<string> s;
+        string res, tmp;
+        stringstream ss(path);
+        while(getline(ss, tmp, '/')) {
+            if(tmp == "" || tmp == ".") continue;
+            if(tmp == ".." && !s.empty()) s.pop_back();
+            else if(tmp != "..") s.push_back(tmp);
+        }
+        for(string c: s) res += "/"+c;
+        return !res.size() ? "/":res;
+    }
+};

### 2018-05-29 LeetCode/713. Subarray Product Less Than K.cpp

@@ -1,0 +1,16 @@
+class Solution {
+public:
+    int numSubarrayProductLessThanK(vector<int>& nums, int k) {
+        int res = (nums[0] < k);
+        for(int i = 1; i < nums.size(); i++) {
+            int local = nums[i];
+            res += (local < k);
+            for(int j = i-1; j >= 0; j--) {
+                local *= nums[j];
+                if(local >= k) break;
+                else res++;
+            }
+        }
+        return res;
+    }
+};

### 2018-05-29 LeetCode/714. Best Time to Buy and Sell Stock with Transaction Fee.cpp

@@ -1,0 +1,13 @@
+class Solution {
+public:
+    int maxProfit(vector<int>& prices, int fee) {
+        if(prices.size() <= 1) return 0;
+        int hold[prices.size()] = {0}, no[prices.size()] = {0};
+        hold[0] = -prices[0]-fee;
+        for(int i = 1; i < prices.size(); i++) {
+            hold[i] = max(hold[i-1], no[i-1]-prices[i]-fee);
+            no[i] = max(no[i-1], hold[i-1]+prices[i]);
+        }
+        return max(hold[prices.size()-1], no[prices.size()-1]);
+    }
+};

### 2018-05-29 LeetCode/79. Word Search.cpp

@@ -1,0 +1,76 @@
+class Solution {
+public:
+    bool exist(vector<vector<char>>& board, string word) {
+        for(int i = 0; i < board.size(); i++) { 
+            for(int j = 0; j < board[0].size(); j++) {
+                    bool res = false;
+                    // vector<vector<int> > vis(board.size(), vector<int>(board[0].size(), 0));
+                    // dfs(board, vis, i, j, 1, word, res);
+                    dfs(board, i, j, 0, word, res);
+                    if(res) return true;
+            }
+        }
+        return false;
+    }
+    
+    void dfs(vector<vector<char> >& board, int i, int j, int k, string& word, bool& res) {
+        // cout << k << endl;
+        if(k == word.size()) {
+            res = true;
+            return;
+        }
+        if(i < 0 || j < 0 || i == board.size() || j == board[0].size()) return;
+        if(board[i][j] != word[k]) return;
+        // char s = board[i][j];
+        // board[i][j] = '#';
+        board[i][j] ^= 256;
+        // if(j > 0 && board[i][j-1] == word[k]) dfs(board, i, j-1, k+1, word, res);
+        // if(j < board[0].size()-1 && board[i][j+1] == word[k]) dfs(board, i, j+1, k+1, word, res);
+        // if(i > 0 && board[i-1][j] == word[k]) dfs(board, i-1, j, k+1, word, res);
+        // if(i < board.size()-1 && board[i+1][j] == word[k]) dfs(board, i+1, j, k+1, word, res);
+        dfs(board, i, j-1, k+1, word, res);
+        dfs(board, i, j+1, k+1, word, res);
+        dfs(board, i-1, j, k+1, word, res);
+        dfs(board, i+1, j, k+1, word, res);
+        // board[i][j] = s;
+        board[i][j] ^= 256;
+        return;
+    }
+    
+    // void dfs(vector<vector<char> >& board, vector<vector<int> >& vis, int i, int j, int k, string& word, bool& res) {
+    //     if(k == word.size()) {
+    //         res = true;
+    //         return;
+    //     }
+    //     vis[i][j] = 1;
+    //     if(j > 0 && !vis[i][j-1] && board[i][j-1] == word[k]) dfs(board, vis, i, j-1, k+1, word, res);
+    //     if(j < board[0].size()-1 && !vis[i][j+1] && board[i][j+1] == word[k]) dfs(board, vis, i, j+1, k+1, word, res);
[…]
